### 2016-05-31 abstract.tex
first commit.

\begin{abstract}
The seismicity of northern Iran between 2005 and 2015 is investigated by means of visibility graph (VG) method. According to the seismicity, in this study the northern Iran is divided into three tectonic seismic regions including Azerbaijan, Alborz, and Kopeh Dagh.  The aftershocks and foreshocks are removed from the catalog and the magnitude time series are generated for each tectonic seismic zone. Using declustered catalog, we studied the VG properties of the magnitude time series. The results show a relationship between the $k-M$ slope and the $b-value$ of the Gutenberg-Richter law. Topological properties (i.e. $< T_c >$, $k-M$ slope) of network and  dynamic properties of magnitude time series (i.e. $b-value$) significantly decrease before large earthquakes. Cumulating the results of this study into two similar previous studies, improves the linear correlation coefficient factor and empower the idea of universal relationship between $b-value$ and $k-M$ slope. The behavior of  the VG's properties are similar to previous studies and could be considered an alternative method to analyze the earthquake sequence. 
\end{abstract}

### 2016-05-31 introduction.tex
first commit.

\section{Introduction}
\noindent
\citet{Lacasa2008} presented a simple and fast computational method; known as visibility algorithm, to convert the time series into the graphs. Basically the visibility graph presents the connection between nodes in the network. In each time series two characteristics are attributed to each incidents, including the time and the value of the incident. Two events are connected to each other, or visible to each other, if there is not any other event to interrupt their linear connection. In mathematical form, event $i$ and event $j$ are visible to each other if the following equation fulfills:

\begin{equation}
\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} 
\end{equation}

\noindent
where, $y$ is the value of the event and $t$ is the time of the event. $k$ is the index of any event between event $i$ and event $j$.

\noindent
The visibility graph that is generated from the time series holds the following conditions, 1) each event is visible to the events at the right and left side (if there is any) of the event  (Connectivity), 2) The algorithm is developed without defining a direction for the links (Undirected),  3) Rescaling or translation of the time series are not changing the resulted visibility graph (Invariant under affine transformations of  the series data)\citep{Lacasa2008}.

\noindent
The analysis of seismicity sequence through visibility graph for various tectonic seismic regions, revealed an alternative approach to study the magnitude time series. \citet{Telesca2012} studied the seismic sequence of Italy between 2005 and 2010 through using the visibility graph method. Using different threshold magnitude, and observing the collapsing effect of all the distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend only on the values of the magnitude and independent of the threshold magnitude. In other study, \citet{Telesca2013} studied the Seismicity of the Mexican subduction zone through visibility graph approach. They extracted the characteristics of the visibility graph for five different tectonic seismic regions.  According to their study visibility graph could identify one of the regions that has a different seismicity characteristics, which is because of different tectonic processes that governs the area. The relationship between Gutenberg-Richter parameters and $k-M$ slope (The slope of regression line of Magnitude  of each event $(M)$ and its connectivity degree $k$) is investigated in their study. In a similar study \citet{Telesca2014}, studied the seismicity of 2002-2011 Pannonian seismicity using the visibility graph. They classified seismic catalog into shallow and deep earthquakes and extract the visibility graph characteristics for each class. According to their study there is close relationship between Gutenberg-Richter $b-value$ and $k-M$ slope of the visibility graph. High linear correlation coefficient of $b-value$ and $k-M$ slope suggests the universal character of the relationship between these parameters \citep{Telesca2014}.  \citet{Telesca2016} , used the $ <T_C>$, as the parameter window mean interval connectivity time ,  that indicates the mean linkage time between earthquakes, to study the 2003-2012 earthquake sequences in the Kachchh region of western India. They found that the $<T_C>$ changes through time, indicating that the topological properties of the earthquake network are not stationary; also $<T_C>$ significantly decrees before the largest shock of the catalog. Analyzing Gutenberg-Richter values of  magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series using the features of networks. \\

\noindent
In this study we used visibility graph analysis to study the earthquake sequence of northern Iran. We divided northern Iran into three tectonic seismic regions including Azerbaijan, Alborz, and Kopeh Dagh.  Recently, northern Iran has been studied in detail from different seismological points of view. \citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran. The frequency of shocks vary widely from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region. \\

\noindent
Northern Iran has an elaborate seismic history.  Having considerable number of earthquake and also being in different seismic tectonic zone, northern Iran is a good platform to analysis the visibility graph method's capabilities for studying the magnitude time series. In this study we present the relationship between $K-M$ slope and the $b-value$ in three different tectonic seismic region. We also investigate the variation of $<T_C>$ value through time.

### 2016-05-31 main.tex
first commit.

% Required packages
%\RequirePackage{fix-cm}

% Document Settings
\documentclass[a4paper,review]{elsarticle}

% Packages
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[margin=3cm]{geometry}

% Journal Name
\journal{Physica A}

% START: The Document
\begin{document}

\begin{frontmatter}

% Long Title
\title{Visibility Graph Analysis of the 2005-2015 Earthquake Sequence in Northern Iran}

% Authors
%\author[label1]{Naeem Khoshnevis\corref{cor1}}
%\author[label1,label2]{Shima AzizzadehRoodpish}
%\cortext[cor1]{Corresponding author. Tel: \\
 %                    Email address: nkhshnvs@memphis.edu (N.Khoshnevis)}

% Affliations
%\address[label1]{Center for Earthquake Research and Information}
%\address[label2]{Department of Civil Engineering}

\input{abstract}

\begin{keyword}
Visibility Graph \sep Earthquake Magnitude \sep North Iran \sep b-value

\end{keyword}

\end{frontmatter}

%% \linenumbers

%% Article Contents

\input{content}
\bibliographystyle{elsarticle-num-names}
\bibliography{VG}

% Bibliography

%\begin{thebibliography}{00}

%% \bibitem{label}
%% Text of bibliographic item

%\bibitem{}

%\end{thebibliography}

% End document
\end{document}
\endinput
%%
%% End of file `elsarticle-template-num.tex'.

### 2016-05-31 results.tex
first commit.

\section{Results}
\noindent
We generated the visibility graph characteristics for three tectonic seismic regions in northern Iran for the period from 2005 to 2015. Number of earthquake in each catalog after declustering and the seismicity parameters are presented in Table.~\ref{tab:b_k_m_param}.

\begin{table}[h]
\centering
\caption{Seismic parameters and K-M slope values for north Iran tectonic seismic zones.}
\begin{tabular}{ccccc}
Region          & Number of Earthquake &  Mc &  b-value & K-M slope \\ \hline
Azerbaijan     & 93                                 & 3.5   & 1.0190  & 9.2004       \\ \hline
Alborz            & 488                               & 2.9   & 0.8532  & 9.2821      \\ \hline
Kopek Dagh  & 282                               & 2.6   & 0.5799  & 6.5818     \\ \hline
\end{tabular}
\label{tab:b_k_m_param}
\end{table}

\noindent
Fig.~\ref{fig:k_m_plot_m} shows the $k-M$ relationship for the study regions.  In general with increasing magnitude the connectivity degree increases which results in increasing the slope of the $k-M$ relationship.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.35]{figures/pdf/Figure05.pdf} 
\caption{ K-M relationship for north Iran seismicity. a) Azerbaijan b) Alborz c)Kopeh Dagh}
\label{fig:k_m_plot_m}
\end{figure}

\noindent
We compared the $k-M$ slope with the $b-value$ of the Gutenberg-Richter law in the whole catalog and also in the sliding window in time. The $b-value$ is generated through the maximum likelihood estimation \citep{Aki1965}.

\begin{equation}
b = \frac{log_{10}(e) }{\overline{M} - M_{min}}  
\end{equation}

 \noindent
 where $\overline{M}$ is the average magnitude and $M_{min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic zone. Number of sequences and threshold magnitude are considerably different for all tectonic seismic zones. \citet{Telesca2013} studied the effect of number of earthquake in catalog on the $k-M$ slop. Comparing the result of Guerrero region with reduced random sequence, \citet{Telesca2013} found that the number of sequence doesn't affect the $k-M$ slope.  According to \citet{Telesca2012}, the threshold magnitude has a minor effect in the VG parameters. In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly picked 200 sequence from the catalogs with various sequence size. The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopek Dagh regions, respectively) and the maximum size is the whole catalog. For each randomly picked magnitude time series we estimated the $Mc$ and calculated the $k-M$ and $b-value$. Fig.~\ref{fig:random} shows the relationship between $k-M$ slope and $b-value$ of the randomly selected data and statistical parameters for variables. Although changing number of events and the threshold magnitude are slightly change the results, they are fairly well clustered for each tectonic seismic region.

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.3]{figures/pdf/Figure066.pdf} 
\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
\label{fig:random}
\end{figure}

 \noindent
The $k-M$ slope shows the maximum coefficient of variation. We may argue that the $k-M$ slope is much dependent to the window size and threshold magnitude than $a-$ and $b-value$, which suggest the idea that $k-M$ slop can better represent the dynamic characteristics of the magnitude-time series.

 \noindent
 Fig.~\ref{fig:regression} shows the relationship between the $k-M$ slope for three tectonic seismic zones in Iran and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. Adding the results of this study into two previous similar studies' results, improves the regression factor (increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} concluded.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.3]{figures/pdf/Figure06.pdf} 
\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
\label{fig:regression}
\end{figure}

\noindent
The relationship between $b-value$ and $K-M$ slope for Azerbaijan and Alborz region, suggested the idea of similar tectonic activity in these zones, in contrast with the $b-value$. In other words, may $K-M$ slope is more robust and less sensitive than $b-value$. Adding the value of this study into two previous similar studies results improves the regression factor (increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} pointed out.

\noindent 
Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time. Having lower number of event, we used 40 events as a window length. We analyzed the sensitivity of the results to the window size. Even though there is a very good similarity between the $K-M$ slope and $b-value$ in Alborz tectonic seismic region, there is no as good as fit for Azerbaijan Tectonic seismic region. The results indicate the fact that, $K-M$ slope may provide extra information about the seismic sequence of the region than the $b-value$.

The value of the K-M is increasing with increasing the magnitude. Fig yy shows the time vacation of the $K-M$ plot and $b-value$ for all tectonic seismic regions.

In general, In all regions the $b-value$ and $K-M$ slope considerably drops before  big earthquakes. Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}

Earthquake is a time dependent phenomenon, so studying the dynamic properties of the earthquake sequence is important to get different time dependent parameters.

 \citet{Telesca2016} observed the decreasing of the $<Tc>$ before large earthquake of Western India earthquake sequence. Fig.~\ref{fig:tc} shows the time variation of $<Tc>$ in the study area. The decreasing of the $<Tc>$ for large earthquakes have been shown in the figure. \citet{Telesca2016} demonstrated that the decrement of $<Tc>$ before large earthquake are independent of window size and the threshold magnitude.

The fluctuation of magnitude time series' topology properties (e.g. the $k-M$ slope and $<Tc>$) could be affected by the window size. Sharp changes in the VG parameters happens through small windows. Using higher number of samples in the window will reduce the temporal effects of small or moderate earthquakes and highlight the effects of big earthquakes, even though the behavior of the parameters in time and also before big earthquake are similar \citep{Telesca2016}. In general, more number of samples in a window smooth the results.

 In this study with increasing window size we can see the same behavior as small window. Undoubtedly, larger window size will reduce the effect of

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.34]{figures/pdf/Figure07.pdf} 
\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
\label{fig:tc}
\end{figure}

### 2016-05-31 seismicity.tex
first commit.

\section{Tectonic seismic zones and seismicity parameters}
\noindent
Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes. These earthquakes are categorized in various tectonic seismic zones. Based on seismicity parameters different tectonic seismic devisions have been defined for Iran.  Some studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}. \citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran. Considering \citet{Mirzaei1998} devision, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz). Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.  Fig.~\ref{fig:study_region} shows the study region and tectonic seismic regions. \\

\begin{figure} [ht]
\centering
\includegraphics[scale=0.6]{figures/pdf/Figure01.pdf} 
\caption{a) Map of Iran and surrounding countries. The study area is presented in gray box. b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities. Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
\label{fig:study_region}
\end{figure}

\noindent
Alborz tectonic seismic region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt. Here a series of historical earthquakes occurred within a time period of more than 1100 years. At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran.  The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression. An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.

\noindent
There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest, as part of Azerbaijna tectonic seismic zone. The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus. The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.

The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 m; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF. Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879. Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7)\citep{Berberian1999}. Most recently, earthquakes with Mw 6.1 in 1997 and Mw 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.

The main Kopeh-Dagh fault system has experienced some historic earthquakes. Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of $Ms$ 7.2 in 1948 and destroyed more than 30 villages in Iran. This was the strongest earthquake to strike this region since at least 1455.
The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs. The regions of overlap are characterized by shorter south-dipping thrust faults striking about E - W \citep{Berberian2001}. \citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km. 
Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.

\subsection{Magnitude Conversion}
\noindent
The catalog of recorded earthquake from 2005-2015 which is downloaded from IIEES is reported the earthquake based on different magnitude scale (reference). We converted the $M_L$, $M_S$, and $mb$ magnitudes through conversion relationships which is defined in \citet{Zare2014}. There also some of data which is recorded in $M_D$ (Duration magnitude). These data are reported by International Seismological Centre (ISC).  \citet{Deniz2010} developed a set of empirical equations to convert earthquake magnitudes in $mb$, $M_D$, $M_L$ and $M_S$ scales to the $M_W$ scales using orthogonal regression procedure. They used data of earthquake that occurred in Turkey from different data centers including ISC. In this study we use the conversion equation of \citet{Deniz2010} to convert the $M_D$ to $M_W$. Although they defined the equation based on $4.5\leqslant M_W$, we extrapolate the equation for lower magnitude. We believe having those earthquakes, even with small error  in magnitude is important for estimating an accurate  Gutenberge-Richter values.

\subsection{Declustering}
\noindent
It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process. Therefore, in order to accomplish this, we declustered the earthquake catalog. In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citet{Gardner1974}. Fig.~\ref{fig:seismicity} shows the epicenter of declustered instrumental  earthquakes.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.6]{figures/pdf/Figure02.pdf} 
\caption{Declustered instrumental seismicity map (2005 - 2015) of Northern Iran.}
\label{fig:seismicity}
\end{figure}

\subsection{Catalog Completeness}
\noindent
Completeness of catalog is an important factor in studying the earthquake sequence.  In this study we used the Maximum curvature method (MAXC) \citep{Wiemer2000}. According to MAXC method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude. The steps for picking the completeness magnitude for each catalog include, 1) Calculating the $a-$ and $b-$ value based on the minimum magnitude, 2) generate  synthetic events based on the achieved value that the cumulative number of events obey the power law distribution, 3) Calculate the goodness of fit for predicted and observed cumulative numbers for each magnitude bin. Higher \citep{Wiemer2000}. We increase the minimum magnitude and repeat the process. For each tectonic seismic region, we pick the magnitude corresponding to the highest goodness of fit.  \citet{Wiemer2000} assumed the threshold of goodness of fit as 90\% in order to completeness of the catalog, however,  not all frequency-magnitude distributions reach the 90\% mark. Fig.~\ref{fig:completeness} , shows the goodness of fit value for three tectonic seismic regions.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.4]{figures/pdf/Figure03.pdf} 
\caption{Goodness of fit value of MAXC method for three tectonic seismic regions for seismicity of 2005-2015 (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
\label{fig:completeness}
\end{figure}

\noindent
In this study we assumed the minimum magnitude for complete recording, $M_C$, are 2.9, 3.5, and 2.6 for Alborz, Azerbaijan, and Kopeh Dagh, respectively. Fig.~\ref{fig:mag-time} shows the magnitude time series of the declustered data for three regions. Earthquake with magnitude bigger than completeness magnitude are represented.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.5]{figures/pdf/Figure04.pdf} 
\caption{Variation of moment magnitude of earthquake in 2005-2015 for north Iran. (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
\label{fig:mag-time}
\end{figure}

### 2016-05-31 figures/gmtcode/Instrumental/Instrumental.sh

@@ -1,0 +1,54 @@
+#!/bin/bash
+# Set stuff up
+# World Topography
+# By : Naeem Khoshnevis
+
+
+ 
+
+LONMIN=43.5
+LONMAX=61.5
+LATMIN=34
+LATMAX=40
+REGION=$LONMIN/$LONMAX/$LATMIN/$LATMAX
+PROJ=-JM18
+MOREPS=-K
+CONTINUEPS="-K -O"
+ENDPS=-O
+DATASET=11
+DATAGRID=-I30c
+LINE=-W1
+
+grdraster $DATASET -G$world.grd $DATAGRID -R$REGION -V
+CPTFILE=/usr/local/GMT4.5.7/share/cpt/GMT_globe.cpt
+TOPOILLUM=220
+
+#grdgradient $world.grd -A$TOPOILLUM -GETOPO5.intns -N2 -V   in this case Dataset = 9
+grdgradient $world.grd -A$TOPOILLUM -GETOPO30s.intns -N2 -V
+
+grdimage $world.grd -IETOPO5.intns -C$CPTFILE -R$REGION $PROJ -N1/4 -K -B4f2/4f2 -Y8 -X8  >  $0.ps
+
+pscoast -R$REGION $PROJ -N1/4 -B4f2/4f2 -K -O -W2 >> $0.ps
+
+
+awk '($7>2.8){print $9,$10,($7^2.5)/140}' Alborz_2005_all_mag.txt|psxy -Sc -G196/19/19 -W2  -R$REGION $PROJ -K -O >> $0.ps
+awk '($7>3.4){print $9,$10,($7^2.5)/140}' Azerbaijan_2005_all_mag.txt|psxy -Sc -G102/178/255 -W2  -R$REGION $PROJ -K -O >> $0.ps
+awk '($7>2.5){print $9,$10,($7^2.5)/140}' KopehDagh_2005_all_mag.txt|psxy -Sc -G160/160/160 -W2  -R$REGION $PROJ -K -O >> $0.ps
+
+cat << EOF |awk '{print $1,$2,($3^2.5)/140}' |psxy -Sc -G196/19/19 -W2  -R$REGION $PROJ -K -O >> $0.ps
+
+
+
+61 37.7   3
+61 38.0   4
+61 38.2   5
+61 38.6   6
+ 
+ 
+EOF
+
+
+
+
+
+

### 2016-05-31 conclusion.tex
First complete draft

\section{Conclusion}
We studied the earthquake sequence of three tectonic seismic regions of north Iran. Results manifest the strong relationship between $k-M$ slope and Gutenberg-Richter parameters. The variation of $k-M$ slope and $b-value$ with time in sliding windows have similar behavior and drops down before big earthquakes. Significant reduction of $<T_C>$ value before big earthquake is observed. Higher coefficient of variation of $k-M$ slope in comparison with $b-value$'s CV, suggests the $k-M$ slope as better parameter for studying the magnitude time series due to higher sensitivity to window size and threshold magnitude than $b-value$. In general, $k-M$ and $b-value$ relationship preserves the behavior with variation of the window size and threshold magnitude, and could be an alternative approach for clustering the earthquake sequences based on different tectonic seismic zones.

### 2016-05-31 results.tex
First complete draft

@@
 \centering
-\includegraphics[scale=0.3]{figures/pdf/Figure066.pdf} 
-\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.
-The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
+\includegraphics[scale=0.4]{figures/pdf/Figure06.pdf} 
+\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones for 200 random sequence.
+The numbers on the mean and standard deviation plots are coefficient of variations $(std/mean)$}
 \label{fig:random}
@@
 \centering
-\includegraphics[scale=0.3]{figures/pdf/Figure06.pdf} 
+\includegraphics[scale=0.3]{figures/pdf/Figure07.pdf} 
 \caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.
@@
 \noindent 
-The relationship between $b-value$ and $K-M$ slope for Azerbaijan and Alborz region, suggested the idea of similar tectonic activity in these zones, in contrast with the $b-value$.
-In other words, may $K-M$ slope is more robust and less sensitive than $b-value$.
-Adding the value of this study into two previous similar studies results improves the regression factor (increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} pointed out.
+Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time.
+Having lower number of event, we used 40 events as a window length with shift of one event between two successive window.
+There is a very good similarity between the $K-M$ slope and $b-value$ in all tectonic seismic regions.
+In general, In all regions the $b-value$ and $K-M$ slope considerably drop before big earthquakes.
+Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}
 
 \noindent
-Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time.
-Having lower number of event, we used 40 events as a window length.
-We analyzed the sensitivity of the results to the window size.
-Even though there is a very good similarity between the $K-M$ slope and $b-value$ in Alborz tectonic seismic region, there is no as good as fit for Azerbaijan Tectonic seismic region.
-The results indicate the fact that, $K-M$ slope may provide extra information about the seismic sequence of the region than the $b-value$.
-
-The value of the K-M is increasing with increasing the magnitude. Fig yy shows the time vacation of the $K-M$ plot and $b-value$ for all tectonic seismic regions.
-
-In general, In all regions the $b-value$ and $K-M$ slope considerably drops before  big earthquakes.
-Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}
-
-Earthquake is a time dependent phenomenon, so studying the dynamic properties of the earthquake sequence is important to get different time dependent parameters.
-
 \citet{Telesca2016} observed the decreasing of the $<Tc>$ before large earthquake of Western India earthquake sequence.
@@
 \citet{Telesca2016} demonstrated that the decrement of $<Tc>$ before large earthquake are independent of window size and the threshold magnitude.
-
 The fluctuation of magnitude time series' topology properties (e.g.
@@
 Using higher number of samples in the window will reduce the temporal effects of small or moderate earthquakes and highlight the effects of big earthquakes, even though the behavior of the parameters in time and also before big earthquake are similar \citep{Telesca2016}.
-In general, more number of samples in a window smooth the results.
-
- In this study with increasing window size we can see the same behavior as small window. Undoubtedly, larger window size will reduce the effect of
+In general, more number of samples in a window smooth the results and highlight the effect of events with big magnitudes.
 
@@
 \centering
-\includegraphics[scale=0.34]{figures/pdf/Figure07.pdf} 
+\includegraphics[scale=0.34]{figures/pdf/Figure08.pdf} 
 \caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.

### 2016-06-01 abstract.tex
Added shima's comments.

@@
 The seismicity of northern Iran between 2005 and 2015 is investigated by means of visibility graph (VG) method.
-According to the seismicity, in this study the northern Iran is divided into three tectonic seismic regions including Azerbaijan, Alborz, and Kopeh Dagh.
+In this study the northern Iran is divided into three tectonic seismic regions: Azerbaijan, Alborz, and Kopeh Dagh.
 The aftershocks and foreshocks are removed from the catalog and the magnitude time series are generated for each tectonic seismic zone.
@@
 $b-value$) significantly decrease before large earthquakes.
-Cumulating the results of this study into two similar previous studies, improves the linear correlation coefficient factor and empower the idea of universal relationship between $b-value$ and $k-M$ slope.
-The behavior of  the VG's properties are similar to previous studies and could be considered an alternative method to analyze the earthquake sequence.
+Combining  the results of this study with two similar previous studies, improves the linear correlation coefficient factor and empower the idea of universal relationship between $b-value$ and $k-M$ slope.
+The behavior of  the VG's properties are similar to previous studies and could be considered an alternative method for analyzing the earthquake sequence.
 \end{abstract}

### 2016-06-01 introduction.tex
Added shima's comments.

@@
 \noindent
-\citet{Lacasa2008} presented a simple and fast computational method; known as visibility algorithm, to convert the time series into the graphs.
+\citet{Lacasa2008} introduced a simple and fast computational method; known as visibility algorithm, to convert time series into graphs.
 Basically the visibility graph presents the connection between nodes in the network.
-In each time series two characteristics are attributed to each incidents, including the time and the value of the incident.
-Two events are connected to each other, or visible to each other, if there is not any other event to interrupt their linear connection.
+For any time series, two characteristics are attributed to each incidents: ocurrance time and value of the incident.
+Two events are in connection or visible to each other, if no other event interrupts their linear connection.
 In mathematical form, event $i$ and event $j$ are visible to each other if the following equation fulfills:
@@
 \noindent
-where, $y$ is the value of the event and $t$ is the time of the event. $k$ is the index of any event between event $i$ and event $j$.
+where, $y$ is the value and $t$ is the time of the event.
+$k$ is the index of any event occurring between event $i$ and event $j$.
+The visibility graph generated from the time series holds the following conditions, 1) each event is visible to the first event at the right and left side (if there is any) of the event  (Connectivity), 2) The algorithm is developed without defining a direction for the links (Undirected),  3) Rescaling or translation of a time series is not changing the resulted visibility graph (Invariant under affine transformations of  the series data)\citep{Lacasa2008}.
+This concept has applications ranging in various fields including geophysical studies.
 
 \noindent
-The visibility graph that is generated from the time series holds the following conditions, 1) each event is visible to the events at the right and left side (if there is any) of the event  (Connectivity), 2) The algorithm is developed without defining a direction for the links (Undirected),  3) Rescaling or translation of the time series are not changing the resulted visibility graph (Invariant under affine transformations of  the series data)\citep{Lacasa2008}.
-
-\noindent
-The analysis of seismicity sequence through visibility graph for various tectonic seismic regions, revealed an alternative approach to study the magnitude time series.
-\citet{Telesca2012} studied the seismic sequence of Italy between 2005 and 2010 through using the visibility graph method.
-Using different threshold magnitude, and observing the collapsing effect of all the distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend only on the values of the magnitude and independent of the threshold magnitude.
-In other study, \citet{Telesca2013} studied the Seismicity of the Mexican subduction zone through visibility graph approach.
+The analysis of seismic sequence through visibility graph for various tectonic seismic regions, revealed an alternative approach to study the magnitude time series.
+\citet{Telesca2012} studied the seismic sequence of Italy between year 2005 and 2010 through using the visibility graph method.
+Applying different threshold magnitude and observing the collapsing effect of all the distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend only on the values of the magnitude and independent of the threshold magnitude.
+In another research, \citet{Telesca2013} studied the Seismicity of the Mexican subduction zone through visibility graph approach.
 They extracted the characteristics of the visibility graph for five different tectonic seismic regions.
 According to their study visibility graph could identify one of the regions that has a different seismicity characteristics, which is because of different tectonic processes that governs the area.
-The relationship between Gutenberg-Richter parameters and $k-M$ slope (The slope of regression line of Magnitude  of each event $(M)$ and its connectivity degree $k$) is investigated in their study.
-In a similar study \citet{Telesca2014}, studied the seismicity of 2002-2011 Pannonian seismicity using the visibility graph.
+The relationship between Gutenberg-Richter parameters and $k-M$ slope (The slope of regression line of Magnitude  of each event $(M)$ and its connectivity degree $(k)$) is investigated in their study.
+In a similar article \citet{Telesca2014}, studied the seismicity of 2002-2011 Pannonian seismicity using the visibility graph.
 They classified seismic catalog into shallow and deep earthquakes and extract the visibility graph characteristics for each class.
-According to their study there is close relationship between Gutenberg-Richter $b-value$ and $k-M$ slope of the visibility graph.
-High linear correlation coefficient of $b-value$ and $k-M$ slope suggests the universal character of the relationship between these parameters \citep{Telesca2014}.
+According to their study there is a close relationship between Gutenberg-Richter $b-value$ and $k-M$ slope of the visibility graph.
+High linear correlation coefficient value (close to 1)of $b-value$ and $k-M$ slope suggests the universal character of the relationship between these parameters \citep{Telesca2014}.
 \citet{Telesca2016} , used the $ <T_C>$, as the parameter window mean interval connectivity time ,  that indicates the mean linkage time between earthquakes, to study the 2003-2012 earthquake sequences in the Kachchh region of western India.
@@
 \noindent
-In this study we used visibility graph analysis to study the earthquake sequence of northern Iran.
+In this study we used visibility graph analysis to investigate the earthquake sequence of northern Iran.
 We divided northern Iran into three tectonic seismic regions including Azerbaijan, Alborz, and Kopeh Dagh.
@@
 Northern Iran has an elaborate seismic history.
-Having considerable number of earthquake and also being in different seismic tectonic zone, northern Iran is a good platform to analysis the visibility graph method's capabilities for studying the magnitude time series.
-In this study we present the relationship between $K-M$ slope and the $b-value$ in three different tectonic seismic region.
+Having considerable number of earthquakes and also being in different tectonic seismic zone, northern Iran is a good platform to analyze the visibility graph method's capabilities for studying the magnitude time series.
+In this study we present the relationship between $k-M$ slope and the $b-value$ in three different tectonic seismic regions.
 We also investigate the variation of $<T_C>$ value through time.

### 2016-06-01 results.tex
Added shima's comments.

@@
 \noindent
-We generated the visibility graph characteristics for three tectonic seismic regions in northern Iran for the period from 2005 to 2015.
-Number of earthquake in each catalog after declustering and the seismicity parameters are presented in Table.~\ref{tab:b_k_m_param}.
+We generated the visibility graph parameters for three tectonic seismic regions in northern Iran for the period from 2005 to 2015.
+Number of earthquakes in each catalog after declustering and the seismicity parameters are presented in Table.~\ref{tab:b_k_m_param}.
 
@@
 \noindent
-We compared the $k-M$ slope with the $b-value$ of the Gutenberg-Richter law in the whole catalog and also in the sliding window in time.
+We compared the $k-M$ slope with the $b-value$ of the Gutenberg-Richter law in the whole catalog and also in the sliding windows in time.
 The $b-value$ is generated through the maximum likelihood estimation \citep{Aki1965}.
@@
  where $\overline{M}$ is the average magnitude and $M_{min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic zone.
-Number of sequences and threshold magnitude are considerably different for all tectonic seismic zones.
-\citet{Telesca2013} studied the effect of number of earthquake in catalog on the $k-M$ slop.
+Number of sequences and threshold magnitudes are considerably different for all tectonic seismic zones.
+\citet{Telesca2013} studied the effect of the number of earthquakes in catalog on the $k-M$ slope.
 Comparing the result of Guerrero region with reduced random sequence, \citet{Telesca2013} found that the number of sequence doesn't affect the $k-M$ slope.
 According to \citet{Telesca2012}, the threshold magnitude has a minor effect in the VG parameters.
-In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly picked 200 sequence from the catalogs with various sequence size.
-The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopek Dagh regions, respectively) and the maximum size is the whole catalog.
-For each randomly picked magnitude time series we estimated the $Mc$ and calculated the $k-M$ and $b-value$.
+In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly pick 200 sequence from the catalogs with various sequence size.
+The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopek Dagh regions, respectively) and the maximum size is the size of the whole catalog.
+For each randomly picked magnitude time series we estimate the $Mc$ and calculated the $k-M$ and $b-value$.
 Fig.~\ref{fig:random} shows the relationship between $k-M$ slope and $b-value$ of the randomly selected data and statistical parameters for variables.
-Although changing number of events and the threshold magnitude are slightly change the results, they are fairly well clustered for each tectonic seismic region.
+Although changing the number of events and the threshold magnitude are slightly changes the results, they are fairly well clustered for each tectonic seismic region.
 
@@
  \noindent
-The $k-M$ slope shows the maximum coefficient of variation.
-We may argue that the $k-M$ slope is much dependent to the window size and threshold magnitude than $a-$ and $b-value$, which suggest the idea that $k-M$ slop can better represent the dynamic characteristics of the magnitude-time series.
+The $k-M$ slope shows higher coefficient of variation.
+We may argue that the $k-M$ slope is much dependent to the window size and threshold magnitude than $a-$ and $b-value$, which suggest the idea that $k-M$ slope can better represent the dynamic characteristics of the magnitude-time series.
 
  \noindent
- Fig.~\ref{fig:regression} shows the relationship between the $k-M$ slope for three tectonic seismic zones in Iran and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.
-Adding the results of this study into two previous similar studies' results, improves the regression factor (increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} concluded.
+ Fig.~\ref{fig:regression} shows the relationship between the $k-M$ slope for three tectonic seismic regions in north of Iran and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.
+Adding the results of the current study into the results of two previous similar studies improves the regression factor (increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} concluded.
 
@@
 \includegraphics[scale=0.3]{figures/pdf/Figure07.pdf} 
-\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.
+\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.
 The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
@@
 Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time.
-Having lower number of event, we used 40 events as a window length with shift of one event between two successive window.
-There is a very good similarity between the $K-M$ slope and $b-value$ in all tectonic seismic regions.
+Having lower number of event, we used 20 events as a window length with shift of one event between two successive windows.
+There is a very good similarity between the $k-M$ slope and $b-value$ in all tectonic seismic regions.
 In general, In all regions the $b-value$ and $K-M$ slope considerably drop before big earthquakes.
@@
 Using higher number of samples in the window will reduce the temporal effects of small or moderate earthquakes and highlight the effects of big earthquakes, even though the behavior of the parameters in time and also before big earthquake are similar \citep{Telesca2016}.
-In general, more number of samples in a window smooth the results and highlight the effect of events with big magnitudes.
+%In general, more number of samples in a window smooth the results and highlight the effect of events with big magnitudes.
 

### 2016-06-01 seismicity.tex
Added shima's comments.

@@
-\section{Tectonic seismic zones and seismicity parameters}
+\section{Tectonic seismic regions and seismicity parameters}
 \noindent
@@
 \citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Considering \citet{Mirzaei1998} devision, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
+Considering \citet{Mirzaei1998} devision as a reference, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
 Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Fig.~\ref{fig:study_region} shows the study region and tectonic seismic regions.
+Fig.~\ref{fig:study_region} shows the study area and tectonic seismic regions.
 \\
@@
 \caption{a) Map of Iran and surrounding countries.
-The study area is presented in gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities.
+The study area is situated in the gray box.
+b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities indicated with circles.
 Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
@@
 \noindent
-The catalog of recorded earthquake from 2005-2015 which is downloaded from IIEES is reported the earthquake based on different magnitude scale (reference).
-We converted the $M_L$, $M_S$, and $mb$ magnitudes through conversion relationships which is defined in \citet{Zare2014}.
-There also some of data which is recorded in $M_D$ (Duration magnitude).
+The catalog of recorded earthquakes from 2005-2015, which is downloaded from IIEES, reported the earthquakes based on different magnitude scale (reference).
+We converted the $M_L$, $M_S$, and $mb$ magnitudes through conversion relationships which are defined in \citet{Zare2014}.
+There are also some of data recorded in $M_D$ (Duration magnitude).
 These data are reported by International Seismological Centre (ISC).
-\citet{Deniz2010} developed a set of empirical equations to convert earthquake magnitudes in $mb$, $M_D$, $M_L$ and $M_S$ scales to the $M_W$ scales using orthogonal regression procedure.
+\citet{Deniz2010} developed a set of empirical equations to convert earthquake magnitudes from $mb$, $M_D$, $M_L$ and $M_S$ scales to $M_W$ scales using orthogonal regression procedure.
 They used data of earthquake that occurred in Turkey from different data centers including ISC.
 In this study we use the conversion equation of \citet{Deniz2010} to convert the $M_D$ to $M_W$.
-Although they defined the equation based on $4.5\leqslant M_W$, we extrapolate the equation for lower magnitude.
-We believe having those earthquakes, even with small error  in magnitude is important for estimating an accurate  Gutenberge-Richter values.
+Although \citet{Deniz2010} defined the equation based on $4.5\leqslant M_W$, we extrapolate the equation for lower magnitude.
+We believe having those earthquakes, even with small error  in magnitude is important for estimating accurate  Gutenberge-Richter values.
 
@@
 According to MAXC method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude.
-The steps for picking the completeness magnitude for each catalog include, 1) Calculating the $a-$ and $b-$ value based on the minimum magnitude, 2) generate  synthetic events based on the achieved value that the cumulative number of events obey the power law distribution, 3) Calculate the goodness of fit for predicted and observed cumulative numbers for each magnitude bin.
-Higher \citep{Wiemer2000}.
+The steps for picking the completeness magnitude for each catalog include, 1) Calculating the $a-$ and $b-$ value based on the minimum magnitude, 2) generating  synthetic events based on the achieved value that the cumulative number of events obey the power law distribution, 3) Calculating the goodness of fit for predicted and observed cumulative numbers for each magnitude bin \citep{Wiemer2000}.
 We increase the minimum magnitude and repeat the process.
 For each tectonic seismic region, we pick the magnitude corresponding to the highest goodness of fit.
-\citet{Wiemer2000} assumed the threshold of goodness of fit as 90\% in order to completeness of the catalog, however,  not all frequency-magnitude distributions reach the 90\% mark.
+\citet{Wiemer2000} assumed the threshold of goodness of fit as 90\% as a threshold to select completeness of the catalog, however,  not all frequency-magnitude distributions reach the 90\% mark.
 Fig.~\ref{fig:completeness} , shows the goodness of fit value for three tectonic seismic regions.
@@
 \noindent
-In this study we assumed the minimum magnitude for complete recording, $M_C$, are 2.9, 3.5, and 2.6 for Alborz, Azerbaijan, and Kopeh Dagh, respectively.
+In this study we assumed the minimum magnitudes for complete recording, $M_C$, are 3.5, 2.9, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively.
 Fig.~\ref{fig:mag-time} shows the magnitude time series of the declustered data for three regions.
-Earthquake with magnitude bigger than completeness magnitude are represented.
+Earthquakes with magnitude bigger than completeness magnitude are represented.
 
@@
 \includegraphics[scale=0.5]{figures/pdf/Figure04.pdf} 
-\caption{Variation of moment magnitude of earthquake in 2005-2015 for north Iran. (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
+\caption{Variation of moment magnitude of 2005-2015 earthquake for north Iran. (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
 \label{fig:mag-time}

### 2016-06-01 introduction.tex
Reduce the seismicity part and remove the earthquakes.

@@
 Basically the visibility graph presents the connection between nodes in the network.
-For any time series, two characteristics are attributed to each incidents: ocurrance time and value of the incident.
+For any time series, two characteristics are attributed to each event: occurrence time and value of the event.
 Two events are in connection or visible to each other, if no other event interrupts their linear connection.
@@
 Northern Iran has an elaborate seismic history.
-Having considerable number of earthquakes and also being in different tectonic seismic zone, northern Iran is a good platform to analyze the visibility graph method's capabilities for studying the magnitude time series.
+Having considerable number of earthquakes and also being in different tectonic seismic region, northern Iran is a good platform to analyze the visibility graph method's capabilities for studying the magnitude time series.
 In this study we present the relationship between $k-M$ slope and the $b-value$ in three different tectonic seismic regions.

### 2016-06-01 seismicity.tex
Reduce the seismicity part and remove the earthquakes.

@@
 Alborz tectonic seismic region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-Here a series of historical earthquakes occurred within a time period of more than 1100 years.
-At least three damaging earthquakes in 958 (western segments), 1655 (eastern segments), and 1830 (central segments), ruptured adjacent segments of the Mosha fault, located in northern Tehran.
 The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression.
-An earthquake with Ms 6.0 in 1978 led to a focal mechanism consistent with a low-angle thrust \citep{Berberian1999}.
+The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression \citep{Berberian1999}.
 
 \noindent
-There were three earthquakes from 1721-86 that ruptured the North Tabriz Fault system from southeast to northwest, as part of Azerbaijna tectonic seismic zone.
-The Tabriz region is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
+ The Tabriz region (located in Azerbaijan tectonic seismic region) is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
 The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-
-The NTF system and nearby reverse faults ruptured from southeast to northwest in three earthquakes over 65 years: the Shebli earthquake with magnitude 7.3 in 1721 on the southeastern NTF with a surface rupture more than 35 km long, reported by \citet{Jones1834} the Tabriz earthquake with magnitude 7.4 in 1780 on the northwestern NTF, with a surface rupture more than 42 km long and vertical separation of 2 to 4 m; and the Marand-Mishu earthquake with magnitude of 6.3 in 1786 on the Mishu reverse fault and the Sufian segment of the NTF.
-Another earthquake with  magnitude 5.5 struck the Tasuj reverse fault farther west in 1807 and an earthquake of M 6.7 took place along the South Bozqush reverse fault farther southeast in 1879.
-Prior to the 1721-86 earthquake sequence, Tabriz was shaken by earthquakes in 858 (M 6.0), 1042 (M 7.3), 1273 (M ~ 6.5), and 1304 (M 6.7)\citep{Berberian1999}.
-Most recently, earthquakes with Mw 6.1 in 1997 and Mw 6.4 in 2012 occurred in Ardabil and Tabriz, respectively.
-
-The main Kopeh-Dagh fault system has experienced some historic earthquakes.
-Ashgabat, the capital city of Turkmenistan, was destroyed by an earthquake of $Ms$ 7.2 in 1948 and destroyed more than 30 villages in Iran.
-This was the strongest earthquake to strike this region since at least 1455.
+\noindent
 The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
@@
 \citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Massive destruction of the capital city of Mithradatkert is attributed to the 10 BC event Ms 7.1, roughly 30 kilometers from the border of Iran (Nesa mound) \citep{Berberian2001}.
-The Neyshabur sequence of four earthquakes between 1209 and 1405 respected the segment boundary between the Neyshabur and Binalud reverse fault system \citep{Berberian1999}.
-Historical records show that in 1209, the district of Neyshabur from Neyshabur city in the west to Daneh village in the east was totally destroyed \citep{Berberian1999}.
 

### 2016-06-01 results.tex
second draft of paper.

@@
  where $\overline{M}$ is the average magnitude and $M_{min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic zone.
-Number of sequences and threshold magnitudes are considerably different for all tectonic seismic zones.
+Number of sequences and threshold magnitudes are considerably different for all tectonic seismic regions.
 \citet{Telesca2013} studied the effect of the number of earthquakes in catalog on the $k-M$ slope.
@@
 According to \citet{Telesca2012}, the threshold magnitude has a minor effect in the VG parameters.
-In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly pick 200 sequence from the catalogs with various sequence size.
+In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly pick 200 sequences from the catalogs with various sequence size.
 The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopek Dagh regions, respectively) and the maximum size is the size of the whole catalog.
@@
 Having lower number of event, we used 20 events as a window length with shift of one event between two successive windows.
+The calculated parameters of each window was associated with the time of occurrence of the last event in sliding window.
 There is a very good similarity between the $k-M$ slope and $b-value$ in all tectonic seismic regions.

### 2016-06-01 seismicity.tex
second draft of paper.

@@
 In this study we use the conversion equation of \citet{Deniz2010} to convert the $M_D$ to $M_W$.
-Although \citet{Deniz2010} defined the equation based on $4.5\leqslant M_W$, we extrapolate the equation for lower magnitude.
-We believe having those earthquakes, even with small error  in magnitude is important for estimating accurate  Gutenberge-Richter values.
 
@@
 According to MAXC method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude.
-The steps for picking the completeness magnitude for each catalog include, 1) Calculating the $a-$ and $b-$ value based on the minimum magnitude, 2) generating  synthetic events based on the achieved value that the cumulative number of events obey the power law distribution, 3) Calculating the goodness of fit for predicted and observed cumulative numbers for each magnitude bin \citep{Wiemer2000}.
+The steps for picking the completeness magnitude for each catalog include: 1) Calculating the $a-$ and $b-$ value based on the minimum magnitude, 2) generating  synthetic events based on the achieved value that the cumulative number of events obey the power law distribution, 3) Calculating the goodness of fit for predicted and observed cumulative numbers for each magnitude bin \citep{Wiemer2000}.
 We increase the minimum magnitude and repeat the process.
@@
 In this study we assumed the minimum magnitudes for complete recording, $M_C$, are 3.5, 2.9, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively.
-Fig.~\ref{fig:mag-time} shows the magnitude time series of the declustered data for three regions.
+Fig.~\ref{fig:mag-time} shows the magnitude time series of the declustered data for the three regions.
 Earthquakes with magnitude bigger than completeness magnitude are represented.

### 2016-06-03 abstract.tex
Reduce the seismicity part and remove the earthquakes.
first draft sent to english review

@@
 In this study the northern Iran is divided into three tectonic seismic regions: Azerbaijan, Alborz, and Kopeh Dagh.
-The aftershocks and foreshocks are removed from the catalog and the magnitude time series are generated for each tectonic seismic zone.
 Using declustered catalog, we studied the VG properties of the magnitude time series.
@@
 $b-value$) significantly decrease before large earthquakes.
-Combining  the results of this study with two similar previous studies, improves the linear correlation coefficient factor and empower the idea of universal relationship between $b-value$ and $k-M$ slope.
-The behavior of  the VG's properties are similar to previous studies and could be considered an alternative method for analyzing the earthquake sequence.
+Combining  the results of this study with two similar previous studies improves the linear correlation coefficient factor between $k-M$ and $b-value$ and empower the idea of universal relationship between $b-value$ and $k-M$ slope.
+The behavior of  the VG's properties are similar to previous studies and could be considered as an alternative method for analyzing earthquake sequences.
 \end{abstract}

### 2016-06-03 conclusion.tex
second draft of paper.
first draft sent to english review

@@
 \section{Conclusion}
+\noindent
 We studied the earthquake sequence of three tectonic seismic regions of north Iran.
@@
 Significant reduction of $<T_C>$ value before big earthquake is observed.
-Higher coefficient of variation of $k-M$ slope in comparison with $b-value$'s CV, suggests the $k-M$ slope as better parameter for studying the magnitude time series due to higher sensitivity to window size and threshold magnitude than $b-value$.
+Higher coefficient of variation of $k-M$ slope in comparison with $b-value$, suggests the $k-M$ slope as better parameter for studying the magnitude time series due to higher sensitivity to window size and threshold magnitude than $b-value$.
 In general, $k-M$ and $b-value$ relationship preserves the behavior with variation of the window size and threshold magnitude, and could be an alternative approach for clustering the earthquake sequences based on different tectonic seismic zones.

### 2016-06-03 introduction.tex
first draft sent to english review

@@
 \begin{equation}
-\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} 
+\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} ,
 \end{equation}
@@
 $k$ is the index of any event occurring between event $i$ and event $j$.
-The visibility graph generated from the time series holds the following conditions, 1) each event is visible to the first event at the right and left side (if there is any) of the event  (Connectivity), 2) The algorithm is developed without defining a direction for the links (Undirected),  3) Rescaling or translation of a time series is not changing the resulted visibility graph (Invariant under affine transformations of  the series data)\citep{Lacasa2008}.
+The visibility graph generated from the time series holds the following conditions, 1) each event is visible to the first event at its right and left side (if there is any) (Connectivity), 2) The algorithm is developed without defining a direction for the links (Undirected),  and 3) Rescaling or translation of a time series is not changing the resulted visibility graph (Invariant under affine transformations of  the series data)\citep{Lacasa2008}.
 This concept has applications ranging in various fields including geophysical studies.
@@
 \citet{Telesca2012} studied the seismic sequence of Italy between year 2005 and 2010 through using the visibility graph method.
-Applying different threshold magnitude and observing the collapsing effect of all the distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend only on the values of the magnitude and independent of the threshold magnitude.
-In another research, \citet{Telesca2013} studied the Seismicity of the Mexican subduction zone through visibility graph approach.
-They extracted the characteristics of the visibility graph for five different tectonic seismic regions.
-According to their study visibility graph could identify one of the regions that has a different seismicity characteristics, which is because of different tectonic processes that governs the area.
-The relationship between Gutenberg-Richter parameters and $k-M$ slope (The slope of regression line of Magnitude  of each event $(M)$ and its connectivity degree $(k)$) is investigated in their study.
-In a similar article \citet{Telesca2014}, studied the seismicity of 2002-2011 Pannonian seismicity using the visibility graph.
-They classified seismic catalog into shallow and deep earthquakes and extract the visibility graph characteristics for each class.
+Applying different threshold magnitudes and observing the collapsing effect of all the distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend only on the values of the magnitude and to be independent of the threshold magnitude.
+In another research, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through visibility graph approach.
+They extracted characteristics of the visibility graph for five different tectonic seismic regions.
+According to their study, visibility graph could distinguish the region with different seismicity characteristics, resulting from its different tectonic processes that governs the area.
+The relationship between Gutenberg-Richter parameters and $k-M$ slope (The slope of regression line fitting the Magnitude  of each event $(M)$ and its connectivity degree $(k)$) was investigated in their study.
+In a similar article, \citet{Telesca2014}, studied the seismicity of 2002-2011 Pannonian seismicity using the visibility graph.
+They classified seismic catalog into shallow and deep earthquakes and extracted the visibility graph characteristics for each class.
 According to their study there is a close relationship between Gutenberg-Richter $b-value$ and $k-M$ slope of the visibility graph.
-High linear correlation coefficient value (close to 1)of $b-value$ and $k-M$ slope suggests the universal character of the relationship between these parameters \citep{Telesca2014}.
-\citet{Telesca2016} , used the $ <T_C>$, as the parameter window mean interval connectivity time ,  that indicates the mean linkage time between earthquakes, to study the 2003-2012 earthquake sequences in the Kachchh region of western India.
+High linear correlation coefficient value (close to 1) of $b-value$ and $k-M$ slope suggests the universal character of the relationship between these parameters \citep{Telesca2014}.
+\citet{Telesca2016} , defined the $ <T_C>$, as the parameter window mean interval connectivity time ,  as an indication of the mean linkage time between earthquakes, to study the 2003-2012 earthquake sequence in the Kachchh region of western India.
 They found that the $<T_C>$ changes through time, indicating that the topological properties of the earthquake network are not stationary; also $<T_C>$ significantly decrees before the largest shock of the catalog.
@@
 \noindent
-In this study we used visibility graph analysis to investigate the earthquake sequence of northern Iran.
+In this study we use visibility graph analysis to investigate the earthquake sequence of northern Iran.
 We divided northern Iran into three tectonic seismic regions including Azerbaijan, Alborz, and Kopeh Dagh.
 Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran.
-The frequency of shocks vary widely from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region.
+\citet{Nemati2015} studied the most recent 200 years of seismicity in northern Iran.
+The frequency of shocks vary widely from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region \citep{Nemati2015} .
 \\

### 2016-06-03 main.tex
Added shima's comments.
first draft sent to english review

@@
 % Document Settings
-\documentclass[a4paper,review]{elsarticle}
+
+% review
+%\documentclass[authoryear,preprint,review,12pt]{elsarticle}
+
+% final
+% \documentclass[final,1p,times,authoryear]{elsarticle}
+
+\documentclass[authoryear,preprint,review,12pt]{elsarticle}
 
@@
 % Long Title
-\title{Visibility Graph Analysis of the 2005-2015 Earthquake Sequence in Northern Iran}
+\title{Analysis of 2005-2015 Earthquake Sequence in Northern Iran Using Visibility Graph Approach}
 
 % Authors
-%\author[label1]{Naeem Khoshnevis\corref{cor1}}
+\author[label1]{Naeem Khoshnevis\corref{cor1}}
 %\author[label1,label2]{Shima AzizzadehRoodpish}
-%\cortext[cor1]{Corresponding author. Tel: \\
- %                    Email address: nkhshnvs@memphis.edu (N.Khoshnevis)}
+\cortext[cor1]{Corresponding author. Tel: \\
+                  Email address: nkhshnvs@memphis.edu (N.Khoshnevis)}
 
@@
 \begin{keyword}
-Visibility Graph \sep Earthquake Magnitude \sep North Iran \sep b-value
+Visibility Graph \sep Earthquake sequence \sep Magnitude \sep North Iran \sep b-value
 

### 2016-06-03 results.tex
first draft sent to english review

@@
 \centering
-\caption{Seismic parameters and K-M slope values for north Iran tectonic seismic zones.}
+\caption{Seismic parameters and $k-M$ slope values for north Iran tectonic seismic zones.}
 \begin{tabular}{ccccc}
-Region          & Number of Earthquake &  Mc &  b-value & K-M slope \\ \hline
+Region          & Number of Earthquake &  $Mc$ &  $b-value$ & $k-M$ slope \\ \hline
 Azerbaijan     & 93                                 & 3.5   & 1.0190  & 9.2004       \\ \hline
-Alborz            & 488                               & 2.9   & 0.8532  & 9.2821      \\ \hline
+Alborz            & 794                               & 2.6   & 0.7717  & 9.0461      \\ \hline
 Kopek Dagh  & 282                               & 2.6   & 0.5799  & 6.5818     \\ \hline
@@
 \includegraphics[scale=0.35]{figures/pdf/Figure05.pdf} 
-\caption{ K-M relationship for north Iran seismicity. a) Azerbaijan b) Alborz c)Kopeh Dagh}
+\caption{ $k-M$ relationship for north Iran seismicity. a) Azerbaijan b) Alborz c)Kopeh Dagh}
 \label{fig:k_m_plot_m}
@@
 \begin{equation}
-b = \frac{log_{10}(e) }{\overline{M} - M_{min}}  
+b = \frac{log_{10}(e) }{\overline{M} - M_{min}},
 \end{equation}
@@
 In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly pick 200 sequences from the catalogs with various sequence size.
-The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopek Dagh regions, respectively) and the maximum size is the size of the whole catalog.
+The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively) and the maximum size is the size of the whole catalog.
 For each randomly picked magnitude time series we estimate the $Mc$ and calculated the $k-M$ and $b-value$.
@@
 \includegraphics[scale=0.4]{figures/pdf/Figure06.pdf} 
-\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones for 200 random sequence.
-The numbers on the mean and standard deviation plots are coefficient of variations $(std/mean)$}
+\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence.
+The numbers on the mean and standard deviation plots are coefficient of variations in percent$(standard \ deviation / mean)$.}
 \label{fig:random}
@@
  \noindent
+The coefficient of variation of parameters are shown in Fig.~\ref{fig:random}.
 The $k-M$ slope shows higher coefficient of variation.
@@
  Fig.~\ref{fig:regression} shows the relationship between the $k-M$ slope for three tectonic seismic regions in north of Iran and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.
-Adding the results of the current study into the results of two previous similar studies improves the regression factor (increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} concluded.
+Adding the results of the current study into the results of two previous similar studies improves the regression factor (with an increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} concluded.
 
@@
 \caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.
-The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
+The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and north Iran)}
 \label{fig:regression}
@@
 There is a very good similarity between the $k-M$ slope and $b-value$ in all tectonic seismic regions.
-In general, In all regions the $b-value$ and $K-M$ slope considerably drop before big earthquakes.
+In general, In all regions the $b-value$ and $k-M$ slope considerably drop before big earthquakes.
 Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}
@@
 \noindent
-\citet{Telesca2016} observed the decreasing of the $<Tc>$ before large earthquake of Western India earthquake sequence.
-Fig.~\ref{fig:tc} shows the time variation of $<Tc>$ in the study area.
-The decreasing of the $<Tc>$ for large earthquakes have been shown in the figure.
+\citet{Telesca2016} observed the decreasing in $<Tc>$ before large earthquake of Western India earthquake sequence.
+Fig.~\ref{fig:tc} shows the time variation of $<Tc>$ in the study area and decrease in $<Tc>$ befor large earthquakes is clearly visible.
 \citet{Telesca2016} demonstrated that the decrement of $<Tc>$ before large earthquake are independent of window size and the threshold magnitude.
-The fluctuation of magnitude time series' topology properties (e.g.
-the $k-M$ slope and $<Tc>$) could be affected by the window size.
-Sharp changes in the VG parameters happens through small windows.
-Using higher number of samples in the window will reduce the temporal effects of small or moderate earthquakes and highlight the effects of big earthquakes, even though the behavior of the parameters in time and also before big earthquake are similar \citep{Telesca2016}.
-%In general, more number of samples in a window smooth the results and highlight the effect of events with big magnitudes.
+Fig.~\ref{fig:tc} shows the decrement of value of $< T_C >$, $k-M$, and $b-value$ before big earthquakes.
 
@@
 \includegraphics[scale=0.34]{figures/pdf/Figure08.pdf} 
-\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.
-The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
+\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_C >$ (Right) with time.
+Black arrows show the occurrence of the major earthquakes.
+Numbers on arrows indicate the moment magnitude of the earthquake.}
 \label{fig:tc}

### 2016-06-03 seismicity.tex
first draft sent to english review

@@
 Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-These earthquakes are categorized in various tectonic seismic zones.
-Based on seismicity parameters different tectonic seismic devisions have been defined for Iran.
+Based on seismicity parameters, different tectonic seismic devisions have been defined for Iran.
 Some studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
@@
 Considering \citet{Mirzaei1998} devision as a reference, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
+Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of the northern Iran.
 Fig.~\ref{fig:study_region} shows the study area and tectonic seismic regions.
@@
 The study area is situated in the gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities indicated with circles.
+b) The study area containing seismotectonic provinces after \citet{Mirzaei1998} is presented, and location of big cities indicated with circles.
 Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
@@
 \noindent
-The catalog of recorded earthquakes from 2005-2015, which is downloaded from IIEES, reported the earthquakes based on different magnitude scale (reference).
+The catalog of recorded earthquakes from 2005-2015, which is downloaded from IIEES, reported the earthquakes based on different magnitude scales \citep{IIEES}.
 We converted the $M_L$, $M_S$, and $mb$ magnitudes through conversion relationships which are defined in \citet{Zare2014}.
@@
 Completeness of catalog is an important factor in studying the earthquake sequence.
-In this study we used the Maximum curvature method (MAXC) \citep{Wiemer2000}.
+In this study we used the Maximum curvature method (MAXC) \citep{Wiemer2000} to determine the completeness magnitude.
 According to MAXC method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude.
-The steps for picking the completeness magnitude for each catalog include: 1) Calculating the $a-$ and $b-$ value based on the minimum magnitude, 2) generating  synthetic events based on the achieved value that the cumulative number of events obey the power law distribution, 3) Calculating the goodness of fit for predicted and observed cumulative numbers for each magnitude bin \citep{Wiemer2000}.
-We increase the minimum magnitude and repeat the process.
-For each tectonic seismic region, we pick the magnitude corresponding to the highest goodness of fit.
-\citet{Wiemer2000} assumed the threshold of goodness of fit as 90\% as a threshold to select completeness of the catalog, however,  not all frequency-magnitude distributions reach the 90\% mark.
-Fig.~\ref{fig:completeness} , shows the goodness of fit value for three tectonic seismic regions.
+The steps for picking the completeness magnitude for each catalog include: 1) Calculating the $a-$ and $b-$ value based on the minimum magnitude, 2) generating  synthetic events based on the achieved value somehow the cumulative number of events obey the power law distribution, and 3) Calculating the goodness of fit for predicted and observed cumulative numbers for each magnitude bin \citep{Wiemer2000}.
+We increase the minimum magnitude and repeat the process in order to calculate the goodness of fit for each magnitude.
+\citet{Wiemer2000} assumed the goodness of fit of 90\% as a threshold to select completeness of the catalog.
+However,  not all frequency-magnitude distributions reach the 90\% mark.
+Fig.~\ref{fig:completeness} , shows the goodness of fit values for three tectonic seismic regions.
+For each tectonic seismic region, we pick the magnitude corresponding to the highest goodness of fit or the first magnitude with goodness of fit bigger than 90\%.
 
@@
 \noindent
-In this study we assumed the minimum magnitudes for complete recording, $M_C$, are 3.5, 2.9, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively.
+In this study we assume the minimum magnitudes for complete recording, $M_C$, are 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively.
 Fig.~\ref{fig:mag-time} shows the magnitude time series of the declustered data for the three regions.

### 2016-07-11 abstract.tex
fix some problem.

@@
 \begin{abstract}
-The seismicity of northern Iran between 2005 and 2015 is investigated by means of visibility graph (VG) method.
+The seismicity of northern Iran between 2005 and 2015 is investigated by means of the visibility graph (VG) method.
+For purposes of this study, northern Iran is divided into three tectonic seismic regions: Azerbaijan, Alborz, and Kopeh Dagh.
+Using the declustered catalog, we studied the VG properties of the magnitude time series.
+The results show a relationship between the $k-M$ slope and the $b-value$ of the Gutenberg-Richter law.
+Topological properties (i.e.
+$< T_c >$, $k-M$ slope) of the network and dynamic properties of magnitude time series (i.e.
+$b-value$) significantly decrease before large earthquakes.
+Combining the results of this study with two similar previous studies improves the linear correlation coefficient factor between $k-M$ and $b-value$, and empowers the idea of a universal relationship between $b-value$ and $k-M$ slope.
+The behaviors of the VG's properties are similar to previous studies and could be considered an alternative method for analyzing earthquake sequences.
+\end{abstract}
+
+%% Original text
+
+%\begin{abstract}
+%The seismicity of northern Iran between 2005 and 2015 is investigated by means of visibility graph (VG) method.
 In this study the northern Iran is divided into three tectonic seismic regions: Azerbaijan, Alborz, and Kopeh Dagh.
@@
 The behavior of  the VG's properties are similar to previous studies and could be considered as an alternative method for analyzing earthquake sequences.
-\end{abstract}
+%\end{abstract}

### 2016-07-11 conclusion.tex
fix some problem.

@@
 \noindent
-We studied the earthquake sequence of three tectonic seismic regions of north Iran.
+We studied the earthquake sequence of three tectonic seismic regions of northern Iran.
 Results manifest the strong relationship between  $k-M$  slope and Gutenberg-Richter parameters.
-The variation of $k-M$ slope and $b-value$ with time in sliding windows have similar behavior and drops down before big earthquakes.
-Significant reduction of $<T_C>$ value before big earthquake is observed.
-Higher coefficient of variation of $k-M$ slope in comparison with $b-value$, suggests the $k-M$ slope as better parameter for studying the magnitude time series due to higher sensitivity to window size and threshold magnitude than $b-value$.
-In general, $k-M$ and $b-value$ relationship preserves the behavior with variation of the window size and threshold magnitude, and could be an alternative approach for clustering the earthquake sequences based on different tectonic seismic zones.
+The variations of  $k-M$  slope and  b-value  with time in sliding windows have similar behavior and decline before large earthquakes.
+A significant reduction of  $<T_C>$  value before large earthquakes was observed.
+The higher coefficient of variation of  $k-M$  slope in comparison with  b-value  suggests that the  $k-M$  slope is a better parameter for studying the magnitude time series due to higher sensitivity to window size and threshold magnitude than  is found in the $b-value$.
+In general,  the $k-M$  and  $b-value$  relationship preserves the behavior with the variation in the window size and threshold magnitude, and could be an alternative approach for clustering earthquake sequences based on different tectonic seismic zones.

### 2016-07-11 introduction.tex
fix some problem.

@@
 \noindent
-\citet{Lacasa2008} introduced a simple and fast computational method; known as visibility algorithm, to convert time series into graphs.
+\citet{Lacasa2008} introduced a simple and fast computational method, known as visibility algorithm, to convert time series into graphs.
+Basically, the visibility graph presents the connection between nodes in a network.
+For any time series, two characteristics are attributed to each event: occurrence time and value of the event.
+Two events are in connection or visible to each other if no other event interrupts their linear connection.
+In mathematical form, events $i$ and $j$ are visible to each other if the following equation is fulfilled:
+
+\begin{equation}
+\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} ,
+\end{equation}
+\noindent
+where $y$ is the value and $t$ is the time of the event, and $k$ is the index of any event occurring between events  $i$  and  $j$.
+The visibility graph generated from a time series holds the following conditions: 1) each event is visible to the first event at its right and left side (if there is any) (Connectivity); 2) the algorithm is developed without defining a direction for the links (Undirected); and 3) rescaling or translation of a time series does not change the resulting visibility graph (invariant under affine transformations of the series data) \citep{Lacasa2008}.
+This concept has applications in fields including geophysical studies.
+\\
+\noindent
+The analysis of seismic sequence through visibility graph for various tectonic seismic regions revealed an alternative approach to studying the magnitude time series.
+\citet{Telesca2012} studied the seismic sequence of Italy between the years 2005 and 2010 using the visibility graph method.
+Applying different threshold magnitudes and observing the collapsing effect of all distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend on only the values of the magnitude and being independent of the threshold magnitude.
+\noindent
+In other research, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through the visibility graph approach.
+They extracted characteristics of the visibility graph for five different tectonic seismic regions.
+According to their study, a visibility graph could distinguish the region with different seismicity characteristics, resulting from its different tectonic processes governing the area.
+Their study investigated the relationship between the Gutenberg-Richter parameters and the $k-M$ slope, which is the slope of the regression line fitting the magnitude of each event  ($M$) and its connectivity degree  ($k$).
+\noindent
+In a similar article, \citet{Telesca2014} studied the seismicity of the 2002-11 Pannonian seismicity using visibility graph.
+They classified the seismic catalog into shallow and deep earthquakes, and extracted the visibility graph characteristics for each class.
+According to their study, a close relationship exists between the Gutenberg-Richter $b-value$ and the $k-M$ slope of the visibility graph.
+The high linear correlation coefficient value (close to 1) of $b-value$ and $k-M$  slope suggests the universal character of the relationship between these parameters \citep{Telesca2014} .
+\noindent
+\citet{Telesca2016}   defined    $<T_C>$  as the parameter window mean interval connectivity time ,  as an indication of the mean linkage time between earthquakes, in studying the 2003-12 earthquake sequence in the Kachchh region of western India.
+They found that  $<T_C>$  changes through time, indicating that the topological properties of the earthquake network are not stationary.
+In addition,  $<T_C>$  significantly decrees before the largest shock of the catalog.
+Analyzing the Gutenberg-Richter values of  the magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series by using the features of networks.
+\noindent
+In this study, we use visibility graph analysis to investigate the earthquake sequence of northern Iran.
+We divided northern Iran into three tectonic seismic regions, namely Azerbaijan, Alborz, and Kopeh Dagh.
+Recently, northern Iran has been studied in detail from different seismological points of view.
+\citet{Nemati2015} studied the most recent 200 years of seismicity in northern Iran.
+The frequency of shocks varied widely, from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years (3.25 event/year) for the Kopeh-Dagh region \citep{Nemati2015}.
+Northern Iran has an extensive seismic history.
+Having a considerable number of earthquakes and being in a unique tectonic seismic region, northern Iran is a good platform from which to analyze the visibility graph method's capabilities for studying the magnitude time series.
+In this study, we present the relationship between  $k-M$  slope and $b-value$  in these three different tectonic seismic regions.
+We also investigate the variation of  $<T_C>$  value through time.
+
+% Original text
+%\section{Introduction}
+%\noindent
+%\citet{Lacasa2008} introduced a simple and fast computational method; known as visibility algorithm, to convert time series into graphs.
 Basically the visibility graph presents the connection between nodes in the network.
@@
 In mathematical form, event $i$ and event $j$ are visible to each other if the following equation fulfills:
-
-\begin{equation}
-\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} ,
-\end{equation}
-
-\noindent
-where, $y$ is the value and $t$ is the time of the event.
+%
+%\begin{equation}
+%\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} ,
+%\end{equation}
+%
+%\noindent
+%where, $y$ is the value and $t$ is the time of the event.
 $k$ is the index of any event occurring between event $i$ and event $j$.
@@
 This concept has applications ranging in various fields including geophysical studies.
-
-\noindent
-The analysis of seismic sequence through visibility graph for various tectonic seismic regions, revealed an alternative approach to study the magnitude time series.
+%
+%\noindent
+%The analysis of seismic sequence through visibility graph for various tectonic seismic regions, revealed an alternative approach to study the magnitude time series.
 \citet{Telesca2012} studied the seismic sequence of Italy between year 2005 and 2010 through using the visibility graph method.
@@
 \\
-
-\noindent
-In this study we use visibility graph analysis to investigate the earthquake sequence of northern Iran.
+%
+%\noindent
+%In this study we use visibility graph analysis to investigate the earthquake sequence of northern Iran.
 We divided northern Iran into three tectonic seismic regions including Azerbaijan, Alborz, and Kopeh Dagh.
@@
 \\
-
-\noindent
-Northern Iran has an elaborate seismic history.
+%
+%\noindent
+%Northern Iran has an elaborate seismic history.
 Having considerable number of earthquakes and also being in different tectonic seismic region, northern Iran is a good platform to analyze the visibility graph method's capabilities for studying the magnitude time series.
@@
 We also investigate the variation of $<T_C>$ value through time.
+%

### 2016-07-11 results.tex
fix some problem.

@@
 \noindent
-We generated the visibility graph parameters for three tectonic seismic regions in northern Iran for the period from 2005 to 2015.
-Number of earthquakes in each catalog after declustering and the seismicity parameters are presented in Table.~\ref{tab:b_k_m_param}.
+We generated the visibility graph parameters for three tectonic seismic regions in northern Iran for the period 2005-15.
+The number of earthquakes in each catalog after declustering and their seismicity parameters is presented in Table.~\ref{tab:b_k_m_param}.
 
@@
 Fig.~\ref{fig:k_m_plot_m}  shows the  $k-M$  relationship for the study regions.
-In general with increasing magnitude the connectivity degree increases which results in increasing the slope of the $k-M$ relationship.
+In general, with increasing magnitude, the connectivity degree increases, which increases the slope of the  $k-M$  relationship.
 
@@
 \end{figure}
-
  \noindent
-We compared the $k-M$ slope with the $b-value$ of the Gutenberg-Richter law in the whole catalog and also in the sliding windows in time.
-The $b-value$ is generated through the maximum likelihood estimation \citep{Aki1965}.
+We compared the  $k-M$  slope with the  $b-value$  of the Gutenberg-Richter law through the entire catalog and in the sliding windows in time.
+The  $b-value$  is generated through the maximum likelihood estimation  \citep{Aki1965} .
 
@@
 \end{equation}
-
  \noindent
- where $\overline{M}$ is the average magnitude and $M_{min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic zone.
-Number of sequences and threshold magnitudes are considerably different for all tectonic seismic regions.
-\citet{Telesca2013} studied the effect of the number of earthquakes in catalog on the $k-M$ slope.
-Comparing the result of Guerrero region with reduced random sequence, \citet{Telesca2013} found that the number of sequence doesn't affect the $k-M$ slope.
-According to \citet{Telesca2012}, the threshold magnitude has a minor effect in the VG parameters.
-In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly pick 200 sequences from the catalogs with various sequence size.
-The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively) and the maximum size is the size of the whole catalog.
-For each randomly picked magnitude time series we estimate the $Mc$ and calculated the $k-M$ and $b-value$.
-Fig.~\ref{fig:random} shows the relationship between $k-M$ slope and $b-value$ of the randomly selected data and statistical parameters for variables.
-Although changing the number of events and the threshold magnitude are slightly changes the results, they are fairly well clustered for each tectonic seismic region.
+where $\overline{M}$ is the average magnitude, and  $M_ {min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic region.
+The number of sequences and threshold magnitudes is considerably different for all tectonic seismic regions.
+\citet{Telesca2013}  studied the effect of the number of earthquakes in the catalog on the  $k-M$  slope.
+Comparing the result with the Guerrero region with reduced random sequence,  \citet{Telesca2013}  found that the number of sequences did not affect the  $k-M$  slope.
+According to  \citet{Telesca2012}, the threshold magnitude has minor effect in the VG parameters.
+In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, we randomly picked 200 sequences from the catalogs with various sequence sizes.
+The minimum size of random windows is 150 events.
+(Note that the number of events in each catalog, before removing the events with magnitude less than the completeness magnitude, is 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively.).
+The maximum size is the size of the entire catalog.
+For each randomly picked magnitude time series,  we estimated $Mc$,  and the  $k-M$  and $b-value$ were calculated.
+Fig.~\ref{fig:random} shows the relationship between  $k-M$  slope and  $b-value$  of the randomly selected data and the statistical parameters for variables.
+Although changing the number of events and the threshold magnitude is a slight change, the results are fairly well clustered for each tectonic seismic region.
 
@@
 \noindent
-The coefficient of variation of parameters are shown in Fig.~\ref{fig:random}.
-The $k-M$ slope shows higher coefficient of variation.
-We may argue that the $k-M$ slope is much dependent to the window size and threshold magnitude than $a-$ and $b-value$, which suggest the idea that $k-M$ slope can better represent the dynamic characteristics of the magnitude-time series.
-
+The coefficient of variation of parameters is shown in Fig.~\ref{fig:random}.
+The  $k-M$  slope shows the higher coefficient of variation.
+The  $k-M$  slope is more dependent on the window size and threshold magnitude than  on the a-  and  b-values , which suggests that  the $k-M$  slope can better represent the dynamic characteristics of the magnitude-time series.
  \noindent
- Fig.~\ref{fig:regression} shows the relationship between the $k-M$ slope for three tectonic seismic regions in north of Iran and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.
-Adding the results of the current study into the results of two previous similar studies improves the regression factor (with an increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} concluded.
+ Fig.~\ref{fig:regression} shows the relationship between the  $k-M$  slope and $b-value$ for the three tectonic seismic regions in northern Iran and two other studies of Mexican zones  \citep{Telesca2013}  and Pannonia zones  \citep{Telesca2014}.
+Adding the results of the current study into the results of two previous similar studies improves the regression factor (with an increase from R=0.95 to R=0.955), and empowers the concept of the universal character of the relationship between the  $b-value$  and the  $k-M$  slope, as  \citet{Telesca2014} concluded.
 
@@
 Fig.\ref{fig:tc} shows the variation of the  $k-M$  slope and  $b-value$  with time.
-Having lower number of event, we used 20 events as a window length with shift of one event between two successive windows.
-The calculated parameters of each window was associated with the time of occurrence of the last event in sliding window.
-There is a very good similarity between the $k-M$ slope and $b-value$ in all tectonic seismic regions.
-In general, In all regions the $b-value$ and $k-M$ slope considerably drop before big earthquakes.
-Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}
-
+Having a lower number of events, we chose 20 events as the window length with a shift of one event between two successive windows.
+The calculated parameters of each window were associated with the time of occurrence of the last event in the sliding window.
+The  $k-M$  slope and  $b-value$  in all tectonic seismic regions are very similar.
+In general, in all regions the $b-value$  and  $k-M$  slope drop considerably before large earthquakes.
+The decline in the  $b-value$  before large earthquakes has been studied in many regions \citep{Wyss2000, Wyss2006, Schorlemmer2005, Chan2012}.
 \noindent
-\citet{Telesca2016} observed the decreasing in $<Tc>$ before large earthquake of Western India earthquake sequence.
-Fig.~\ref{fig:tc} shows the time variation of $<Tc>$ in the study area and decrease in $<Tc>$ befor large earthquakes is clearly visible.
-\citet{Telesca2016} demonstrated that the decrement of $<Tc>$ before large earthquake are independent of window size and the threshold magnitude.
-Fig.~\ref{fig:tc} shows the decrement of value of $< T_C >$, $k-M$, and $b-value$ before big earthquakes.
+\citet{Telesca2016}  observed the decrease in  $<T_C>$  before the large earthquake of the western India earthquake sequence.
+Fig.\ref{fig:tc}  shows the time variation of  $<T_C>$   in the study area, and the decrease in  $<T_C>$   before a large earthquake is clearly visible.
+\citet{Telesca2016}  demonstrated that the decrement of  $<T_C>$   before a large earthquake is independent of window size and threshold magnitude.
+Fig.\ref{fig:tc}  shows the decrement in the value of  $<T_C>$  ,  $k-M$ , and  $b-value$  before large earthquakes.
 
@@
 \end{figure}
+
+ % Original text
+%\section{Results}
+%\noindent
+%We generated the visibility graph parameters for three tectonic seismic regions in northern Iran for the period from 2005 to 2015.
+Number of earthquakes in each catalog after declustering and the seismicity parameters are presented in Table.~\ref{tab:b_k_m_param}.
+%
+%
+%\begin{table}[h]
+%\centering
+%\caption{Seismic parameters and $k-M$ slope values for north Iran tectonic seismic zones.}
+%\begin{tabular}{ccccc}
+%Region          & Number of Earthquake &  $Mc$ &  $b-value$ & $k-M$ slope \\ \hline
+%Azerbaijan     & 93                                 & 3.5   & 1.0190  & 9.2004       \\ \hline
+%Alborz            & 794                               & 2.6   & 0.7717  & 9.0461      \\ \hline
+%Kopek Dagh  & 282                               & 2.6   & 0.5799  & 6.5818     \\ \hline
+%\end{tabular}
+%\label{tab:b_k_m_param}
+%\end{table}
+%
+%\noindent
+%Fig.~\ref{fig:k_m_plot_m} shows the $k-M$ relationship for the study regions.
+In general with increasing magnitude the connectivity degree increases which results in increasing the slope of the $k-M$ relationship.
+%
+%\begin{figure} [ht]
+%\centering
+%\includegraphics[scale=0.35]{figures/pdf/Figure05.pdf} 
+%\caption{ $k-M$ relationship for north Iran seismicity. a) Azerbaijan b) Alborz c)Kopeh Dagh}
+%\label{fig:k_m_plot_m}
+%\end{figure}
+%
+%\noindent
+%We compared the $k-M$ slope with the $b-value$ of the Gutenberg-Richter law in the whole catalog and also in the sliding windows in time.
+The $b-value$ is generated through the maximum likelihood estimation \citep{Aki1965}.
+%
+%\begin{equation}
+%b = \frac{log_{10}(e) }{\overline{M} - M_{min}},
+%\end{equation}
+% 
+% \noindent
+% where $\overline{M}$ is the average magnitude and $M_{min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic zone.
+Number of sequences and threshold magnitudes are considerably different for all tectonic seismic regions.
+\citet{Telesca2013} studied the effect of the number of earthquakes in catalog on the $k-M$ slope.
+Comparing the result of Guerrero region with reduced random sequence, \citet{Telesca2013} found that the number of sequence doesn't affect the $k-M$ slope.
+According to \citet{Telesca2012}, the threshold magnitude has a minor effect in the VG parameters.
+In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly pick 200 sequences from the catalogs with various sequence size.
+The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively) and the maximum size is the size of the whole catalog.
+For each randomly picked magnitude time series we estimate the $Mc$ and calculated the $k-M$ and $b-value$.
+Fig.~\ref{fig:random} shows the relationship between $k-M$ slope and $b-value$ of the randomly selected data and statistical parameters for variables.
+Although changing the number of events and the threshold magnitude are slightly changes the results, they are fairly well clustered for each tectonic seismic region.
+% 
+% \begin{figure} [ht]
+%\centering
+%\includegraphics[scale=0.4]{figures/pdf/Figure06.pdf} 
+%\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence.
+The numbers on the mean and standard deviation plots are coefficient of variations in percent$(standard \ deviation / mean)$.}
+%\label{fig:random}
+%\end{figure}
+% 
+% \noindent
+%The coefficient of variation of parameters are shown in Fig.~\ref{fig:random}.
+The $k-M$ slope shows higher coefficient of variation.
+We may argue that the $k-M$ slope is much dependent to the window size and threshold magnitude than $a-$ and $b-value$, which suggest the idea that $k-M$ slope can better represent the dynamic characteristics of the magnitude-time series.
+% 
+% 
+%
+% 
+% \noindent
+% Fig.~\ref{fig:regression} shows the relationship between the $k-M$ slope for three tectonic seismic regions in north of Iran and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.
+Adding the results of the current study into the results of two previous similar studies improves the regression factor (with an increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} concluded.
+%
+%\begin{figure} [ht]
+%\centering
+%\includegraphics[scale=0.3]{figures/pdf/Figure07.pdf} 
+%\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.
+The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and north Iran)}
+%\label{fig:regression}
+%\end{figure}
+%
+%
+%\noindent 
+%Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time.
+Having lower number of event, we used 20 events as a window length with shift of one event between two successive windows.
+The calculated parameters of each window was associated with the time of occurrence of the last event in sliding window.
+There is a very good similarity between the $k-M$ slope and $b-value$ in all tectonic seismic regions.
+In general, In all regions the $b-value$ and $k-M$ slope considerably drop before big earthquakes.
+Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}
+%
+%\noindent
+%\citet{Telesca2016} observed the decreasing in $<Tc>$ before large earthquake of Western India earthquake sequence.
+Fig.~\ref{fig:tc} shows the time variation of $<Tc>$ in the study area and decrease in $<Tc>$ befor large earthquakes is clearly visible.
+\citet{Telesca2016} demonstrated that the decrement of $<Tc>$ before large earthquake are independent of window size and the threshold magnitude.
+Fig.~\ref{fig:tc} shows the decrement of value of $< T_C >$, $k-M$, and $b-value$ before big earthquakes.
+% 
+% \begin{figure} [ht]
+%\centering
+%\includegraphics[scale=0.34]{figures/pdf/Figure08.pdf} 
+%\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_C >$ (Right) with time.
+Black arrows show the occurrence of the major earthquakes.
+Numbers on arrows indicate the moment magnitude of the earthquake.}
+%\label{fig:tc}
+%\end{figure}

### 2016-07-11 seismicity.tex
fix some problem.

@@
 \noindent
-Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-Based on seismicity parameters, different tectonic seismic devisions have been defined for Iran.
-Some studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Considering \citet{Mirzaei1998} devision as a reference, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of the northern Iran.
+Iran is situated over the Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
+Based on seismicity parameters, different tectonic seismic divisions have been defined for Iran.
+Some studies have defined more detailed divisions \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province  \citep{Stocklin1968,Takin1972,Berberian1976}.
+\citet{Mirzaei1998},  dividing Iran into five tectonic regions, called Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
+Considering  \citet{Mirzaei1998}  a division as a reference,  \citet{Karimiparidari2013}  divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and the Alborz Mountain Range (hereinafter, Alborz).
+Azerbaijan, Alborz, and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
 Fig.~\ref{fig:study_region} shows the study area and tectonic seismic regions.
@@
 \noindent
-Alborz tectonic seismic region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression \citep{Berberian1999}.
+The Alborz tectonic seismic region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
+The North Tehran Thrust adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
+The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression  \citep{Berberian1999}.\\
+\noindent
+The Tabriz region (located in the Azerbaijan tectonic seismic region) is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains toward the Caucasus.
+The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement  \citep{Berberian1999}.
 
-\noindent
- The Tabriz region (located in Azerbaijan tectonic seismic region) is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-\noindent
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about E - W \citep{Berberian2001}.
+The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall  NW - SE  structure with step-overs.
+The regions of overlap are characterized by shorter south-dipping thrust faults, striking roughly E - W  \citep{Berberian2001}.
 \citet{Trifonov1978}  reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
@@
 \noindent
-The catalog of recorded earthquakes from 2005-2015, which is downloaded from IIEES, reported the earthquakes based on different magnitude scales \citep{IIEES}.
-We converted the $M_L$, $M_S$, and $mb$ magnitudes through conversion relationships which are defined in \citet{Zare2014}.
-There are also some of data recorded in $M_D$ (Duration magnitude).
-These data are reported by International Seismological Centre (ISC).
-\citet{Deniz2010} developed a set of empirical equations to convert earthquake magnitudes from $mb$, $M_D$, $M_L$ and $M_S$ scales to $M_W$ scales using orthogonal regression procedure.
-They used data of earthquake that occurred in Turkey from different data centers including ISC.
-In this study we use the conversion equation of \citet{Deniz2010} to convert the $M_D$ to $M_W$.
+The catalog of recorded earthquakes from 2005-15, downloaded from IIEES, reported earthquakes based on different magnitude scales \citep{IIEES}.
+The  $M_L$ ,  $M_S$, and  $mb$  magnitudes were converted through conversion relationships, as defined in  \citet{Zare2014}.
+Some data were also recorded in  $M_D$  (duration magnitude).
+These data are reported by the International Seismological Centre (ISC).
+\citet{Deniz2010}  developed a set of empirical equations to convert earthquake magnitudes from  $mb$,  $M_D$,  $M_L$, and  $M_S$  scales to  $M_W$  scale using the orthogonal regression procedure.
+They used data from different data centers, including the ISC, of earthquakes that occurred in Turkey.
+In this study, we use the conversion equation of  \citet{Deniz2010}  to convert  $M_D$  to  $M_W$.
 
@@
 Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citet{Gardner1974}.
+In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology  \citep{Gardner1974}.
 Fig.~\ref{fig:seismicity}  shows the epicenter of declustered instrumental  earthquakes.
@@
 \noindent
-Completeness of catalog is an important factor in studying the earthquake sequence.
+Catalog completeness is an important factor in studying an earthquake sequence.
+In this study, we used the Goodness-of-fit test (GFT) \citep{Wiemer2000} to determine the completeness magnitude.
+According to the GFT method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude.
+The steps for selecting the completeness magnitude for each catalog include: 1) calculating the a-  and  b-  value based on minimum magnitude; 2) generating  synthetic events based on the achieved value when the cumulative number of events obey the power law distribution; and 3) calculating goodness of fit for predicted and observed cumulative numbers for each magnitude bin  \citep{Wiemer2000}.
+We increased the minimum magnitude and repeated the process in order to calculate the goodness of fit for each magnitude.
+\citet{Wiemer2000} assumed a goodness of fit of 90\% as a threshold to select completeness of the catalog.
+However,  not all frequency-magnitude distributions reach the 90\% mark.
+Fig.~\ref{fig:completeness} shows the goodness-of-fit values for three tectonic seismic regions.
+For each tectonic seismic region, we selected the magnitude corresponding to the highest goodness of fit or the first magnitude with goodness of fit greater than 90\%.
+
+\begin{figure} [ht]
+\centering
+\includegraphics[scale=0.4]{figures/pdf/Figure03.pdf} 
+\caption{Goodness of fit value of GFT method for three tectonic seismic regions for seismicity of 2005-2015 (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
+\label{fig:completeness}
+\end{figure}
+
+In this study, we assume the minimum magnitudes for complete recording,  $M_C$ , is 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively.
+Fig.~\ref{fig:mag-time}  shows the magnitude time series of the declustered data for the three regions.
+Earthquakes with magnitude greater than the completeness magnitude are represented.
+
+\begin{figure} [ht]
+\centering
+\includegraphics[scale=0.5]{figures/pdf/Figure04.pdf} 
+\caption{Variation of moment magnitude of 2005-2015 earthquake for north Iran. (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
+\label{fig:mag-time}
+\end{figure}
+
+% Original text
+%\section{Tectonic seismic regions and seismicity parameters}
+%\noindent
+%Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
+Based on seismicity parameters, different tectonic seismic devisions have been defined for Iran.
+Some studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
+\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
+Considering \citet{Mirzaei1998} devision as a reference, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
+Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of the northern Iran.
+Fig.~\ref{fig:study_region} shows the study area and tectonic seismic regions.
+\\
+%
+%\begin{figure} [ht]
+%\centering
+%\includegraphics[scale=0.6]{figures/pdf/Figure01.pdf} 
+%\caption{a) Map of Iran and surrounding countries.
+The study area is situated in the gray box.
+b) The study area containing seismotectonic provinces after \citet{Mirzaei1998} is presented, and location of big cities indicated with circles.
+Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
+%\label{fig:study_region}
+%\end{figure}
+%
+%
+%
+%
+%\noindent
+%Alborz tectonic seismic region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
+The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
+%The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression \citep{Berberian1999}.
+%
+%\noindent
+% The Tabriz region (located in Azerbaijan tectonic seismic region) is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
+The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
+%\noindent
+%The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
+The regions of overlap are characterized by shorter south-dipping thrust faults striking about E - W \citep{Berberian2001}.
+\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
+%
+%\subsection{Magnitude Conversion}
+%\noindent
+%The catalog of recorded earthquakes from 2005-2015, which is downloaded from IIEES, reported the earthquakes based on different magnitude scales \citep{IIEES}.
+We converted the $M_L$, $M_S$, and $mb$ magnitudes through conversion relationships which are defined in \citet{Zare2014}.
+There are also some of data recorded in $M_D$ (Duration magnitude).
+These data are reported by International Seismological Centre (ISC).
+\citet{Deniz2010} developed a set of empirical equations to convert earthquake magnitudes from $mb$, $M_D$, $M_L$ and $M_S$ scales to $M_W$ scales using orthogonal regression procedure.
+They used data of earthquake that occurred in Turkey from different data centers including ISC.
+In this study we use the conversion equation of \citet{Deniz2010} to convert the $M_D$ to $M_W$.
+%
+%\subsection{Declustering}
+%\noindent
+%It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
+Therefore, in order to accomplish this, we declustered the earthquake catalog.
+In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citet{Gardner1974}.
+Fig.~\ref{fig:seismicity} shows the epicenter of declustered instrumental  earthquakes.
+%
+%\begin{figure} [ht]
+%\centering
+%\includegraphics[scale=0.6]{figures/pdf/Figure02.pdf} 
+%\caption{Declustered instrumental seismicity map (2005 - 2015) of Northern Iran.}
+%\label{fig:seismicity}
+%\end{figure}
+%
+%
+%\subsection{Catalog Completeness}
+%\noindent
+%Completeness of catalog is an important factor in studying the earthquake sequence.
 In this study we used the Maximum curvature method (MAXC) \citep{Wiemer2000} to determine the completeness magnitude.
@@
 For each tectonic seismic region, we pick the magnitude corresponding to the highest goodness of fit or the first magnitude with goodness of fit bigger than 90\%.
-
-\begin{figure} [ht]
-\centering
-\includegraphics[scale=0.4]{figures/pdf/Figure03.pdf} 
-\caption{Goodness of fit value of MAXC method for three tectonic seismic regions for seismicity of 2005-2015 (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
-\label{fig:completeness}
-\end{figure}
-
-\noindent
-In this study we assume the minimum magnitudes for complete recording, $M_C$, are 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively.
+%
+%\begin{figure} [ht]
+%\centering
+%\includegraphics[scale=0.4]{figures/pdf/Figure03.pdf} 
+%\caption{Goodness of fit value of MAXC method for three tectonic seismic regions for seismicity of 2005-2015 (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
+%\label{fig:completeness}
+%\end{figure} 
+%
+%
+%
+%
+%
+%\noindent
+%In this study we assume the minimum magnitudes for complete recording, $M_C$, are 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively.
 Fig.~\ref{fig:mag-time} shows the magnitude time series of the declustered data for the three regions.
 Earthquakes with magnitude bigger than completeness magnitude are represented.
-
-\begin{figure} [ht]
-\centering
-\includegraphics[scale=0.5]{figures/pdf/Figure04.pdf} 
-\caption{Variation of moment magnitude of 2005-2015 earthquake for north Iran. (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
-\label{fig:mag-time}
-\end{figure}
+%
+%\begin{figure} [ht]
+%\centering
+%\includegraphics[scale=0.5]{figures/pdf/Figure04.pdf} 
+%\caption{Variation of moment magnitude of 2005-2015 earthquake for north Iran. (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
+%\label{fig:mag-time}
+%\end{figure}

### 2016-07-30 abstract.tex
Adding the synthetic data of Telesca 2014 (POne) paper. And general review.

@@
 $b-value$) significantly decrease before large earthquakes.
-Combining the results of this study with two similar previous studies improves the linear correlation coefficient factor between $k-M$ and $b-value$, and empowers the idea of a universal relationship between $b-value$ and $k-M$ slope.
+Combining the results of this study with three similar previous studies improves the linear correlation coefficient factor between $k-M$ and $b-value$, and empowers the idea of a universal relationship between $b-value$ and $k-M$ slope.
 The behaviors of the VG's properties are similar to previous studies and could be considered an alternative method for analyzing earthquake sequences.

### 2016-07-30 acknowledgements.tex
Adding the synthetic data of Telesca 2014 (POne) paper. And general review.

\section{Acknowledgements}
\noindent
We greatly appreciate the International Institute of Earthquake Engineering and Seismology (IIEES) in Tehran for maintaining and providing access to the seismic catalog. This research was possible thanks to support by the Center for Earthquake Research and Information (CERI) at the University of Memphis. CERI is designated as a Center of Excellence by the Tennessee Board of Regents and is funded in part by the State of Tennessee under State Sunsent Laws (SB 1510 and HB 1608, 2015{2016).

### 2016-07-30 introduction.tex
Adding the synthetic data of Telesca 2014 (POne) paper. And general review.

@@
 \noindent
+This article presents the application of VG method on seismicity of northern Iran using the recorded earthquake during the last 10 years (2005-15).
 \citet{Lacasa2008} introduced a simple and fast computational method, known as visibility algorithm, to convert time series into graphs.
@@
 According to their study, a close relationship exists between the Gutenberg-Richter $b-value$ and the $k-M$ slope of the visibility graph.
-The high linear correlation coefficient value (close to 1) of $b-value$ and $k-M$  slope suggests the universal character of the relationship between these parameters \citep{Telesca2014} .
+The high linear correlation coefficient value (close to 1) of $b-value$ and $k-M$  slope suggests the universal character of the relationship between these parameters \citep{Telesca2014}.
+Using the synthetic seismicity generated by a simple stick-slip system with asperities, \citet{Telesca2014-pone} investigated the relationship between the $b-value$ of the Gutenberg-Richter law and the slope of the $k-M$ plot as obtained by the VG method.
+They build up a frictional system as a proxy of geological faults under tectonic stress and defined different asperities by means of modifying the sandpaper grade.
+They collected data after the first run ($R_1$) and the fifth run ($R_5$) mimicking the younger and mature faults, respectively.
+They calculated the magnitude as a normalized displacement in range of $1-10$.
+According to their study the $b-value$ and the $k-M$ slope are linearly correlated to each other with a high correlation coefficient.\\
 \noindent
+VG method also is applied through considering the timespan between earthquakes.
 \citet{Telesca2016}   defined    $<T_C>$  as the parameter window mean interval connectivity time ,  as an indication of the mean linkage time between earthquakes, in studying the 2003-12 earthquake sequence in the Kachchh region of western India.
@@
 In this study, we use visibility graph analysis to investigate the earthquake sequence of northern Iran.
-We divided northern Iran into three tectonic seismic regions, namely Azerbaijan, Alborz, and Kopeh Dagh.
+We divided northern Iran into three tectonic seismic regions, namely Azerbaijan (Az), Alborz Mountain Range (Al), and Kopeh Dagh (Ko).
 Recently, northern Iran has been studied in detail from different seismological points of view.
@@
 The frequency of shocks varied widely, from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years (3.25 event/year) for the Kopeh-Dagh region \citep{Nemati2015}.
-Northern Iran has an extensive seismic history.
-Having a considerable number of earthquakes and being in a unique tectonic seismic region, northern Iran is a good platform from which to analyze the visibility graph method's capabilities for studying the magnitude time series.
-In this study, we present the relationship between  $k-M$  slope and $b-value$  in these three different tectonic seismic regions.
+Using the smoothed seismicity method, \citet{Khoshnevis2016} studied the seismic hazard of the three northern tectonic seismic regions.
+Having a considerable number of recorded earthquakes, extensive seismic history, and being in a unique tectonic seismic region, northern Iran is a good platform from which to analyze the visibility graph method's capabilities for studying the magnitude time series.
+Significant aspect of our work include the compassion of earthquake catalog, conversion of the earthquake magnitude and computation of the completeness magnitude for each tectonic seismic zones.
+We present the relationship between  $k-M$  slope and $b-value$  in these three tectonic seismic regions.
+We analyze the sensitivity of the catalogs to the number of events and the threshold magnitude.
 We also investigate the variation of  $<T_C>$  value through time.

### 2016-07-30 main.tex
change the reference style to numerical.
fix some problem.
Adding the synthetic data of Telesca 2014 (POne) paper. And general review.

@@
 
-\documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
+%\documentclass[authoryear,preprint,review,12pt]{elsarticle}
+\documentclass[a4paper,review]{elsarticle}
 % Packages
@@
 % Journal Name
-\journal{Physica A}
+\journal{TBD}
 
@@
 \author[label1]{Naeem Khoshnevis\corref{cor1}}
-%\author[label1,label2]{Shima AzizzadehRoodpish}
+\author[label1,label2]{Shima AzizzadehRoodpish}
+\author[label1,label2]{Ricardo Taborda}
+\author[label3]{Luciano Telesca}
 \cortext[cor1]{Corresponding author. Tel: \\
@@
 % Affliations
-%\address[label1]{Center for Earthquake Research and Information}
-%\address[label2]{Department of Civil Engineering}
+\address[label1]{Center for Earthquake Research and Information, University of Memphis, 3890 Central Ave., Memphis TN 38152, USA}
+\address[label2]{Department of Civil Engineering, University of Memphis, 3890 Central Ave., Memphis TN 38152, USA}
+\address[label3]{Institute of Methodologies for Environmental Analysis, National Research Council, Tito, Italy}
 
@@
 \begin{keyword}
-Visibility Graph \sep Earthquake sequence \sep Magnitude \sep North Iran \sep b-value
+Visibility Graph \sep Earthquake Sequence \sep Magnitude \sep North Iran \sep b-value
 
@@
 \bibliographystyle{elsarticle-num-names}
+
 \bibliography{VG}

### 2016-07-30 results.tex
Adding the synthetic data of Telesca 2014 (POne) paper. And general review.

@@
 \centering
-\caption{Seismic parameters and $k-M$ slope values for north Iran tectonic seismic zones.}
+\caption{Declustered number of earthquakes, seismic parameters and $k-M$ slope values for north Iran tectonic seismic zones.}
 \begin{tabular}{ccccc}
@@
 Fig.~\ref{fig:k_m_plot_m}  shows the  $k-M$  relationship for the study regions.
+We categorized magnitudes in small magnitude bins ($\Delta M=0.1$).
+It is clear from the Fig.~\ref{fig:mag-time} that the specific magnitude bin can result in different connectivity degrees regarding the occurring time of the earthquake event.
 In general, with increasing magnitude, the connectivity degree increases, which increases the slope of the  $k-M$  relationship.
@@
 \centering
-\includegraphics[scale=0.35]{figures/pdf/Figure05.pdf} 
-\caption{ $k-M$ relationship for north Iran seismicity. a) Azerbaijan b) Alborz c)Kopeh Dagh}
+\includegraphics[scale=0.35]{figures/pdf/Figure06.pdf} 
+\caption{ $k-M$ relationship for north Iran tectonic seismic regions.
+The blue circles indicate the connectivity degrees.
+The red line is the linear regression line fits the data.
+The numbers on the lines is the slope of the lines.}
 \label{fig:k_m_plot_m}
@@
 The maximum size is the size of the entire catalog.
-For each randomly picked magnitude time series,  we estimated $Mc$,  and the  $k-M$  and $b-value$ were calculated.
+For each randomly picked magnitude time series,  we estimate $Mc$; then the $k-M$  and $b-value$ are calculated.
 Fig.~\ref{fig:random} shows the relationship between  $k-M$  slope and  $b-value$  of the randomly selected data and the statistical parameters for variables.
@@
 \centering
-\includegraphics[scale=0.4]{figures/pdf/Figure06.pdf} 
+\includegraphics[scale=0.5]{figures/pdf/Figure07.pdf} 
 \caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence.
@@
 The coefficient of variation of parameters is shown in Fig.~\ref{fig:random}.
-The  $k-M$  slope shows the higher coefficient of variation.
-The  $k-M$  slope is more dependent on the window size and threshold magnitude than  on the a-  and  b-values , which suggests that  the $k-M$  slope can better represent the dynamic characteristics of the magnitude-time series.
+The  $k-M$  slope shows the higher coefficient of variation which indicates the fact that the  $k-M$  slope is more dependent on the window size and threshold magnitude than on the a-  and  b-values , which suggests that  the $k-M$  slope can better represent the dynamic characteristics of the magnitude-time series.
  \noindent
- Fig.~\ref{fig:regression} shows the relationship between the  $k-M$  slope and $b-value$ for the three tectonic seismic regions in northern Iran and two other studies of Mexican zones  \citep{Telesca2013}  and Pannonia zones  \citep{Telesca2014}.
-Adding the results of the current study into the results of two previous similar studies improves the regression factor (with an increase from R=0.95 to R=0.955), and empowers the concept of the universal character of the relationship between the  $b-value$  and the  $k-M$  slope, as  \citet{Telesca2014} concluded.
+ Fig.~\ref{fig:regression} shows the relationship between the  $k-M$  slope and $b-value$ for the three tectonic seismic regions in northern Iran and three other studies of Mexican zones  \citep{Telesca2013}, Pannonia zones  \citep{Telesca2014}, and synthetic data \citet{Telesca2014-pone}.
+Adding the results of the current study into the results of three previous similar studies improves the regression factor, and empowers the concept of the universal character of the relationship between the  $b-value$  and the  $k-M$  slope, as  \citet{Telesca2014} concluded.
 
@@
 \centering
-\includegraphics[scale=0.3]{figures/pdf/Figure07.pdf} 
-\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.
-The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and north Iran)}
+\includegraphics[scale=0.6]{figures/pdf/Figure08.pdf} 
+\caption{ Relationship between $k-M$ slope and $b-value$ of three Iranian tectonic seismic zones (this study) and three other studies of Mexican zones \citep{Telesca2013}, Pannonia zones \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}.
+The lines represent the linear regression fit of data.
+The correlation coefficients (R) are represented for different combination of data.
+}
 \label{fig:regression}
@@
 \citet{Telesca2016}  observed the decrease in  $<T_C>$  before the large earthquake of the western India earthquake sequence.
-Fig.\ref{fig:tc}  shows the time variation of  $<T_C>$   in the study area, and the decrease in  $<T_C>$   before a large earthquake is clearly visible.
+Fig.\ref{fig:tc}  shows the time variation of  $<T_C>$   in the study area.
+The reduction of  $<T_C>$   before large earthquakes is clearly visible.
 \citet{Telesca2016}  demonstrated that the decrement of  $<T_C>$   before a large earthquake is independent of window size and threshold magnitude.
-Fig.\ref{fig:tc}  shows the decrement in the value of  $<T_C>$  ,  $k-M$ , and  $b-value$  before large earthquakes.
+Decreasing the value of  $<T_C>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions (see Fig.\ref{fig:tc} for reference.)
 
@@
 \centering
-\includegraphics[scale=0.34]{figures/pdf/Figure08.pdf} 
-\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_C >$ (Right) with time.
+\includegraphics[scale=0.4]{figures/pdf/Figure09.pdf} 
+\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_C >$ (Right) as a function of time for three tectonic seismic regions in north Iran.
 Black arrows show the occurrence of the major earthquakes.
-Numbers on arrows indicate the moment magnitude of the earthquake.}
+Numbers on arrows indicate the moment magnitude of the earthquake (see Fig.~\ref{fig:mag-time} for reference).
+Decreasing the value of  $<T_C>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions.}
 \label{fig:tc}

### 2016-07-30 seismicity.tex
Adding the synthetic data of Telesca 2014 (POne) paper. And general review.

@@
 \noindent
-Iran is situated over the Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-Based on seismicity parameters, different tectonic seismic divisions have been defined for Iran.
-Some studies have defined more detailed divisions \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province  \citep{Stocklin1968,Takin1972,Berberian1976}.
+The Iranian plateau is located on the Himalayan-Alpine seismic belt.
+It has a long history of large magnitude ($M>7$) earthquakes that are well documented dating back to the eighth century.
+Based on seismicity parameters and the geologic provinces of the plateau, Iranian earthquakes have been categorized into various seismic zones, ranging from the definition of four to nine major seismic zones in the more traditional studies \citep[e.g.,][]{Stocklin1968,Takin1972,Berberian1976}, and up to twenty to twenty-three tectonic seismic regions in the most elaborate ones \citep[e.g.,][]{Nowroozi1976,Tavakoli1999}.
 \citet{Mirzaei1998},  dividing Iran into five tectonic regions, called Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Considering  \citet{Mirzaei1998}  a division as a reference,  \citet{Karimiparidari2013}  divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and the Alborz Mountain Range (hereinafter, Alborz).
+Considering the devision of  \citet{Mirzaei1998} as a reference,  \citet{Karimiparidari2013}  divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and the Alborz Mountain Range (hereinafter, Alborz).
 Azerbaijan, Alborz, and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
@@
 \centering
-\includegraphics[scale=0.6]{figures/pdf/Figure01.pdf} 
-\caption{a) Map of Iran and surrounding countries.
-The study area is situated in the gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998} is presented, and location of big cities indicated with circles.
+\includegraphics[scale=1]{figures/pdf/Figure01.pdf} 
+\caption{Region of interest and tectonic seismic regions.
+At the top, the map of Iran and surrounding countries.
+The study area is located in the gray box.
+At the bottom, the study area containing seismotectonic provinces after \citet{Mirzaei1998} is presented.
 Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
@@
 The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement  \citep{Berberian1999}.
-
+\noindent
 The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall  NW - SE  structure with step-overs.
@@
 \citet{Trifonov1978}  reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
+Main fault lines and fault systems in the interest region is represented in Fig.~\ref{fig:faults}.
+
+\begin{figure} [ht]
+\centering
+\includegraphics[scale=1]{figures/pdf/Figure02.pdf} 
+\caption{Main fault line and fault system in the region of interest. The borderlines of the seismic zones shown in Fig.~\ref{fig:study_region} are shown in background in gray.}
+\label{fig:faults}
+\end{figure}
 
@@
 It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology  \citep{Gardner1974}.
+Therefore, in order to accomplish this, we decluster the earthquake catalog.
+In compiling the catalog of events, foreshocks and aftershocks are removed using a declustering methodology  presented by \citet{Gardner1974}.
 Fig.~\ref{fig:seismicity}  shows the epicenter of declustered instrumental  earthquakes.
@@
 \centering
-\includegraphics[scale=0.6]{figures/pdf/Figure02.pdf} 
-\caption{Declustered instrumental seismicity map (2005 - 2015) of Northern Iran.}
+\includegraphics[scale=1]{figures/pdf/Figure03.pdf} 
+\caption{Declustered instrumental seismicity map (2005 - 2015) of Northern Iran.
+Different colors indicate the seismicity of different regions.
+Size of symbols are proportional to the magnitude of the events.}
 \label{fig:seismicity}
@@
 Catalog completeness is an important factor in studying an earthquake sequence.
-In this study, we used the Goodness-of-fit test (GFT) \citep{Wiemer2000} to determine the completeness magnitude.
+This characteristic measured as the minimum magnitude of complete recording for earthquake catalog .
+The completeness magnitude $(M_c)$ is often determined using simple numerical analysis.
+Two common approaches are maximum curvature method and (MAXC) and goodness-of-fit test (GFT)(see \citet{Wiemer2000}).
+We use the Goodness-of-fit test and compute $M_c$ for each region's catalog.
 According to the GFT method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude.
 The steps for selecting the completeness magnitude for each catalog include: 1) calculating the a-  and  b-  value based on minimum magnitude; 2) generating  synthetic events based on the achieved value when the cumulative number of events obey the power law distribution; and 3) calculating goodness of fit for predicted and observed cumulative numbers for each magnitude bin  \citep{Wiemer2000}.
-We increased the minimum magnitude and repeated the process in order to calculate the goodness of fit for each magnitude.
-\citet{Wiemer2000} assumed a goodness of fit of 90\% as a threshold to select completeness of the catalog.
+We increase the minimum magnitude and repeate the process in order to calculate the goodness of fit for each magnitude.
+\citet{Wiemer2000} assumed a goodness of fit of 90\% as a threshold to select the completeness of the catalog.
 However,  not all frequency-magnitude distributions reach the 90\% mark.
 Fig.~\ref{fig:completeness} shows the goodness-of-fit values for three tectonic seismic regions.
-For each tectonic seismic region, we selected the magnitude corresponding to the highest goodness of fit or the first magnitude with goodness of fit greater than 90\%.
+For each tectonic seismic region, we select the magnitude corresponding to the highest goodness of fit or the first magnitude with the goodness of fit greater than 90\%.
 
@@
 \centering
-\includegraphics[scale=0.4]{figures/pdf/Figure03.pdf} 
-\caption{Goodness of fit value of GFT method for three tectonic seismic regions for seismicity of 2005-2015 (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
+\includegraphics[scale=0.4]{figures/pdf/Figure04.pdf} 
+\caption{ Selection of completeness magnitude $M_c$ of the three tectonic seismic regions in northern Iran in 2005-15 period.
+The symbols indicate the computed GFT values as function of the earthquake magnitude.
+The horizontal dashed line indicates the desired threshold for the goodness of fit value at 90 percent.}
 \label{fig:completeness}
 \end{figure} 
-
-In this study, we assume the minimum magnitudes for complete recording,  $M_C$ , is 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively.
+\noindent
+Based on the results represented in Fig.~\ref{fig:completeness}, we select the minimum magnitudes for complete recording,  $M_c$ , is 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively.
 Fig.~\ref{fig:mag-time}  shows the magnitude time series of the declustered data for the three regions.
@@
 \centering
-\includegraphics[scale=0.5]{figures/pdf/Figure04.pdf} 
-\caption{Variation of moment magnitude of 2005-2015 earthquake for north Iran. (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
+\includegraphics[scale=0.8]{figures/pdf/Figure05.pdf} 
+\caption{Variation of moment magnitude ($M_w$) of 2005-2015 earthquake for north Iran as a function of time.
+The figure only represents the reclustered events greater than minimum magnitude.
+The 2012 $M_w 6.4$ East Azerbaijan, 2010 $M_w 5.8$ Damghan, and 2012 $M_w 5.4$ Neyshabur earthquakes are clearly visible as maximum values in Azerbaijan (Az),  Alborz (Az), and Kopeh Dagh (Ko) magnitude-time series.}
 \label{fig:mag-time}

### 2016-07-30 figures/gmtcode/Instrumental/Instrumental.sh

@@ -6,49 +6,68 @@
 
  
 
-LONMIN=43.5
-LONMAX=61.5
-LATMIN=34
-LATMAX=40
-REGION=$LONMIN/$LONMAX/$LATMIN/$LATMAX
-PROJ=-JM18
-MOREPS=-K
-CONTINUEPS="-K -O"
-ENDPS=-O
-DATASET=11
-DATAGRID=-I30c
-LINE=-W1
+rm gmt.conf gmt.history
 
-grdraster $DATASET -G$world.grd $DATAGRID -R$REGION -V
-CPTFILE=/usr/local/GMT4.5.7/share/cpt/GMT_globe.cpt
-TOPOILLUM=220
+# Set GMT constants
+# ------------------------------------------------------------------------------
 
-#grdgradient $world.grd -A$TOPOILLUM -GETOPO5.intns -N2 -V   in this case Dataset = 9
-grdgradient $world.grd -A$TOPOILLUM -GETOPO30s.intns -N2 -V
+gmt gmtset FONT                     8
 
-grdimage $world.grd -IETOPO5.intns -C$CPTFILE -R$REGION $PROJ -N1/4 -K -B4f2/4f2 -Y8 -X8  >  $0.ps
-
-pscoast -R$REGION $PROJ -N1/4 -B4f2/4f2 -K -O -W2 >> $0.ps
-
-
-awk '($7>2.8){print $9,$10,($7^2.5)/140}' Alborz_2005_all_mag.txt|psxy -Sc -G196/19/19 -W2  -R$REGION $PROJ -K -O >> $0.ps
-awk '($7>3.4){print $9,$10,($7^2.5)/140}' Azerbaijan_2005_all_mag.txt|psxy -Sc -G102/178/255 -W2  -R$REGION $PROJ -K -O >> $0.ps
-awk '($7>2.5){print $9,$10,($7^2.5)/140}' KopehDagh_2005_all_mag.txt|psxy -Sc -G160/160/160 -W2  -R$REGION $PROJ -K -O >> $0.ps
-
-cat << EOF |awk '{print $1,$2,($3^2.5)/140}' |psxy -Sc -G196/19/19 -W2  -R$REGION $PROJ -K -O >> $0.ps
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
[…]

### 2016-07-30 figures/gmtcode/codes/Figure_1_a.sh

@@ -1,0 +1,69 @@
+clear
+
+rm gmt.conf
+rm gmt.hist
+
+
+# Set GMT constants
+# ------------------------------------------------------------------------------
+
+gmt gmtset FONT                     8
+
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
+
+
+
+# Set script constants
+# ------------------------------------------------------------------------------
+
+OUTNAME=figure1_a
+PSNAME=${OUTNAME}.ps
+
+
+ 
+gmt grdgradient etopo1_bedrock.grd -A300 -Gmytopo.grad -Nt
+gmt psbasemap -R25/80/20/45 -JM5i  -B10f5/10f5 -Y8i -V -P -K > ${PSNAME}
+gmt grdimage etopo1_bedrock.grd -R -J -Bwnes  -Cetopo1.cpt  -V -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Dh -W0.25p -N1/0.25p -A500 -V -P -O -K -Lf73/23/23/1000 >> ${PSNAME}
+gmt pscoast -R -J -B -Slightblue -A500 -Dh -W0.25p -V -P -O -K >> ${PSNAME}
+
+
+
+cat << EOF13 |gmt psxy  -Sc0.05  -W1 -JM5i -R25/80/20/45 -K -O  >> ${PSNAME}
+
+43.5	34
+43.5	40
+61.5    40
+61.5    34
+44.228  39.4
+48.971  31.136
+60.173  36.429
+61.435  25.075
+
+EOF13
+
+
+
+# Creating PDF
+# ------------------------------------------------------------------------------
+
+gmt ps2raster ${PSNAME} -Tf -Au0.25c
+rm ${PSNAME}
+rm mytopo.grad
+
+
+# Opening PDF
[…]

### 2016-07-30 figures/gmtcode/codes/Figure_1_b.sh

@@ -1,0 +1,140 @@
+clear
+
+rm gmt.conf gmt.history
+
+# Set GMT constants
+# ------------------------------------------------------------------------------
+
+gmt gmtset FONT                     8
+
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
+
+
+
+# Set script constants
+# ------------------------------------------------------------------------------
+
+OUTNAME=figure1_b
+PSNAME=${OUTNAME}.ps
+
+PROJ=-JM5i
+ 
+gmt grdgradient etopo1_bedrock.grd -A300 -Gmytopo.grad -Nt
+gmt psbasemap -R43.5/61.5/34/40 -JM5i  -B4f2/4f2 -Y8i -V -P -K > ${PSNAME}
+gmt grdimage etopo1_bedrock.grd -R -J -Bwnes  -CGMT_globe.cpt  -V -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Dh -W0.25p -N1/0.25p -A500 -V -P -O -K -Lf73/23/23/1000 >> ${PSNAME}
+gmt pscoast -R -J -B -Slightblue -A500 -Dh -W0.25p -V -P -O -K >> ${PSNAME}
+
+
+cat << EOF13 |gmt psxy   -W1 -R$REGION $PROJ -K -O  >> ${PSNAME}
+47.344753	40.72171
+49.599926	39.52165
+49.26277	38.11627
+51.85228	36.86008
+54.88121	38.01132
+53.19502	39.433327
+53.29621	39.878605
+55.519176	39.318867
+61.2336	36.95889
+61.145393	34.578835
+59.67538	35.37419
+58.63931	35.737476
+56.517025	36.478027
+54.994373	35.992893
+55.327847	35.49136
+53.06872	34.645313
[…]

### 2016-07-30 figures/gmtcode/codes/seismicity.sh

@@ -1,0 +1,99 @@
+
+clear
+
+rm gmt.conf gmt.history
+
+# Set GMT constants
+# ------------------------------------------------------------------------------
+
+gmt gmtset FONT                     8
+
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
+
+# Set script constants
+# ------------------------------------------------------------------------------
+
+OUTNAME=seismicity
+PSNAME=${OUTNAME}.ps
+
+# Top Map - Notable
+# ------------------------------------------------------------------------------
+
+gmt grdgradient mytopo.grd -A300 -Gmytopo.grad -Nt
+#gmt grdhisteq mytopo.grad -Gmytopo.hist -N
+#gmt grdmath mytopo.hist 3 DIV = mytopo.norm
+
+# Top Map - Historical
+# ------------------------------------------------------------------------------
+
+gmt psbasemap -R43.5/61.5/34/40 -JM5i -BWnes -Ba2f1 -Y8i -V -P -K > ${PSNAME}
+
+# gmt psbasemap -R -J -BWnes -Ba2f1 -Y-3.5i -V -P -O -K >> ${PSNAME}
+gmt grdimage mytopo.grd -R -J -Bwnes -Imytopo.norm -Cgray -t50 -V -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Dh -W0.25p -N1/0.25p -A500 -V -P -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Slightblue -A500 -Dh -W0.25p -V -P -O -K >> ${PSNAME}
+
+gmt makecpt -Chot -T0/1800/100 -Z -V > historical.cpt
[…]

### 2016-07-30 figures/gmtcode/codes/selectedfaults.sh

@@ -1,0 +1,3238 @@
+
+clear
+
+rm gmt.conf gmt.history
+
+# Set GMT constants
+# ------------------------------------------------------------------------------
+
+gmt gmtset FONT                     8
+
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
+
+# Set script constants
+# ------------------------------------------------------------------------------
+
+OUTNAME=selectedfaults
+PSNAME=${OUTNAME}.ps
+
+# Top Map - Notable
+# ------------------------------------------------------------------------------
+
+gmt grdgradient mytopo.grd -A300 -Gmytopo.grad -Nt
+gmt grdhisteq mytopo.grad -Gmytopo.hist -N
+gmt grdmath mytopo.hist 3 DIV = mytopo.norm
+
+gmt psbasemap -R43.5/61.5/34/40 -JM5i -BWneS -Ba2f1 -Y8i -V -P -K > ${PSNAME}
+gmt grdimage mytopo.grd -R -J -Bwnes -Imytopo.norm -Cgray -t50 -V -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Dh -W0.25p -N1/0.25p -A500 -V -P -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Slightblue -A500 -Dh -W0.25p -V -P -O -K >> ${PSNAME}
+
+#Garmsar Fault
+gmt psxy  -W0.35p,black  -R -J -B -V -O -K >> ${PSNAME} << END
+51.863075	35.202847
+51.893387	35.209576
+51.91615	35.213024
+51.942707	35.21652
+51.96547	35.219967
+52.01144	35.198116
+52.030754	35.179165
+52.053814	35.163452
+52.08808	35.16064
+52.129898	35.161106
[…]

### 2016-07-30 figures/gmtcode/figure1/Figure_1_a.sh

@@ -1,0 +1,67 @@
+clear
+
+# Set GMT constants
+# ------------------------------------------------------------------------------
+
+gmt gmtset FONT                     8
+
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
+
+
+
+# Set script constants
+# ------------------------------------------------------------------------------
+
+OUTNAME=figure1_a
+PSNAME=${OUTNAME}.ps
+
+
+ 
+gmt grdgradient etopo1_bedrock.grd -A300 -Gmytopo.grad -Nt
+gmt psbasemap -R32/72/24/44 -JM5i  -B8f4/8f4 -Y8i -V -P -K > ${PSNAME}
+gmt grdimage etopo1_bedrock.grd -R -J -Bwnes  -Cetopo1.cpt  -V -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Dh -W0.25p -N1/0.25p -A500 -V -P -O -K -Lf73/23/23/1000 >> ${PSNAME}
+gmt pscoast -R -J -B -Slightblue -A500 -Dh -W0.25p -V -P -O -K >> ${PSNAME}
+
+
+
+cat << EOF13 |gmt psxy  -Sc0.05  -W1 -JM5i -R32/72/24/44 -K -O  >> ${PSNAME}
+
+43.5	34
+43.5	40
+61.5    40
+61.5    34
+44.228  39.4
+48.971  31.136
+60.173  36.429
+61.435  25.075
+
+EOF13
+
+
+
+# Creating PDF
+# ------------------------------------------------------------------------------
+
+gmt ps2raster ${PSNAME} -Tf -Au0.25c
+rm ${PSNAME}
+rm data.txt
+rm mytopo.grad
+rm mytopo.hist
+rm mytopo.norm
+
+# Opening PDF
[…]

### 2016-07-30 figures/gmtcode/figure1/Figure_1_b.sh

@@ -1,0 +1,140 @@
+clear
+
+rm gmt.conf gmt.history
+
+# Set GMT constants
+# ------------------------------------------------------------------------------
+
+gmt gmtset FONT                     8
+
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
+
+
+
+# Set script constants
+# ------------------------------------------------------------------------------
+
+OUTNAME=figure1_b
+PSNAME=${OUTNAME}.ps
+
+PROJ=-JM5i
+ 
+gmt grdgradient etopo1_bedrock.grd -A300 -Gmytopo.grad -Nt
+gmt psbasemap -R43.5/61.5/34/40 -JM5i  -B2f1/2f1 -Y8i -V -P -K > ${PSNAME}
+gmt grdimage etopo1_bedrock.grd -R -J -Bwnes  -Cetopo1.cpt  -V -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Dh -W0.25p -N1/0.25p -A500 -V -P -O -K -Lf48/23/23/500 >> ${PSNAME}
+gmt pscoast -R -J -B -Slightblue -A500 -Dh -W0.25p -V -P -O -K >> ${PSNAME}
+
+
+cat << EOF13 |gmt psxy   -W1 -R$REGION $PROJ -K -O  >> ${PSNAME}
+47.344753	40.72171
+49.599926	39.52165
+49.26277	38.11627
+51.85228	36.86008
+54.88121	38.01132
+53.19502	39.433327
+53.29621	39.878605
+55.519176	39.318867
+61.2336	36.95889
+61.145393	34.578835
+59.67538	35.37419
+58.63931	35.737476
+56.517025	36.478027
+54.994373	35.992893
+55.327847	35.49136
+53.06872	34.645313
[…]

### 2016-07-30 figures/gmtcode/figure2/selectedfaults.sh

@@ -1,0 +1,3238 @@
+
+clear
+
+rm gmt.conf gmt.history
+
+# Set GMT constants
+# ------------------------------------------------------------------------------
+
+gmt gmtset FONT                     8
+
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
+
+# Set script constants
+# ------------------------------------------------------------------------------
+
+OUTNAME=selectedfaults
+PSNAME=${OUTNAME}.ps
+
+# Top Map - Notable
+# ------------------------------------------------------------------------------
+
+gmt grdgradient mytopo.grd -A300 -Gmytopo.grad -Nt
+#gmt grdhisteq mytopo.grad -Gmytopo.hist -N
+#gmt grdmath mytopo.hist 3 DIV = mytopo.norm
+
+gmt psbasemap -R43.5/61.5/34/40 -JM5i -BWneS -Ba2f1 -Y8i -V -P -K > ${PSNAME}
+gmt grdimage etopo1_bedrock.grd -R -J -Bwnes -Cetopo1.cpt  -V -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Dh -W0.25p -N1/0.25p -A500 -V -P -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Slightblue -A500 -Dh -W0.25p -V -P -O -K >> ${PSNAME}
+
+#Garmsar Fault
+gmt psxy  -W0.35p,black  -R -J -B -V -O -K >> ${PSNAME} << END
+51.863075	35.202847
+51.893387	35.209576d
+51.91615	35.213024
+51.942707	35.21652
+51.96547	35.219967
+52.01144	35.198116
+52.030754	35.179165
+52.053814	35.163452
+52.08808	35.16064
+52.129898	35.161106
[…]

### 2016-07-30 figures/gmtcode/figure3/Instrumental.sh

@@ -1,0 +1,71 @@
+#!/bin/bash
+
+
+
+ 
+
+rm gmt.conf gmt.history
+
+# Set GMT constants
+# ------------------------------------------------------------------------------
+
+gmt gmtset FONT                     8
+
+gmt gmtset MAP_DEFAULT_PEN          0.75p
+gmt gmtset MAP_FRAME_PEN            0.75p
+gmt gmtset MAP_FRAME_WIDTH          3p
+gmt gmtset MAP_TICK_PEN             0.75p
+gmt gmtset MAP_TICK_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_PEN_SECONDARY   0.75p
+gmt gmtset MAP_GRID_PEN_PRIMARY     0.75p
+gmt gmtset MAP_TICK_LENGTH_PRIMARY  6p/3p
+gmt gmtset MAP_LABEL_OFFSET         8p
+gmt gmtset MAP_ANNOT_OFFSET_PRIMARY 5p
+
+
+
+# Set script constants
+# ------------------------------------------------------------------------------
+
+OUTNAME=figure2
+PSNAME=${OUTNAME}.ps
+
+PROJ=-JM5i
+
+gmt grdgradient etopo1_bedrock.grd -A300 -Gmytopo.grad -Nt
+gmt grdhisteq mytopo.grad -Gmytopo.hist -N
+gmt grdmath mytopo.hist 3 DIV = mytopo.norm
+
+gmt psbasemap -R43.5/61.5/34/40 -JM5i  -B2f1/2f1 -Y8i -V -P -K > ${PSNAME}
+gmt grdimage etopo1_bedrock.grd -R -J -Bwnes  -Cetopo1.cpt  -V -O -K >> ${PSNAME}
+gmt pscoast -R -J -B -Dh -W0.25p -N1/0.25p -A500 -V -P -O -K -Lf73/23/23/1000 >> ${PSNAME}
+gmt pscoast -R -J -B -Slightblue -A500 -Dh -W0.25p -V -P -O -K >> ${PSNAME}
+
+
+awk '($7>2.8){print $9,$10,($7^2.5)/140}' Alborz_2005_all_mag.txt|gmt psxy -Sc -G196/19/19 -W0.5  -R$REGION $PROJ -K -O >> ${PSNAME}
[…]

### 2016-08-09 abstract.tex
commit before adding methodology.

--- 2016-07-11 abstract.tex
@@
 $b-value$) significantly decrease before large earthquakes.
-Combining the results of this study with two similar previous studies improves the linear correlation coefficient factor between $k-M$ and $b-value$, and empowers the idea of a universal relationship between $b-value$ and $k-M$ slope.
+Combining the results of this study with three similar previous studies improves the linear correlation coefficient factor between $k-M$ slope and $b-value$, and empowers the idea of a universal relationship between $b-value$ and $k-M$ slope.
 The behaviors of the VG's properties are similar to previous studies and could be considered an alternative method for analyzing earthquake sequences.

### 2016-08-09 acknowledgements.tex
commit before adding methodology.

@@
 This research was possible thanks to support by the Center for Earthquake Research and Information (CERI) at the University of Memphis.
-CERI is designated as a Center of Excellence by the Tennessee Board of Regents and is funded in part by the State of Tennessee under State Sunsent Laws (SB 1510 and HB 1608, 2015{2016).
+CERI is designated as a Center of Excellence by the Tennessee Board of Regents and is funded in part by the State of Tennessee under State Sunsent Laws (SB 1510 and HB 1608, 2015--2016).

### 2016-08-09 introduction.tex
commit before adding methodology.

@@
 Having a considerable number of recorded earthquakes, extensive seismic history, and being in a unique tectonic seismic region, northern Iran is a good platform from which to analyze the visibility graph method's capabilities for studying the magnitude time series.
-Significant aspect of our work include the compassion of earthquake catalog, conversion of the earthquake magnitude and computation of the completeness magnitude for each tectonic seismic zones.
+Significant aspect of our work includes the compassion of earthquake catalog, conversion of the earthquake magnitude and computation of the completeness magnitude for each tectonic seismic zone.
 We present the relationship between  $k-M$  slope and $b-value$  in these three tectonic seismic regions.

### 2016-08-09 results.tex
commit before adding methodology.

@@
 Alborz            & 794                               & 2.6   & 0.7717  & 9.0461      \\ \hline
-Kopek Dagh  & 282                               & 2.6   & 0.5799  & 6.5818     \\ \hline
+Kopeh Dagh  & 282                               & 2.6   & 0.5799  & 6.5818     \\ \hline
 \end{tabular}
@@
 Fig.~\ref{fig:random} shows the relationship between  $k-M$  slope and  $b-value$  of the randomly selected data and the statistical parameters for variables.
-Although changing the number of events and the threshold magnitude is a slight change, the results are fairly well clustered for each tectonic seismic region.
+Although changing the number of events and the threshold magnitude is slightly changing the results, however,  the results are fairly well clustered for each tectonic seismic region.
 
@@
 \caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence.
-The numbers on the mean and standard deviation plots are coefficient of variations in percent$(standard \ deviation / mean)$.}
+The numbers on the mean and standard deviation plots are coefficient of variations in percent $(standard \ deviation / mean)$.}
 \label{fig:random}
@@
  \noindent
- Fig.~\ref{fig:regression} shows the relationship between the  $k-M$  slope and $b-value$ for the three tectonic seismic regions in northern Iran and three other studies of Mexican zones  \citep{Telesca2013}, Pannonia zones  \citep{Telesca2014}, and synthetic data \citet{Telesca2014-pone}.
+ Fig.~\ref{fig:regression} shows the relationship between the  $k-M$  slope and $b-value$ for the three tectonic seismic regions in northern Iran and three other studies of Mexican zones  \citep{Telesca2013}, Pannonia zones  \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}.
 Adding the results of the current study into the results of three previous similar studies improves the regression factor, and empowers the concept of the universal character of the relationship between the  $b-value$  and the  $k-M$  slope, as  \citet{Telesca2014} concluded.
@@
 The lines represent the linear regression fit of data.
-The correlation coefficients (R) are represented for different combination of data.
-}
+The correlation coefficients (R) are represented for different combination of data.}
 \label{fig:regression}

### 2016-08-09 seismicity.tex
commit before adding methodology.

@@
 \citet{Mirzaei1998},  dividing Iran into five tectonic regions, called Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Considering the devision of  \citet{Mirzaei1998} as a reference,  \citet{Karimiparidari2013}  divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and the Alborz Mountain Range (hereinafter, Alborz).
+Considering the division of  \citet{Mirzaei1998} as a reference,  \citet{Karimiparidari2013}  divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and the Alborz Mountain Range (hereinafter, Alborz).
 Azerbaijan, Alborz, and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
@@
 \caption{Region of interest and tectonic seismic regions.
-At the top, the map of Iran and surrounding countries.
+At the top, the map of Iran and surrounding countries is presented.
 The study area is located in the gray box.
@@
 The catalog of recorded earthquakes from 2005-15, downloaded from IIEES, reported earthquakes based on different magnitude scales \citep{IIEES}.
-The  $M_L$ ,  $M_S$, and  $mb$  magnitudes were converted through conversion relationships, as defined in  \citet{Zare2014}.
+The  $M_L$,  $M_S$, and  $mb$  magnitudes were converted through conversion relationships, as defined in  \citet{Zare2014}.
 Some data were also recorded in  $M_D$  (duration magnitude).
@@
 \includegraphics[scale=1]{figures/pdf/Figure03.pdf} 
-\caption{Declustered instrumental seismicity map (2005 - 2015) of Northern Iran.
+\caption{Declustered instrumental seismicity map (2005 - 2015) of northern Iran.
 Different colors indicate the seismicity of different regions.
@@
 Catalog completeness is an important factor in studying an earthquake sequence.
-This characteristic measured as the minimum magnitude of complete recording for earthquake catalog .
+This characteristic measured as the minimum magnitude of complete recording for earthquake catalog.
 The completeness magnitude $(M_c)$ is often determined using simple numerical analysis.
@@
 The steps for selecting the completeness magnitude for each catalog include: 1) calculating the a-  and  b-  value based on minimum magnitude; 2) generating  synthetic events based on the achieved value when the cumulative number of events obey the power law distribution; and 3) calculating goodness of fit for predicted and observed cumulative numbers for each magnitude bin  \citep{Wiemer2000}.
-We increase the minimum magnitude and repeate the process in order to calculate the goodness of fit for each magnitude.
+We increase the minimum magnitude and repeat the process in order to calculate the goodness of fit for each magnitude.
 \citet{Wiemer2000} assumed a goodness of fit of 90\% as a threshold to select the completeness of the catalog.
@@
 \caption{Variation of moment magnitude ($M_w$) of 2005-2015 earthquake for north Iran as a function of time.
-The figure only represents the reclustered events greater than minimum magnitude.
+The figure only represents the declustered events greater than minimum magnitude.
 The 2012 $M_w 6.4$ East Azerbaijan, 2010 $M_w 5.8$ Damghan, and 2012 $M_w 5.4$ Neyshabur earthquakes are clearly visible as maximum values in Azerbaijan (Az),  Alborz (Az), and Kopeh Dagh (Ko) magnitude-time series.}

### 2016-08-11 introduction.tex
Ricardo's comments added.

@@
 This article presents the application of VG method on seismicity of northern Iran using the recorded earthquake during the last 10 years (2005-15).
+Recent studies show that this period (2005-15) has the most complete catalog especially for small earthquakes $(M < 3)$ \citep[e.g.][]{Khoshnevis2016}.
 \citet{Lacasa2008} introduced a simple and fast computational method, known as visibility algorithm, to convert time series into graphs.
 Basically, the visibility graph presents the connection between nodes in a network.
-For any time series, two characteristics are attributed to each event: occurrence time and value of the event.
-Two events are in connection or visible to each other if no other event interrupts their linear connection.
-In mathematical form, events $i$ and $j$ are visible to each other if the following equation is fulfilled:
-
-\begin{equation}
-\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} ,
-\end{equation}
-\noindent
-where $y$ is the value and $t$ is the time of the event, and $k$ is the index of any event occurring between events  $i$  and  $j$.
-The visibility graph generated from a time series holds the following conditions: 1) each event is visible to the first event at its right and left side (if there is any) (Connectivity); 2) the algorithm is developed without defining a direction for the links (Undirected); and 3) rescaling or translation of a time series does not change the resulting visibility graph (invariant under affine transformations of the series data) \citep{Lacasa2008}.
-This concept has applications in fields including geophysical studies.
+This concept has applications in many fields including geophysical studies\citep[e.g.,][]{Telesca2012_CSF,Long2013,Wang2012}.
 \\
@@
 VG method also is applied through considering the timespan between earthquakes.
-\citet{Telesca2016}   defined    $<T_C>$  as the parameter window mean interval connectivity time ,  as an indication of the mean linkage time between earthquakes, in studying the 2003-12 earthquake sequence in the Kachchh region of western India.
+\citet{Telesca2016}   defined    $<T_c>$  as the parameter window mean interval connectivity time ,  as an indication of the mean linkage time between earthquakes, in studying the 2003-12 earthquake sequence in the Kachchh region of western India.
 They found that  $<T_C>$  changes through time, indicating that the topological properties of the earthquake network are not stationary.
-In addition,  $<T_C>$  significantly decrees before the largest shock of the catalog.
+In addition,  $<T_c>$  significantly decrees before the largest shock of the catalog.
 Analyzing the Gutenberg-Richter values of  the magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series by using the features of networks.
@@
 We analyze the sensitivity of the catalogs to the number of events and the threshold magnitude.
-We also investigate the variation of  $<T_C>$  value through time.
+We also investigate the variation of  $<T_c>$  value through time.
 

### 2016-08-11 methodology.tex
Ricardo's comments added.

\section{Methodology}
\noindent
For any time series, two characteristics are attributed to each event: occurrence time and value of the event. Two events are in connection or visible to each other if no other event interrupts their linear connection. In mathematical form, events $i$ and $j$ are visible to each other if the following equation is fulfilled:

\begin{equation}
\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} ,
\end{equation}
\noindent
where $y$ is the value and $t$ is the time of the event, and $k$ is the index of any event occurring between events  $i$  and  $j$. The visibility graph generated from a time series holds the following conditions: 1) each event is visible to the first event at its right and left side (if there is any) (Connectivity); 2) the algorithm is developed without defining a direction for the links (Undirected); and 3) rescaling or translation of a time series does not change the resulting visibility graph (invariant under affine transformations of the series data) \citep{Lacasa2008}. 
\noindent
For each seismic event we calculate the connectivity degree $(K)$. The connectivity degree of each event is sum of all connections of the event with the visible events. We categorized events in small magnitude bins $(\Delta M=0.1)$ and plot connectivity degree as a function of the bin-magnitude. Two earthquakes with the same magnitude could have different connectivity degrees, based on event time and surrounding events. We compute the linear regression line for scatter data points. The slope of the line is $k-M$ slope of the time series. Fig.~\ref{fig:vg} shows initial events of KopehDagh magnitude-time series with connectivity degree of each event.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.24]{figures/pdf/Figure01.pdf} 
\caption{Sketch of the VG method. The initial events of Kopeh Dagh region are represented. Couple of events were deleted due to illustration purposes. The blue vertical lines indicate the events. Height of each line is corresponding the magnitude of the event. The green dashed lines show the allowable connections between events. The connectivity degree (K) of each event is presented. The red arrows show the time difference between events. The $T_c$ and $< T_c >$ values of the last event are represented. Note that the mean of all $<T_c>$ values in each window will be the window mean interval connectivity time.}
\label{fig:vg}
\end{figure}
\noindent
\citet{Telesca2014} defined the VG window mean interval connectivity time $<T_c>$ as an indication of mean linkage time between earthquakes. For each event in a window we compute the interval connectivity time $(T_c)$ for each connection which is the time difference between occurrence of two events. Average interval connectivity time gives the mean interval connectivity time $<T_c>$  for each event. The average of all the $<T_{ce}>$  values in a window results the window mean connectivity time $<T_c>$. We attribute this value to the last event in each window. Fig.~\ref{fig:vg} shows the  $T_c$ and $< T_c >$ values of the last event.

### 2016-08-11 results.tex
Ricardo's comments added.

@@
 Fig.~\ref{fig:k_m_plot_m}  shows the  $k-M$  relationship for the study regions.
-We categorized magnitudes in small magnitude bins ($\Delta M=0.1$).
 It is clear from the Fig.~\ref{fig:mag-time} that the specific magnitude bin can result in different connectivity degrees regarding the occurring time of the earthquake event.
@@
 \centering
-\includegraphics[scale=0.35]{figures/pdf/Figure06.pdf} 
+\includegraphics[scale=0.35]{figures/pdf/Figure07.pdf} 
 \caption{ $k-M$ relationship for north Iran tectonic seismic regions.
@@
 The red line is the linear regression line fits the data.
-The numbers on the lines is the slope of the lines.}
+The numbers on the lines is the slope of the regression lines.}
 \label{fig:k_m_plot_m}
@@
  \noindent
-where $\overline{M}$ is the average magnitude, and  $M_ {min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic region.
+where $e$ is the mathematical constant, $\overline{M}$ is the average magnitude, and  $M_ {min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic region.
 The number of sequences and threshold magnitudes is considerably different for all tectonic seismic regions.
@@
 Comparing the result with the Guerrero region with reduced random sequence,  \citet{Telesca2013}  found that the number of sequences did not affect the  $k-M$  slope.
-According to  \citet{Telesca2012}, the threshold magnitude has minor effect in the VG parameters.
+According to  \citet{Telesca2012}, the threshold magnitude has minor effect in the VG parameters.\\
+\noindent
 In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, we randomly picked 200 sequences from the catalogs with various sequence sizes.
-The minimum size of random windows is 150 events.
-(Note that the number of events in each catalog, before removing the events with magnitude less than the completeness magnitude, is 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively.).
+Number of events at each sequence should be low enough to be able to choose 200 random sequence from the catalog (note that the number of events in each catalog, before removing the events with magnitude less than the completeness magnitude, is 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively).
+Also it should be long enough to preserve the seismic characteristic of each tectonic seismic region.
+Based on mentioned criteria, we choose the minimum size of random windows as 150 events.
 The maximum size is the size of the entire catalog.
+The random sequences are consecutive, in other words, we randomly determine the initial event and sequence size, then we pick that size of event starting from the initial event.
 For each randomly picked magnitude time series,  we estimate $Mc$; then the $k-M$  and $b-value$ are calculated.
@@
 \centering
-\includegraphics[scale=0.5]{figures/pdf/Figure07.pdf} 
+\includegraphics[scale=0.5]{figures/pdf/Figure08.pdf} 
 \caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence.
@@
 \centering
-\includegraphics[scale=0.6]{figures/pdf/Figure08.pdf} 
+\includegraphics[scale=0.6]{figures/pdf/Figure09.pdf} 
 \caption{ Relationship between $k-M$ slope and $b-value$ of three Iranian tectonic seismic zones (this study) and three other studies of Mexican zones \citep{Telesca2013}, Pannonia zones \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}.
@@
 Fig.\ref{fig:tc} shows the variation of the  $k-M$  slope and  $b-value$  with time.
-Having a lower number of events, we chose 20 events as the window length with a shift of one event between two successive windows.
-The calculated parameters of each window were associated with the time of occurrence of the last event in the sliding window.
+Due to lower number of events in Azerbaijan's catalog, we choose 20 events as the window length with a shift of one event between two successive windows.
+With higher window length we loose the variation of considerable amount of information in time (e.g.
+with n=40 we loose almost half of the Azerbaijan catalog).
+Due to taking average values of successive windows, very small window length can not display the seismicity behavior especially before big earthquake.
+Maintaining consistency, we use the window length equal to 20 events for all three regions.
+The calculated parameters of each window are associated with the time of occurrence of the last event in the sliding window.
 The  $k-M$  slope and  $b-value$  in all tectonic seismic regions are very similar.
@@
 \noindent
-\citet{Telesca2016}  observed the decrease in  $<T_C>$  before the large earthquake of the western India earthquake sequence.
-Fig.\ref{fig:tc}  shows the time variation of  $<T_C>$   in the study area.
-The reduction of  $<T_C>$   before large earthquakes is clearly visible.
-\citet{Telesca2016}  demonstrated that the decrement of  $<T_C>$   before a large earthquake is independent of window size and threshold magnitude.
-Decreasing the value of  $<T_C>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions (see Fig.\ref{fig:tc} for reference.)
+\citet{Telesca2016}  observed the decrease in  $<T_c>$  before the large earthquake of the western India earthquake sequence.
+Fig.\ref{fig:tc}  shows the time variation of  $<T_c>$   in the study area.
+The reduction of  $<T_c>$   before large earthquakes is clearly visible.
+\citet{Telesca2016}  demonstrated that the decrement of  $<T_c>$   before a large earthquake is independent of window size and threshold magnitude.
+Decreasing the value of  $<T_c>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions (see Fig.\ref{fig:tc} for reference.)
 
@@
 \centering
-\includegraphics[scale=0.4]{figures/pdf/Figure09.pdf} 
-\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_C >$ (Right) as a function of time for three tectonic seismic regions in north Iran.
+\includegraphics[scale=0.4]{figures/pdf/Figure10.pdf} 
+\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_c >$ (Right) as a function of time for three tectonic seismic regions in north Iran.
 Black arrows show the occurrence of the major earthquakes.
 Numbers on arrows indicate the moment magnitude of the earthquake (see Fig.~\ref{fig:mag-time} for reference).
-Decreasing the value of  $<T_C>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions.}
+The magnitude-time series are presented as a filled plot blew each plot.
+The variation of the heigh of filled plots are corresponding to the event magnitudes.
+Decreasing the value of  $<T_c>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions.}
 \label{fig:tc}

### 2016-08-11 seismicity.tex
Ricardo's comments added.

@@
 \centering
-\includegraphics[scale=1]{figures/pdf/Figure01.pdf} 
+\includegraphics[scale=1]{figures/pdf/Figure02.pdf} 
 \caption{Region of interest and tectonic seismic regions.
@@
 \centering
-\includegraphics[scale=1]{figures/pdf/Figure02.pdf} 
+\includegraphics[scale=1]{figures/pdf/Figure03.pdf} 
 \caption{Main fault line and fault system in the region of interest. The borderlines of the seismic zones shown in Fig.~\ref{fig:study_region} are shown in background in gray.}
@@
 \centering
-\includegraphics[scale=1]{figures/pdf/Figure03.pdf} 
+\includegraphics[scale=1]{figures/pdf/Figure04.pdf} 
 \caption{Declustered instrumental seismicity map (2005 - 2015) of northern Iran.
@@
 The completeness magnitude $(M_c)$ is often determined using simple numerical analysis.
-Two common approaches are maximum curvature method and (MAXC) and goodness-of-fit test (GFT)(see \citet{Wiemer2000}).
+Two common approaches are maximum curvature method (MAXC) and goodness-of-fit test (GFT)(see \citet{Wiemer2000}).
 We use the Goodness-of-fit test and compute $M_c$ for each region's catalog.
@@
 \centering
-\includegraphics[scale=0.4]{figures/pdf/Figure04.pdf} 
+\includegraphics[scale=0.4]{figures/pdf/Figure05.pdf} 
 \caption{ Selection of completeness magnitude $M_c$ of the three tectonic seismic regions in northern Iran in 2005-15 period.
 The symbols indicate the computed GFT values as function of the earthquake magnitude.
-The horizontal dashed line indicates the desired threshold for the goodness of fit value at 90 percent.}
+The horizontal dashed line indicates the desired threshold for the goodness of fit value at 90 percent.
+The vertical dashed lines indicate the completeness magnitude of each tectonic seismic region.}
 \label{fig:completeness}
@@
 \centering
-\includegraphics[scale=0.8]{figures/pdf/Figure05.pdf} 
+\includegraphics[scale=0.8]{figures/pdf/Figure06.pdf} 
 \caption{Variation of moment magnitude ($M_w$) of 2005-2015 earthquake for north Iran as a function of time.

### 2016-08-11 introduction.tex
formating for srl

@@
 \section{Introduction}
-\noindent
+
 This article presents the application of VG method on seismicity of northern Iran using the recorded earthquake during the last 10 years (2005-15).
@@
 This concept has applications in many fields including geophysical studies\citep[e.g.,][]{Telesca2012_CSF,Long2013,Wang2012}.
-\\
-\noindent
+
 The analysis of seismic sequence through visibility graph for various tectonic seismic regions revealed an alternative approach to studying the magnitude time series.
@@
 Applying different threshold magnitudes and observing the collapsing effect of all distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend on only the values of the magnitude and being independent of the threshold magnitude.
-\noindent
+
 In other research, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through the visibility graph approach.
@@
 Their study investigated the relationship between the Gutenberg-Richter parameters and the $k-M$ slope, which is the slope of the regression line fitting the magnitude of each event ($M$) and its connectivity degree ($k$).
-\noindent
+
 In a similar article, \citet{Telesca2014} studied the seismicity of the 2002-11 Pannonian seismicity using visibility graph.
@@
 They calculated the magnitude as a normalized displacement in range of $1-10$.
-According to their study the $b-value$ and the $k-M$ slope are linearly correlated to each other with a high correlation coefficient.\\
-\noindent
+According to their study the $b-value$ and the $k-M$ slope are linearly correlated to each other with a high correlation coefficient.
+
 VG method also is applied through considering the timespan between earthquakes.
-\citet{Telesca2016}   defined    $<T_c>$  as the parameter window mean interval connectivity time ,  as an indication of the mean linkage time between earthquakes, in studying the 2003-12 earthquake sequence in the Kachchh region of western India.
+\citet{Telesca2016} defined $<T_c>$ as the parameter window mean interval connectivity time, as an indication of the mean linkage time between earthquakes, in studying the 2003-12 earthquake sequence in the Kachchh region of western India.
 They found that $<T_C>$ changes through time, indicating that the topological properties of the earthquake network are not stationary.
@@
 Analyzing the Gutenberg-Richter values of  the magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series by using the features of networks.
-\noindent
+
 In this study, we use visibility graph analysis to investigate the earthquake sequence of northern Iran.
@@
 Significant aspect of our work includes the compassion of earthquake catalog, conversion of the earthquake magnitude and computation of the completeness magnitude for each tectonic seismic zone.
-We present the relationship between  $k-M$  slope and $b-value$  in these three tectonic seismic regions.
+We present the relationship between  $k$-$M$  slope and $b$-value in these three tectonic seismic regions.
 We analyze the sensitivity of the catalogs to the number of events and the threshold magnitude.
 We also investigate the variation of  $<T_c>$  value through time.
-
-% Original text
-%\section{Introduction}
-%\noindent
-%\citet{Lacasa2008} introduced a simple and fast computational method; known as visibility algorithm, to convert time series into graphs.
-Basically the visibility graph presents the connection between nodes in the network.
-For any time series, two characteristics are attributed to each event: occurrence time and value of the event.
-Two events are in connection or visible to each other, if no other event interrupts their linear connection.
-In mathematical form, event $i$ and event $j$ are visible to each other if the following equation fulfills:
-%
-%\begin{equation}
-%\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} ,
-%\end{equation}
-%
-%\noindent
-%where, $y$ is the value and $t$ is the time of the event.
-$k$ is the index of any event occurring between event $i$ and event $j$.
-The visibility graph generated from the time series holds the following conditions, 1) each event is visible to the first event at its right and left side (if there is any) (Connectivity), 2) The algorithm is developed without defining a direction for the links (Undirected),  and 3) Rescaling or translation of a time series is not changing the resulted visibility graph (Invariant under affine transformations of  the series data)\citep{Lacasa2008}.
-This concept has applications ranging in various fields including geophysical studies.
-%
-%\noindent
-%The analysis of seismic sequence through visibility graph for various tectonic seismic regions, revealed an alternative approach to study the magnitude time series.
-\citet{Telesca2012} studied the seismic sequence of Italy between year 2005 and 2010 through using the visibility graph method.
-Applying different threshold magnitudes and observing the collapsing effect of all the distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend only on the values of the magnitude and to be independent of the threshold magnitude.
-In another research, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through visibility graph approach.
-They extracted characteristics of the visibility graph for five different tectonic seismic regions.
-According to their study, visibility graph could distinguish the region with different seismicity characteristics, resulting from its different tectonic processes that governs the area.
-The relationship between Gutenberg-Richter parameters and $k-M$ slope (The slope of regression line fitting the Magnitude  of each event $(M)$ and its connectivity degree $(k)$) was investigated in their study.
-In a similar article, \citet{Telesca2014}, studied the seismicity of 2002-2011 Pannonian seismicity using the visibility graph.
-They classified seismic catalog into shallow and deep earthquakes and extracted the visibility graph characteristics for each class.
-According to their study there is a close relationship between Gutenberg-Richter $b-value$ and $k-M$ slope of the visibility graph.
-High linear correlation coefficient value (close to 1) of $b-value$ and $k-M$ slope suggests the universal character of the relationship between these parameters \citep{Telesca2014}.
-\citet{Telesca2016} , defined the $ <T_C>$, as the parameter window mean interval connectivity time ,  as an indication of the mean linkage time between earthquakes, to study the 2003-2012 earthquake sequence in the Kachchh region of western India.
-They found that the $<T_C>$ changes through time, indicating that the topological properties of the earthquake network are not stationary; also $<T_C>$ significantly decrees before the largest shock of the catalog.
-Analyzing Gutenberg-Richter values of  magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series using the features of networks.
-\\
-%
-%\noindent
-%In this study we use visibility graph analysis to investigate the earthquake sequence of northern Iran.
-We divided northern Iran into three tectonic seismic regions including Azerbaijan, Alborz, and Kopeh Dagh.
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years of seismicity in northern Iran.
-The frequency of shocks vary widely from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region \citep{Nemati2015} .
-\\
-%
-%\noindent
-%Northern Iran has an elaborate seismic history.
-Having considerable number of earthquakes and also being in different tectonic seismic region, northern Iran is a good platform to analyze the visibility graph method's capabilities for studying the magnitude time series.
-In this study we present the relationship between $k-M$ slope and the $b-value$ in three different tectonic seismic regions.
-We also investigate the variation of $<T_C>$ value through time.
-%

### 2016-08-11 methodology.tex
formating for srl

@@
 \section{Methodology}
-\noindent
+
 For any time series, two characteristics are attributed to each event: occurrence time and value of the event.
@@
 In mathematical form, events $i$ and $j$ are visible to each other if the following equation is fulfilled:
-
+%
 \begin{equation}
@@
 \end{equation}
+%
 \noindent
@@
 The visibility graph generated from a time series holds the following conditions: 1) each event is visible to the first event at its right and left side (if there is any) (Connectivity); 2) the algorithm is developed without defining a direction for the links (Undirected); and 3) rescaling or translation of a time series does not change the resulting visibility graph (invariant under affine transformations of the series data) \citep{Lacasa2008}.
-\noindent
+
 For each seismic event we calculate the connectivity degree $(K)$.
@@
 
-\begin{figure} [ht]
+\begin{figure*} [ht]
 \centering
@@
 \label{fig:vg}
-\end{figure}
-\noindent
+\end{figure*}
+
 \citet{Telesca2014} defined the VG window mean interval connectivity time $<T_c>$ as an indication of mean linkage time between earthquakes.

### 2016-08-11 results.tex
formating for srl

@@
 \section{Results}
-\noindent
+
 We generated the visibility graph parameters for three tectonic seismic regions in northern Iran for the period 2005-15.
@@
 	\begin{tabular}{ccccc}
-Region          & Number of Earthquake &  $Mc$ &  $b-value$ & $k-M$ slope \\ \hline
-Azerbaijan     & 93                                 & 3.5   & 1.0190  & 9.2004       \\ \hline
-Alborz            & 794                               & 2.6   & 0.7717  & 9.0461      \\ \hline
-Kopeh Dagh  & 282                               & 2.6   & 0.5799  & 6.5818     \\ \hline
+		Region      & Num.~of Earthq. &  $Mc$ & $b$-value & $k-M$ slope \\ 
+		\hline
+		Azerbaijan  & 93              & 3.5   & 1.0190    & 9.2004      \\
+		Alborz      & 794             & 2.6   & 0.7717    & 9.0461      \\
+		Kopeh Dagh  & 282             & 2.6   & 0.5799    & 6.5818      \\
+		\hline
 	\end{tabular}
@@
 
-\noindent
 Fig.~\ref{fig:k_m_plot_m}  shows the  $k-M$  relationship for the study regions.
@@
 
-\begin{figure} [ht]
+\begin{figure*}[t]
 	\centering
@@
 	\label{fig:k_m_plot_m}
-\end{figure}
- \noindent
-We compared the  $k-M$  slope with the  $b-value$  of the Gutenberg-Richter law through the entire catalog and in the sliding windows in time.
-The  $b-value$  is generated through the maximum likelihood estimation  \citep{Aki1965} .
+\end{figure*}
+
+We compared the  $k$-$M$  slope with the  $b$-value  of the Gutenberg-Richter law through the entire catalog and in the sliding windows in time.
+The $b$-value is generated through the maximum likelihood estimation \citep{Aki1965}.
 
@@
 \end{equation}
+
 \noindent
@@
 According to  \citet{Telesca2012}, the threshold magnitude has minor effect in the VG parameters.\\
-\noindent
+
 In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, we randomly picked 200 sequences from the catalogs with various sequence sizes.
@@
 
- \begin{figure} [ht]
+\begin{figure*}[t]
 	\centering
@@
 	\label{fig:random}
-\end{figure}
+\end{figure*}
 
-\noindent
 The coefficient of variation of parameters is shown in Fig.~\ref{fig:random}.
 The  $k-M$  slope shows the higher coefficient of variation which indicates the fact that the  $k-M$  slope is more dependent on the window size and threshold magnitude than on the a-  and  b-values , which suggests that  the $k-M$  slope can better represent the dynamic characteristics of the magnitude-time series.
- \noindent
+
 Fig.~\ref{fig:regression} shows the relationship between the  $k-M$  slope and $b-value$ for the three tectonic seismic regions in northern Iran and three other studies of Mexican zones  \citep{Telesca2013}, Pannonia zones  \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}.
@@
 	\label{fig:regression}
-\end{figure}
+\end{figure*}
 
-\noindent
 Fig.\ref{fig:tc} shows the variation of the  $k-M$  slope and  $b-value$  with time.
@@
 The decline in the  $b-value$  before large earthquakes has been studied in many regions \citep{Wyss2000, Wyss2006, Schorlemmer2005, Chan2012}.
-\noindent
+
 \citet{Telesca2016}  observed the decrease in  $<T_c>$  before the large earthquake of the western India earthquake sequence.
@@
 	\label{fig:tc}
-\end{figure}
-
- % Original text
-%\section{Results}
-%\noindent
-%We generated the visibility graph parameters for three tectonic seismic regions in northern Iran for the period from 2005 to 2015.
-Number of earthquakes in each catalog after declustering and the seismicity parameters are presented in Table.~\ref{tab:b_k_m_param}.
-%
-%
-%\begin{table}[h]
-%\centering
-%\caption{Seismic parameters and $k-M$ slope values for north Iran tectonic seismic zones.}
-%\begin{tabular}{ccccc}
-%Region          & Number of Earthquake &  $Mc$ &  $b-value$ & $k-M$ slope \\ \hline
-%Azerbaijan     & 93                                 & 3.5   & 1.0190  & 9.2004       \\ \hline
-%Alborz            & 794                               & 2.6   & 0.7717  & 9.0461      \\ \hline
-%Kopek Dagh  & 282                               & 2.6   & 0.5799  & 6.5818     \\ \hline
-%\end{tabular}
-%\label{tab:b_k_m_param}
-%\end{table}
-%
-%\noindent
-%Fig.~\ref{fig:k_m_plot_m} shows the $k-M$ relationship for the study regions.
-In general with increasing magnitude the connectivity degree increases which results in increasing the slope of the $k-M$ relationship.
-%
-%\begin{figure} [ht]
-%\centering
-%\includegraphics[scale=0.35]{figures/pdf/Figure05.pdf} 
-%\caption{ $k-M$ relationship for north Iran seismicity. a) Azerbaijan b) Alborz c)Kopeh Dagh}
-%\label{fig:k_m_plot_m}
-%\end{figure}
-%
-%\noindent
-%We compared the $k-M$ slope with the $b-value$ of the Gutenberg-Richter law in the whole catalog and also in the sliding windows in time.
-The $b-value$ is generated through the maximum likelihood estimation \citep{Aki1965}.
-%
-%\begin{equation}
-%b = \frac{log_{10}(e) }{\overline{M} - M_{min}},
-%\end{equation}
-% 
-% \noindent
-% where $\overline{M}$ is the average magnitude and $M_{min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic zone.
-Number of sequences and threshold magnitudes are considerably different for all tectonic seismic regions.
-\citet{Telesca2013} studied the effect of the number of earthquakes in catalog on the $k-M$ slope.
-Comparing the result of Guerrero region with reduced random sequence, \citet{Telesca2013} found that the number of sequence doesn't affect the $k-M$ slope.
-According to \citet{Telesca2012}, the threshold magnitude has a minor effect in the VG parameters.
-In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly pick 200 sequences from the catalogs with various sequence size.
-The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively) and the maximum size is the size of the whole catalog.
-For each randomly picked magnitude time series we estimate the $Mc$ and calculated the $k-M$ and $b-value$.
-Fig.~\ref{fig:random} shows the relationship between $k-M$ slope and $b-value$ of the randomly selected data and statistical parameters for variables.
-Although changing the number of events and the threshold magnitude are slightly changes the results, they are fairly well clustered for each tectonic seismic region.
-% 
-% \begin{figure} [ht]
-%\centering
-%\includegraphics[scale=0.4]{figures/pdf/Figure06.pdf} 
-%\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence.
-The numbers on the mean and standard deviation plots are coefficient of variations in percent$(standard \ deviation / mean)$.}
-%\label{fig:random}
-%\end{figure}
-% 
-% \noindent
-%The coefficient of variation of parameters are shown in Fig.~\ref{fig:random}.
-The $k-M$ slope shows higher coefficient of variation.
-We may argue that the $k-M$ slope is much dependent to the window size and threshold magnitude than $a-$ and $b-value$, which suggest the idea that $k-M$ slope can better represent the dynamic characteristics of the magnitude-time series.
-% 
-% 
-%
-% 
-% \noindent
-% Fig.~\ref{fig:regression} shows the relationship between the $k-M$ slope for three tectonic seismic regions in north of Iran and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.
-Adding the results of the current study into the results of two previous similar studies improves the regression factor (with an increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} concluded.
-%
-%\begin{figure} [ht]
-%\centering
-%\includegraphics[scale=0.3]{figures/pdf/Figure07.pdf} 
-%\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}.
-The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and north Iran)}
-%\label{fig:regression}
-%\end{figure}
-%
-%
-%\noindent 
-%Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time.
-Having lower number of event, we used 20 events as a window length with shift of one event between two successive windows.
-The calculated parameters of each window was associated with the time of occurrence of the last event in sliding window.
-There is a very good similarity between the $k-M$ slope and $b-value$ in all tectonic seismic regions.
-In general, In all regions the $b-value$ and $k-M$ slope considerably drop before big earthquakes.
-Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}
-%
-%\noindent
-%\citet{Telesca2016} observed the decreasing in $<Tc>$ before large earthquake of Western India earthquake sequence.
-Fig.~\ref{fig:tc} shows the time variation of $<Tc>$ in the study area and decrease in $<Tc>$ befor large earthquakes is clearly visible.
-\citet{Telesca2016} demonstrated that the decrement of $<Tc>$ before large earthquake are independent of window size and the threshold magnitude.
-Fig.~\ref{fig:tc} shows the decrement of value of $< T_C >$, $k-M$, and $b-value$ before big earthquakes.
-% 
-% \begin{figure} [ht]
-%\centering
-%\includegraphics[scale=0.34]{figures/pdf/Figure08.pdf} 
-%\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_C >$ (Right) with time.
-Black arrows show the occurrence of the major earthquakes.
-Numbers on arrows indicate the moment magnitude of the earthquake.}
-%\label{fig:tc}
-%\end{figure}
+\end{figure*}

### 2016-08-11 seismicity.tex
formating for srl

@@
 \section{Tectonic seismic regions and seismicity parameters}
-\noindent
+
 The Iranian plateau is located on the Himalayan-Alpine seismic belt.
@@
 Fig.~\ref{fig:study_region} shows the study area and tectonic seismic regions.
-\\
 
-\begin{figure} [ht]
+\begin{figure*}[t]
 	\centering
-\includegraphics[scale=1]{figures/pdf/Figure02.pdf} 
+	\includegraphics[width=0.75\textwidth]{figures/pdf/Figure02} 
 	\caption{Region of interest and tectonic seismic regions.
@@
 	\label{fig:study_region}
-\end{figure}
+\end{figure*}
 
-\noindent
 The Alborz tectonic seismic region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
@@
 The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression  \citep{Berberian1999}.\\
-\noindent
 The Tabriz region (located in the Azerbaijan tectonic seismic region) is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains toward the Caucasus.
 The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement  \citep{Berberian1999}.
-\noindent
+
 The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall  NW - SE  structure with step-overs.
@@
 
-\begin{figure} [ht]
+\begin{figure*}[t]
 \centering
@@
 \label{fig:faults}
-\end{figure}
+\end{figure*}
 
 \subsection{Magnitude Conversion}
-\noindent
+
 The catalog of recorded earthquakes from 2005-15, downloaded from IIEES, reported earthquakes based on different magnitude scales \citep{IIEES}.
@@
 \subsection{Declustering}
-\noindent
+
 It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
@@
 \label{fig:seismicity}
-\end{figure}
+\end{figure*}
 
 \subsection{Catalog Completeness}
-\noindent
+
 Catalog completeness is an important factor in studying an earthquake sequence.
@@
 
-\begin{figure} [ht]
+\begin{figure}[t]
 \centering
-\includegraphics[scale=0.4]{figures/pdf/Figure05.pdf} 
+\includegraphics[width=0.45\textwidth]{figures/pdf/Figure05.pdf} 
 \caption{ Selection of completeness magnitude $M_c$ of the three tectonic seismic regions in northern Iran in 2005-15 period.
@@
 \end{figure}
-\noindent
+
 Based on the results represented in Fig.~\ref{fig:completeness}, we select the minimum magnitudes for complete recording,  $M_c$ , is 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively.
@@
 	\label{fig:mag-time}
-\end{figure}
-
-% Original text
-%\section{Tectonic seismic regions and seismicity parameters}
-%\noindent
-%Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes.
-Based on seismicity parameters, different tectonic seismic devisions have been defined for Iran.
-Some studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}.
-\citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Considering \citet{Mirzaei1998} devision as a reference, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of the northern Iran.
-Fig.~\ref{fig:study_region} shows the study area and tectonic seismic regions.
-\\
-%
-%\begin{figure} [ht]
-%\centering
-%\includegraphics[scale=0.6]{figures/pdf/Figure01.pdf} 
-%\caption{a) Map of Iran and surrounding countries.
-The study area is situated in the gray box.
-b) The study area containing seismotectonic provinces after \citet{Mirzaei1998} is presented, and location of big cities indicated with circles.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
-%\label{fig:study_region}
-%\end{figure}
-%
-%
-%
-%
-%\noindent
-%Alborz tectonic seismic region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-The North Tehran Thrust (NTT) adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
-%The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression \citep{Berberian1999}.
-%
-%\noindent
-% The Tabriz region (located in Azerbaijan tectonic seismic region) is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains towards the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement \citep{Berberian1999}.
-%\noindent
-%The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall $NW - SE$ structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults striking about E - W \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-%
-%\subsection{Magnitude Conversion}
-%\noindent
-%The catalog of recorded earthquakes from 2005-2015, which is downloaded from IIEES, reported the earthquakes based on different magnitude scales \citep{IIEES}.
-We converted the $M_L$, $M_S$, and $mb$ magnitudes through conversion relationships which are defined in \citet{Zare2014}.
-There are also some of data recorded in $M_D$ (Duration magnitude).
-These data are reported by International Seismological Centre (ISC).
-\citet{Deniz2010} developed a set of empirical equations to convert earthquake magnitudes from $mb$, $M_D$, $M_L$ and $M_S$ scales to $M_W$ scales using orthogonal regression procedure.
-They used data of earthquake that occurred in Turkey from different data centers including ISC.
-In this study we use the conversion equation of \citet{Deniz2010} to convert the $M_D$ to $M_W$.
-%
-%\subsection{Declustering}
-%\noindent
-%It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we declustered the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks were removed using a declustering methodology \citet{Gardner1974}.
-Fig.~\ref{fig:seismicity} shows the epicenter of declustered instrumental  earthquakes.
-%
-%\begin{figure} [ht]
-%\centering
-%\includegraphics[scale=0.6]{figures/pdf/Figure02.pdf} 
-%\caption{Declustered instrumental seismicity map (2005 - 2015) of Northern Iran.}
-%\label{fig:seismicity}
-%\end{figure}
-%
-%
-%\subsection{Catalog Completeness}
-%\noindent
-%Completeness of catalog is an important factor in studying the earthquake sequence.
-In this study we used the Maximum curvature method (MAXC) \citep{Wiemer2000} to determine the completeness magnitude.
-According to MAXC method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude.
-The steps for picking the completeness magnitude for each catalog include: 1) Calculating the $a-$ and $b-$ value based on the minimum magnitude, 2) generating  synthetic events based on the achieved value somehow the cumulative number of events obey the power law distribution, and 3) Calculating the goodness of fit for predicted and observed cumulative numbers for each magnitude bin \citep{Wiemer2000}.
-We increase the minimum magnitude and repeat the process in order to calculate the goodness of fit for each magnitude.
-\citet{Wiemer2000} assumed the goodness of fit of 90\% as a threshold to select completeness of the catalog.
-However,  not all frequency-magnitude distributions reach the 90\% mark.
-Fig.~\ref{fig:completeness} , shows the goodness of fit values for three tectonic seismic regions.
-For each tectonic seismic region, we pick the magnitude corresponding to the highest goodness of fit or the first magnitude with goodness of fit bigger than 90\%.
-%
-%\begin{figure} [ht]
-%\centering
-%\includegraphics[scale=0.4]{figures/pdf/Figure03.pdf} 
-%\caption{Goodness of fit value of MAXC method for three tectonic seismic regions for seismicity of 2005-2015 (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
-%\label{fig:completeness}
-%\end{figure} 
-%
-%
-%
-%
-%
-%\noindent
-%In this study we assume the minimum magnitudes for complete recording, $M_C$, are 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively.
-Fig.~\ref{fig:mag-time} shows the magnitude time series of the declustered data for the three regions.
-Earthquakes with magnitude bigger than completeness magnitude are represented.
-%
-%\begin{figure} [ht]
-%\centering
-%\includegraphics[scale=0.5]{figures/pdf/Figure04.pdf} 
-%\caption{Variation of moment magnitude of 2005-2015 earthquake for north Iran. (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
-%\label{fig:mag-time}
-%\end{figure}
+\end{figure*}

### 2016-08-11 title-and-authors.tex
formating for srl

\pretitle{
    \vspace{-30pt}
    \begin{flushleft}
    \usefont{T1}{phv}{bc}{it}
    \Huge
}

\posttitle{
    \end{flushleft}
}

\preauthor{
    \begin{flushleft}
    \vspace{3pt}
    \usefont{T1}{phv}{bc}{n}
    \LARGE
}

\postauthor{
    \end{flushleft}
    \vspace{0.3em}
    \section{Abstract}
    \vspace{-3em}
}

\predate{
    \begin{flushleft}
    \makeatletter
}

\postdate{
    \end{flushleft}
}

\title{%
    Analysis of 2005--2015 Earthquake Sequence in Northern Iran Using Visibility Graph Approach
}

\makeatletter
\if@twocolumn
    \date{}
    \renewcommand*\@fnsymbol[1]{\the#1}
    \author{by Naeem Khoshnevis, Shima Azizzadeh-Roodpish, Ricardo Taborda, and Luciano Telesca}
\else
    \author{
    	Naeem Khoshnevis,\myaffil{1,$\ast$} Shima Azizzadeh-Roodpish,\myaffil{1,2} Ricardo Taborda\myaffil{1,2} and Luciano Telesca\myaffil{3}\\
    	\normalsize\normalfont    	    	
        \vspace{20pt}
    	1.~
    	Center for Earthquake Research and Information\\
    	\hspace{1.1em} The University of Memphis, Memphis, TN 38152, U.S.A.\\
        \vspace{20pt}
        2.~
        Department of Civil Engineering\\
        \hspace{1.1em} The University of Memphis, Memphis, TN 38152, U.S.A.\\
        \vspace{20pt}
        3.~
        Institute of Methodologies for Environmental Analysis\\
        \hspace{1.1em} National Research Council, Tito, Italy\\
        \vspace{20pt}
        *.~
    	Corresponding author\\
    	\hspace{1.1em} Email: nkhshnvs@memphis.edu\\
        \vspace{40pt}
    }
\fi
\makeatother

### 2016-08-11 abstract.tex
formating for srl
improved abstract

--- 2016-07-11 abstract.tex
@@
-\begin{abstract}
-The seismicity of northern Iran between 2005 and 2015 is investigated by means of the visibility graph (VG) method.
+%
+We present an analysis of the seismicity of northern Iran in the period between 2005 and 2015 using a recently introduced method based on concepts of graph theory.
+The method relies on the inter-event visibility defined in terms of a connectivity degree parameter, $k$, which is correlated with the earthquake magnitude, $M$.
+Previous studies show that the slope of the $k$-$M$ correlation also observes a relationship with the $b$-value from the Gutenber-Richter law.
+Thus rendering the graph analysis useful to examine the seismicity of a region.
+In addition, other topological properties of the network and dynamic properties of the magnitude-time series exhibit characteristics that seem to be associated with the occurrence of earthquakes, offering the possibility of correlating seismicity parameters with time.
+We apply this approach to the case of the seismicity of northern Iran, using a declustered seismic catalogs for the tectonic seismic regions of Azerbaijan, Alborz, and Kopeh Dagh.
+We use results draw for this region with the visibility graph approach in combination with results from other similar studies to further improve the universal correlation between $k$-$M$ and $b$-values and show that the visibility graph approach can be considered as a valid alternative for analyzing regional seismicity properties and earthquake sequences.
+
+% --------------------------------------------------------------------------------------------------
+
+% NAEEM'S ABSTRACT
+% ----------------
+
+% The seismicity of northern Iran between 2005 and 2015 is investigated by means of the visibility graph (VG) method.
 For purposes of this study, northern Iran is divided into three tectonic seismic regions: Azerbaijan, Alborz, and Kopeh Dagh.
@@
 $b-value$) significantly decrease before large earthquakes.
-Combining the results of this study with two similar previous studies improves the linear correlation coefficient factor between $k-M$ and $b-value$, and empowers the idea of a universal relationship between $b-value$ and $k-M$ slope.
+Combining the results of this study with three similar previous studies improves the linear correlation coefficient factor between $k-M$ slope and $b-value$, and empowers the idea of a universal relationship between $b-value$ and $k-M$ slope.
 The behaviors of the VG's properties are similar to previous studies and could be considered an alternative method for analyzing earthquake sequences.
-\end{abstract}
-
-%% Original text
-
-%\begin{abstract}
-%The seismicity of northern Iran between 2005 and 2015 is investigated by means of visibility graph (VG) method.
-In this study the northern Iran is divided into three tectonic seismic regions: Azerbaijan, Alborz, and Kopeh Dagh.
-Using declustered catalog, we studied the VG properties of the magnitude time series.
-The results show a relationship between the $k-M$ slope and the $b-value$ of the Gutenberg-Richter law.
-Topological properties (i.e.
-$< T_c >$, $k-M$ slope) of network and  dynamic properties of magnitude time series (i.e.
-$b-value$) significantly decrease before large earthquakes.
-Combining  the results of this study with two similar previous studies improves the linear correlation coefficient factor between $k-M$ and $b-value$ and empower the idea of universal relationship between $b-value$ and $k-M$ slope.
-The behavior of  the VG's properties are similar to previous studies and could be considered as an alternative method for analyzing earthquake sequences.
-%\end{abstract}

### 2016-08-11 acknowledgements.tex
improved abstract

@@
 \section{Acknowledgements}
-\noindent
+
 We greatly appreciate the International Institute of Earthquake Engineering and Seismology (IIEES) in Tehran for maintaining and providing access to the seismic catalog.

### 2016-08-11 introduction.tex
working on introduction

@@
 
-This article presents the application of VG method on seismicity of northern Iran using the recorded earthquake during the last 10 years (2005-15).
+In a relatively recent study, \citet{Lacasa2008} introduced a simple and computationally inexpensive approach to convert time-series into mathematical graphs.
+The method, known as the visibility algorithm, represents the connection between nodes in a network based on the visibility of each node in a time sequence with respect to previous and later nodes in the sequence.
+Over the last decade, this method has been found to be applicable to multiple fields, including economics and geophysics \citep[e.g.,][]{Telesca2012_CSF, Long2013, Wang2012}.
+
+For the particular case of seismological applications, previous studies have proposed the nodes in the graph to be considered as the earthquakes in a given time series of events, and analyzed the properties of the graph with respect to traditional seismicity parameters.
+The analysis of seismic sequences through the visibility graph approach for various tectonic seismic regions has proven to be a valid alternative to studying magnitude time series.
+\citet{Telesca2012}, for instance, studied the seismicity of Italy between the years 2005 and 2010 using the visibility graph method.
+Applying different threshold magnitudes to construct the graph and observing the collapsing effect of all distribution degrees, they observed that the properties of the visibility graph seemed to depend only on the magnitude values, and not on the threshold magnitude used in the analysis.
+
+Subsequently, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through the visibility graph approach and found that the properties of the graph were correlated to the seismic $b$-value in the Gutenber-Richter law \citep{Gutenberg1944}.
+In particular, \citet{Telesca2013} extracted the characteristics of the visibility graph for five different tectonic seismic regions in the subduction zone and found that the slope in the linear relationship between earthquake magnitude, $M$, and the inter-event visibility in the graph defined as the connectivity degree parameter, $k$, was correlated with the $b$-value.
+
+In a similar article, \citet{Telesca2014} studied the seismicity of the 2002--2011 Pannonian seismicity using the visibility graph method for two sub-catalogs of shallow and deep earthquakes.
+They extracted the visibility graph characteristics for each group of events and confirmed that there was a close correlation between the Gutenberg-Richter $b$-value and the slop of the $k$-$M$ relationship obtained from the visibility graph.
+According to \citet{Telesca2014}, the high linear correlation coefficient value (close to 1.0) between the $b$-value and the $k$-$M$ slope indicates that this relationship exhibits a nearly universal character.
+This observation was reinforced experimentally by \citet{Telesca2014-pone}, who investigated the behavior of a mechanical stick-slip system with different asperities (sandpaper of different grades).
+After collecting data for different experiments emulating young and mature faults, \citet{Telesca2014-pone} found again that the $b$-value was linearly correlated with the $k$-$M$ slope derived from the visibility graph of the experimental events.
+
+More recently, \citet{Telesca2016} used the visibility graph method to gain insight about the timespan between earthquakes.
+The authors defined the parameter window mean interval connectivity time <$T_c$>, which provides information about the average of all the time intervals between visible events.
+Applying this concept to the 2003--2012 earthquake sequence in Kachchh, western India, \citet{Telesca2016} found that the variation of <$T_c$> in time exhibited a plausible relationship with the occurrence of earthquakes.
+In particular, they observed that the value of <$T_c$> decreases significantly before the largest shock in the Kachchh catalog.
+
+In this article we use the visibility graph method to analyze the seismicity of northern Iran for the 2005--2015 period.
+We focus our analysis the last decade period because previous studies on the analysis of seismic catalogs for the region have shown that this period has the most complete datasets, especially for the case of small earthquakes with $M<4$ \citep[e.g.][]{Khoshnevis2016}.
+We analyze this region considering three dominant seismic areas: Azerbaijan, Alborz, and Kopeh Dagh.
+
+...
+
+% NAEEM'S INTRODUCTION
+% --------------------
+
+% This article presents the application of VG method on seismicity of northern Iran using the recorded earthquake during the last 10 years (2005-15).
 Recent studies show that this period (2005-15) has the most complete catalog especially for small earthquakes $(M < 3)$ \citep[e.g.][]{Khoshnevis2016}.
@@
 
-The analysis of seismic sequence through visibility graph for various tectonic seismic regions revealed an alternative approach to studying the magnitude time series.
+% The analysis of seismic sequence through visibility graph for various tectonic seismic regions revealed an alternative approach to studying the magnitude time series.
 \citet{Telesca2012} studied the seismic sequence of Italy between the years 2005 and 2010 using the visibility graph method.
@@
 
-In other research, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through the visibility graph approach.
+% In other research, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through the visibility graph approach.
 They extracted characteristics of the visibility graph for five different tectonic seismic regions.
@@
 
-In a similar article, \citet{Telesca2014} studied the seismicity of the 2002-11 Pannonian seismicity using visibility graph.
+% In a similar article, \citet{Telesca2014} studied the seismicity of the 2002-11 Pannonian seismicity using visibility graph.
 They classified the seismic catalog into shallow and deep earthquakes, and extracted the visibility graph characteristics for each class.
@@
 
-VG method also is applied through considering the timespan between earthquakes.
+% VG method also is applied through considering the timespan between earthquakes.
 \citet{Telesca2016} defined $<T_c>$ as the parameter window mean interval connectivity time, as an indication of the mean linkage time between earthquakes, in studying the 2003-12 earthquake sequence in the Kachchh region of western India.
@@
 
-In this study, we use visibility graph analysis to investigate the earthquake sequence of northern Iran.
+% In this study, we use visibility graph analysis to investigate the earthquake sequence of northern Iran.
 We divided northern Iran into three tectonic seismic regions, namely Azerbaijan (Az), Alborz Mountain Range (Al), and Kopeh Dagh (Ko).

### 2016-08-12 introduction.tex
done with introduction, for now. next is the methodology section

@@
 In this article we use the visibility graph method to analyze the seismicity of northern Iran for the 2005--2015 period.
-We focus our analysis the last decade period because previous studies on the analysis of seismic catalogs for the region have shown that this period has the most complete datasets, especially for the case of small earthquakes with $M<4$ \citep[e.g.][]{Khoshnevis2016}.
-We analyze this region considering three dominant seismic areas: Azerbaijan, Alborz, and Kopeh Dagh.
-
-...
+We focus our analysis on the last decade period because previous studies using seismic catalogs for the region of interest have shown that this period has the most complete datasets, especially for the case of small $M<4$ earthquakes \citep[e.g.][]{Khoshnevis2016}.
+Upon a brief review of the basic concepts of the method and its applications, we describe the seismicity of northern Iran considering three dominant seismic areas, namely: Azerbaijan, Alborz, and Kopeh Dagh.
+These are regional areas of considerable ground shaking activity, with average seismic rates varying between about 0.17 and 3.25 events per year \citep[e.g.,][]{Nemati2015}.
+The considerable amount of earthquakes registered in a 10-year period facilitates the analysis done with the visibility graph approach within what would otherwise be considered a relatively short period of time, and serves as a good case study to test the capabilities of the method.
+We first summarize the dataset, including a description of the seismic catalog and its completeness based on a recent work on the seismicity of the region \citep{Khoshnevis2016}.
+We then present results obtained for the region regarding the relationship between the the graph's $k$-$M$ slope and the seismicity $b$-values for the three seismic areas, analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, and present results for the variation of <$T_c$> through time.
 

### 2016-08-13 introduction.tex
finished revising the methodology section

@@
 
-In a relatively recent study, \citet{Lacasa2008} introduced a simple and computationally inexpensive approach to convert time-series into mathematical graphs.
-The method, known as the visibility algorithm, represents the connection between nodes in a network based on the visibility of each node in a time sequence with respect to previous and later nodes in the sequence.
+In a relatively recent study, \citet{Lacasa2008} introduced a simple and computationally inexpensive approach to convert time-series into a particular kind of mathematical graphs known as visibility graphs.
+In this approach, the connection between the nodes in a network---here understood as events in a time series---is based on the visibility of each node or event with respect to other previous and later events in a time sequence.
 Over the last decade, this method has been found to be applicable to multiple fields, including economics and geophysics \citep[e.g.,][]{Telesca2012_CSF, Long2013, Wang2012}.

### 2016-08-13 methodology.tex
finished revising the methodology section

@@
 
-For any time series, two characteristics are attributed to each event: occurrence time and value of the event.
-Two events are in connection or visible to each other if no other event interrupts their linear connection.
-In mathematical form, events $i$ and $j$ are visible to each other if the following equation is fulfilled:
+Discrete mathematics and computer science often deal with different types of data abstractions and structures such as sets, trees, and graphs, where concepts like nodes and links are used to describe the topology a collection of objects and manipulate their data \citep[e.g.,][]{Skiena_2008_Book}.
+In graphs, the data---sometimes also referred to as the payload---resides at the vertices or nodes who are connected through links or edges, which may or may not have an associated direction.
+A visibility graph is a special type of undirected graphs in which the links are straight lines connecting intervisible nodes; that is, straight lines that do not overlap any obstacle while connecting nodes that can see each other in a physical space \citet{LozanoPerez_1979_CACM}.
+Visibility graphs have been mostly used in robotics for navigation path planning \citep[e.g.,][]{Huang_2004_Proc, Oommen_1987_JRA} but have also seen applications in other fields including urban studies, interior architecture, medicine and geosciences \citep[e.g.,][]{Raman_2010_UE, Ahmadlou_2010_JNT, Varoudis_2014_JSS, Phillips_2015_ESR}.
+
+In a relatively recent study, \citet{Lacasa2008} applied the concepts of visibility graphs to the representation and analysis of time series.
+Multiple applications have been found to this idea in fields like economics \citep{Yang_2009_PA, Wang2012} and climate \citep{Elsner_2009_GRL}.
+In this study, we are particularly interested in the application of visibility graphs to the analysis of seismic sequences \citep{Telesca2012}.
+In this case, the nodes in the visibility graphs are considered to be seismic events distributed over time.
+For any seismic time series, two characteristics are attributed to each event: (a) its occurrence time, and (b) the value associated to the event, here considered as the magnitude.
+The obstacles in the time space are the vertical lines (or sticks) between the time axis and the magnitude of the event in a time-magnitude series.
+Two events are in connection, or visible to each other, whenever no other event interrupts their linear connection.
+
+In mathematical form, events $i$ and $j$ are visible to each other if they satisfy the inequality
 %
 \begin{equation}
-\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} ,
+	\frac{y_i - y_p }{t_p - t_i} > \frac{y_i - y_j}{ t_j - t_i} \, ,
 \end{equation}
@@
 \noindent
-where $y$ is the value and $t$ is the time of the event, and $k$ is the index of any event occurring between events  $i$  and  $j$.
-The visibility graph generated from a time series holds the following conditions: 1) each event is visible to the first event at its right and left side (if there is any) (Connectivity); 2) the algorithm is developed without defining a direction for the links (Undirected); and 3) rescaling or translation of a time series does not change the resulting visibility graph (invariant under affine transformations of the series data) \citep{Lacasa2008}.
+where $y$ is the value associated with the event and $t$ is the time of the event.
+The index $p$ indicates any event occurring between events $i$  and $j$.
+It follows from this that the visibility graph generated from a time series holds the following conditions.
+Connectivity: each event is visible to the immediate first events to its right and left sides, if there is any.
+Directivity: the graph is considered undirected by definition; that is, the algorithm explaining the connections between events is developed without defining a direction for the links between the events.
+And invariance: scaling or time-shifting the series does not change the resulting visibility graph, provided the transformation is done under affine conditions \citep{Lacasa2008}.
 
-For each seismic event we calculate the connectivity degree $(K)$.
-The connectivity degree of each event is sum of all connections of the event with the visible events.
-We categorized events in small magnitude bins $(\Delta M=0.1)$ and plot connectivity degree as a function of the bin-magnitude.
-Two earthquakes with the same magnitude could have different connectivity degrees, based on event time and surrounding events.
-We compute the linear regression line for scatter data points.
-The slope of the line is $k-M$ slope of the time series.
-Fig.~\ref{fig:vg} shows initial events of KopehDagh magnitude-time series with connectivity degree of each event.
+Figure \ref{fig:vg} shows an example of a visibility graph for one of the magnitude-time series to be considered later in this study.
+For each event $i$ we compute the connectivity degree, $k$, which is the sum of the connections to all other events $j$ visible by the $i$th event.
+Events are often categorized in small magnitude bins with $\Delta M = 0.1$ and we plot the connectivity degree as a function of the bin magnitude.
+Note that two earthquakes with the same magnitude can have different $k$ values, which ultimately depend on the occurrence time of the event and whether the time-neighboring events are of a larger or smaller magnitude.
 
-\begin{figure*} [ht]
+\begin{figure*}[t]
 	\centering
-\includegraphics[scale=0.24]{figures/pdf/Figure01.pdf} 
+	\includegraphics[width=0.8\textwidth]{figures/pdf/Figure01} 
 	\caption{Sketch of the VG method.
@@
 
-\citet{Telesca2014} defined the VG window mean interval connectivity time $<T_c>$ as an indication of mean linkage time between earthquakes.
-For each event in a window we compute the interval connectivity time $(T_c)$ for each connection which is the time difference between occurrence of two events.
-Average interval connectivity time gives the mean interval connectivity time $<T_c>$  for each event.
-The average of all the $<T_{ce}>$ values in a window results the window mean connectivity time $<T_c>$.
-We attribute this value to the last event in each window.
-Fig.~\ref{fig:vg} shows the  $T_c$ and $< T_c >$ values of the last event.
+Plotting $k$ against magnitude results on a scattered set of points which have been shown to be acceptably represented by a linear correlation, here referred to as the $k$-$M$ relationship, the slope of which also shows a linear relationship with the seismicity $b$-value of the seismic zone under consideration, or a universal sample of $k$-$M$ slope and $b$ values \citep{Telesca2013, Telesca2014}.
+\citet{Telesca2014} also observed that it was reasonable to draw a relationship between the distribution of the events when considering whether these were connected (visible to each other) or not and time.
+Let $T_c$ be the interval connectivity time, which is nothing but the time difference between two inter-visible events (see Fig.~\ref{fig:vg}); and <$T_c^e$> be the average of all $T_c$ values computed for event $e$; then it is possible to compute the visibility graph mean interval connectivity time <$T_c$>, which is the mean value of all <$T_c^e$> in a given time sequence of events.
+
+Because <$T_c$> can be obtained for any sub-graph within a larger graph, that is, for any time window in a larger magnitude-time series of events, then it is possible to investigate the evolution of <$T_c$> (and that of the $k$-$M$ slope and the $b$-value) for a moving window sliding along the magnitude-time series.
+When doing so, \citet{Telesca2014} suggested to associate the values of each sub-sequence with the last event in the sequence.
+Following this approach, \citet{Telesca2014, Telesca2016} found that the variation of <$T_c$> over time exhibited a possible relationship with the occurrence of earthquakes.
+This and the aforementioned relationship between the $k$-$M$ slope and the $b$-value are aspects we explore next for our region and earthquake-sequence of interest.
+
+% Fig.~\ref{fig:vg} shows initial events of KopehDagh magnitude-time series with connectivity degree of each event.

### 2016-08-15 methodology.tex
fixed 2016 telesca for Tc

@@
 
-Plotting $k$ against magnitude results on a scattered set of points which have been shown to be acceptably represented by a linear correlation, here referred to as the $k$-$M$ relationship, the slope of which also shows a linear relationship with the seismicity $b$-value of the seismic zone under consideration, or a universal sample of $k$-$M$ slope and $b$ values \citep{Telesca2013, Telesca2014}.
-\citet{Telesca2014} also observed that it was reasonable to draw a relationship between the distribution of the events when considering whether these were connected (visible to each other) or not and time.
+Plotting $k$ against magnitude results on a scattered set of points which have been shown to be acceptably represented by a linear correlation.
+We referred to this correlation as the $k$-$M$ relationship.
+More important, the slope of the $k$-$M$ relationship also shows a linear relationship with the seismicity $b$-value of the seismic zone under consideration.
+This is also true for a universal sample of $k$-$M$ slopes and $b$ values \citep{Telesca2013, Telesca2014}.
+\citet{Telesca2014} also observed that it was reasonable to draw a relationship between the distribution of the events when considering whether these were connected (visible to each other) or not, and time.
 Let $T_c$ be the interval connectivity time, which is nothing but the time difference between two inter-visible events (see Fig.~\ref{fig:vg}); and <$T_c^e$> be the average of all $T_c$ values computed for event $e$; then it is possible to compute the visibility graph mean interval connectivity time <$T_c$>, which is the mean value of all <$T_c^e$> in a given time sequence of events.
@@
 Because <$T_c$> can be obtained for any sub-graph within a larger graph, that is, for any time window in a larger magnitude-time series of events, then it is possible to investigate the evolution of <$T_c$> (and that of the $k$-$M$ slope and the $b$-value) for a moving window sliding along the magnitude-time series.
-When doing so, \citet{Telesca2014} suggested to associate the values of each sub-sequence with the last event in the sequence.
-Following this approach, \citet{Telesca2014, Telesca2016} found that the variation of <$T_c$> over time exhibited a possible relationship with the occurrence of earthquakes.
+When doing so, \citet{Telesca2016} suggested to associate the values of each sub-sequence with the last event in the sequence.
+Following this approach, \citet{Telesca2016} found that the variation of <$T_c$> over time exhibited a possible relationship with the occurrence of earthquakes.
 This and the aforementioned relationship between the $k$-$M$ slope and the $b$-value are aspects we explore next for our region and earthquake-sequence of interest.

### 2016-08-16 methodology.tex
improved figure 1

@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{figures/pdf/Figure01} 
-	\caption{Sketch of the VG method.
-The initial events of Kopeh Dagh region are represented.
-Couple of events were deleted due to illustration purposes.
-The blue vertical lines indicate the events.
-Height of each line is corresponding the magnitude of the event.
-The green dashed lines show the allowable connections between events.
-The connectivity degree (K) of each event is presented.
-The red arrows show the time difference between events.
-The $T_c$ and $< T_c >$ values of the last event are represented.
-Note that the mean of all $<T_c>$ values in each window will be the window mean interval connectivity time.}
+	\includegraphics[width=0.8\textwidth]{figures/pdf/figure-01} 
+	\caption{Illustration of the visibility graph method, as applied to a subset of events in a window of the magnitude-time series of the north Iranian seismic region of Kopeh Dagh.
+The events are identified by vertical thick lines (or sticks) on the horizontal time axis with size equal to the magnitude as indicated by the labels at the bottom of each stick.
+These sticks are considered to be the obstacles in the time-magnitude space where the graph resides.
+The visibility graph is composed by the nodes, represented with circles at the tip of each event stick, and the edges or links connecting them.
+The values inside each node correspond to the connectivity degree, $k$.
+This value indicates the number straight lines that can be draw between two (mutually visible) nodes without intersecting any obstacle (event stick).
+The values and time ranges shown at the top correspond to the time difference between events visible by the last event.
+These times are given in minutes and correspond to individual $T_c$ values.
+The mean <$T_c^e$> value associated with this event is also shown at the top right.
+The mean value of all <$T_c^e$> for the events in the graph is the window mean interval connectivity time, <$T_c^e$>.}
 	\label{fig:vg}

### 2016-08-16 seismicity.tex
modified figure 2 and started working on section about region of interest

@@
-\section{Tectonic seismic regions and seismicity parameters}
+\section{Seismicity of Northern Iran}
 
-The Iranian plateau is located on the Himalayan-Alpine seismic belt.
+We are interested in applying the visibility graph method to northern Iran.
+This region is part of the Iranian plateau, on the Himalayan-Alpine seismic belt.
+It is confined by the relative movements between the Arabian, Eurasian, eastern Asia-Minor, and Indian plates; and has a long history of large magnitude ($M>7$) earthquakes that are well documented dating back to the eight century  \citep[e.g.,][]{Berberian_1981_Chap}.
+According to the tectonic settings and geologic provinces of the plateau, the seismic activity in Iran has been categorized into different seismic zones.
+These vary between four to nine major seismic zones, in the more traditional models \citep[e.g.,][]{Stocklin1968, Takin1972, Berberian1976}; and up to twenty to twenty-three seismotectonic provinces in the most elaborate models \citep[e.g.,][]{Nowroozi1976, Tavakoli1999}.
+We adopt the model proposed by \citet{Mirzaei1998} with modifications introduced by \citet{Karimiparidari2013}, in which Iran is divided into six tectonic regions: Azerbaijan, Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
+Our focus, however, is on the northern part of Iran, for which we define a region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:study_region}.
+Although this region encloses part of the Zagros and Central-East Iran seismic zones, we will concentrate in the analysis of the seismicity of Azerbaijan, Alborz and Kopeh-Dagh.
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=\textwidth]{figures/pdf/figure-02} 
+	\caption{Region of interest.
+and tectonic seismic regions.
+At the top, the map of Iran and surrounding countries is presented.
+The study area is located in the gray box.
+At the bottom, the study area containing seismotectonic provinces after \citet{Mirzaei1998} is presented.
+Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
+	\label{fig:study_region}
+\end{figure*}
+
+% \section{Tectonic seismic regions and seismicity parameters}
+
+% The Iranian plateau is located on the Himalayan-Alpine seismic belt.
 It has a long history of large magnitude ($M>7$) earthquakes that are well documented dating back to the eighth century.
@@
 
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=0.75\textwidth]{figures/pdf/Figure02} 
-	\caption{Region of interest and tectonic seismic regions.
-At the top, the map of Iran and surrounding countries is presented.
-The study area is located in the gray box.
-At the bottom, the study area containing seismotectonic provinces after \citet{Mirzaei1998} is presented.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
-	\label{fig:study_region}
-\end{figure*}
-
-The Alborz tectonic seismic region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
+% The Alborz tectonic seismic region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
 The North Tehran Thrust adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
 The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression  \citep{Berberian1999}.\\
-The Tabriz region (located in the Azerbaijan tectonic seismic region) is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains toward the Caucasus.
+% The Tabriz region (located in the Azerbaijan tectonic seismic region) is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains toward the Caucasus.
 The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement  \citep{Berberian1999}.
 
-The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall  NW - SE  structure with step-overs.
+% The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall  NW - SE  structure with step-overs.
 The regions of overlap are characterized by shorter south-dipping thrust faults, striking roughly E - W  \citep{Berberian2001}.
@@
 
-\begin{figure*}[t]
-\centering
-\includegraphics[scale=1]{figures/pdf/Figure03.pdf} 
-\caption{Main fault line and fault system in the region of interest. The borderlines of the seismic zones shown in Fig.~\ref{fig:study_region} are shown in background in gray.}
-\label{fig:faults}
-\end{figure*}
+% \begin{figure*}[t]
+% \centering
+% \includegraphics[scale=1]{figures/pdf/Figure03.pdf} 
+% \caption{Main fault line and fault system in the region of interest. The borderlines of the seismic zones shown in Fig.~\ref{fig:study_region} are shown in background in gray.}
+% \label{fig:faults}
+% \end{figure*}
 
-\subsection{Magnitude Conversion}
+% \subsection{Magnitude Conversion}
 
-The catalog of recorded earthquakes from 2005-15, downloaded from IIEES, reported earthquakes based on different magnitude scales \citep{IIEES}.
+% The catalog of recorded earthquakes from 2005-15, downloaded from IIEES, reported earthquakes based on different magnitude scales \citep{IIEES}.
 The  $M_L$,  $M_S$, and  $mb$  magnitudes were converted through conversion relationships, as defined in  \citet{Zare2014}.
@@
 
-\subsection{Declustering}
+% \subsection{Declustering}
 
-It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
+% It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
 Therefore, in order to accomplish this, we decluster the earthquake catalog.
@@
 
-\begin{figure*}[t]
-\centering
-\includegraphics[scale=1]{figures/pdf/Figure04.pdf} 
-\caption{Declustered instrumental seismicity map (2005 - 2015) of northern Iran.
+% \begin{figure*}[t]
+% \centering
+% \includegraphics[scale=1]{figures/pdf/Figure04.pdf} 
+% \caption{Declustered instrumental seismicity map (2005 - 2015) of northern Iran.
 Different colors indicate the seismicity of different regions.
 Size of symbols are proportional to the magnitude of the events.}
-\label{fig:seismicity}
-\end{figure*}
+% \label{fig:seismicity}
+% \end{figure*}
 
-\subsection{Catalog Completeness}
+% \subsection{Catalog Completeness}
 
-Catalog completeness is an important factor in studying an earthquake sequence.
+% Catalog completeness is an important factor in studying an earthquake sequence.
 This characteristic measured as the minimum magnitude of complete recording for earthquake catalog.
@@
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.45\textwidth]{figures/pdf/Figure05.pdf} 
-\caption{ Selection of completeness magnitude $M_c$ of the three tectonic seismic regions in northern Iran in 2005-15 period.
+% \begin{figure}[t]
+% \centering
+% \includegraphics[width=0.45\textwidth]{figures/pdf/Figure05.pdf} 
+% \caption{ Selection of completeness magnitude $M_c$ of the three tectonic seismic regions in northern Iran in 2005-15 period.
 The symbols indicate the computed GFT values as function of the earthquake magnitude.
@@
 The vertical dashed lines indicate the completeness magnitude of each tectonic seismic region.}
-\label{fig:completeness}
-\end{figure}
+% \label{fig:completeness}
+% \end{figure}
 
-Based on the results represented in Fig.~\ref{fig:completeness}, we select the minimum magnitudes for complete recording,  $M_c$ , is 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively.
+% Based on the results represented in Fig.~\ref{fig:completeness}, we select the minimum magnitudes for complete recording,  $M_c$ , is 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively.
 Fig.~\ref{fig:mag-time}  shows the magnitude time series of the declustered data for the three regions.
@@
 
-\begin{figure*}[t]
-	\centering
-	\includegraphics[scale=0.8]{figures/pdf/Figure06.pdf} 
-	\caption{Variation of moment magnitude ($M_w$) of 2005-2015 earthquake for north Iran as a function of time.
+% \begin{figure*}[t]
+% 	\centering
+% 	\includegraphics[scale=0.8]{figures/pdf/Figure06.pdf} 
+% 	\caption{Variation of moment magnitude ($M_w$) of 2005-2015 earthquake for north Iran as a function of time.
 The figure only represents the declustered events greater than minimum magnitude.
 The 2012 $M_w 6.4$ East Azerbaijan, 2010 $M_w 5.8$ Damghan, and 2012 $M_w 5.4$ Neyshabur earthquakes are clearly visible as maximum values in Azerbaijan (Az),  Alborz (Az), and Kopeh Dagh (Ko) magnitude-time series.}
-	\label{fig:mag-time}
-\end{figure*}
+% 	\label{fig:mag-time}
+% \end{figure*}

### 2016-08-17 seismicity.tex
half way through section about seismicity and catalog

@@
 According to the tectonic settings and geologic provinces of the plateau, the seismic activity in Iran has been categorized into different seismic zones.
-These vary between four to nine major seismic zones, in the more traditional models \citep[e.g.,][]{Stocklin1968, Takin1972, Berberian1976}; and up to twenty to twenty-three seismotectonic provinces in the most elaborate models \citep[e.g.,][]{Nowroozi1976, Tavakoli1999}.
-We adopt the model proposed by \citet{Mirzaei1998} with modifications introduced by \citet{Karimiparidari2013}, in which Iran is divided into six tectonic regions: Azerbaijan, Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
+These vary between four to nine major seismic zones, in the more traditional models \citep[e.g.,][]{Stocklin1968, Takin1972, Berberian1976}, up to twenty to twenty-three seismotectonic provinces in the most elaborate ones \citep[e.g.,][]{Nowroozi1976, Tavakoli1999}.
+We adopt the model proposed by \citet{Mirzaei1998} with modifications introduced by \citet{Karimiparidari2013}.
+In it, Iran is divided into six seismic regions: Azerbaijan, Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
 Our focus, however, is on the northern part of Iran, for which we define a region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:study_region}.
-Although this region encloses part of the Zagros and Central-East Iran seismic zones, we will concentrate in the analysis of the seismicity of Azerbaijan, Alborz and Kopeh-Dagh.
+Although this region encloses part of the Zagros and Central-East seismic zones, we concentrate in the analysis of the seismicity of Azerbaijan, Alborz and Kopeh-Dagh.
 
@@
 	\includegraphics[width=\textwidth]{figures/pdf/figure-02} 
-	\caption{Region of interest.
-and tectonic seismic regions.
-At the top, the map of Iran and surrounding countries is presented.
-The study area is located in the gray box.
-At the bottom, the study area containing seismotectonic provinces after \citet{Mirzaei1998} is presented.
-Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
+	\caption{Region of interest, highlighting the seismic zones that are the focus of this study (Azerbaijan, Alborz, and Kopeh-Dagh) for the application of the visibility graph method.
+The top-right location map shows Iran and the selected area with respect to neighboring countries.
+The solid dark lines show the boundaries of the additional Zagros and Central-East seismic zones.
+This zonation follows the divisinos proposed and madofied by \citet{Mirzaei1998} and \citet{Karimiparidari2013}, respectively.}
 	\label{fig:study_region}
@@
 
+Northern Iran houses about 41 percent (32 million) of the total population of the country, and has suffered devastating earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}.
+At the northwest, the seismic zone of Azerbaijan is strongly controlled by the North Tabriz Fault system in the vicinity of the city of Tabriz, shown in Fig.~\ref{fig:study_region}.
+Historical accounts document the occurrence of strong $M>6$ earthquakes in this region as far back as the ninth century \citep{Berberian1999}, and a few $M>7$ earthquakes in 1042, 1721 and 1780 \citep{Jones1834}.
+More recently, this region was struck by the $M_w$ 6.1 1997 Ardabil earthquake near the city of Ardabil and $M_w$ 6.4 2012 Tabriz earthquake northeast of the city of Tabriz.
+These earthquakes caused extensive damage and took the lives of more than 1500 people.
+
+The seismicity in the north-central region of Alborz is dominated by multiple fault systems, including the Talesh, Rubdar, North Alborz, and North Tehran faults, which also have a history of producing strong ground shaking.
+According to \citet{Ambraseys_1982_Book}, Tehran was devastated by severe $M>7$ earthquakes in 743, 958, 1177, 1665, and 1830.
+This region has also seen some significant recent seismic activity \citep{Berberian1999}, including the $M_w$ 7.4 1990 Manjil-Rudbar earthquake, which caused numerous deaths and damage to the region in the south Caspian depression, south from the city of Rasht and northwest from Tehran.
+
+Last, there is the Kopeh-Dagh seismic zone to the east and northeast.
+This region is dominated by the Main Kopeh-Dagh Fault system, which exhibits active tectonic displacements along a distance of more than 500 km \citep{Trifonov1978}.
+This fault is responsible for the $M_w$ 7.3 1948 earthquake, which struck the capital city of Ashgabat in Turkmenistan and destroyed more than 30 villages in Iran.
+Historically, the Kopeh-Dagh seismic zone is also responsible for the $M_s$ 7.1 earthquake in 10 A.D.~\citep{Berberian2001} near Ashgabat, and two significant earthquakes in 1209 and 1405 at the boundary between the Neyshabur and Binalud faults near the city of Mashhad \citep{Berberian1999}.
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=\textwidth]{figures/pdf/figure-03} 
+	\caption{Declustered instrumental seismicity of northern Iran for the 2005--2015 period, considering only the events in the seismic zones of interest, namely Azerbaila, Alborz, and Kopeh-Dagh.
+The size of symbols are proportional to the magnitude of the events, as indicated by the artificial scale shown on the right.}
+	\label{fig:seismicity}
+\end{figure*}
+
 % \section{Tectonic seismic regions and seismicity parameters}
-
-% The Iranian plateau is located on the Himalayan-Alpine seismic belt.
-It has a long history of large magnitude ($M>7$) earthquakes that are well documented dating back to the eighth century.
-Based on seismicity parameters and the geologic provinces of the plateau, Iranian earthquakes have been categorized into various seismic zones, ranging from the definition of four to nine major seismic zones in the more traditional studies \citep[e.g.,][]{Stocklin1968,Takin1972,Berberian1976}, and up to twenty to twenty-three tectonic seismic regions in the most elaborate ones \citep[e.g.,][]{Nowroozi1976,Tavakoli1999}.
-\citet{Mirzaei1998},  dividing Iran into five tectonic regions, called Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
-Considering the division of  \citet{Mirzaei1998} as a reference,  \citet{Karimiparidari2013}  divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and the Alborz Mountain Range (hereinafter, Alborz).
-Azerbaijan, Alborz, and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.
-Fig.~\ref{fig:study_region} shows the study area and tectonic seismic regions.
-
-% The Alborz tectonic seismic region has active reverse faults, which are parallel to the northwest-trending structural gain of the Alborz Mountains belt.
-The North Tehran Thrust adds more complexity due to the presence of south-dipping reverse faults, which are in part blind, such as the Davudieh, Shian, and Bagh-E Feyz.
-The northwest continuation of the Alborz Mountains, known as the Rocks of the Talesh Mountains, have been thrust northeastward and eastward over rocks of the south Caspian depression  \citep{Berberian1999}.\\
-% The Tabriz region (located in the Azerbaijan tectonic seismic region) is in the Araxes structural block of northwestern Iran, southwest of the continuation of the western Alborz Mountains toward the Caucasus.
-The North Tabriz Fault (NTF) is a complex northwest-trending structure, which contains evidence observed on aerial photographs, and vertical displacement with the north side up, of right-lateral strike-slip displacement  \citep{Berberian1999}.
-
-% The main Kopeh-Dagh fault consists of several partly overlapping segments parallel to the overall  NW - SE  structure with step-overs.
-The regions of overlap are characterized by shorter south-dipping thrust faults, striking roughly E - W  \citep{Berberian2001}.
-\citet{Trifonov1978} reported active displacement along the main Kopeh-Dagh fault for more than 500 km.
-Main fault lines and fault systems in the interest region is represented in Fig.~\ref{fig:faults}.
 

### 2016-08-17 seismicity.tex
working...

@@
 \end{figure*}
+
+It follows from this that the region of interest is one of significant seismic activity, which goes back centuries.
+We are, however, interested in the most recent instrumental seismicity.
+In particular, we focus on events recorded in the last decade, between January 2005 and December 2015.
+We downloaded a catalog of recorded earthquakes
 

### 2016-08-18 introduction.tex
almost done with seismicity section

@@
 
-In this article we use the visibility graph method to analyze the seismicity of northern Iran for the 2005--2015 period.
-We focus our analysis on the last decade period because previous studies using seismic catalogs for the region of interest have shown that this period has the most complete datasets, especially for the case of small $M<4$ earthquakes \citep[e.g.][]{Khoshnevis2016}.
+In this article we use the visibility graph method to analyze the seismicity of northern Iran from 2005 to 2015.
+We focus our analysis on these years window because in a previous study we observed the latest decade of seismic records in the region offered the most complete catalog of events \citep[e.g.][]{Khoshnevis2016}.
 Upon a brief review of the basic concepts of the method and its applications, we describe the seismicity of northern Iran considering three dominant seismic areas, namely: Azerbaijan, Alborz, and Kopeh Dagh.

### 2016-08-18 methodology.tex
almost done with seismicity section

@@
 	\includegraphics[width=0.8\textwidth]{figures/pdf/figure-01} 
-	\caption{Illustration of the visibility graph method, as applied to a subset of events in a window of the magnitude-time series of the north Iranian seismic region of Kopeh Dagh.
+	\caption{Illustration of the visibility graph method, as applied to a subset of events in a window of the magnitude-time series of the north Iranian seismic region of Kopeh-Dagh.
 The events are identified by vertical thick lines (or sticks) on the horizontal time axis with size equal to the magnitude as indicated by the labels at the bottom of each stick.
@@
 The mean <$T_c^e$> value associated with this event is also shown at the top right.
-The mean value of all <$T_c^e$> for the events in the graph is the window mean interval connectivity time, <$T_c^e$>.}
+The mean value of all <$T_c^e$> for the events in the graph is the window mean interval connectivity time, <$T_c^e$>.
+The color version of this figure is available only in the electronic edition.}
 	\label{fig:vg}

### 2016-08-18 seismicity.tex
almost done with seismicity section

@@
 	\includegraphics[width=\textwidth]{figures/pdf/figure-02} 
-	\caption{Region of interest, highlighting the seismic zones that are the focus of this study (Azerbaijan, Alborz, and Kopeh-Dagh) for the application of the visibility graph method.
-The top-right location map shows Iran and the selected area with respect to neighboring countries.
+	\caption{Region of interest, highlighting the seismic zones that are the focus of this study: Azerbaijan, Alborz, and Kopeh-Dagh.
+The top-right location-map shows Iran and the selected area with respect to neighboring countries.
 The solid dark lines show the boundaries of the additional Zagros and Central-East seismic zones.
-This zonation follows the divisinos proposed and madofied by \citet{Mirzaei1998} and \citet{Karimiparidari2013}, respectively.}
+This zonation follows the division proposed by \citet{Mirzaei1998} and later modified by \citet{Karimiparidari2013}.
+The background shows fault lines and the shaded relief.
+The color version of this figure is available only in the electronic edition.}
 	\label{fig:study_region}
@@
 	\caption{Declustered instrumental seismicity of northern Iran for the 2005--2015 period, considering only the events in the seismic zones of interest, namely Azerbaila, Alborz, and Kopeh-Dagh.
-The size of symbols are proportional to the magnitude of the events, as indicated by the artificial scale shown on the right.}
+The size of symbols are proportional to the magnitude of the events, as indicated by the artificial scale shown on the right.
+The background shows fault lines and the shaded relief.
+The color version of this figure is available only in the electronic edition.}
 	\label{fig:seismicity}
@@
 
-It follows from this that the region of interest is one of significant seismic activity, which goes back centuries.
+It follows from this description that the region of interest is one of significant seismic activity, which goes back centuries.
 We are, however, interested in the most recent instrumental seismicity.
 In particular, we focus on events recorded in the last decade, between January 2005 and December 2015.
-We downloaded a catalog of recorded earthquakes
+We focus our analysis on this magnitude-time sequence period because in a previous study we observed that the latest decade of seismic records in northern Iran offered the most complete dataset of recorded events, especially for the case of small $M < 4$ earthquakes \citep[e.g.][]{Khoshnevis2016}.
 
-% \section{Tectonic seismic regions and seismicity parameters}
+We compiled a catalog of recorded earthquakes with magnitude $M>3$ using data downloaded from the International Institute of Earthquake Engineering and Seismology, IIEES (see the Data and Resources section).
+The obtained dataset contained a mixture of earthquake magnitude scales, including: moment, $M_w$; local, $M_L$; body wave, $m_b$; surface wave, $M_s$; and duration $M_D$ magnitudes.
+We converted all earthquakes to moment magnitude, $M_w$.
+Magnitudes in the $M_L$, $m_b$, and $M_s$ scales were converted using the relationships defined in \citet{Zare2014}, whereas $M_D$ magnitudes were converted using the empirical relationship proposed by \citet{Deniz2010}.
 
-% \begin{figure*}[t]
-% \centering
-% \includegraphics[scale=1]{figures/pdf/Figure03.pdf} 
-% \caption{Main fault line and fault system in the region of interest. The borderlines of the seismic zones shown in Fig.~\ref{fig:study_region} are shown in background in gray.}
-% \label{fig:faults}
-% \end{figure*}
+Foreshocks and aftershocks were removed from the catalog following a Poissonian occurrence model using the declustering method of \citet{Gardner1974}, in a manner consistent with previous catalog compilations for the region \citep[e.g.,][]{Zare2014}.
+Upon declustering, we divide the catalog into three sub-catalogs, each for one of the seismic zones under consideration.
+Fig.~\ref{fig:seismicity} shows the epicenter location of declustered instrumental earthquakes for the three seismic zones of interest.
 
-% \subsection{Magnitude Conversion}
+We then proceeded to determine the minimum magnitude of completeness, $M_c$, for each region's sub-catalog.
+The value of $M_c$ is often determined using simple numerical analyses in combination with data inspection.
+Two common approaches are the maximum curvature (MAXC) and the goodness-of-fit test (GFT) methods \citep{Wiemer2001}.
+We use the GFT method as introduced by \citet{Wiemer2000}.
+In this method, the completeness magnitude is obtained such that the catalog satisfies---at a certain acceptance threshold---the Gutenberg-Richter power low, given an extended dataset of events.
+This extended dataset is composed of predicted and observed events, where the predicted events are generated based on a trial minimum magnitude.
+The process is repeated for increasing values of the reference minimum magnitude until finding a desirable fit with the power law.
+\citet{Wiemer2000} suggests a goodness of fit of 90\% as an acceptable threshold to select $M_c$.
+However, not all frequency-magnitude distributions reach the 90\% mark, in which case $M_c$ can be selected by inspection.
 
-% The catalog of recorded earthquakes from 2005-15, downloaded from IIEES, reported earthquakes based on different magnitude scales \citep{IIEES}.
-The  $M_L$,  $M_S$, and  $mb$  magnitudes were converted through conversion relationships, as defined in  \citet{Zare2014}.
-Some data were also recorded in  $M_D$  (duration magnitude).
-These data are reported by the International Seismological Centre (ISC).
-\citet{Deniz2010}  developed a set of empirical equations to convert earthquake magnitudes from  $mb$,  $M_D$,  $M_L$, and  $M_S$  scales to  $M_W$  scale using the orthogonal regression procedure.
-They used data from different data centers, including the ISC, of earthquakes that occurred in Turkey.
-In this study, we use the conversion equation of  \citet{Deniz2010}  to convert  $M_D$  to  $M_W$.
+Figure \ref{fig:completeness} shows the goodness-of-fit values for the three seismic zones.
+We indicate the selected value of $M_c$ for each region in the figure.
+We also obtained the $b$-value in the Gutenberg-Richter law for each region following the maximum likelihood estimation \citep{Aki1965}:
+% 
+\begin{equation}
+	b = \frac{log_{10}(e)}{\overline{M} - M_{min}} \, ,
+\end{equation}
+% 
+where $e$ is the mathematical constant or Euler's number, $\overline{M}$ is the average magnitude, and $M_{\min}$ is the minimum magnitude in the sample.
+Here, the value of $M_{\min}$ is the taken as the minimum completeness magnitude $M_c$ obtained or selected for each region's sub-catalog.
+Table \ref{tab:seismicity} shows the number of declustered events for each region, and the corresponding values of $M_c$ and $b$.
 
-% \subsection{Declustering}
+\begin{table}[h]
+	\fontfamily{lmss}\selectfont
+	\caption{Declustered number of earthquakes and seismic parameters for the three seismic zones of northern Iran.}
+	\centering\small
+	\begin{tabular}{|cccc|}
+		\hline
+		Region      & Num.      & \textit{M}c & \textit{b}-value \\ 
+		            & of Events &             &                  \\
+		\hline
+		Azerbaijan  &        93 &         3.5 &             1.02 \\
+		Alborz      &       794 &         2.6 &             0.77 \\
+		Kopeh Dagh  &       282 &         2.6 &             0.58 \\
+		\hline
+	\end{tabular}
+	\label{tab:seismicity}
+\end{table}
 
-% It is generally assumed that the seismicity of each tectonic seismic source follows a Poissonian occurrence process.
-Therefore, in order to accomplish this, we decluster the earthquake catalog.
-In compiling the catalog of events, foreshocks and aftershocks are removed using a declustering methodology  presented by \citet{Gardner1974}.
-Fig.~\ref{fig:seismicity}  shows the epicenter of declustered instrumental  earthquakes.
-
-% \begin{figure*}[t]
-% \centering
-% \includegraphics[scale=1]{figures/pdf/Figure04.pdf} 
-% \caption{Declustered instrumental seismicity map (2005 - 2015) of northern Iran.
-Different colors indicate the seismicity of different regions.
-Size of symbols are proportional to the magnitude of the events.}
-% \label{fig:seismicity}
-% \end{figure*}
-
-% \subsection{Catalog Completeness}
-
-% Catalog completeness is an important factor in studying an earthquake sequence.
-This characteristic measured as the minimum magnitude of complete recording for earthquake catalog.
-The completeness magnitude $(M_c)$ is often determined using simple numerical analysis.
-Two common approaches are maximum curvature method (MAXC) and goodness-of-fit test (GFT)(see \citet{Wiemer2000}).
-We use the Goodness-of-fit test and compute $M_c$ for each region's catalog.
-According to the GFT method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude.
-The steps for selecting the completeness magnitude for each catalog include: 1) calculating the a-  and  b-  value based on minimum magnitude; 2) generating  synthetic events based on the achieved value when the cumulative number of events obey the power law distribution; and 3) calculating goodness of fit for predicted and observed cumulative numbers for each magnitude bin  \citep{Wiemer2000}.
-We increase the minimum magnitude and repeat the process in order to calculate the goodness of fit for each magnitude.
-\citet{Wiemer2000} assumed a goodness of fit of 90\% as a threshold to select the completeness of the catalog.
-However,  not all frequency-magnitude distributions reach the 90\% mark.
-Fig.~\ref{fig:completeness} shows the goodness-of-fit values for three tectonic seismic regions.
-For each tectonic seismic region, we select the magnitude corresponding to the highest goodness of fit or the first magnitude with the goodness of fit greater than 90\%.
-
-% \begin{figure}[t]
-% \centering
-% \includegraphics[width=0.45\textwidth]{figures/pdf/Figure05.pdf} 
-% \caption{ Selection of completeness magnitude $M_c$ of the three tectonic seismic regions in northern Iran in 2005-15 period.
+\begin{figure}%[t]
+	\centering
+	\includegraphics[width=0.45\textwidth]{figures/pdf/Figure05.pdf} 
+	\caption{Selection of completeness magnitude $M_c$ of the three tectonic seismic regions in northern Iran in 2005-15 period.
 The symbols indicate the computed GFT values as function of the earthquake magnitude.
@@
 The vertical dashed lines indicate the completeness magnitude of each tectonic seismic region.}
-% \label{fig:completeness}
-% \end{figure}
+	\label{fig:completeness}
+\end{figure}
 

### 2016-08-18 seismicity.tex
ompleted revision of seismicity section

@@
 
-\begin{table}[h]
+\begin{figure}%[t]
+	\centering
+	\includegraphics[width=0.45\textwidth]{figures/pdf/figure-04} 
+	\caption{Completeness magnitude goodness-of-fit test (GFT) results and selected $M_c$ values for the three tectonic seismic regions in northern Iran as evaluated from the time-magnitude sequence of earthquakes during the 2005--2015 period.
+The symbols indicate the computed GFT values as function of the earthquake magnitude.
+The horizontal dashed line indicates the desired threshold for the GFT value at 90 percent.
+The vertical dashed lines and solid symbols indicate the selected completeness magnitude for each region.
+The color version of this figure is available only in the electronic edition.}
+	\label{fig:completeness}
+\end{figure}
+
+\begin{table}
 	\fontfamily{lmss}\selectfont
@@
 
-\begin{figure}%[t]
+\begin{figure*}[t]
 	\centering
-	\includegraphics[width=0.45\textwidth]{figures/pdf/Figure05.pdf} 
-	\caption{Selection of completeness magnitude $M_c$ of the three tectonic seismic regions in northern Iran in 2005-15 period.
-The symbols indicate the computed GFT values as function of the earthquake magnitude.
-The horizontal dashed line indicates the desired threshold for the goodness of fit value at 90 percent.
-The vertical dashed lines indicate the completeness magnitude of each tectonic seismic region.}
-	\label{fig:completeness}
-\end{figure}
+	\includegraphics[width=\textwidth]{figures/pdf/figure-05} 
+	\caption{Time-magnitude sequences for the northern Iran seismic zones of Azerbaijan, Alborz and Kopeh-Dagh, during the period between 1 January 2005 and 31 December 2015.
+The event occurrences are represented by vertical bars or sticks of length equal to the $M_w$ magnitude of each earthquake.
+These sequences correspond to the declustered catalog but in each case we consider only events with $M_w \geq M_c$.
+As shown in Fig.~\ref{fig:vg}, the dots at the top of each stick represent the nodes of the visibility graphs.
+The edges or links are omitted for visual convenience.
+Highlighted in the figure are the largest events in each sub-catalog, namely the 2012 $M_w 6.4$ East Azerbaijan, 2010 $M_w 5.8$ Damghan, and 2012 $M_w 5.4$ Neyshabur earthquakes.
+The color version of this figure is available only in the electronic edition.}
+	\label{fig:mag-time}
+\end{figure*}
 
-% Based on the results represented in Fig.~\ref{fig:completeness}, we select the minimum magnitudes for complete recording,  $M_c$ , is 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively.
-Fig.~\ref{fig:mag-time}  shows the magnitude time series of the declustered data for the three regions.
-Earthquakes with magnitude greater than the completeness magnitude are represented.
-
-% \begin{figure*}[t]
-% 	\centering
-% 	\includegraphics[scale=0.8]{figures/pdf/Figure06.pdf} 
-% 	\caption{Variation of moment magnitude ($M_w$) of 2005-2015 earthquake for north Iran as a function of time.
-The figure only represents the declustered events greater than minimum magnitude.
-The 2012 $M_w 6.4$ East Azerbaijan, 2010 $M_w 5.8$ Damghan, and 2012 $M_w 5.4$ Neyshabur earthquakes are clearly visible as maximum values in Azerbaijan (Az),  Alborz (Az), and Kopeh Dagh (Ko) magnitude-time series.}
-% 	\label{fig:mag-time}
-% \end{figure*}
+In addition to using $M_c$ to determine the $b$-value for each sub-catalog, we also use $M_c$ as the threshold for limiting the minimum magnitude to be considered in the construction of the visibility graph of each region.
+Figure \ref{fig:mag-time} shows the final time-magnitude sequences for Azerbaijan, Alborz and Kopeh-Dagh.
+Note that in the case of Alborz and Kopeh-Dagh, we consider events in the declustered catalog down to $M_w \geq 2.6$, whereas in the case of Azerbaijan all events are $M_w \geq 3.5$.
+We omit showing the graph links as it will make the figure difficult to interpret, but rely on the example we presented on Fig.~\ref{fig:vg}.

### 2016-08-19 acknowledgements.tex
started with results section, added improved figure 6

@@
-\section{Acknowledgements}
+\section{Acknowledgments}
 
-We greatly appreciate the International Institute of Earthquake Engineering and Seismology (IIEES) in Tehran for maintaining and providing access to the seismic catalog.
-This research was possible thanks to support by the Center for Earthquake Research and Information (CERI) at the University of Memphis.
-CERI is designated as a Center of Excellence by the Tennessee Board of Regents and is funded in part by the State of Tennessee under State Sunsent Laws (SB 1510 and HB 1608, 2015--2016).
+This research was possible thanks to support from the Center for Earthquake Research and Information (CERI) at the University of Memphis.
+CERI is designated as a Center of Excellence by the Tennessee Board of Regents and is funded in part by the State of Tennessee under State Sunset Laws (SB 1510 and HB 1608, 2015--2016).

### 2016-08-19 data-and-resources.tex
started with results section, added improved figure 6

\section{Data and Resources}

Data used to compile the seismic catalog employed in the analysis was obtained using the Web browser search application from the International Institute of Earthquake Engineering and Seismology, IIEES (\url{http://www.iiees.ac.ir/en/eqcatalog/}, last accessed September 2016). The raw versions of figures were prepared using MATLAB\textsuperscript{\textregistered}, release 13b; and the Generic Mapping Tools, version 5.1 \citep[\url{http://gmt.soest.hawaii.edu;}][]{Wessel_2013_EOS}. Final versions of figures were prepared using Adobe\textsuperscript{\textregistered} Illustrator\textsuperscript{\textregistered}.

### 2016-08-19 results.tex
started with results section, added improved figure 6

@@
 
-We generated the visibility graph parameters for three tectonic seismic regions in northern Iran for the period 2005-15.
+We generate the visibility graph based on the sub-catalog data shown in the time-magnitude sequences in Fig.~\ref{fig:mag-time} for the regions of Azerbaijan, Alborz and Kopeh-Dagh.
+The number of nodes in each graph is the same as the number of events shown in Table \ref{tab:seismicity}.
+Although we omit a visualization of the graphs, we collect information about the number of inter-visibility links associated to each event and categorize the events in magnitude bins of size $\Delta M = 0.1$ as explained in the Methodology section.
+Figure \ref{fig:km} shows the...
+
+% We generated the visibility graph parameters for three tectonic seismic regions in northern Iran for the period 2005-15.
 The number of earthquakes in each catalog after declustering and their seismicity parameters is presented in Table.~\ref{tab:b_k_m_param}.
 
-\begin{table}[h]
-	\centering
-	\caption{Declustered number of earthquakes, seismic parameters and $k-M$ slope values for north Iran tectonic seismic zones.}
-	\begin{tabular}{ccccc}
-		Region      & Num.~of Earthq. &  $Mc$ & $b$-value & $k-M$ slope \\ 
-		\hline
-		Azerbaijan  & 93              & 3.5   & 1.0190    & 9.2004      \\
-		Alborz      & 794             & 2.6   & 0.7717    & 9.0461      \\
-		Kopeh Dagh  & 282             & 2.6   & 0.5799    & 6.5818      \\
-		\hline
-	\end{tabular}
-	\label{tab:b_k_m_param}
-\end{table}
-
-Fig.~\ref{fig:k_m_plot_m}  shows the  $k-M$  relationship for the study regions.
+% Fig.~\ref{fig:k_m_plot_m}  shows the  $k-M$  relationship for the study regions.
 It is clear from the Fig.~\ref{fig:mag-time} that the specific magnitude bin can result in different connectivity degrees regarding the occurring time of the earthquake event.
@@
 	\centering
-	\includegraphics[scale=0.35]{figures/pdf/Figure07.pdf} 
+	\includegraphics[width=\textwidth]{figures/pdf/figure-06} 
 	\caption{ $k-M$ relationship for north Iran tectonic seismic regions.
@@
 The numbers on the lines is the slope of the regression lines.}
-	\label{fig:k_m_plot_m}
+	\label{fig:km}
 \end{figure*}
 
-We compared the  $k$-$M$  slope with the  $b$-value  of the Gutenberg-Richter law through the entire catalog and in the sliding windows in time.
+% We compared the  $k$-$M$  slope with the  $b$-value  of the Gutenberg-Richter law through the entire catalog and in the sliding windows in time.
 The $b$-value is generated through the maximum likelihood estimation \citep{Aki1965}.
 
-\begin{equation}
-	b = \frac{log_{10}(e) }{\overline{M} - M_{min}},
-\end{equation}
+% \begin{equation}
+% 	b = \frac{log_{10}(e) }{\overline{M} - M_{min}},
+% \end{equation}
 
-\noindent
-where $e$ is the mathematical constant, $\overline{M}$ is the average magnitude, and  $M_ {min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic region.
+% \noindent
+% where $e$ is the mathematical constant, $\overline{M}$ is the average magnitude, and  $M_ {min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic region.
 The number of sequences and threshold magnitudes is considerably different for all tectonic seismic regions.
@@
 
-In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, we randomly picked 200 sequences from the catalogs with various sequence sizes.
+% In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, we randomly picked 200 sequences from the catalogs with various sequence sizes.
 Number of events at each sequence should be low enough to be able to choose 200 random sequence from the catalog (note that the number of events in each catalog, before removing the events with magnitude less than the completeness magnitude, is 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively).
@@
 
-\begin{figure*}[t]
-	\centering
-	\includegraphics[scale=0.5]{figures/pdf/Figure08.pdf} 
-	\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence.
+% \begin{figure*}[t]
+% 	\centering
+% 	\includegraphics[scale=0.5]{figures/pdf/Figure08.pdf} 
+% 	\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence.
 The numbers on the mean and standard deviation plots are coefficient of variations in percent $(standard \ deviation / mean)$.}
-	\label{fig:random}
-\end{figure*}
+% 	\label{fig:random}
+% \end{figure*}
 
-The coefficient of variation of parameters is shown in Fig.~\ref{fig:random}.
+% The coefficient of variation of parameters is shown in Fig.~\ref{fig:random}.
 The  $k-M$  slope shows the higher coefficient of variation which indicates the fact that the  $k-M$  slope is more dependent on the window size and threshold magnitude than on the a-  and  b-values , which suggests that  the $k-M$  slope can better represent the dynamic characteristics of the magnitude-time series.
 
-Fig.~\ref{fig:regression} shows the relationship between the  $k-M$  slope and $b-value$ for the three tectonic seismic regions in northern Iran and three other studies of Mexican zones  \citep{Telesca2013}, Pannonia zones  \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}.
+% Fig.~\ref{fig:regression} shows the relationship between the  $k-M$  slope and $b-value$ for the three tectonic seismic regions in northern Iran and three other studies of Mexican zones  \citep{Telesca2013}, Pannonia zones  \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}.
 Adding the results of the current study into the results of three previous similar studies improves the regression factor, and empowers the concept of the universal character of the relationship between the  $b-value$  and the  $k-M$  slope, as  \citet{Telesca2014} concluded.
 
-\begin{figure*}[t]
-	\centering
-	\includegraphics[scale=0.6]{figures/pdf/Figure09.pdf} 
-	\caption{ Relationship between $k-M$ slope and $b-value$ of three Iranian tectonic seismic zones (this study) and three other studies of Mexican zones \citep{Telesca2013}, Pannonia zones \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}.
+% \begin{figure*}[t]
+% 	\centering
+% 	\includegraphics[scale=0.6]{figures/pdf/Figure09.pdf} 
+% 	\caption{ Relationship between $k-M$ slope and $b-value$ of three Iranian tectonic seismic zones (this study) and three other studies of Mexican zones \citep{Telesca2013}, Pannonia zones \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}.
 The lines represent the linear regression fit of data.
 The correlation coefficients (R) are represented for different combination of data.}
-	\label{fig:regression}
-\end{figure*}
+% 	\label{fig:regression}
+% \end{figure*}
 
-Fig.\ref{fig:tc} shows the variation of the  $k-M$  slope and  $b-value$  with time.
+% Fig.\ref{fig:tc} shows the variation of the  $k-M$  slope and  $b-value$  with time.
 Due to lower number of events in Azerbaijan's catalog, we choose 20 events as the window length with a shift of one event between two successive windows.
@@
 
-\citet{Telesca2016}  observed the decrease in  $<T_c>$  before the large earthquake of the western India earthquake sequence.
+% \citet{Telesca2016}  observed the decrease in  $<T_c>$  before the large earthquake of the western India earthquake sequence.
 Fig.\ref{fig:tc}  shows the time variation of  $<T_c>$   in the study area.
@@
 
-\begin{figure*}[t]
-	\centering
-	\includegraphics[scale=0.4]{figures/pdf/Figure10.pdf} 
-	\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_c >$ (Right) as a function of time for three tectonic seismic regions in north Iran.
+% \begin{figure*}[t]
+% 	\centering
+% 	\includegraphics[scale=0.4]{figures/pdf/Figure10.pdf} 
+% 	\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_c >$ (Right) as a function of time for three tectonic seismic regions in north Iran.
 Black arrows show the occurrence of the major earthquakes.
@@
 Decreasing the value of  $<T_c>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions.}
-	\label{fig:tc}
-\end{figure*}
+% 	\label{fig:tc}
+% \end{figure*}

### 2016-08-19 results.tex
revised figure 7

@@
 	\includegraphics[width=\textwidth]{figures/pdf/figure-06} 
-	\caption{ $k-M$ relationship for north Iran tectonic seismic regions.
+	\caption{$k-M$ relationship for north Iran tectonic seismic regions.
 The blue circles indicate the connectivity degrees.
@@
 
-% \begin{figure*}[t]
-% 	\centering
-% 	\includegraphics[scale=0.5]{figures/pdf/Figure08.pdf} 
-% 	\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence.
+\begin{figure*}%[t]
+	\centering
+	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-07} 
+	\caption{Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence.
 The numbers on the mean and standard deviation plots are coefficient of variations in percent $(standard \ deviation / mean)$.}
-% 	\label{fig:random}
-% \end{figure*}
+	\label{fig:random}
+\end{figure*}
 

### 2016-08-19 results.tex
improved new figure 8

@@
 
-% \begin{figure*}[t]
-% 	\centering
-% 	\includegraphics[scale=0.6]{figures/pdf/Figure09.pdf} 
-% 	\caption{ Relationship between $k-M$ slope and $b-value$ of three Iranian tectonic seismic zones (this study) and three other studies of Mexican zones \citep{Telesca2013}, Pannonia zones \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}.
+\begin{figure}[h]%[t]
+	\centering
+	\includegraphics[width=0.45\textwidth]{figures/pdf/figure-08} 
+	\caption{Relationship between $k-M$ slope and $b-value$ of three Iranian tectonic seismic zones (this study) and three other studies of Mexican zones \citep{Telesca2013}, Pannonia zones \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}.
 The lines represent the linear regression fit of data.
 The correlation coefficients (R) are represented for different combination of data.}
-% 	\label{fig:regression}
-% \end{figure*}
+	\label{fig:regression}
+\end{figure}
 

### 2016-08-20 results.tex
finished new  figure 9

@@
 
-% \begin{figure*}[t]
-% 	\centering
-% 	\includegraphics[scale=0.4]{figures/pdf/Figure10.pdf} 
-% 	\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_c >$ (Right) as a function of time for three tectonic seismic regions in north Iran.
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=\textwidth]{figures/pdf/figure-09} 
+	\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_c >$ (Right) as a function of time for three tectonic seismic regions in north Iran.
 Black arrows show the occurrence of the major earthquakes.
@@
 Decreasing the value of  $<T_c>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions.}
-% 	\label{fig:tc}
-% \end{figure*}
+	\label{fig:tc}
+\end{figure*}

### 2016-08-21 results.tex
working on last versions of figures in and on results section

@@
 
-We generate the visibility graph based on the sub-catalog data shown in the time-magnitude sequences in Fig.~\ref{fig:mag-time} for the regions of Azerbaijan, Alborz and Kopeh-Dagh.
-The number of nodes in each graph is the same as the number of events shown in Table \ref{tab:seismicity}.
-Although we omit a visualization of the graphs, we collect information about the number of inter-visibility links associated to each event and categorize the events in magnitude bins of size $\Delta M = 0.1$ as explained in the Methodology section.
-Figure \ref{fig:km} shows the...
-
-% We generated the visibility graph parameters for three tectonic seismic regions in northern Iran for the period 2005-15.
-The number of earthquakes in each catalog after declustering and their seismicity parameters is presented in Table.~\ref{tab:b_k_m_param}.
-
-% Fig.~\ref{fig:k_m_plot_m}  shows the  $k-M$  relationship for the study regions.
-It is clear from the Fig.~\ref{fig:mag-time} that the specific magnitude bin can result in different connectivity degrees regarding the occurring time of the earthquake event.
-In general, with increasing magnitude, the connectivity degree increases, which increases the slope of the  $k-M$  relationship.
+We generate the visibility graph for each sub-regions of interest using the time-magnitude sequences shown in Fig.~\ref{fig:mag-time}.
+The number of nodes in each graph is the same as the (declustered) number of events shown in Table \ref{tab:seismicity}, and the links between intervisible events are established following the condition in Eq.~\ref{eq:vg}, as in the example shown in Fig.~\ref{fig:vg}.
+(We do not include a visualization of the complete sequence graphs because the links are so many, it is only practical to visualize the graphs of short sequences).
+We then collect information about the number of inter-visibility links associated to each event (connectivity degree, $k$) and categorize the events in magnitude bins of size $\Delta M = 0.1$ as mentioned in the Methodology section.
+Figure \ref{fig:km} shows the scattered distribution of events in the magnitude-connectivity degree plane.
+The figure shows that, in general, the value of $k$ increases with $M_w$.
+Figure \ref{fig:km} also shows the result of obtaining linear $k$-$M$ regressions for the datasets and the values of the $k$-$M$ slope for each of the three zones.
 
@@
 	\includegraphics[width=\textwidth]{figures/pdf/figure-06} 
-	\caption{$k-M$ relationship for north Iran tectonic seismic regions.
-The blue circles indicate the connectivity degrees.
-The red line is the linear regression line fits the data.
-The numbers on the lines is the slope of the regression lines.}
+	\caption{Scattered distribution of events in the magnitude-connectivity degree plane and the linear regressions obtained for the $k$-$M$ relationship for the three seismic regions in northern Iran.
+The values next to each of the regression lines corresponds to the slope of each line, which is referred here as the $k$-$M$ slope.
+The color version of this figure is available only in the electronic edition.}
 	\label{fig:km}
@@
 
+Next, we examine the relationship between the $b$-values and the from Table \ref{tab:seismicity} and the $k$-$M$ slope values shown in Fig.~\ref{fig:km}.
+Figure \ref{fig:regression} shows the scattered results for $k-M$ slope versus $b$-value for the three tectonic seismic regions in northern Iran along with the data-points obtained for analysis of the magnitude-time sequences of the Mexican subduction zone \citep{Telesca2013} and the Pannoninan seismic zone \citep{Telesca2014}, as well as other experimental results \citep{Telesca2014-pone}.
+Figure \ref{fig:regression} also include the results of different linear regressions between $b$ and the $k$-$M$ slope.
+Each regression shows the addition of new data-points from different studies over time, with the present study adding the latest set of data.
+Note that the regression improves as new data-points are added over time, which is indicated by the correlation coefficient $R$, whose values are also shown in the figure.
+This was previously pointed out by \citet{Telesca2014}.
+
+\begin{figure}[h]%[t]
+	\centering
+	\includegraphics[width=0.45\textwidth]{figures/pdf/figure-07} 
+	\caption{Relationship between $k-M$ slope and $b-value$ of three Iranian tectonic seismic zones (this study) and three other studies of Mexican zones \citep{Telesca2013}, Pannonia zones \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}.
+The lines represent the linear regression fit of data.
+The correlation coefficients (R) are represented for different combination of data.}
+	\label{fig:regression}
+\end{figure}
+
+\begin{center}
+* \hspace{2em} * \hspace{2em} *
+\end{center}
+
+Although the number of events vary significantly between the three zones (see Table \ref{tab:seismicity}, \citet{Telesca2013} observed that the value of the $k$-$M$ slope is not particularly sensitive to the sample size in the sequence---at least not when considering sufficiently large sequences.
+On the other hand, as we will see below, if the sequence window is sufficiently short, then the $k$-$M$ slope value shows a relative dependence on time and thus provides insight about the variation of the seismicity as the sequence progresses.
+Note also that the threshold value of $M_c$ is significantly smaller for Azerbaijan than for Alborz or Kopeh-Dagh.
+This is due in part to the fact that the latter two zones were more seismically active in the time period under consideration.
+However, according to \citet{Telesca2012}, the threshold magnitude has a minor effect in the graph parameters.
+
+To further explore the sensitivity of the graph properties to the number of events in each catalog and the value of the minimum magnitude to be considered, we randomly picked a significant number of sub-sequences from within the catalog of each region and repeated the analysis.
+This was done starting with the catalogs before declustering.
+In total, for each region, we extracted 200 new sub-sequences.
+The number of events in each sub-sequence was varied randomly but chosen to be large enough to represent the seismic characteristics of each seismic region.
+In particular, the minimum size of each subsequence was set to be $\geq 150$, whereas the maximum size in the sequence was set to be as large as the original (pre-declustering) catalog.
+We forced the random sub-sequences to progress positively in time without altering the natural occurrence of events.
+In other words, we randomly determined the initial event and the sub-sequence size (number of events to be considered), then picked that number of events following the initial event.
+Next, we determined the value of $M_c$ and $b$ and created the graph to extract the connectivity degree of the events in each sub-sequence.
+Figure \ref{fig:random}a shows...
+
+% =========
+
 % We compared the $k$-$M$ slope with the $b$-value of the Gutenberg-Richter law through the entire catalog and in the sliding windows in time.
-The $b$-value is generated through the maximum likelihood estimation \citep{Aki1965}.
 
-% \begin{equation}
-% 	b = \frac{log_{10}(e) }{\overline{M} - M_{min}},
-% \end{equation}
-
-% \noindent
-% where $e$ is the mathematical constant, $\overline{M}$ is the average magnitude, and  $M_ {min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic region.
-The number of sequences and threshold magnitudes is considerably different for all tectonic seismic regions.
-\citet{Telesca2013}  studied the effect of the number of earthquakes in the catalog on the  $k-M$  slope.
-Comparing the result with the Guerrero region with reduced random sequence,  \citet{Telesca2013}  found that the number of sequences did not affect the  $k-M$  slope.
-According to  \citet{Telesca2012}, the threshold magnitude has minor effect in the VG parameters.\\
+% Comparing the result with the Guerrero region with reduced random sequence,  \citet{Telesca2013}  found that the number of sequences did not affect the $k-M$ slope.
 
@@
 
+% The coefficient of variation of parameters is shown in Fig.~\ref{fig:random}.
+The  $k-M$  slope shows the higher coefficient of variation which indicates the fact that the  $k-M$  slope is more dependent on the window size and threshold magnitude than on the a-  and  b-values , which suggests that  the $k-M$  slope can better represent the dynamic characteristics of the magnitude-time series.
+
 \begin{figure*}%[t]
 	\centering
-	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-07} 
+	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-08} 
 	\caption{Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence.
@@
 
-% The coefficient of variation of parameters is shown in Fig.~\ref{fig:random}.
-The  $k-M$  slope shows the higher coefficient of variation which indicates the fact that the  $k-M$  slope is more dependent on the window size and threshold magnitude than on the a-  and  b-values , which suggests that  the $k-M$  slope can better represent the dynamic characteristics of the magnitude-time series.
-
-% Fig.~\ref{fig:regression} shows the relationship between the  $k-M$  slope and $b-value$ for the three tectonic seismic regions in northern Iran and three other studies of Mexican zones  \citep{Telesca2013}, Pannonia zones  \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}.
-Adding the results of the current study into the results of three previous similar studies improves the regression factor, and empowers the concept of the universal character of the relationship between the  $b-value$  and the  $k-M$  slope, as  \citet{Telesca2014} concluded.
-
-\begin{figure}[h]%[t]
-	\centering
-	\includegraphics[width=0.45\textwidth]{figures/pdf/figure-08} 
-	\caption{Relationship between $k-M$ slope and $b-value$ of three Iranian tectonic seismic zones (this study) and three other studies of Mexican zones \citep{Telesca2013}, Pannonia zones \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}.
-The lines represent the linear regression fit of data.
-The correlation coefficients (R) are represented for different combination of data.}
-	\label{fig:regression}
-\end{figure}
+% *******
 

### 2016-08-21 seismicity.tex
started with results section, added improved figure 6
working on last versions of figures in and on results section

@@
 Here, the value of $M_{\min}$ is the taken as the minimum completeness magnitude $M_c$ obtained or selected for each region's sub-catalog.
-Table \ref{tab:seismicity} shows the number of declustered events for each region, and the corresponding values of $M_c$ and $b$.
+Table \ref{tab:seismicity} shows the the corresponding values of $M_c$ and $b$.
 
@@
 	\fontfamily{lmss}\selectfont
-	\caption{Declustered number of earthquakes and seismic parameters for the three seismic zones of northern Iran.}
+	\caption{Total and declustered number of earthquakes and seismic parameters $M_c$ and $b$ for the three seismic zones of northern Iran.}
 	\centering\small
-	\begin{tabular}{|cccc|}
+	\begin{tabular}{|ccccc|}
 		\hline
-		Region      & Num.      & \textit{M}c & \textit{b}-value \\ 
-		            & of Events &             &                  \\
+		Region      & Total Num. & Declus.~Num. & \textit{M}c & \textit{b}-value \\ 
+		            & of Events  & of Events &             &                  \\
 		\hline
-		Azerbaijan  &        93 &         3.5 &             1.02 \\
-		Alborz      &       794 &         2.6 &             0.77 \\
-		Kopeh Dagh  &       282 &         2.6 &             0.58 \\
+		Azerbaijan  &        271 &        93 &         3.5 &             1.02 \\
+		Alborz      &       1262 &       794 &         2.6 &             0.77 \\
+		Kopeh Dagh  &        399 &       282 &         2.6 &             0.58 \\
 		\hline
@@
 In addition to using $M_c$ to determine the $b$-value for each sub-catalog, we also use $M_c$ as the threshold for limiting the minimum magnitude to be considered in the construction of the visibility graph of each region.
+The resulting number of events for each region is included in Table \ref{tab:seismicity}.
 Figure \ref{fig:mag-time} shows the final time-magnitude sequences for Azerbaijan, Alborz and Kopeh-Dagh.

### 2016-08-21 results.tex
improving figure 8

@@
 
-We generate the visibility graph for each sub-regions of interest using the time-magnitude sequences shown in Fig.~\ref{fig:mag-time}.
-The number of nodes in each graph is the same as the (declustered) number of events shown in Table \ref{tab:seismicity}, and the links between intervisible events are established following the condition in Eq.~\ref{eq:vg}, as in the example shown in Fig.~\ref{fig:vg}.
+We generate the visibility graph for each sub-region of interest using the time-magnitude sequences shown in Fig.~\ref{fig:mag-time}.
+The number of nodes in each graph is the same as the (declustered) number of events shown in Table \ref{tab:seismicity}, and the links between inter-visible events are established following the condition in equation (\ref{eq:vg}), as in the example shown in Fig.~\ref{fig:vg}.
 (We do not include a visualization of the complete sequence graphs because the links are so many, it is only practical to visualize the graphs of short sequences).
-We then collect information about the number of inter-visibility links associated to each event (connectivity degree, $k$) and categorize the events in magnitude bins of size $\Delta M = 0.1$ as mentioned in the Methodology section.
-Figure \ref{fig:km} shows the scattered distribution of events in the magnitude-connectivity degree plane.
+We then collect information about the number of inter-visibility links associated with each event (connectivity degree, $k$) and categorize the events in magnitude bins of size $\Delta M = 0.1$, as mentioned in the Methodology section.
+Figure \ref{fig:km} shows the scattered distribution of events in the magnitude-connectivity degree plane for each sub-region.
 The figure shows that, in general, the value of $k$ increases with $M_w$.
-Figure \ref{fig:km} also shows the result of obtaining linear $k$-$M$ regressions for the datasets and the values of the $k$-$M$ slope for each of the three zones.
+Figure \ref{fig:km} also shows the results of obtaining linear $k$-$M$ regressions for each dataset and the values of the $k$-$M$ slopes for the three seismic zones.
 
@@
 	\includegraphics[width=\textwidth]{figures/pdf/figure-06} 
-	\caption{Scattered distribution of events in the magnitude-connectivity degree plane and the linear regressions obtained for the $k$-$M$ relationship for the three seismic regions in northern Iran.
-The values next to each of the regression lines corresponds to the slope of each line, which is referred here as the $k$-$M$ slope.
+	\caption{Scattered distribution of events in the magnitude-connectivity degree plane and linear regressions obtained for the $k$-$M$ relationships for the three seismic regions in northern Iran.
+The value next to each of regression line corresponds to the slope of the line, which is referred here as the $k$-$M$ slope.
 The color version of this figure is available only in the electronic edition.}
@@
 
-Next, we examine the relationship between the $b$-values and the from Table \ref{tab:seismicity} and the $k$-$M$ slope values shown in Fig.~\ref{fig:km}.
+Next, we examine the relationship between the $b$-values from Table \ref{tab:seismicity} and the $k$-$M$ slope values shown in Fig.~\ref{fig:km}.
 Figure \ref{fig:regression} shows the scattered results for $k-M$ slope versus $b$-value for the three tectonic seismic regions in northern Iran along with the data-points obtained for analysis of the magnitude-time sequences of the Mexican subduction zone \citep{Telesca2013} and the Pannoninan seismic zone \citep{Telesca2014}, as well as other experimental results \citep{Telesca2014-pone}.
-Figure \ref{fig:regression} also include the results of different linear regressions between $b$ and the $k$-$M$ slope.
+Figure \ref{fig:regression} also include the results of different linear regressions between the $b$-value and the $k$-$M$ slope.
 Each regression shows the addition of new data-points from different studies over time, with the present study adding the latest set of data.
-Note that the regression improves as new data-points are added over time, which is indicated by the correlation coefficient $R$, whose values are also shown in the figure.
+Note that the regression improves as new data-points are added, which is indicated by the correlation coefficient $R$.
 This was previously pointed out by \citet{Telesca2014}.
+The values of the correlation coefficients are also shown in the figure.
+According to these results, the universal relationship between the $b$-value and the $k$-$M$ slope is given by:
+% 
+\begin{equation}
+	b = 000 + 000 m \, 
+	\label{eq:universal.bm}
+\end{equation}
+% 
+where $m$ is the value of the $k$-$M$ slope.
 
@@
 
-\begin{center}
-* \hspace{2em} * \hspace{2em} *
-\end{center}
+The level of correlation indicated by the values of $R$ in Fig.~\ref{fig:regression} being close to 1 is indicative of the stability of the relationship, which could be considered universal provided that future tests continue to reinforce these results.
+Another aspect of interest is the stability of the data points themselves.
+Note that as presented in Fig.~\ref{fig:regression}, the analysis of the sequences shown in Fig.~\ref{fig:mag-time} only contribute one data point per sub-region of interest.
+Furthermore, each data-point comes from sequences that vary significantly in terms of the number of events and seismic parameters.
 
-Although the number of events vary significantly between the three zones (see Table \ref{tab:seismicity}, \citet{Telesca2013} observed that the value of the $k$-$M$ slope is not particularly sensitive to the sample size in the sequence---at least not when considering sufficiently large sequences.
+\citet{Telesca2013} observed that the value of the $k$-$M$ slope is not particularly sensitive to the sample size in the sequence---at least not when considering sufficiently large sequences.
 On the other hand, as we will see below, if the sequence window is sufficiently short, then the $k$-$M$ slope value shows a relative dependence on time and thus provides insight about the variation of the seismicity as the sequence progresses.
@@
 
-To further explore the sensitivity of the graph properties to the number of events in each catalog and the value of the minimum magnitude to be considered, we randomly picked a significant number of sub-sequences from within the catalog of each region and repeated the analysis.
-This was done starting with the catalogs before declustering.
-In total, for each region, we extracted 200 new sub-sequences.
-The number of events in each sub-sequence was varied randomly but chosen to be large enough to represent the seismic characteristics of each seismic region.
-In particular, the minimum size of each subsequence was set to be $\geq 150$, whereas the maximum size in the sequence was set to be as large as the original (pre-declustering) catalog.
+To further explore the sensitivity of the graph properties to the number of events in each catalog and the value of the minimum magnitude to be considered, we randomly picked a significant number of sub-sequences from within the initial catalog compiled for each region, and repeated the analysis for each sub-sequence.
+In total, for each region, we extracted 200 new sub-sequences from the initial (pre-declustering) catalog.
+The number of events in each sub-sequence was varied randomly but chosen to be large enough to represent the seismic characteristics of each region.
+In particular, the minimum size of each sub-sequence was set to be $n \geq 150$, whereas the maximum size in the sequence was set to be as large as the original (pre-declustering) catalog.
 We forced the random sub-sequences to progress positively in time without altering the natural occurrence of events.
-In other words, we randomly determined the initial event and the sub-sequence size (number of events to be considered), then picked that number of events following the initial event.
-Next, we determined the value of $M_c$ and $b$ and created the graph to extract the connectivity degree of the events in each sub-sequence.
-Figure \ref{fig:random}a shows...
+In other words, we randomly determined the initial event and the sub-sequence size (number of events to be considered), then picked that number of events following the initial earthquake in the sub-sequence.
+Next, we determined the value of $M_c$ and $b$, created the graph for all events with $M \geq M_c$, and extracted the connectivity degree of the events in each sub-sequence.
+
+Figure \ref{fig:random}a shows scattered points for all the individual $k$-$M$ slope and $b$-value pairs for all the sub-sequences that were randomly generated for each region in northern Iran.
+Next to it, Figs.~\ref{fig:random}b and \ref{fig:random}c show the
+
+The figure also shows the linear correlation for the
+
+the relationship between  $k-M$  slope and  $b-value$  of the randomly selected data and the statistical parameters for variables.
+Although changing the number of events and the threshold magnitude is slightly changing the results, however,  the results are fairly well clustered for each tectonic seismic region.
 
@@
 
-% In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, we randomly picked 200 sequences from the catalogs with various sequence sizes.
-Number of events at each sequence should be low enough to be able to choose 200 random sequence from the catalog (note that the number of events in each catalog, before removing the events with magnitude less than the completeness magnitude, is 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively).
-Also it should be long enough to preserve the seismic characteristic of each tectonic seismic region.
-Based on mentioned criteria, we choose the minimum size of random windows as 150 events.
-The maximum size is the size of the entire catalog.
-The random sequences are consecutive, in other words, we randomly determine the initial event and sequence size, then we pick that size of event starting from the initial event.
-For each randomly picked magnitude time series,  we estimate $Mc$; then the $k-M$  and $b-value$ are calculated.
-Fig.~\ref{fig:random} shows the relationship between  $k-M$  slope and  $b-value$  of the randomly selected data and the statistical parameters for variables.
+% Fig.~\ref{fig:random} shows the relationship between  $k-M$  slope and  $b-value$  of the randomly selected data and the statistical parameters for variables.
 Although changing the number of events and the threshold magnitude is slightly changing the results, however,  the results are fairly well clustered for each tectonic seismic region.

### 2016-08-21 results.tex
improved results section.... not finished yet.

@@
 Each regression shows the addition of new data-points from different studies over time, with the present study adding the latest set of data.
-Note that the regression improves as new data-points are added, which is indicated by the correlation coefficient $R$.
-This was previously pointed out by \citet{Telesca2014}.
-The values of the correlation coefficients are also shown in the figure.
-According to these results, the universal relationship between the $b$-value and the $k$-$M$ slope is given by:
+Note that the regression improves as new data-points are added, which is indicated by the correlation coefficient $R$, also shown in the figure.
+The correlation fitting various regional seismic data was previously pointed out by \citet{Telesca2014}.
+
+According to these results, a universal relationship between the $b$-value and the $k$-$M$ slope ($m$) can be expressed as:
 % 
 \begin{equation}
-	b = 000 + 000 m \, 
+	b = 000 + 000 m \, .
 	\label{eq:universal.bm}
 \end{equation}
-% 
-where $m$ is the value of the $k$-$M$ slope.
 
@@
 
-The level of correlation indicated by the values of $R$ in Fig.~\ref{fig:regression} being close to 1 is indicative of the stability of the relationship, which could be considered universal provided that future tests continue to reinforce these results.
 Another aspect of interest is the stability of the data points themselves.
-Note that as presented in Fig.~\ref{fig:regression}, the analysis of the sequences shown in Fig.~\ref{fig:mag-time} only contribute one data point per sub-region of interest.
-Furthermore, each data-point comes from sequences that vary significantly in terms of the number of events and seismic parameters.
+Note that as presented in Fig.~\ref{fig:regression}, the analysis of the sequences shown in Fig.~\ref{fig:mag-time} only contribute one data point per region of interest.
+Furthermore, each data-point comes from sequences that vary significantly in terms of the number of events and seismic parameters (see Table \ref{tab:seismicity}).
 
 \citet{Telesca2013} observed that the value of the $k$-$M$ slope is not particularly sensitive to the sample size in the sequence---at least not when considering sufficiently large sequences.
-On the other hand, as we will see below, if the sequence window is sufficiently short, then the $k$-$M$ slope value shows a relative dependence on time and thus provides insight about the variation of the seismicity as the sequence progresses.
+On the other hand, as we will see below, if the sequence window is sufficiently small, then the $k$-$M$ slope value shows a relative dependence on time and thus provides insight about the variation of the seismicity as the sequence progresses.
 Note also that the threshold value of $M_c$ is significantly smaller for Azerbaijan than for Alborz or Kopeh-Dagh.
@@
 The number of events in each sub-sequence was varied randomly but chosen to be large enough to represent the seismic characteristics of each region.
-In particular, the minimum size of each sub-sequence was set to be $n \geq 150$, whereas the maximum size in the sequence was set to be as large as the original (pre-declustering) catalog.
+In particular, the minimum size of each sub-sequence was set to be $n \geq 150$, whereas the maximum size in the sequence was set to be as large as the original (pre-declustering) catalog (see Table \ref{tab:seismicity}).
 We forced the random sub-sequences to progress positively in time without altering the natural occurrence of events.
-In other words, we randomly determined the initial event and the sub-sequence size (number of events to be considered), then picked that number of events following the initial earthquake in the sub-sequence.
-Next, we determined the value of $M_c$ and $b$, created the graph for all events with $M \geq M_c$, and extracted the connectivity degree of the events in each sub-sequence.
+In other words, we randomly determined the initial event and the sub-sequence size (number of events to be considered), and then picked that number of events following the initial earthquake in the sub-sequence.
+Next, we determined the value of $M_c$ and $b$ as previously done for the complete catalogs, created the graph for all events with $M \geq M_c$, and extracted the connectivity degree of the events in each sub-sequence.
 
-Figure \ref{fig:random}a shows scattered points for all the individual $k$-$M$ slope and $b$-value pairs for all the sub-sequences that were randomly generated for each region in northern Iran.
-Next to it, Figs.~\ref{fig:random}b and \ref{fig:random}c show the
+\begin{figure*}%[t]
+	\centering
+	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-08} 
+	\caption{Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence.
+The numbers on the mean and standard deviation plots are coefficient of variations in percent $(standard \ deviation / mean)$.}
+	\label{fig:random}
+\end{figure*}
 
-The figure also shows the linear correlation for the
+Figure \ref{fig:random}a shows scattered points for all the individual $k$-$M$ slope and $b$-value pairs for all the sub-sequences that were randomly picked from the initial catalogs of each region in northern Iran.
+Figures \ref{fig:random}b and \ref{fig:random}c show the variability of the $k$-$M$ slope and $b$-value, respectively.
+These latter figures show the mean values of each parameter for all the random sub-sequences and the amplitudes of $\pm 1$ standard deviation, as well as the coefficients of variation (in percentage).
+Figure \ref{fig:random}a also includes the data points corresponding to the complete catalogs (solid symbols); the points corresponding to the mean values of the $k$-$M$ slope and $b$, from Figs.~\ref{fig:random}b and \ref{fig:random}c; and the linear regression from equation \ref{eq:universal.bm} as well as the linear regression obtained using the random sub-catalog visual graph analysis for northern Iran, which corresponds to:
+% 
+\begin{equation}
+	b = 000 + 000 m \, .
+	\label{eq:iran.bm}
+\end{equation}
 
-the relationship between  $k-M$  slope and  $b-value$  of the randomly selected data and the statistical parameters for variables.
+The results presented in Fig.~\ref{fig:random} indicate there exist only but a small bias (between 5 and 10 percent) depending on the analysis being done with multiple sub-sequences as opposed to the complete catalog sequences.
+In particular, $k$-$M$ slopes are slightly smaller when done with the random sequence analysis; whereas $b$-values seem more stable.
+This is also reflected by the differences between the linear regressions for the data of northern Iran exclusively, as opposed to the regression obtained using the data points from this and other studies.
+In this case, we note that the universal regression increases at a smaller rate than the regression obtain only for northern Iran, as can be seen from the difference between the slope coefficients in equations (\ref{eq:universal.bm}) and (\ref{eq:iran.bm}).
+
+\begin{figure*}%[t]
+	\centering
+	\includegraphics[width=\textwidth]{figures/pdf/figure-09} 
+	\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_c >$ (Right) as a function of time for three tectonic seismic regions in north Iran.
+Black arrows show the occurrence of the major earthquakes.
+Numbers on arrows indicate the moment magnitude of the earthquake (see Fig.~\ref{fig:mag-time} for reference).
+The magnitude-time series are presented as a filled plot blew each plot.
+The variation of the heigh of filled plots are corresponding to the event magnitudes.
+Decreasing the value of  $<T_c>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions.}
+	\label{fig:tc}
+\end{figure*}
+
+We now investigate the relationship of parameters obtained through the visibility graph analysis and the seismicity of northern Iran with time. Figure \ref{fig:tc} shows...
+
+% =========
+
+% the relationship between  $k-M$  slope and  $b-value$  of the randomly selected data and the statistical parameters for variables.
 Although changing the number of events and the threshold magnitude is slightly changing the results, however,  the results are fairly well clustered for each tectonic seismic region.
@@
 The  $k-M$  slope shows the higher coefficient of variation which indicates the fact that the  $k-M$  slope is more dependent on the window size and threshold magnitude than on the a-  and  b-values , which suggests that  the $k-M$  slope can better represent the dynamic characteristics of the magnitude-time series.
-
-\begin{figure*}%[t]
-	\centering
-	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-08} 
-	\caption{Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence.
-The numbers on the mean and standard deviation plots are coefficient of variations in percent $(standard \ deviation / mean)$.}
-	\label{fig:random}
-\end{figure*}
 
@@
 Decreasing the value of  $<T_c>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions (see Fig.\ref{fig:tc} for reference.)
-
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=\textwidth]{figures/pdf/figure-09} 
-	\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_c >$ (Right) as a function of time for three tectonic seismic regions in north Iran.
-Black arrows show the occurrence of the major earthquakes.
-Numbers on arrows indicate the moment magnitude of the earthquake (see Fig.~\ref{fig:mag-time} for reference).
-The magnitude-time series are presented as a filled plot blew each plot.
-The variation of the heigh of filled plots are corresponding to the event magnitudes.
-Decreasing the value of  $<T_c>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions.}
-	\label{fig:tc}
-\end{figure*}

### 2016-08-21 seismicity.tex
improved results section.... not finished yet.

@@
 The edges or links are omitted for visual convenience.
-Highlighted in the figure are the largest events in each sub-catalog, namely the 2012 $M_w 6.4$ East Azerbaijan, 2010 $M_w 5.8$ Damghan, and 2012 $M_w 5.4$ Neyshabur earthquakes.
+Highlighted in the figure are the largest events in each sub-catalog, namely the 2012 $M_w$ 6.4 East Azerbaijan, 2010 $M_w$ 5.8 Damghan, and 2012 $M_w$ 5.4 Neyshabur earthquakes.
 The color version of this figure is available only in the electronic edition.}

### 2016-08-21 conclusion.tex
Adding the synthetic data of Telesca 2014 (POne) paper. And general review.
Ricardo's comments added.
finished revising the results section

--- 2016-05-31 conclusion.tex
@@
-\section{Conclusion}
-We studied the earthquake sequence of three tectonic seismic regions of north Iran.
+\section{Conclusions}
+
+Pending...
+
+% We studied the earthquake sequence of three tectonic seismic regions of northern Iran.
 Results manifest the strong relationship between  $k-M$  slope and Gutenberg-Richter parameters.
-The variation of $k-M$ slope and $b-value$ with time in sliding windows have similar behavior and drops down before big earthquakes.
-Significant reduction of $<T_C>$ value before big earthquake is observed.
-Higher coefficient of variation of $k-M$ slope in comparison with $b-value$'s CV, suggests the $k-M$ slope as better parameter for studying the magnitude time series due to higher sensitivity to window size and threshold magnitude than $b-value$.
-In general, $k-M$ and $b-value$ relationship preserves the behavior with variation of the window size and threshold magnitude, and could be an alternative approach for clustering the earthquake sequences based on different tectonic seismic zones.
+The variations of  $k-M$  slope and  b-value  with time in sliding windows have similar behavior and decline before large earthquakes.
+A significant reduction of  $<T_c>$  value before large earthquakes was observed.
+The higher coefficient of variation of  $k-M$  slope in comparison with  b-value  suggests that the  $k-M$  slope is a better parameter for studying the magnitude time series due to higher sensitivity to window size and threshold magnitude than  is found in the $b-value$.
+Sensitivity analysis revealed that the VG parameters behave independently than threshold magnitude and number of events.
+In general,  the $k-M$  and  $b-value$  relationship preserves the behavior with the variation in the window size and threshold magnitude, and could be an alternative approach for clustering earthquake sequences based on different tectonic seismic zones.

### 2016-08-21 results.tex
finished revising the results section

@@
 \begin{equation}
-	b = 000 + 000 m \, .
+	b = 0.078 + 0.085 m \, .
 	\label{eq:universal.bm}
@@
 	\includegraphics[width=0.45\textwidth]{figures/pdf/figure-07} 
-	\caption{Relationship between $k-M$ slope and $b-value$ of three Iranian tectonic seismic zones (this study) and three other studies of Mexican zones \citep{Telesca2013}, Pannonia zones \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}.
-The lines represent the linear regression fit of data.
-The correlation coefficients (R) are represented for different combination of data.}
+	\caption{Correlation between $k$-$M$ slope and $b$-value as drawn from the results of the present study for the region of northern Iranian and three other previous studies, including analysis of the Mexican subduction zone \citep{Telesca2013}, the Pannonian seismic zone \citep{Telesca2014}, and results from two experiments \citep{Telesca2014-pone}.
+The lines represent linear regressions obtained to fit the different data points, considering different combinations.
+The values of the correlation coefficient, $R$, are indicated for each regression line.
+The color version of this figure is available only in the electronic edition.}
 	\label{fig:regression}
@@
 	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-08} 
-	\caption{Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence.
-The numbers on the mean and standard deviation plots are coefficient of variations in percent $(standard \ deviation / mean)$.}
+	\caption{\textbf{(a)} Correlation between $k$-$M$ slope and $b$-values for 200 random sequences extracted from the initial catalogs of the three northern Iranian seismic regions considered in this study (scattered symbols), including the mean values (empty symbols with thick border) and the data points obtained from the analysis of the complete catalog (solid symbols), along with the linear regressions of each sample as indicated in the legend.
+\textbf{(b)} Mean, $\pm1$ standard deviation, and coefficient of variation (in percent) for the $k$-$M$ slope values of the three seismic zones in northern Iran.
+\textbf{(c)} Same as part (b), but corresponding to the $b$-value.
+The color version of this figure is available only in the electronic edition.}
 	\label{fig:random}
@@
 These latter figures show the mean values of each parameter for all the random sub-sequences and the amplitudes of $\pm 1$ standard deviation, as well as the coefficients of variation (in percentage).
-Figure \ref{fig:random}a also includes the data points corresponding to the complete catalogs (solid symbols); the points corresponding to the mean values of the $k$-$M$ slope and $b$, from Figs.~\ref{fig:random}b and \ref{fig:random}c; and the linear regression from equation \ref{eq:universal.bm} as well as the linear regression obtained using the random sub-catalog visual graph analysis for northern Iran, which corresponds to:
+Figure \ref{fig:random}a also includes the data points corresponding to the complete catalogs (solid symbols); the points corresponding to the mean values of the $k$-$M$ slope and $b$, from Figs.~\ref{fig:random}b and \ref{fig:random}c; and the universal linear regression from equation (\ref{eq:universal.bm}) (thick line), as well as the linear regressions for northern Iran when using the complete catalogs (dashed, thin line) and the random sub-catalogs (continuous, thin line).
+
+The comparison between the mean values of the random sequences analysis versus the complete catalogs presented in Fig.~\ref{fig:random} indicate there exist only a small bias, which is well within the standard deviation of the different value samples.
+We note that the values of the $k$-$M$ slope are slightly smaller when done with the random sequence analysis; whereas $b$-values seem more stable.
+The comparisons of the regressions, however, seem to indicate that the analysis of random sub-catalogs leads to a result more in line with the universal results obtained when considering multiple seismic zones.
+The linear regress of the random sub-catalogs yields the following equation:
 % 
 \begin{equation}
-	b = 000 + 000 m \, .
+	b = 0.080 + 0.093 m \, .
 	\label{eq:iran.bm}
@@
 
-The results presented in Fig.~\ref{fig:random} indicate there exist only but a small bias (between 5 and 10 percent) depending on the analysis being done with multiple sub-sequences as opposed to the complete catalog sequences.
-In particular, $k$-$M$ slopes are slightly smaller when done with the random sequence analysis; whereas $b$-values seem more stable.
-This is also reflected by the differences between the linear regressions for the data of northern Iran exclusively, as opposed to the regression obtained using the data points from this and other studies.
-In this case, we note that the universal regression increases at a smaller rate than the regression obtain only for northern Iran, as can be seen from the difference between the slope coefficients in equations (\ref{eq:universal.bm}) and (\ref{eq:iran.bm}).
+Note that equations (\ref{eq:universal.bm}) and (\ref{eq:iran.bm}) have share similar intercepts with the $b$-value axis, and only slightly different slopes, with the analysis for northern Iran leading to the $b$-value to increase more rapidly with $m$ than the universal data regression suggests.
+The similarity, however, is a positive sign of the stability of the method.
 
@@
 	\includegraphics[width=\textwidth]{figures/pdf/figure-09} 
-	\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_c >$ (Right) as a function of time for three tectonic seismic regions in north Iran.
-Black arrows show the occurrence of the major earthquakes.
-Numbers on arrows indicate the moment magnitude of the earthquake (see Fig.~\ref{fig:mag-time} for reference).
-The magnitude-time series are presented as a filled plot blew each plot.
-The variation of the heigh of filled plots are corresponding to the event magnitudes.
-Decreasing the value of  $<T_c>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions.}
+	\caption{Variation of <$T_c$>, $k$-$M$ slope and $b$-value as with respect to time for three seismic zones for a moving window analysis of the visibility graphs of sub-sequences of 20 consecutive events, along with the magnitude of events in the 2005--2015 period.
+Black triangles indicate the occurrence of major earthquakes in each of the regions, with the corresponding magnitude at the top of each symbol.
+In the middle frame of each region, the dashed line corresponds to the $k$-$M$ values, whereas the continuous plot shows the variation of the $b$-value.
+The color version of this figure is available only in the electronic edition.}
 	\label{fig:tc}
@@
 
-We now investigate the relationship of parameters obtained through the visibility graph analysis and the seismicity of northern Iran with time. Figure \ref{fig:tc} shows...
+We now investigate the relationship of the parameters obtained through the visibility graph analysis with time.
+Here, the visibility graph analysis is done by windows of equal number of events moving in time across the catalog sequence.
+The number of events in the window is kept fixed independently of the time between them, and the results of the visibility graph analysis are associated with the last event in the window.
+In this case, we are interested in using a small number of events to capture the relevance of each new event as the window moves in time.
+We tried different numbers and finally chose 20 events as the moving window sequence size.
+This selection was also convenient given the smaller total number of declustered events in the catalog of Azerbaijan.
+When we tested larger number of events, we found that we could not properly observe the changes in the different parameters with time.
+On the other hand, when we used smaller sequence sizes, the values deviated more significantly from the random and complete catalog results obtained previously.
+At this point it is also of interest to compute the value of <$T_c$> explained int he Methodology section.
 
-% =========
+Figure \ref{fig:tc} shows the variation of <$T_c$>, the $k$-$M$ slope, and the $b$-value with time for each of the three seismic zones in northern Iran.
+Note that the behavior of the $k$-$M$ slope and the $b$-value is very similar along time for all three zones.
+This is consistent with the results discussed above.
+In the figure we also highlight the occurrence of relevant earthquakes in each seismic zone in the last decade.
+We note that there seems to be a correlation between the behavior of the $b$-value in time with the occurrence of some of these events.
+In particular, some of the events in the figure seem to coincide with a drop in the $b$-value.
 
-% the relationship between  $k-M$  slope and  $b-value$  of the randomly selected data and the statistical parameters for variables.
-Although changing the number of events and the threshold magnitude is slightly changing the results, however,  the results are fairly well clustered for each tectonic seismic region.
-
-% =========
-
-% We compared the $k$-$M$ slope with the $b$-value of the Gutenberg-Richter law through the entire catalog and in the sliding windows in time.
-
-% Comparing the result with the Guerrero region with reduced random sequence,  \citet{Telesca2013}  found that the number of sequences did not affect the $k-M$ slope.
-
-% Fig.~\ref{fig:random} shows the relationship between  $k-M$  slope and  $b-value$  of the randomly selected data and the statistical parameters for variables.
-Although changing the number of events and the threshold magnitude is slightly changing the results, however,  the results are fairly well clustered for each tectonic seismic region.
-
-% The coefficient of variation of parameters is shown in Fig.~\ref{fig:random}.
-The  $k-M$  slope shows the higher coefficient of variation which indicates the fact that the  $k-M$  slope is more dependent on the window size and threshold magnitude than on the a-  and  b-values , which suggests that  the $k-M$  slope can better represent the dynamic characteristics of the magnitude-time series.
-
-% *******
-
-% Fig.\ref{fig:tc} shows the variation of the  $k-M$  slope and  $b-value$  with time.
-Due to lower number of events in Azerbaijan's catalog, we choose 20 events as the window length with a shift of one event between two successive windows.
-With higher window length we loose the variation of considerable amount of information in time (e.g.
-with n=40 we loose almost half of the Azerbaijan catalog).
-Due to taking average values of successive windows, very small window length can not display the seismicity behavior especially before big earthquake.
-Maintaining consistency, we use the window length equal to 20 events for all three regions.
-The calculated parameters of each window are associated with the time of occurrence of the last event in the sliding window.
-The  $k-M$  slope and  $b-value$  in all tectonic seismic regions are very similar.
-In general, in all regions the $b-value$  and  $k-M$  slope drop considerably before large earthquakes.
-The decline in the  $b-value$  before large earthquakes has been studied in many regions \citep{Wyss2000, Wyss2006, Schorlemmer2005, Chan2012}.
-
-% \citet{Telesca2016}  observed the decrease in  $<T_c>$  before the large earthquake of the western India earthquake sequence.
-Fig.\ref{fig:tc}  shows the time variation of  $<T_c>$   in the study area.
-The reduction of  $<T_c>$   before large earthquakes is clearly visible.
-\citet{Telesca2016}  demonstrated that the decrement of  $<T_c>$   before a large earthquake is independent of window size and threshold magnitude.
-Decreasing the value of  $<T_c>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions (see Fig.\ref{fig:tc} for reference.)
+The decline in $b$-value before large earthquakes has been studied in other regions before \citep[e.g.,][]{Wyss2000, Wyss2006, Schorlemmer2005, Chan2012}.
+In the context of the visibility graph analysis, \citet{Telesca2016} observed a decrease in <$T_c$> before the large earthquake of the western India earthquake sequence.
+We recognize, however, that the lack of larger events in our region of interest in the last decade prevents us from drawing a stronger conclusion on this regard.

### 2016-08-21 title-and-authors.tex
improved abstract
almost done with seismicity section
finished revising the results section

@@
-\pretitle{
-    \vspace{-30pt}
-    \begin{flushleft}
-    \usefont{T1}{phv}{bc}{it}
-    \Huge
-}
-
-\posttitle{
-    \end{flushleft}
-}
-
-\preauthor{
-    \begin{flushleft}
-    \vspace{3pt}
-    \usefont{T1}{phv}{bc}{n}
-    \LARGE
-}
-
-\postauthor{
-    \end{flushleft}
-    \vspace{0.3em}
-    \section{Abstract}
-    \vspace{-3em}
-}
-
-\predate{
-    \begin{flushleft}
-    \makeatletter
-}
-
-\postdate{
-    \end{flushleft}
-}
-
 \title{%
-    Analysis of 2005--2015 Earthquake Sequence in Northern Iran Using Visibility Graph Approach
+    Analysis of the 2005--2015 Earthquake Sequence in Northern Iran Using the Visibility Graph Method
 }
@@
     \renewcommand*\@fnsymbol[1]{\the#1}
-    \author{by Naeem Khoshnevis, Shima Azizzadeh-Roodpish, Ricardo Taborda, and Luciano Telesca}
+    \author{by Naeem Khoshnevis, Ricardo Taborda, Shima Azizzadeh-Roodpish, and Luciano Telesca}
 \else
     \author{
-    	Naeem Khoshnevis,\myaffil{1,$\ast$} Shima Azizzadeh-Roodpish,\myaffil{1,2} Ricardo Taborda\myaffil{1,2} and Luciano Telesca\myaffil{3}\\
+        Naeem Khoshnevis,\myaffil{1,$\ast$} Ricardo Taborda\myaffil{1,2} Shima Azizzadeh-Roodpish,\myaffil{1,2} and Luciano Telesca\myaffil{3}\\
         \normalsize\normalfont    	    	

### 2016-08-22 abstract.tex
fixed minor details in text

@@
 The method relies on the inter-event visibility defined in terms of a connectivity degree parameter, $k$, which is correlated with the earthquake magnitude, $M$.
-Previous studies show that the slope of the $k$-$M$ correlation also observes a relationship with the $b$-value from the Gutenber-Richter law.
-Thus rendering the graph analysis useful to examine the seismicity of a region.
+Previous studies show that the slope of the $k$-$M$ correlation also observes a relationship with the $b$-value from the Gutenber-Richter law, thus rendering the graph analysis useful to examine the seismicity of a region.
 In addition, other topological properties of the network and dynamic properties of the magnitude-time series exhibit characteristics that seem to be associated with the occurrence of earthquakes, offering the possibility of correlating seismicity parameters with time.
-We apply this approach to the case of the seismicity of northern Iran, using a declustered seismic catalogs for the tectonic seismic regions of Azerbaijan, Alborz, and Kopeh Dagh.
+We apply this approach to the case of the seismicity of northern Iran, using an earthquake catalog for the tectonic seismic regions of Azerbaijan, Alborz, and Kopeh Dagh.
 We use results draw for this region with the visibility graph approach in combination with results from other similar studies to further improve the universal correlation between $k$-$M$ and $b$-values and show that the visibility graph approach can be considered as a valid alternative for analyzing regional seismicity properties and earthquake sequences.
-
-% --------------------------------------------------------------------------------------------------
-
-% NAEEM'S ABSTRACT
-% ----------------
-
-% The seismicity of northern Iran between 2005 and 2015 is investigated by means of the visibility graph (VG) method.
-For purposes of this study, northern Iran is divided into three tectonic seismic regions: Azerbaijan, Alborz, and Kopeh Dagh.
-Using the declustered catalog, we studied the VG properties of the magnitude time series.
-The results show a relationship between the $k-M$ slope and the $b-value$ of the Gutenberg-Richter law.
-Topological properties (i.e.
-$< T_c >$, $k-M$ slope) of the network and dynamic properties of magnitude time series (i.e.
-$b-value$) significantly decrease before large earthquakes.
-Combining the results of this study with three similar previous studies improves the linear correlation coefficient factor between $k-M$ slope and $b-value$, and empowers the idea of a universal relationship between $b-value$ and $k-M$ slope.
-The behaviors of the VG's properties are similar to previous studies and could be considered an alternative method for analyzing earthquake sequences.

### 2016-08-22 introduction.tex
fixed minor details in text

@@
 
-For the particular case of seismological applications, previous studies have proposed the nodes in the graph to be considered as the earthquakes in a given time series of events, and analyzed the properties of the graph with respect to traditional seismicity parameters.
+For the particular case of seismological applications, previous studies have proposed to consider the nodes in the graph to be the earthquakes in a given time series of events, and analyzed the properties of the graph with respect to traditional seismicity parameters.
 The analysis of seismic sequences through the visibility graph approach for various tectonic seismic regions has proven to be a valid alternative to studying magnitude time series.
@@
 
-In a similar article, \citet{Telesca2014} studied the seismicity of the 2002--2011 Pannonian seismicity using the visibility graph method for two sub-catalogs of shallow and deep earthquakes.
+In a similar article, \citet{Telesca2014} studied the seismicity of the 2002--2011 Pannonian region using the visibility graph method for two sub-catalogs of shallow and deep earthquakes.
 They extracted the visibility graph characteristics for each group of events and confirmed that there was a close correlation between the Gutenberg-Richter $b$-value and the slop of the $k$-$M$ relationship obtained from the visibility graph.
@@
 More recently, \citet{Telesca2016} used the visibility graph method to gain insight about the timespan between earthquakes.
-The authors defined the parameter window mean interval connectivity time <$T_c$>, which provides information about the average of all the time intervals between visible events.
+The authors defined the parameter <$T_c$> as the window mean interval connectivity time, which provides information about the average of all the time intervals between visible events.
 Applying this concept to the 2003--2012 earthquake sequence in Kachchh, western India, \citet{Telesca2016} found that the variation of <$T_c$> in time exhibited a plausible relationship with the occurrence of earthquakes.
@@
 In this article we use the visibility graph method to analyze the seismicity of northern Iran from 2005 to 2015.
-We focus our analysis on these years window because in a previous study we observed the latest decade of seismic records in the region offered the most complete catalog of events \citep[e.g.][]{Khoshnevis2016}.
-Upon a brief review of the basic concepts of the method and its applications, we describe the seismicity of northern Iran considering three dominant seismic areas, namely: Azerbaijan, Alborz, and Kopeh Dagh.
+We focus our analysis on these years because in a previous study we observed that the latest decade of seismic records in the region offered the most complete catalog of events \citep[e.g.][]{Khoshnevis2016}.
+Upon a brief review of the basic concepts of the method and its applications, we describe the seismicity of northern Iran considering three dominant seismic regions: Azerbaijan, Alborz, and Kopeh Dagh.
 These are regional areas of considerable ground shaking activity, with average seismic rates varying between about 0.17 and 3.25 events per year \citep[e.g.,][]{Nemati2015}.
@@
 We then present results obtained for the region regarding the relationship between the the graph's $k$-$M$ slope and the seismicity $b$-values for the three seismic areas, analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, and present results for the variation of <$T_c$> through time.
-
-% NAEEM'S INTRODUCTION
-% --------------------
-
-% This article presents the application of VG method on seismicity of northern Iran using the recorded earthquake during the last 10 years (2005-15).
-Recent studies show that this period (2005-15) has the most complete catalog especially for small earthquakes $(M < 3)$ \citep[e.g.][]{Khoshnevis2016}.
-\citet{Lacasa2008} introduced a simple and fast computational method, known as visibility algorithm, to convert time series into graphs.
-Basically, the visibility graph presents the connection between nodes in a network.
-This concept has applications in many fields including geophysical studies\citep[e.g.,][]{Telesca2012_CSF,Long2013,Wang2012}.
-
-% The analysis of seismic sequence through visibility graph for various tectonic seismic regions revealed an alternative approach to studying the magnitude time series.
-\citet{Telesca2012} studied the seismic sequence of Italy between the years 2005 and 2010 using the visibility graph method.
-Applying different threshold magnitudes and observing the collapsing effect of all distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend on only the values of the magnitude and being independent of the threshold magnitude.
-
-% In other research, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through the visibility graph approach.
-They extracted characteristics of the visibility graph for five different tectonic seismic regions.
-According to their study, a visibility graph could distinguish the region with different seismicity characteristics, resulting from its different tectonic processes governing the area.
-Their study investigated the relationship between the Gutenberg-Richter parameters and the $k-M$ slope, which is the slope of the regression line fitting the magnitude of each event ($M$) and its connectivity degree ($k$).
-
-% In a similar article, \citet{Telesca2014} studied the seismicity of the 2002-11 Pannonian seismicity using visibility graph.
-They classified the seismic catalog into shallow and deep earthquakes, and extracted the visibility graph characteristics for each class.
-According to their study, a close relationship exists between the Gutenberg-Richter $b-value$ and the $k-M$ slope of the visibility graph.
-The high linear correlation coefficient value (close to 1) of $b-value$ and $k-M$  slope suggests the universal character of the relationship between these parameters \citep{Telesca2014}.
-Using the synthetic seismicity generated by a simple stick-slip system with asperities, \citet{Telesca2014-pone} investigated the relationship between the $b-value$ of the Gutenberg-Richter law and the slope of the $k-M$ plot as obtained by the VG method.
-They build up a frictional system as a proxy of geological faults under tectonic stress and defined different asperities by means of modifying the sandpaper grade.
-They collected data after the first run ($R_1$) and the fifth run ($R_5$) mimicking the younger and mature faults, respectively.
-They calculated the magnitude as a normalized displacement in range of $1-10$.
-According to their study the $b-value$ and the $k-M$ slope are linearly correlated to each other with a high correlation coefficient.
-
-% VG method also is applied through considering the timespan between earthquakes.
-\citet{Telesca2016} defined $<T_c>$ as the parameter window mean interval connectivity time, as an indication of the mean linkage time between earthquakes, in studying the 2003-12 earthquake sequence in the Kachchh region of western India.
-They found that $<T_C>$ changes through time, indicating that the topological properties of the earthquake network are not stationary.
-In addition, $<T_c>$ significantly decrees before the largest shock of the catalog.
-Analyzing the Gutenberg-Richter values of  the magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series by using the features of networks.
-
-% In this study, we use visibility graph analysis to investigate the earthquake sequence of northern Iran.
-We divided northern Iran into three tectonic seismic regions, namely Azerbaijan (Az), Alborz Mountain Range (Al), and Kopeh Dagh (Ko).
-Recently, northern Iran has been studied in detail from different seismological points of view.
-\citet{Nemati2015} studied the most recent 200 years of seismicity in northern Iran.
-The frequency of shocks varied widely, from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years (3.25 event/year) for the Kopeh-Dagh region \citep{Nemati2015}.
-Using the smoothed seismicity method, \citet{Khoshnevis2016} studied the seismic hazard of the three northern tectonic seismic regions.
-Having a considerable number of recorded earthquakes, extensive seismic history, and being in a unique tectonic seismic region, northern Iran is a good platform from which to analyze the visibility graph method's capabilities for studying the magnitude time series.
-Significant aspect of our work includes the compassion of earthquake catalog, conversion of the earthquake magnitude and computation of the completeness magnitude for each tectonic seismic zone.
-We present the relationship between  $k$-$M$  slope and $b$-value in these three tectonic seismic regions.
-We analyze the sensitivity of the catalogs to the number of events and the threshold magnitude.
-We also investigate the variation of  $<T_c>$  value through time.

### 2016-08-22 methodology.tex
working on last versions of figures in and on results section
fixed minor details in text

@@
 
-Discrete mathematics and computer science often deal with different types of data abstractions and structures such as sets, trees, and graphs, where concepts like nodes and links are used to describe the topology a collection of objects and manipulate their data \citep[e.g.,][]{Skiena_2008_Book}.
+Discrete mathematics and computer science often deal with different types of data abstractions and structures such as sets, trees, and graphs, where concepts like nodes and links are used to describe the topology of a collection of objects and manipulate their data \citep[e.g.,][]{Skiena_2008_Book}.
 In graphs, the data---sometimes also referred to as the payload---resides at the vertices or nodes who are connected through links or edges, which may or may not have an associated direction.
-A visibility graph is a special type of undirected graphs in which the links are straight lines connecting intervisible nodes; that is, straight lines that do not overlap any obstacle while connecting nodes that can see each other in a physical space \citet{LozanoPerez_1979_CACM}.
+A visibility graph is a special type of undirected graphs in which the links are straight lines connecting intervisible nodes; that is, straight lines that do not overlap any obstacle while connecting nodes that can see each other in a physical space \citep{LozanoPerez_1979_CACM}.
 Visibility graphs have been mostly used in robotics for navigation path planning \citep[e.g.,][]{Huang_2004_Proc, Oommen_1987_JRA} but have also seen applications in other fields including urban studies, interior architecture, medicine and geosciences \citep[e.g.,][]{Raman_2010_UE, Ahmadlou_2010_JNT, Varoudis_2014_JSS, Phillips_2015_ESR}.
@@
 In a relatively recent study, \citet{Lacasa2008} applied the concepts of visibility graphs to the representation and analysis of time series.
-Multiple applications have been found to this idea in fields like economics \citep{Yang_2009_PA, Wang2012} and climate \citep{Elsner_2009_GRL}.
+Multiple applications have been found to this idea in fields such as economics \citep{Yang_2009_PA, Wang2012} and climate studies \citep{Elsner_2009_GRL}.
 In this study, we are particularly interested in the application of visibility graphs to the analysis of seismic sequences \citep{Telesca2012}.
@@
 	\frac{y_i - y_p }{t_p - t_i} > \frac{y_i - y_j}{ t_j - t_i} \, ,
+	\label{eq:vg}
 \end{equation}
@@
 It follows from this that the visibility graph generated from a time series holds the following conditions.
-Connectivity: each event is visible to the immediate first events to its right and left sides, if there is any.
+Connectivity: each event is visible to the two events to its immediate right and left sides, if there is any.
 Directivity: the graph is considered undirected by definition; that is, the algorithm explaining the connections between events is developed without defining a direction for the links between the events.
@@
 
-Figure \ref{fig:vg} shows an example of a visibility graph for one of the magnitude-time series to be considered later in this study.
+Figure \ref{fig:vg} shows an example of a visibility graph for a portion of one of the magnitude-time series to be considered later in this study.
 For each event $i$ we compute the connectivity degree, $k$, which is the sum of the connections to all other events $j$ visible by the $i$th event.
@@
 
-Plotting $k$ against magnitude results on a scattered set of points which have been shown to be acceptably represented by a linear correlation.
+Plotting $k$ against magnitude results on a scattered set of points which have been shown to be acceptably represented by a linear regression.
 We referred to this correlation as the $k$-$M$ relationship.
-More important, the slope of the $k$-$M$ relationship also shows a linear relationship with the seismicity $b$-value of the seismic zone under consideration.
+More important, the slope of the $k$-$M$ relationship also shows a linear regression with the seismicity $b$-value of the seismic zone under consideration.
 This is also true for a universal sample of $k$-$M$ slopes and $b$ values \citep{Telesca2013, Telesca2014}.
@@
 
-Because <$T_c$> can be obtained for any sub-graph within a larger graph, that is, for any time window in a larger magnitude-time series of events, then it is possible to investigate the evolution of <$T_c$> (and that of the $k$-$M$ slope and the $b$-value) for a moving window sliding along the magnitude-time series.
-When doing so, \citet{Telesca2016} suggested to associate the values of each sub-sequence with the last event in the sequence.
+Because <$T_c$> can be obtained for any sub-graph within a larger graph, that is, for any time window in a larger magnitude-time series of events, then it is possible to investigate the evolution of <$T_c$> (and that of the $k$-$M$ slope and the $b$-value) for a moving window---with a constant number of events---sliding along the magnitude-time series.
+When doing so, \citet{Telesca2016} suggested to associate the values of each sub-sequence with the last event in the sub-sequence.
 Following this approach, \citet{Telesca2016} found that the variation of <$T_c$> over time exhibited a possible relationship with the occurrence of earthquakes.
-This and the aforementioned relationship between the $k$-$M$ slope and the $b$-value are aspects we explore next for our region and earthquake-sequence of interest.
-
-% Fig.~\ref{fig:vg} shows initial events of KopehDagh magnitude-time series with connectivity degree of each event.
+This and the aforementioned relationship between the $k$-$M$ slope and the $b$-value are aspects we explore next for our region and years-interval of interest.

### 2016-08-22 results.tex
fixed minor details in text

@@
 The number of nodes in each graph is the same as the (declustered) number of events shown in Table \ref{tab:seismicity}, and the links between inter-visible events are established following the condition in equation (\ref{eq:vg}), as in the example shown in Fig.~\ref{fig:vg}.
-(We do not include a visualization of the complete sequence graphs because the links are so many, it is only practical to visualize the graphs of short sequences).
-We then collect information about the number of inter-visibility links associated with each event (connectivity degree, $k$) and categorize the events in magnitude bins of size $\Delta M = 0.1$, as mentioned in the Methodology section.
+(We do not include a visualization of the complete sequence graphs because the links are so many, it is only practical to visualize the graphs of short sequences.) We then collect information about the number of inter-visibility links associated with each event (connectivity degree, $k$) and categorize the events in magnitude bins of size $\Delta M = 0.1$, as mentioned in the Methodology section.
 Figure \ref{fig:km} shows the scattered distribution of events in the magnitude-connectivity degree plane for each sub-region.
@@
 Next, we examine the relationship between the $b$-values from Table \ref{tab:seismicity} and the $k$-$M$ slope values shown in Fig.~\ref{fig:km}.
-Figure \ref{fig:regression} shows the scattered results for $k-M$ slope versus $b$-value for the three tectonic seismic regions in northern Iran along with the data-points obtained for analysis of the magnitude-time sequences of the Mexican subduction zone \citep{Telesca2013} and the Pannoninan seismic zone \citep{Telesca2014}, as well as other experimental results \citep{Telesca2014-pone}.
-Figure \ref{fig:regression} also include the results of different linear regressions between the $b$-value and the $k$-$M$ slope.
-Each regression shows the addition of new data-points from different studies over time, with the present study adding the latest set of data.
-Note that the regression improves as new data-points are added, which is indicated by the correlation coefficient $R$, also shown in the figure.
+Figure \ref{fig:regression} shows the scattered results for $k$-$M$ slope versus $b$-value for the three tectonic seismic regions in northern Iran along with the data-points obtained for the analysis of the magnitude-time sequences of the Mexican subduction zone \citep{Telesca2013} and the Pannoninan seismic zone \citep{Telesca2014}, as well as other experimental results \citep{Telesca2014-pone}.
+Figure \ref{fig:regression} also includes the results of different linear regressions between the $b$-value and the $k$-$M$ slope.
+Each regression reflects the addition of new data-points from different studies.
+Note that the regression improves as new data-points are added, which is indicated by the correlation coefficient $R$, also included in the figure.
 The correlation fitting various regional seismic data was previously pointed out by \citet{Telesca2014}.
@@
 
-To further explore the sensitivity of the graph properties to the number of events in each catalog and the value of the minimum magnitude to be considered, we randomly picked a significant number of sub-sequences from within the initial catalog compiled for each region, and repeated the analysis for each sub-sequence.
+To further explore the sensitivity of the graph properties to the number of events in each catalog and the value of the minimum magnitude, we randomly picked a significant number of sub-sequences from within the initial catalog compiled for each region, and repeated the analysis for each sub-sequence.
 In total, for each region, we extracted 200 new sub-sequences from the initial (pre-declustering) catalog.
 The number of events in each sub-sequence was varied randomly but chosen to be large enough to represent the seismic characteristics of each region.
-In particular, the minimum size of each sub-sequence was set to be $n \geq 150$, whereas the maximum size in the sequence was set to be as large as the original (pre-declustering) catalog (see Table \ref{tab:seismicity}).
+In particular, the minimum size of each sub-sequence was set to be $n \geq 150$, and the maximum size in the sequence was set to be as large as the original catalog (pre-declustering; see Table \ref{tab:seismicity}).
 We forced the random sub-sequences to progress positively in time without altering the natural occurrence of events.
@@
 
-Figure \ref{fig:random}a shows scattered points for all the individual $k$-$M$ slope and $b$-value pairs for all the sub-sequences that were randomly picked from the initial catalogs of each region in northern Iran.
+Figure \ref{fig:random}a shows scattered points for all the individual $k$-$M$ slope and $b$-value pairs for all the sub-sequences that were randomly picked from the initial catalogs of each region in northern Iran (small symbols).
 Figures \ref{fig:random}b and \ref{fig:random}c show the variability of the $k$-$M$ slope and $b$-value, respectively.
 These latter figures show the mean values of each parameter for all the random sub-sequences and the amplitudes of $\pm 1$ standard deviation, as well as the coefficients of variation (in percentage).
-Figure \ref{fig:random}a also includes the data points corresponding to the complete catalogs (solid symbols); the points corresponding to the mean values of the $k$-$M$ slope and $b$, from Figs.~\ref{fig:random}b and \ref{fig:random}c; and the universal linear regression from equation (\ref{eq:universal.bm}) (thick line), as well as the linear regressions for northern Iran when using the complete catalogs (dashed, thin line) and the random sub-catalogs (continuous, thin line).
+Figure \ref{fig:random}a also includes the data points corresponding to the complete catalogs (large solid symbols); the points corresponding to the mean values of the $k$-$M$ slope and $b$, from Figs.~\ref{fig:random}b and \ref{fig:random}c (large hollow symbols); and the universal linear regression from equation (\ref{eq:universal.bm}) (thick line), as well as the linear regressions for northern Iran when using the complete catalogs (dashed thin line) and the random sub-catalogs (continuous thin line).
 
-The comparison between the mean values of the random sequences analysis versus the complete catalogs presented in Fig.~\ref{fig:random} indicate there exist only a small bias, which is well within the standard deviation of the different value samples.
-We note that the values of the $k$-$M$ slope are slightly smaller when done with the random sequence analysis; whereas $b$-values seem more stable.
-The comparisons of the regressions, however, seem to indicate that the analysis of random sub-catalogs leads to a result more in line with the universal results obtained when considering multiple seismic zones.
-The linear regress of the random sub-catalogs yields the following equation:
+The comparison between the mean values of the random sequences analysis versus the complete catalogs presented in Fig.~\ref{fig:random} indicates that there exists only a small bias, which is well within the standard deviation of the different value samples.
+We note that the values of the $k$-$M$ slope are slightly smaller when obtained with the random sequence analysis, whereas the $b$ values seem more stable.
+The comparisons of the regressions, however, indicate that the analysis of the random sub-catalogs leads to a result more in line with the universal results obtained when considering multiple seismic zones.
+The linear regression of the random sub-catalogs yields the following equation:
 % 
@@
 
-Note that equations (\ref{eq:universal.bm}) and (\ref{eq:iran.bm}) have share similar intercepts with the $b$-value axis, and only slightly different slopes, with the analysis for northern Iran leading to the $b$-value to increase more rapidly with $m$ than the universal data regression suggests.
-The similarity, however, is a positive sign of the stability of the method.
+Note that equations (\ref{eq:universal.bm}) and (\ref{eq:iran.bm}) have similar intercepts with the $b$-value axis, and only slightly different slope constants.
+In this particular case, the analysis for northern Iran leads to a relationship in which the $b$-value increases more rapidly with $m$ than in the case of the regression obtained for the universal data.
+The similarity between the two equations, however, is a positive sign of the stability of the method.
 
@@
 Here, the visibility graph analysis is done by windows of equal number of events moving in time across the catalog sequence.
-The number of events in the window is kept fixed independently of the time between them, and the results of the visibility graph analysis are associated with the last event in the window.
+The number of events in the window is kept fixed independently of the time between them, and the results are associated with the last event in the window.
 In this case, we are interested in using a small number of events to capture the relevance of each new event as the window moves in time.
@@
 On the other hand, when we used smaller sequence sizes, the values deviated more significantly from the random and complete catalog results obtained previously.
-At this point it is also of interest to compute the value of <$T_c$> explained int he Methodology section.
+At this point it is also of interest to compute the value of <$T_c$> explained in the Methodology section.
 
@@
 Note that the behavior of the $k$-$M$ slope and the $b$-value is very similar along time for all three zones.
-This is consistent with the results discussed above.
-In the figure we also highlight the occurrence of relevant earthquakes in each seismic zone in the last decade.
-We note that there seems to be a correlation between the behavior of the $b$-value in time with the occurrence of some of these events.
+This is consistent with the results presented before.
+In the figure, and include the time-magnitude sequences.
+We note that there seems to be a correlation between the behavior of the $b$-value in time with the occurrence of some of these larger events.
 In particular, some of the events in the figure seem to coincide with a drop in the $b$-value.
 
-The decline in $b$-value before large earthquakes has been studied in other regions before \citep[e.g.,][]{Wyss2000, Wyss2006, Schorlemmer2005, Chan2012}.
+The decline of the $b$-value before large earthquakes has been studied in other regions before \citep[e.g.,][]{Wyss2000, Wyss2006, Schorlemmer2005, Chan2012}.
 In the context of the visibility graph analysis, \citet{Telesca2016} observed a decrease in <$T_c$> before the large earthquake of the western India earthquake sequence.
-We recognize, however, that the lack of larger events in our region of interest in the last decade prevents us from drawing a stronger conclusion on this regard.
+We recognize, however, that the lack of larger ($M>6$) events in our region of interest in the last decade prevents us from drawing a stronger conclusion on this regard.

### 2016-08-22 seismicity.tex
fixed minor details in text

@@
 
-We are interested in applying the visibility graph method to northern Iran.
+We are interested in applying the visibility graph method to analyze the seismicity of northern Iran.
 This region is part of the Iranian plateau, on the Himalayan-Alpine seismic belt.
@@
 We adopt the model proposed by \citet{Mirzaei1998} with modifications introduced by \citet{Karimiparidari2013}.
-In it, Iran is divided into six seismic regions: Azerbaijan, Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran.
+In it, Iran is divided into six seismic regions: Azerbaijan, Alborz, Kopeh Dagh, Zagros, Central-East Iran, and Makran.
 Our focus, however, is on the northern part of Iran, for which we define a region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:study_region}.
-Although this region encloses part of the Zagros and Central-East seismic zones, we concentrate in the analysis of the seismicity of Azerbaijan, Alborz and Kopeh-Dagh.
+Although this region encloses part of the Zagros and Central-East seismic zones, we concentrate in the analysis of the seismicity of Azerbaijan, Alborz and Kopeh Dagh.
 
@@
 Historical accounts document the occurrence of strong $M>6$ earthquakes in this region as far back as the ninth century \citep{Berberian1999}, and a few $M>7$ earthquakes in 1042, 1721 and 1780 \citep{Jones1834}.
-More recently, this region was struck by the $M_w$ 6.1 1997 Ardabil earthquake near the city of Ardabil and $M_w$ 6.4 2012 Tabriz earthquake northeast of the city of Tabriz.
-These earthquakes caused extensive damage and took the lives of more than 1500 people.
+More recently, this region was struck by the $M_w$ 6.1 1997 Ardabil earthquake near the city of Ardabil and the $M_w$ 6.4 2012 Tabriz earthquake northeast of the city of Tabriz.
+These earthquakes caused extensive damage and took the lives of more than 1,500 people.
 
@@
 
-Last, there is the Kopeh-Dagh seismic zone to the east and northeast.
-This region is dominated by the Main Kopeh-Dagh Fault system, which exhibits active tectonic displacements along a distance of more than 500 km \citep{Trifonov1978}.
+Last, there is the Kopeh Dagh seismic zone to the east and northeast.
+This region is dominated by the Main Kopeh Dagh Fault system, which exhibits active tectonic displacements along a distance of more than 500 km \citep{Trifonov1978}.
 This fault is responsible for the $M_w$ 7.3 1948 earthquake, which struck the capital city of Ashgabat in Turkmenistan and destroyed more than 30 villages in Iran.
-Historically, the Kopeh-Dagh seismic zone is also responsible for the $M_s$ 7.1 earthquake in 10 A.D.~\citep{Berberian2001} near Ashgabat, and two significant earthquakes in 1209 and 1405 at the boundary between the Neyshabur and Binalud faults near the city of Mashhad \citep{Berberian1999}.
+Historically, the Kopeh Dagh seismic zone is also responsible for the $M_s$ 7.1 earthquake in 10 A.D.~\citep{Berberian2001} near Ashgabat, and two significant earthquakes in 1209 and 1405 at the boundary between the Neyshabur and Binalud faults near the city of Mashhad \citep{Berberian1999}.
 
@@
 
-We compiled a catalog of recorded earthquakes with magnitude $M>3$ using data downloaded from the International Institute of Earthquake Engineering and Seismology, IIEES (see the Data and Resources section).
+We compiled a catalog of all recorded earthquakes using data downloaded from the International Institute of Earthquake Engineering and Seismology, IIEES (see the Data and Resources section).
 The obtained dataset contained a mixture of earthquake magnitude scales, including: moment, $M_w$; local, $M_L$; body wave, $m_b$; surface wave, $M_s$; and duration $M_D$ magnitudes.
@@
 
-Foreshocks and aftershocks were removed from the catalog following a Poissonian occurrence model using the declustering method of \citet{Gardner1974}, in a manner consistent with previous catalog compilations for the region \citep[e.g.,][]{Zare2014}.
+Foreshocks and aftershocks were removed from the catalog following a Poissonian occurrence model using the declustering method of \citet{Gardner1974}, in a manner consistent with previous catalog compilations available for the region \citep[e.g.,][]{Zare2014}.
 Upon declustering, we divide the catalog into three sub-catalogs, each for one of the seismic zones under consideration.
@@
 where $e$ is the mathematical constant or Euler's number, $\overline{M}$ is the average magnitude, and $M_{\min}$ is the minimum magnitude in the sample.
-Here, the value of $M_{\min}$ is the taken as the minimum completeness magnitude $M_c$ obtained or selected for each region's sub-catalog.
-Table \ref{tab:seismicity} shows the the corresponding values of $M_c$ and $b$.
+Here, the value of $M_{\min}$ is taken as the minimum completeness magnitude $M_c$ obtained or selected for each region's sub-catalog.
+Table \ref{tab:seismicity} shows the corresponding values of $M_c$ and $b$.
 
@@
 The resulting number of events for each region is included in Table \ref{tab:seismicity}.
-Figure \ref{fig:mag-time} shows the final time-magnitude sequences for Azerbaijan, Alborz and Kopeh-Dagh.
-Note that in the case of Alborz and Kopeh-Dagh, we consider events in the declustered catalog down to $M_w \geq 2.6$, whereas in the case of Azerbaijan all events are $M_w \geq 3.5$.
-We omit showing the graph links as it will make the figure difficult to interpret, but rely on the example we presented on Fig.~\ref{fig:vg}.
+Figure \ref{fig:mag-time} shows the final time-magnitude sequences for Azerbaijan, Alborz and Kopeh Dagh.
+Note that in the case of Alborz and Kopeh Dagh, we consider events in the declustered catalog down to $M_w \geq 2.6$, whereas in the case of Azerbaijan all events are $M_w \geq 3.5$.

### 2016-08-22 methodology.tex
deleted the hyphen in kopeh dagh from text and figures

@@
 	\includegraphics[width=0.8\textwidth]{figures/pdf/figure-01} 
-	\caption{Illustration of the visibility graph method, as applied to a subset of events in a window of the magnitude-time series of the north Iranian seismic region of Kopeh-Dagh.
+	\caption{Illustration of the visibility graph method, as applied to a subset of events in a window of the magnitude-time series of the north Iranian seismic region of Kopeh Dagh.
 The events are identified by vertical thick lines (or sticks) on the horizontal time axis with size equal to the magnitude as indicated by the labels at the bottom of each stick.

### 2016-08-22 seismicity.tex
deleted the hyphen in kopeh dagh from text and figures

@@
 	\includegraphics[width=\textwidth]{figures/pdf/figure-02} 
-	\caption{Region of interest, highlighting the seismic zones that are the focus of this study: Azerbaijan, Alborz, and Kopeh-Dagh.
+	\caption{Region of interest, highlighting the seismic zones that are the focus of this study: Azerbaijan, Alborz, and Kopeh Dagh.
 The top-right location-map shows Iran and the selected area with respect to neighboring countries.
@@
 	\includegraphics[width=\textwidth]{figures/pdf/figure-03} 
-	\caption{Declustered instrumental seismicity of northern Iran for the 2005--2015 period, considering only the events in the seismic zones of interest, namely Azerbaila, Alborz, and Kopeh-Dagh.
+	\caption{Declustered instrumental seismicity of northern Iran for the 2005--2015 period, considering only the events in the seismic zones of interest, namely Azerbaila, Alborz, and Kopeh Dagh.
 The size of symbols are proportional to the magnitude of the events, as indicated by the artificial scale shown on the right.
@@
 	\includegraphics[width=\textwidth]{figures/pdf/figure-05} 
-	\caption{Time-magnitude sequences for the northern Iran seismic zones of Azerbaijan, Alborz and Kopeh-Dagh, during the period between 1 January 2005 and 31 December 2015.
+	\caption{Time-magnitude sequences for the northern Iran seismic zones of Azerbaijan, Alborz and Kopeh Dagh, during the period between 1 January 2005 and 31 December 2015.
 The event occurrences are represented by vertical bars or sticks of length equal to the $M_w$ magnitude of each earthquake.

### 2016-08-22 conclusion.tex
done with conclusions and final fixes

@@
 
-Pending...
+We studied the seismicity of the three main seismic regions in northern Iran in the time period between January 2005 and December 2015 using an approach based on the visibility graph method.
+We tested the applicability of this method for the specific region of interest and in reference to previous results from similar studies.
+The results confirm previous observations about the correlation that exists between the connectivity parameter $k$, the magnitude of the events in the sequence, the slope of this relationship or $k$-$M$ slope, and the $b$-value from the Gutenberg-Richter law.
+We obtained mathematical expressions for the region of interest as well as for so-called universal data collected from this study and previous additional analysis for other regions as well as data from experiments and found the relationships to have a good level of similarity.
+This is indicative of the general nature of the relationship between the $k$-$M$ slope and the $b$ value.
+We also explored the potential relationships that can be drawn from a time-dependent visibility graph analysis and the variation of the seismicity in the region of interest.
+We found there may be a potential relationship between the the $b$ value and the occurrence of earthquakes as well as with the graph's mean interval connectivity time parameter <$T_c$>, but additional research in regions with stronger events may be necessary before drawing stronger conclusions in this regard.
+The method used here, nonetheless, seems to provide an alternative and interesting approach to the analysis of the seismicity of a region.
 

### 2016-08-22 introduction.tex
done with conclusions and final fixes

@@
 In this approach, the connection between the nodes in a network---here understood as events in a time series---is based on the visibility of each node or event with respect to other previous and later events in a time sequence.
-Over the last decade, this method has been found to be applicable to multiple fields, including economics and geophysics \citep[e.g.,][]{Telesca2012_CSF, Long2013, Wang2012}.
+Over the last decade, this method has been found to be applicable to multiple fields, including economics, medicine, and geophysics \citep[e.g.,][]{Yang_2009_PA, Elsner_2009_GRL, Telesca2012_CSF, Wang2012, Long2013}.
 

### 2016-08-26 introduction.tex
final changes suggested by Luciano

@@
 
-Subsequently, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through the visibility graph approach and found that the properties of the graph were correlated to the seismic $b$-value in the Gutenber-Richter law \citep{Gutenberg1944}.
+Subsequently, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through the visibility graph approach and found that the properties of the graph were correlated to the seismic $b$-value in the Gutenberg-Richter law \citep{Gutenberg1944}.
 In particular, \citet{Telesca2013} extracted the characteristics of the visibility graph for five different tectonic seismic regions in the subduction zone and found that the slope in the linear relationship between earthquake magnitude, $M$, and the inter-event visibility in the graph defined as the connectivity degree parameter, $k$, was correlated with the $b$-value.
@@
 In a similar article, \citet{Telesca2014} studied the seismicity of the 2002--2011 Pannonian region using the visibility graph method for two sub-catalogs of shallow and deep earthquakes.
-They extracted the visibility graph characteristics for each group of events and confirmed that there was a close correlation between the Gutenberg-Richter $b$-value and the slop of the $k$-$M$ relationship obtained from the visibility graph.
+They extracted the visibility graph characteristics for each group of events and confirmed that there was a close correlation between the Gutenberg-Richter $b$-value and the slope of the $k$-$M$ relationship obtained from the visibility graph.
 According to \citet{Telesca2014}, the high linear correlation coefficient value (close to 1.0) between the $b$-value and the $k$-$M$ slope indicates that this relationship exhibits a nearly universal character.
@@
 We first summarize the dataset, including a description of the seismic catalog and its completeness based on a recent work on the seismicity of the region \citep{Khoshnevis2016}.
-We then present results obtained for the region regarding the relationship between the the graph's $k$-$M$ slope and the seismicity $b$-values for the three seismic areas, analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, and present results for the variation of <$T_c$> through time.
+We then present results obtained for the region regarding the relationship between the the graph's $k$-$M$ slope and the seismicity $b$-value for the three seismic areas, analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, and present results for the variation of <$T_c$> through time.

### 2016-08-26 results.tex
deleted the hyphen in kopeh dagh from text and figures
final changes suggested by Luciano

@@
 On the other hand, as we will see below, if the sequence window is sufficiently small, then the $k$-$M$ slope value shows a relative dependence on time and thus provides insight about the variation of the seismicity as the sequence progresses.
-Note also that the threshold value of $M_c$ is significantly smaller for Azerbaijan than for Alborz or Kopeh-Dagh.
+Note also that the threshold value of $M_c$ is significantly smaller for Azerbaijan than for Alborz or Kopeh Dagh.
 This is due in part to the fact that the latter two zones were more seismically active in the time period under consideration.
@@
 Figure \ref{fig:tc} shows the variation of <$T_c$>, the $k$-$M$ slope, and the $b$-value with time for each of the three seismic zones in northern Iran.
+The time-magnitude sequence is also included for reference.
 Note that the behavior of the $k$-$M$ slope and the $b$-value is very similar along time for all three zones.
 This is consistent with the results presented before.
-In the figure, and include the time-magnitude sequences.
 We note that there seems to be a correlation between the behavior of the $b$-value in time with the occurrence of some of these larger events.

### 2017-06-14 response.tex
First revision draft for PAAG.

\setlength{\paperwidth}{210mm}
\setlength{\paperheight}{297mm}% fixed.

\documentclass{article}

\usepackage[review]{myreviewpckg}

\usepackage{textcomp}
\usepackage{simplemargins}

\clubpenalty=10000  % Orphan - First of paragraph left behind
\widowpenalty=10000 % Widow  - Last of paragraph sent ahead

\setallmargins{1in}

\begin{document}

% ******************************************************************
% *************************** REVIEWER 1 ***************************
% ******************************************************************

Here are the main changes:

1) We use the whole catalog instead of declustered catalog
2) We added also 2016 seismicity
3)

\begin{center}
	\bf
	\large
	Authors' Response to Reviewer 1
\end{center}

\noindent
We thank the reviewer for his/her comments and suggestions, which helped us improve the manuscript. To help the review process, in the annotated manuscript version of the paper, we have highlighted the most relevant changes that resulted from these comments in green font. In the following, we provide a response to each comment. The original comments are in italic black font, followed by our responses in regular blue font.
\vspace{2ex}
\newline

\introcomment{~}{%
The authors perform a seismic hazard analysis for northern Iran using a newly developed source model from smoothed seismicity. The work is an important contribution to seismic hazard analyses in Iran. Development of the seismic source model follows a careful analysis of the earthquake catalogs for information about spatially varying earthquake rates, maximum magnitudes and b-values. The authors are careful to acknowledge that alternative means for estimating earthquake recurrence - and for other components of the source and ground motion characterization - also exist, and that this work is only one approach for characterizing hazard in the region.
}

\comment{1}{%
Page 3, Line 71: A short, summary description of previous source models would highlight the contribution of this work. In particular, summary details of the work by Khodaverdian et al should be included to indicate how the approach of the authors differs from previous work.
}

\response{%
We modified parts of the introduction as well as other sections to highlight in a more explicit manner the differences in our study with respect to other previous efforts. In the case of Khodaverdian et al (2016), the major difference is in the way the seismicity parameters $b$ and $M_{\max}$ are calculated. This is mentioned in the Introduction, and addressed with more clarity in Section 4 (page 11, line 312) and in Section (page 17, line 495). As mentioned there, the difference resides in the fact that Khodaverdian et al (2016) compute seismic parameters for grid cells of size 1\textdegree{} $\times$ 1\textdegree{}. This means the they compile earthquake catalogs for each grid point considering events within 200 km radius from the grid point, whereas we assume the seismic parameters to be uniform for each tectonic seismic region.
}

\comment{2}{%
Page 3, line 77: Fault-based/geologic-based earthquake recurrence estimates
}

\response{%
Added, thanks.
}

\comment{3}{%
Page 4, line 106: Should this be northwest?
}

\response{%
Yes. Fixed.
}

\comment{4}{%
Page 6, line 168: It would be good to add a reference for the GEM effort.
}

\response{%
We do not have a direct reference to GEM but added a citation to Zare et al (2014), where the connection to GEM is mentioned explicitly.
}

\comment{5}{%
Pages 7--8: Discussion about identifying the completeness level of the earthquake catalogs is a bit confusing. Typically, one either specifies a minimum magnitude of completeness ($M_c$) and then tries to identify the earliest time for which events or complete; or, one specifies a year and computes the corresponding $M_c$. In reading the text, it appears that both methods were used. Please clarify.
}

\response{%
The new version of the Completeness sub-section now clarifies this point. The reviewer is right in that we used both methods, but we originally did not clearly explain the procedure. We first compute the $b$ and $M_{\max}$ values for each region, or the uniform model, using the HA3 package written by Dr.~Kijko. At this point, $M_c$ is used as an input to the HA3 software. We then used the Seiskit package written by Dr.~Frankel to compute the smoothed seismicity $a$-values. At this point, SeisKit uses the start year of completeness for each magnitude range. Please see changes in page 8, lines 211 and 229.
}

\comment{6}{%
Pages 7--8: The authors should note that some authors use an alternative smoothing kernel $(~exp(-(D/2*sigma)^2)$. Comparison of the smoothing length between different studies may require consideration of a $sqrt(2)$ factor.
}

\response{%
We added a note to this effect in Section 4, and cite the work of Moschetti (2015) as an example. A complete analysis of the smoothing length and its influence on the hazard analysis, however, is out of the scope of the present study. The modifications done can be found in page 10, line 295.
}

\comment{7}{%
Page 7--8: In addition to the Mirzaei et al (1997) reference, some authors employ likelihood testing of smoothed seismicity rate models to identify optimal smoothing lengths for adaptive and fixed smoothed seismicity methods (e.g., Werner et al., 2011; Moschetti, 2015).
}

\response{%
We included a note to reflect this and added the references suggested by the reviewer. The changes can be seen in page 11, line 304.
}

\comment{7}{%
Page 9: Kagan and Jackson (1994) should also be included in the reference list.
}

\response{%
We added the suggested reference to the list provided in page 10, line 278.
}

\comment{8}{%
Page 10, line 302: ``...subjective decisions and any reasonable choice...'' I would disagree that these are subjective decisions. My opinion is that you have applied scientific judgment. You clearly need to communicate where judgment is applied; however:
\\[5pt]
Details about the implementation of the two seismicity rate models (U, R) should be expanded. Are sub-catalogs developed for the five separate regions and then used to develop separate a-grids? Presumably, the separate rate files are then used to compute hazard curves and are summed at each location.
\\[5pt]
A logic tree would be of great benefit in clarifying how the source models are combined. In particular, it would clarify the weighting from different completeness levels.
\\[5pt]
Plots of seismicity rates from the R and U models would be of interest and particularly relevant given that the smoothed seismicity model is the main contribution of this work to hazard analyses for Iran.
}

\response{%
The reviewer was right to suggest that our original approach to present a combination of the R and U models was not the best. In the revised manuscript we have addressed this in two basic manners. First, we now provide a better explanation of the rationale behind both models and the reasons to provide a combined result. Second, we adopted the suggestion of implementing a logic tree approach in our analysis. The adopted logic tree allows us to consider the epistemic uncertainty in the defintion of the seismic zones and also allowed us to include uncertainties in the seismic parameters $b$ and $M_{\max}$. For each branch of the logic tree we assigned weights following literature recommendations and our own judgement. In total, traversing and combining the different branches meant to conduct 162 runs ( $3 M_{\max} \times 3 b \times (5 \mbox{regions} + 1 \mbox{uniform}) \times 3 \mbox{GMPE}$) to get the combined results of the 2 basic models (R and U), three values of $b$ and $M_{\max}$ and three GMPE alternatives. The associated changes can be seen in various sections of the revised manuscript, and in particular in the new Section 7 and the Results Section 8.
}

\comment{9}{%
Page 14, line 391: The incorporation of smaller earthquakes $(M<5)$ will have a significant influence on the hazard associated with PGA. Recent papers by Atkinson and others have demonstrated this effect. You may wish to argue that $M_{\min}$ was chosen based on the expected smallest magnitude capable of causing damage.
}

\response{%
We revised the computations and now present results for events with $M_w > 4.5$. The text was modified accordingly (see page 4, line 94).
}

\comment{10}{%
Figure 7: Is the magnitude-frequency distribution just a truncated ($M_{\min}$, $M_{\max}$) Gutenberg-Richter model? Figure 7 suggests that the MFD may be tapered?
}

\response{%
Yes, it is truncated Gutenberg-Richter model. We now make this explicit in the caption of the figure.
}

\comment{11}{%
Page 12, line 345: ``...controls the spatial extent to which the local occurrence of earthquakes...'' I would argue that the smoothed seismicity controls the local occurrence and spatial distribution of earthquakes and that the GMPEs control the intensity level at a particular site given earthquake locations and magnitudes from your source model.
}

\response{%
That is correct. We have modified this sentence accordingly. Please se changes in page 13, line 365.
}

\comment{12}{%
Page 13, line 361: Change ``approached'' to ``approach'' and ``lead'' to ``led.''
}

\response{%
This part of the text was modified and the requested change may no longer apply, at least in regard to the first suggestion. Regarding the second suggestion, we do not quite agree. Although there was a typo, the way the sentence was structured, the corrected version uses ``leads'' instead.
}

\comment{13}{%
The approach to generating Figure 10 should be clarified. It appears that the probabilistic ground motions from the R and U model are averaged and used to compute a standard deviation. The formal method for combining alternative models in PSHA is through the logic tree; this is equivalent to weighting the models in hazard (rate) space, rather than in ground motion (intensity, PGA) space. It appears that the authors have done the latter, though I may be incorrect. If this is the case, please correct. It is very reasonable to combine the R and U models to produce another alternative model. This work is not a comprehensive seismic hazard analysis, and presentation of probabilistic ground motions from the R, U and a weighted model would be reasonable goal. However, I would caution against comparing probabilistic ground motion maps with maps of seismicity because the varying $b$- and $M_{\max}$-values for the R model greatly complicate the comparison. As mentioned earlier, formal testing methods exist for ensuring consistency of observed earthquake locations with the smoothed seismicity models (see CSEP references, Zechar, Schorlemmer, Werner, Helmstetter, Jackson; Moschetti, 2015). Applying these methods is beyond the scope of this work, but might be recognized as a future direction.
}

\response{%
Thanks for the informative comment. In the original figure 10 we combined the regional (R) and uniform (U) results (i.e., we combined the probabilities of exceedance, and then computed the PGA) with similar weights (i.e., 0.5). The positive and negative standard deviation plots came from GMPE + Uncertainty and GMPE -- Uncertainty. Our original intention was to show the range of variation for PGA around the median value. However, in the revised version of the manuscript this is no longer done. The new figure corresponding to the (R,U) combined model (Fig.~12) is now the result of the complete logic tree analysis, which is a more appropriate approach to presenting the results of our analysis.
}

% ******************************************************************
% *************************** REVIEWER 2 ***************************
% ******************************************************************

\newpage

\begin{center}
	\bf
	\large
	Authors' Response to Reviewer 2
	\end{center}

\noindent
We thank the reviewer for his/her comments and suggestions, which helped us improve the manuscript. To help the review process, in the annotated manuscript version of the paper, we have highlighted the most relevant changes that resulted from these comments in green font. In the following, we provide a response to each comment. The original comments are in italic black font, followed by our responses in regular blue font.
\vspace{2ex}
\newline

\introcomment{~}{%
Review of Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity by Naeem Khoshnevis, Ricardo Taborda, Shima Azizzadeh-Roodpish, and Chris H. Cramer
}

\introcomment{~}{%
In this paper, the researchers present a new seismic hazard analysis of northern Iran. The paper makes use of the latest available data and methods, is thorough in its review of previous work, and is very well presented and written. I have a few suggestions that I think would improve the impact of their results. The annotated version of the manuscript contains additional and more specific suggestions.
}

\comment{1}{%
The authors present uncertainty in their hazard estimate but do not include a more exhaustive logic tree analysis. Effectively, they have two branches: a regional model and uniform model. It appears that they apply the aleatory uncertainty in the ground motion prediction relation to a form of epistemic uncertainty, effectively double counting this uncertainty in the hazard analysis. I would prefer to see a more standard logic tree analysis where multiple GMPEs (or a backbone plus and minus one standard deviation) and uncertainty in $a$-value, $b$-value, and $M_{\max}$, for example, are considered. Barring this analysis, I would remove figure 10 and references to hazard uncertainty.
}

\response{Thanks for the comment. Based on explanation of GMPEs section (please also see comment No.~27) we decided to address uncertainty with a backbone GMPE plus and minus one standard deviation. We also consider uncertainty in tectonic seismic regions through variations in the seismicity parameters $M_{\max}$, $b$, and combine the results using a standard logic tree analysis, as suggested. These changes are reflected at various points throughout the revised manuscript.}

\comment{2}{%
While I think that the regional and uniform models are generally correct within 1.5 degrees of the border, I think that outside of this region, they may be moderately underestimating hazard by not considering sources with 200 km of their region of interest. Their buffer zone for sources is presently 50 km.
}

\response{That is right. We increased the buffer zone up to 2 degrees. See page 4, line 100.}

\comment{3}{%
It would be good if the abstract is more specific about the results. Where is the hazard greatest? What sources contribute to regions of higher hazard?
}

\response{We modified the abstract accordingly, but do not provide too much detail as that would significantly increase the length of the abstract, which is not desirable. See new lines 23--25.}

\comment{4}{%
In the second paragraph of the introduction, I would include a reference to a figure of the region to help readers less familiar with the area. This figure should also be referred to in subsequent paragraphs. It is probably sufficient to move reference to figure 1 here.
}

\response{We added a reference to figure 1 in page 2, line 40.}

\comment{5}{%
Line 39: eight $\to$ eighth
}

\response{Fixed.}

\comment{6}{%
Line 55: focuses in $\to$ focuses on
}

\response{Done. Thanks.}

\comment{7}{%
Line 56: Please be more specific about how your analysis differs from previous analyses.
}

\response{We modified the introduction to better explain the method and parameters. However, there are some details we still believe go better within the subsequent sections. Changes correspond to lines 54 to 76.}

\comment{8}{%
Line 60: Can you be more specific? What are the other indicators?
}

\response{In hindsight that was not the best choice of words. Since we modified this part of the introduction, the new text does no longer includes this sentence.}

\comment{9}{%
Line 71: Include reference.
}

\response{Done. Thanks.}

\comment{10}{%
Line 78: reduce $\to$ acknowledge
}

\response{Fixed.}

\comment{11}{%
Line 99: Is 0.5 degrees enough? To what distance do you do your ground motion calculations? In the western United States, they are done to 200 km. In the central and eastern, they are done to 1000 km. Depending on this value, you should include sources up to this distance from your region of interest.
}

\response{We reanalyze the hazard with 2 degrees buffer zone. This is reflected in the new Figures 1 and 3, and in the text (line 100) as well as, of course, in the results.}

\comment{12}{%
Line106: northeast $\to$ northwest
}

\response{Done. Thanks}

\comment{13}{%
Line 114: There is no previous mention of this earthquake. I am not sure to which earthquake you are referring. Should either the 1721 or 1780 earthquakes be the Shebli earthquake?
}
\response{Thanks for the comment. It is the 26 April 1721 $M_s$ 7.7 earthquake. The change is now in page 4, line 114.}

\comment{14}{%
Line 180: The smaller events should also help to inform the G-R relationship.
}

\response{Thanks for the comment. Added to the text in line 182.}

\comment{15}{%
Line 182: How come this study doesn't appear in Table 3. Do they not calculate PGA for 2 and 10\% exceedance in 50 years?
}

\response{They did not provide a numerical value, or numbers on the contour lines. However, we read the images with Matlab and located the values and now include them in the new version of Table 3.}

\comment{16}{%
Line 192: What is the total number of events before and after declustering?
}

\response{Number of events before decluttering: 10,441; total foreshocks: 971; total aftershocks: 4,206; declustered data: 5,254. It should be noted that these numbers are representing the events in the complete study region (including the buffer zone). It partly includes events from Central and Zagros region. For the completeness, we studied the whole data for each region. This is now explained in page 7, line 195.}

\comment{17}{%
Line 224: Why did you use this method? What are the benefits of one or the other?
}

\response{Both methods have been used extensively in previous studies. We just picked one, mainly so due to ease of implementation, which also allowed us to have complete control over the final selection. The text was incorrectly implying that the goodness-of-fit rest method had benefits over the MAXC method. We fixed this and now state our reasons in a more transparent way. See page 8, line 229.}

\comment{18}{%
Line 232: It is unclear how you chose $M_c$. In some cases, it looks like you chose the peak goodness-of-fit value, but in others you did not. Please be more specific about how Mc was chosen.
}

\response{According to Wiemer and Wyss (2000), the priority is picking the magnitude which has the peak goodness-of-fit value. However, in some cases for two or a couple of magnitudes the goodness-of-fit scores are not considerably different. In these cases, we pick the minimum magnitude, even though it does not have the peak goodness-of-fit value, in order to preserve more data. We also consider the decay of the cumulative number of events. This is now explained in the revised manuscript in pages 8 and 9.}

\comment{19}{%
Line 267: add 'and'
}
\response{Added. Thanks.}

\comment{20}{%
Line 289: You might also cite the 2014 USGS National Model (Petersen et al., 2014) and the Afghanistan seismic hazard maps (Boyd et al, 2007), which include spatial variability in the smoothing parameter.
}

\response{We included the suggested reference, though the actual publication year is 2015.}

\comment{21}{%
Line 297: provided below $\to$ provided in the next section.
}

\response{Fixed.}

\comment{22}{%
Line 300: allows to draw information $\to$ allows one to draw information
}

\response{Done.}

\comment{23}{%
Line 323: Be more specific about how HA3 computes $b$ and $M_{\max}$. What is its method?
}

\response{This code uses the procedure described in Kijko and Sellevoll (1989). We added a sentence making this explicit in page 12, line 341.}

\comment{24}{%
Line 335: Different seismic zone will not necessarily have difference values of $b$ and $M_{\max}$. Change to this: Different seismic zone may have different values of $b$ and $M_{\max}$.
}

\response{Modified. Thanks. See line 354.}

\comment{25}{%
Line 337: a means to reduce epistemic $\to$ a means to account for epistemic
}

\response{Done.}

\comment{26}{%
Line 361: lead $\to$ leads
}

\response{Fixed. Thanks.}

\comment{27}{%
Line 364: How do you address the epistemic uncertainty generally introduced by using a suite of GMPEs?
}

\response{This is a point that was also raised by Reviewer 1. As mentioned in Atkinson and Adam (2013) and Atkinson et al (2014), using different GMPEs with different logic tree weights from different literature is not necessarily the best way to model the epistemic uncertainty in GMPEs. Especially when the mean of various GMPEs are too close to each other. We prefer to use the alternative GMPEs and applicable data to guide the choice of a representative or central GMPE, and to define representative upper and lower GMPEs using the standard deviation of the chosen relationship. In order to address these concerns we now use the logic tree scheme shown in Fig.~9 and make comments with respect to this in various points throughout the revised version of the manuscript, but in particular in pages 13 and 14, lines 380--397.}

\comment{28}{%
Line 365: add 'and'
}

\response{Added. Thanks.}

\comment{29}{%
Line 370: Could you consider other depths to help fill out your range of epistemic uncertainty?
}

\response{Not really. At least we think it would not be appropriate to do so. The Kalkan and Gulkan (2004) attenuation relationship was originally generated for Turkey. Later, Zafarani and Mousavi (2014) found that this GMPE yielded acceptable results for PGA for northern Iran if calibrated with the values we report in the manuscript. Since the high accuracy achieved by using this GMPE depends on the the current choice of depth, we ignore what would be the effect of considering the variability of $h$, and suspect it will likely be to the detriment of the analysis. We make tangential mention to this in the new Section 7. See page 15, line 424.}

\comment{30}{%
Line 371: How does this value compare with the models you decided not to use?
}

\response{In the revised version we use a backbone GMPE, in addition to GMPEs derived using plus and minus one standard deviation. Therefore, this comment does no longer apply.}

\comment{31}{%
Line 376: In this case, you should consider all sources with 200 km of your area of interest.
}
\response{We modified the buffer zone and now do this. Thanks.}

\comment{32}{%
Line 394: 50-years $\to$ 50-year
}
\response{Done.}

\comment{33}{%
Line 420: with concentration $\to$ with a concentration
}

\response{Added. Thanks.}

\comment{34}{%
Line 422: I would have stated this differently. It looks like the lower $b$-value in Kopeh Dagh yields relatively high hazard in the R model whereas in the U model, this low b-value has leaked into the entire region and subsequently elevated seismic hazard in all areas outside of Kopeh Dagh.
}

\response{Based on the modification in GMPEs and uncertainties, we rewrote this description.}

\comment{35}{%
Line 428: Why equal weights?
}

\response{We added a comprehensive logic tree analysis and modified the weights. Please see figure 9, and the description given in the new Section 7.}

\comment{36}{%
Line 431: I'm not sure I quite understand this. The standard deviation in the attenuation relation is considered aleatory uncertainty and is present within the hazard curve. Adding it as epistemic as well will cause double counting. If you want to include figure 10, a proper logic tree analysis to include more forms of epistemic uncertainty should be performed. For example, add branches for uncertainty in which GMPE you choose, uncertainty in $b$-value, uncertainty in $M_{\max}$, uncertainty in $a$-value, uncertainty in smoothing parameter, etc.
}

\response{We modified the approach and now consider the uncertainties explicitly via a logic tree analysis. Therefore, we believe this no longer applies as the new approach is more appropriate.}

\comment{37}{%
Line 434: Just because the basic pattern appears to better follow faults in the region does not mean it's a better assessment, especially if the $b$-values are truly different between regions and better represented by the regional analysis.
}

\response{Agree. We believe, however, that this can be interpreted as a good indication of how the data is being captured by the analysis. We modified this.}

\comment{38}{%
Line 439: of city of Tabriz $\to$ of the city of Tabriz.
}

\response{Fixed. Thanks.}

\comment{39}{%
Line 450: for 2 and 10\%, respectively $\to$ for 2 and 10\% in 50 years, respectively.
}

\response{Done.}

\comment{40}{%
Line 453: for a 10\% probability of exceedance $\to$ for a 10\% probability of exceedance in 50 years.
}

\response{Done.}

\comment{41}{%
Line 455: 0.27--0.31 g for 10\% probability of exceedance $\to$ 0.27-0.31 g for the same exceedance probability
}

\response{Done.}

\comment{42}{%
Line 458: for 2 and 10\% $\to$ for 2 and 10\% in 50 years
}

\response{Done.}

\comment{43}{%
Line 461: our results are close or within $\to$ our results are close to or within
}

\response{Done.}

\comment{44}{%
Line 462: Can you explain the differences in their analysis relative to yours that lead to higher values?
}

\response{They used Maximum Credible Earthquake as $M_{\max}$. The maximum credible earthquake is largest earthquake that appears capable of occurring under the known tectonic framework for a specific fault or seismic source, as based on geologic and seismologic data, so it is higher than observation or data driven $M_{\max}$. We added the explanation to the text (see page 18, line 511).}

\comment{45}{%
Line 466: exceedance as functions of PGA $\to$ exceedance as functions of PGA, also known as hazard curves}

\response{Done.}

\comment{46}{%
Line 475: Can you explain the differences in the hazard analysis that led to differences in hazard?}

\response{We modified this paragraph and included a better description of the differences and results. See pages 18 and 19, lines 524--549.}

\comment{47}{%
Line 488: Not sure you can say this because you don't include fault specific sources, and you do not consider a more full range of epistemic uncertainty, e.g. you only use one GMPE (though you do consider two $b$-value and $M_{\max}$ based models).
}

\response{That is right. We restate the sentence and modified the conclusions accordingly.}

\comment{48}{%
Line 488: hazard analysis $\to$ hazard analyses
}

\response{Done.}

\comment{49}{%
Line 490: models as a mean $\to$ models as a means}

\response{Done.}

\comment{50}{%
Line 493: Though you suggest the uniform model is unrealistic on line 334.
}

\response{Our choice of words was not the best. We meant to say less realistic. We fixed the text accordingly.}

\comment{51}{%
Line 502: for providing advise $\to$ for providing advice}
\response{Done.}

\comment{52}{%
Line 509: Should this be Sunset?
}

\response{Yes. Thank you.}

\comment{53}{%
Page 25, Table 2: What did you do for the earthquakes occurring outside of these five zones?
}

\response{
As it can be seen in Figure 1, earthquakes outside the regions would be too far to be included. There are earthquakes above the Caspian see, for instance, and others in the country of Azerbaijan which were ignored because they were beyond the buffer zone (which as it was mentioned before, was expanded).}

\comment{54}{%
Page 26, Table 3: Specify units.}

\response{Done. Thanks.}

\comment{55}{%
Page 32, Figure 3: You should also show events in the buffer zone used to compute hazard.}

\response{Done.}

\comment{56}{%
Page 34, Figure 5: Which seismic zone corresponds to which color? It looks like either reporting or rates have changed over time. For example, I might argue that the red region was not complete for M3 and above until 2005.
}

\response{%
Thanks for the comment. The problem with that region is having less than and equal sign on magnitude 4. There are many earthquakes go to that category because of that condition. Since converting earthquake magnitude always has an error margin, we think the comment is relevant. Based on the data we assume 2005 as a completeness magnitude. We presented the legends at the bottom of the figure.
}

\comment{57}{%
Page 37: 10 percent of probability $\to$ 10 percent probability
}

\response{Done.}

\comment{58}{%
Page 39, Figure 11: Include horizontal lines indicating 2 and 10\% probability of exceedance in 50 years.
}

\response{Included.}

\comment{59}{%
Page 41, Figure 12: Can you include curves or points for the other studies in Table 3?
}

\response{We did and made comments about this in the Results section.}

\end{document}

### 2017-06-14 abstract.tex
First revision draft for PAAG.

@@
 %
-We present an analysis of the seismicity of northern Iran in the period between 2005 and 2015 using a recently introduced method based on concepts of graph theory.
+We present an analysis of the seismicity of northern Iran in the period between 2005 and \myrevision{2016} using a recently introduced method based on concepts of graph theory.
 The method relies on the inter-event visibility defined in terms of a connectivity degree parameter, $k$, which is correlated with the earthquake magnitude, $M$.
-Previous studies show that the slope of the $k$-$M$ correlation also observes a relationship with the $b$-value from the Gutenber-Richter law, thus rendering the graph analysis useful to examine the seismicity of a region.
+Previous studies show that the slope of the $k$-$M$ correlation also observes a relationship with the $b$-value from the Gutenberg-Richter law, thus rendering the graph analysis useful to examine the seismicity of a region.
 In addition, other topological properties of the network and dynamic properties of the magnitude-time series exhibit characteristics that seem to be associated with the occurrence of earthquakes, offering the possibility of correlating seismicity parameters with time.
 We apply this approach to the case of the seismicity of northern Iran, using an earthquake catalog for the tectonic seismic regions of Azerbaijan, Alborz, and Kopeh Dagh.
-We use results draw for this region with the visibility graph approach in combination with results from other similar studies to further improve the universal correlation between $k$-$M$ and $b$-values and show that the visibility graph approach can be considered as a valid alternative for analyzing regional seismicity properties and earthquake sequences.
+We use results drawn for this region with the visibility graph approach in combination with results from other similar studies to further improve the universal relationship between the slope of $k$-$M$ and $b$-value, and show that the visibility graph approach can be considered as a valid alternative for analyzing regional seismicity properties and earthquake sequences.

### 2017-06-14 conclusion.tex
First revision draft for PAAG.

--- 2016-08-21 conclusion.tex
@@
 
-Pending...
+We studied the seismicity of the three main seismic regions in northern Iran in the time period between January 2005 and December \myrevision{2016} using an approach based on the visibility graph method.
+We tested the applicability of this method for the specific region of interest and in reference to previous results from similar studies.
+The results confirm previous observations about the correlation that exists between the connectivity parameter $k$, the magnitude of the events in the sequence, the slope of this relationship or $k$-$M$ slope, and the $b$-value from the Gutenberg-Richter law.
+We obtained mathematical expressions for the region of interest as well as for so-called universal data collected from this study and previous additional analysis for other regions as well as data from experiments and found the relationships to have a good level of similarity.
+This is indicative of the general nature of the relationship between the $k$-$M$ slope and the $b$ value.
+\myrevision{The relationship found between k-M slope and b-value suggest that the topological properties of the VG are not unlinked with the seismological properties of  an earthquake sequence.} We also explored the potential relationships that can be drawn from a time-dependent visibility graph analysis and the variation of the seismicity in the region of interest.
+We found there may be a potential relationship between the $b$ value and the occurrence of earthquakes as well as with the graph's mean interval connectivity time parameter <$T_c$>, but additional research in regions with stronger events may be necessary before drawing stronger conclusions in this regard.
+\myrevision{Also further investigation has to be performed in the future to clarify the relationship between the k-M slopes as a pure mathematical object and the b-value and investigate the k-M slope with other earthquake network models.} The method used here, nonetheless, seems to provide an alternative and interesting approach to the analysis of the seismicity of a region.
 

### 2017-06-14 introduction.tex
First revision draft for PAAG.

@@
 
-In a relatively recent study, \citet{Lacasa2008} introduced a simple and computationally inexpensive approach to convert time-series into a particular kind of mathematical graphs known as visibility graphs.
+In a relatively recent study, \citet{Lacasa2008} introduced a simple and computationally inexpensive approach to convert time-series into a particular kind of mathematical graphs known as visibility graphs \myrevision{(VG)}.
 In this approach, the connection between the nodes in a network---here understood as events in a time series---is based on the visibility of each node or event with respect to other previous and later events in a time sequence.
-Over the last decade, this method has been found to be applicable to multiple fields, including economics, medicine, and geophysics \citep[e.g.,][]{Yang_2009_PA, Elsner_2009_GRL, Telesca2012_CSF, Wang2012, Long2013}.
+Over the last decade, this method has been found to be applicable to multiple fields, including economics, medicine, and geophysics  \myrevision{in different ways, including directed and undirected 1D or 2D approaches} \citep[e.g.,][]{Yang_2009_PA, Elsner_2009_GRL, Telesca2012_CSF, Wang2012, Long2013}.
 
@@
 
-In this article we use the visibility graph method to analyze the seismicity of northern Iran from 2005 to 2015.
-We focus our analysis on these years because in a previous study we observed that the latest decade of seismic records in the region offered the most complete catalog of events \citep[e.g.][]{Khoshnevis2016}.
+In this article we use the visibility graph method to analyze the seismicity of northern Iran from 2005 to \myrevision{2016}.
+We focus our analysis on these years because in a previous study we observed that the latest decade of seismic records in the region offered the most complete catalog of events \myrevision{\citep[][]{Khoshnevis2017}}.
 Upon a brief review of the basic concepts of the method and its applications, we describe the seismicity of northern Iran considering three dominant seismic regions: Azerbaijan, Alborz, and Kopeh Dagh.
 These are regional areas of considerable ground shaking activity, with average seismic rates varying between about 0.17 and 3.25 events per year \citep[e.g.,][]{Nemati2015}.
-The considerable amount of earthquakes registered in a 10-year period facilitates the analysis done with the visibility graph approach within what would otherwise be considered a relatively short period of time, and serves as a good case study to test the capabilities of the method.
-We first summarize the dataset, including a description of the seismic catalog and its completeness based on a recent work on the seismicity of the region \citep{Khoshnevis2016}.
+The considerable amount of earthquakes registered in a \myrevision{11}-year period facilitates the analysis done with the visibility graph approach within what would otherwise be considered a relatively short period of time, and serves as a good case study to test the capabilities of the method.
+We first summarize the dataset, including a description of the seismic catalog and its completeness based on a recent work on the seismicity of the region \myrevision{\citep{Khoshnevis2017}}.
 We then present results obtained for the region regarding the relationship between the the graph's $k$-$M$ slope and the seismicity $b$-value for the three seismic areas, analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, and present results for the variation of <$T_c$> through time.

### 2017-06-14 methodology.tex
First revision draft for PAAG.

@@
 And invariance: scaling or time-shifting the series does not change the resulting visibility graph, provided the transformation is done under affine conditions \citep{Lacasa2008}.
+\\
+\myrevision{In terms of earthquake catalog, the visibility graph studies the relation between earthquake events.
+Relation between small and large earthquakes are investigated in different studies.
+Lee et al (2009), based on developing LRCS model, in which is assumed that the occurrence of an earthquake leads to a release of energy with long range effects like in real earthquake fault systems, it has been known that earthquakes are long-range correlated.
+The visibility connections between the "hubs" (large events) and events even located very far on time could represent such long-range correlated behavior.}
 
 Figure \ref{fig:vg} shows an example of a visibility graph for a portion of one of the magnitude-time series to be considered later in this study.
+\myrevision{It is worth to mention that we apply 1D visibility graph analysis (which applies on time dimension and not space) on the catalog as a magnitude time series}.
 For each event $i$ we compute the connectivity degree, $k$, which is the sum of the connections to all other events $j$ visible by the $i$th event.

### 2017-06-14 results.tex
First revision draft for PAAG.

@@
 
-We generate the visibility graph for each sub-region of interest using the time-magnitude sequences shown in Fig.~\ref{fig:mag-time}.
-The number of nodes in each graph is the same as the (declustered) number of events shown in Table \ref{tab:seismicity}, and the links between inter-visible events are established following the condition in equation (\ref{eq:vg}), as in the example shown in Fig.~\ref{fig:vg}.
+We generate the \myrevision{1D} visibility graph for each sub-region of interest using the time-magnitude sequences shown in Fig.~\ref{fig:mag-time}.
+The number of nodes in each graph is the same as the (\myrevision{complete catalog}) number of events shown in Table \ref{tab:seismicity}, and the links between inter-visible events are established following the condition in equation (\ref{eq:vg}), as in the example shown in Fig.~\ref{fig:vg}.
 (We do not include a visualization of the complete sequence graphs because the links are so many, it is only practical to visualize the graphs of short sequences.) We then collect information about the number of inter-visibility links associated with each event (connectivity degree, $k$) and categorize the events in magnitude bins of size $\Delta M = 0.1$, as mentioned in the Methodology section.
@@
 	\centering
-	\includegraphics[width=\textwidth]{figures/pdf/figure-06} 
+	\includegraphics[width=\textwidth]{figures/pdf/figure-06-rev.pdf} 
 	\caption{Scattered distribution of events in the magnitude-connectivity degree plane and linear regressions obtained for the $k$-$M$ relationships for the three seismic regions in northern Iran.
@@
 Next, we examine the relationship between the $b$-values from Table \ref{tab:seismicity} and the $k$-$M$ slope values shown in Fig.~\ref{fig:km}.
-Figure \ref{fig:regression} shows the scattered results for $k$-$M$ slope versus $b$-value for the three tectonic seismic regions in northern Iran along with the data-points obtained for the analysis of the magnitude-time sequences of the Mexican subduction zone \citep{Telesca2013} and the Pannoninan seismic zone \citep{Telesca2014}, as well as other experimental results \citep{Telesca2014-pone}.
-Figure \ref{fig:regression} also includes the results of different linear regressions between the $b$-value and the $k$-$M$ slope.
+\myrevision{The b-value, by definition, represents the proportion between the amount of large events and that of small events.} Fig.~\ref{fig:regression} shows the scattered results for $k$-$M$ slope versus $b$-value for the three tectonic seismic regions in northern Iran along with the data-points obtained for the analysis of the magnitude-time sequences of the Mexican subduction zone \citep{Telesca2013} and the Pannoninan seismic zone \citep{Telesca2014}, as well as other experimental results \citep{Telesca2014-pone}.
+\myrevision{According to Scholtz (1968) b-value for microfractures in rocks is reported ranging between 0.11 and 2.58.
+Using different synthetic and real catalog, in this study we cover a broad range from low b-value (synthetics) to high b-value(subduction zone)}.
+Fig.~\ref{fig:regression} also includes the results of different linear regressions between the $b$-value and the $k$-$M$ slope.
 Each regression reflects the addition of new data-points from different studies.
@@
 \begin{equation}
-	b = 0.078 + 0.085 m \, .
+	b = 0.073 + 0.084 m \, .
 	\label{eq:universal.bm}
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{figures/pdf/figure-07} 
+	\includegraphics[width=0.45\textwidth]{figures/pdf/figure-07-rev.pdf} 
 	\caption{Correlation between $k$-$M$ slope and $b$-value as drawn from the results of the present study for the region of northern Iranian and three other previous studies, including analysis of the Mexican subduction zone \citep{Telesca2013}, the Pannonian seismic zone \citep{Telesca2014}, and results from two experiments \citep{Telesca2014-pone}.
@@
 On the other hand, as we will see below, if the sequence window is sufficiently small, then the $k$-$M$ slope value shows a relative dependence on time and thus provides insight about the variation of the seismicity as the sequence progresses.
-Note also that the threshold value of $M_c$ is significantly smaller for Azerbaijan than for Alborz or Kopeh Dagh.
-This is due in part to the fact that the latter two zones were more seismically active in the time period under consideration.
+\cmmnt{Note also that the threshold value of $M_c$ is significantly smaller for Azerbaijan than for Alborz or Kopeh Dagh.
+This is due in part to the fact that the latter two zones were more seismically active in the time period under consideration} \myrevision{In this study due to using windowing method, we consider a very conservative completeness magnitude}.
 However, according to \citet{Telesca2012}, the threshold magnitude has a minor effect in the graph parameters.
@@
 To further explore the sensitivity of the graph properties to the number of events in each catalog and the value of the minimum magnitude, we randomly picked a significant number of sub-sequences from within the initial catalog compiled for each region, and repeated the analysis for each sub-sequence.
-In total, for each region, we extracted 200 new sub-sequences from the initial (pre-declustering) catalog.
+In total, for each region, we extracted 200 new sub-sequences from the \myrevision{whole} catalog.
 The number of events in each sub-sequence was varied randomly but chosen to be large enough to represent the seismic characteristics of each region.
-In particular, the minimum size of each sub-sequence was set to be $n \geq 150$, and the maximum size in the sequence was set to be as large as the original catalog (pre-declustering; see Table \ref{tab:seismicity}).
+In particular, the minimum size of each sub-sequence was set to be $n \geq 200$, and the maximum size in the sequence was set to be as large as the original catalog (\myrevision{whole catalog}; see Table \ref{tab:seismicity}).
 We forced the random sub-sequences to progress positively in time without altering the natural occurrence of events.
@@
 Next, we determined the value of $M_c$ and $b$ as previously done for the complete catalogs, created the graph for all events with $M \geq M_c$, and extracted the connectivity degree of the events in each sub-sequence.
+\myrevision{Note that the results of the whole catalog for each seismic region is different from Fig.~\ref{fig:regression}.
+In Fig.~\ref{fig:regression} we choose a time dependent completeness magnitude which is conservative and requires inspection.
+In order to keep uniformity in the random data test we computed the completeness magnitude through GFT for all subsamples and the whole catalog of each seismic region.
+Determination of completeness magnitude based on the best score of GFT between synthetic catalog and subsamples could be controversial.
+It is possible to choose very large $M_c$ just because of slightly higher GFT score than smaller magnitudes.
+This could result in a sequence  of data where is not completely a representative of the domain.
+However, knowing these source of uncertainties, the randomly generated data conforms the fact that the method is fairly robust for the catalog size and completeness magnitude; where we can easily distinguish the 3 seismic region border.
+There are some outlier data due to subsamples of aftershocks of big earthquakes.
+These sequences represent different $k-M$ and $b-value$ relationship.
+These sequences do not represent the dominant seismicity pattern of the region.
+In the declustered catalog (is not presented here) we do not see these outliers.}
 
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-08} 
-	\caption{\textbf{(a)} Correlation between $k$-$M$ slope and $b$-values for 200 random sequences extracted from the initial catalogs of the three northern Iranian seismic regions considered in this study (scattered symbols), including the mean values (empty symbols with thick border) and the data points obtained from the analysis of the complete catalog (solid symbols), along with the linear regressions of each sample as indicated in the legend.
+	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-08-rev.pdf} 
+	\caption{\textbf{(a)} Correlation between $k$-$M$ slope and $b$-values for 200 random sequences extracted from the \myrevision{whole} catalogs of the three northern Iranian seismic regions considered in this study (scattered symbols), including the mean values (empty symbols with thick border) and the data points obtained from the analysis of the complete catalog (solid symbols), along with the linear regressions of each sample as indicated in the legend.
 \textbf{(b)} Mean, $\pm1$ standard deviation, and coefficient of variation (in percent) for the $k$-$M$ slope values of the three seismic zones in northern Iran.
@@
 
-Figure \ref{fig:random}a shows scattered points for all the individual $k$-$M$ slope and $b$-value pairs for all the sub-sequences that were randomly picked from the initial catalogs of each region in northern Iran (small symbols).
+Fig.~\ref{fig:random}a shows scattered points for all the individual $k$-$M$ slope and $b$-value pairs for all the sub-sequences that were randomly picked from the initial catalogs of each region in northern Iran (small symbols).
 Figures \ref{fig:random}b and \ref{fig:random}c show the variability of the $k$-$M$ slope and $b$-value, respectively.
@@
 We note that the values of the $k$-$M$ slope are slightly smaller when obtained with the random sequence analysis, whereas the $b$ values seem more stable.
+
+\cmmnt{
  The comparisons of the regressions, however, indicate that the analysis of the random sub-catalogs leads to a result more in line with the universal results obtained when considering multiple seismic zones.
@@
 \begin{equation}
-	b = 0.080 + 0.093 m \, .
+   	b = 0.045  +0.390 m \, .
 	\label{eq:iran.bm}
@@
 In this particular case, the analysis for northern Iran leads to a relationship in which the $b$-value increases more rapidly with $m$ than in the case of the regression obtained for the universal data.
-The similarity between the two equations, however, is a positive sign of the stability of the method.
+The similarity between the two equations, however, is a positive sign of the stability of the method.}
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{figures/pdf/figure-09} 
-	\caption{Variation of <$T_c$>, $k$-$M$ slope and $b$-value as with respect to time for three seismic zones for a moving window analysis of the visibility graphs of sub-sequences of 20 consecutive events, along with the magnitude of events in the 2005--2015 period.
+	\includegraphics[width=0.75\textwidth]{figures/pdf/figure-09-rev.pdf} 
+	\caption{Variation of <$T_c$>, $k$-$M$ slope and $b$-value as with respect to time for three seismic zones for a moving window analysis of the visibility graphs of sub-sequences of \myrevision{50} consecutive events, along with the magnitude of events in the 2005--\myrevision{2016} period.
 Black triangles indicate the occurrence of major earthquakes in each of the regions, with the corresponding magnitude at the top of each symbol.
@@
 In this case, we are interested in using a small number of events to capture the relevance of each new event as the window moves in time.
-We tried different numbers and finally chose 20 events as the moving window sequence size.
-This selection was also convenient given the smaller total number of declustered events in the catalog of Azerbaijan.
-When we tested larger number of events, we found that we could not properly observe the changes in the different parameters with time.
-On the other hand, when we used smaller sequence sizes, the values deviated more significantly from the random and complete catalog results obtained previously.
-At this point it is also of interest to compute the value of <$T_c$> explained in the Methodology section.
+We tried different \myrevision{window size (20-100 events per window) for each seismic zone.
+The characteristics of major events are not considerably changing due to window size.
+There is a trade of in choosing the window size.
+Small windowing size will highlight the local changes in the time series, however, in the mean time it won't represent a true seismicity characteristic of the subsample (e.g., b-value).
+We choose window size as 50 to be small enough to represent the variation of k-M, b-value and Tc in time and large enough in agreement with Woessner and Wiemer (2005) who found that at least the number of events has to be 50 to get reliable estimate of b-value.}  At this point it is also of interest to compute the value of <$T_c$> explained in the Methodology section.
 
@@
 Note that the behavior of the $k$-$M$ slope and the $b$-value is very similar along time for all three zones.
-This is consistent with the results presented before.
+\myrevision{Specially in the case of Alborz where because of higher number of events the correlation is easily seen.} This is consistent with the results presented before.
 We note that there seems to be a correlation between the behavior of the $b$-value in time with the occurrence of some of these larger events.

### 2017-06-14 seismicity.tex
First revision draft for PAAG.

@@
 In it, Iran is divided into six seismic regions: Azerbaijan, Alborz, Kopeh Dagh, Zagros, Central-East Iran, and Makran.
+\myrevision{Each of these seismic regions and in general Iranian plateau are studied from different perspectives \citep[e.g.,][]{Zafarani2017testing,Sedaghati2017partially,Golara2014, Nemati2015}}.
 Our focus, however, is on the northern part of Iran, for which we define a region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:study_region}.
@@
 	\includegraphics[width=\textwidth]{figures/pdf/figure-03} 
-	\caption{Declustered instrumental seismicity of northern Iran for the 2005--2015 period, considering only the events in the seismic zones of interest, namely Azerbaila, Alborz, and Kopeh Dagh.
+	\caption{\myrevision{Instrumental} seismicity of northern Iran for the 2005--\myrevision{2016} period, considering only the events in the seismic zones of interest, namely Azerbaila, Alborz, and Kopeh Dagh.
 The size of symbols are proportional to the magnitude of the events, as indicated by the artificial scale shown on the right.
@@
 We are, however, interested in the most recent instrumental seismicity.
-In particular, we focus on events recorded in the last decade, between January 2005 and December 2015.
-We focus our analysis on this magnitude-time sequence period because in a previous study we observed that the latest decade of seismic records in northern Iran offered the most complete dataset of recorded events, especially for the case of small $M < 4$ earthquakes \citep[e.g.][]{Khoshnevis2016}.
+In particular, we focus on events recorded in the last decade, between January 2005 and December \myrevision{2016}.
+We focus our analysis on this magnitude-time sequence period because in a previous study we observed that the latest decade of seismic records in northern Iran offered the most complete dataset of recorded events, especially for the case of small $M < 4$ earthquakes \myrevision{\citep[][]{Khoshnevis2017}}.
 
 We compiled a catalog of all recorded earthquakes using data downloaded from the International Institute of Earthquake Engineering and Seismology, IIEES (see the Data and Resources section).
-The obtained dataset contained a mixture of earthquake magnitude scales, including: moment, $M_w$; local, $M_L$; body wave, $m_b$; surface wave, $M_s$; and duration $M_D$ magnitudes.
-We converted all earthquakes to moment magnitude, $M_w$.
-Magnitudes in the $M_L$, $m_b$, and $M_s$ scales were converted using the relationships defined in \citet{Zare2014}, whereas $M_D$ magnitudes were converted using the empirical relationship proposed by \citet{Deniz2010}.
+\myrevision{Instrumental catalog provided by IIEES} contained a mixture of earthquake magnitude scales, including: moment, $M_w$; local, $M_L$; body wave, $m_b$; surface wave, $M_s$; and duration $M_D$ magnitudes.
+\myrevision{All earthquakes of this study are reported in local $M_L$ magnitude scale.
+However, in order to keep consistency with other studies (e.g., completeness magnitude) we converted them to moment magnitude, $M_w$}.
+Magnitudes were converted using the relationships defined in \citet{Zare2014}.
 
-Foreshocks and aftershocks were removed from the catalog following a Poissonian occurrence model using the declustering method of \citet{Gardner1974}, in a manner consistent with previous catalog compilations available for the region \citep[e.g.,][]{Zare2014}.
+\myrevision{After conducting separate studies on the whole and declustered catalog, we found that the whole catalog results are ,although slightly different, comprehensive.
+On the other hand declustering could add some unwanted uncertainty (in using parameters for time and distance windows) to the resultant catalog and considerably reduce the number of events in each region's catalog}.
+Fig.~\ref{fig:seismicity} shows the epicenter location of instrumental earthquakes for the three seismic zones of interest.
+
+%Foreshocks and aftershocks were removed from the catalog following a Poissonian occurrence model using the declustering method of \citet{Gardner1974}, in a manner consistent with previous catalog compilations available for the region \citep[e.g.,][]{Zare2014}.
 Upon declustering, we divide the catalog into three sub-catalogs, each for one of the seismic zones under consideration.
-Fig.~\ref{fig:seismicity} shows the epicenter location of declustered instrumental earthquakes for the three seismic zones of interest.
 
-We then proceeded to determine the minimum magnitude of completeness, $M_c$, for each region's sub-catalog.
+We \cmmnt{then proceeded to} determine the minimum magnitude of completeness, $M_c$, for each region's sub-catalog.
 The value of $M_c$ is often determined using simple numerical analyses in combination with data inspection.
 Two common approaches are the maximum curvature (MAXC) and the goodness-of-fit test (GFT) methods \citep{Wiemer2001}.
-We use the GFT method as introduced by \citet{Wiemer2000}.
-In this method, the completeness magnitude is obtained such that the catalog satisfies---at a certain acceptance threshold---the Gutenberg-Richter power low, given an extended dataset of events.
+\myrevision{We compute the $M_c$ versus time using the \myrevision{MAXC} \cmmnt{GFT} method coded in ZMAP software} as introduced by \citet{Wiemer2000}.
+
+\cmmnt{In this method, the completeness magnitude is obtained such that the catalog satisfies---at a certain acceptance threshold---the Gutenberg-Richter power low, given an extended dataset of events.
 This extended dataset is composed of predicted and observed events, where the predicted events are generated based on a trial minimum magnitude.
@@
 \citet{Wiemer2000} suggests a goodness of fit of 90\% as an acceptable threshold to select $M_c$.
-However, not all frequency-magnitude distributions reach the 90\% mark, in which case $M_c$ can be selected by inspection.
+However, not all frequency-magnitude distributions reach the 90\% mark, in which case $M_c$ can be selected by inspection.}
 
-Figure \ref{fig:completeness} shows the goodness-of-fit values for the three seismic zones.
+Figure \ref{fig:completeness} shows the \cmmnt{goodness-of-fit} \myrevision{$M_c\ vs\ Time$} values for the three seismic zones.
 We indicate the selected value of $M_c$ for each region in the figure.
 We also obtained the $b$-value in the Gutenberg-Richter law for each region following the maximum likelihood estimation \citep{Aki1965}:
+\myrevision{
 % 
 \begin{equation}
-	b = \frac{log_{10}(e)}{\overline{M} - M_{min}} \, ,
+	b = \frac{log_{10}(e)}{\overline{M} - (M_{min} - \frac{\Delta M_{bin}}{2})} \, ,
 \end{equation}
+}
 % 
@@
 Here, the value of $M_{\min}$ is taken as the minimum completeness magnitude $M_c$ obtained or selected for each region's sub-catalog.
-Table \ref{tab:seismicity} shows the corresponding values of $M_c$ and $b$.
+\myrevision{In this study we assumed $\Delta M_{bin} = 0.1$}.
+Table \ref{tab:seismicity} shows the corresponding values of $M_c$ and $b$.\myrevision{The standard deviation of the estimate of b is calculated by using \citet{Shi1982standard} formula:}
+\myrevision{
+\begin{equation}
+	\sigma b = 2.3b^2\sqrt{\frac{\sum_{i=1}^{N}(M_i - \overline{M})^2}{N(N-1)}},
+\end{equation}
+where $N$ is the number of events in each catalog.
+}
 
+\cmmnt{
 \begin{figure}%[t]
 	\centering
-	\includegraphics[width=0.45\textwidth]{figures/pdf/figure-04} 
+	\includegraphics[width=0.45\textwidth]{figures/pdf/figure-04-rev} 
 	\caption{Completeness magnitude goodness-of-fit test (GFT) results and selected $M_c$ values for the three tectonic seismic regions in northern Iran as evaluated from the time-magnitude sequence of earthquakes during the 2005--2015 period.
@@
 \end{figure} 
+}
+
+\begin{figure}%[t]
+	\centering
+	\includegraphics[width=0.8\textwidth]{figures/pdf/figure-04-rev.pdf}
+
+	\caption{\myrevision{Completeness magnitude vs time results and selected $M_c$ values for the three tectonic seismic regions in northern Iran as evaluated from the time-magnitude sequence of earthquakes during the 2005--2016 period.}}
+	\label{fig:completeness}
+\end{figure}
 
@@
 	\fontfamily{lmss}\selectfont
-	\caption{Total and declustered number of earthquakes and seismic parameters $M_c$ and $b$ for the three seismic zones of northern Iran.}
+	\caption{Total number of earthquakes \myrevision{(before and after considering completeness magnitude)} and seismic parameters $M_c$ and $b$ for the three seismic zones of northern Iran.}
 	\centering\small
+	\myrevision{
 	\begin{tabular}{|ccccc|}
 		\hline
-		Region      & Total Num. & Declus.~Num. & \textit{M}c & \textit{b}-value \\ 
-		            & of Events  & of Events &             &                  \\
+		Region           & Total Num.  & $M_c$  & Num. of Events          & $b-value$ \\ 
+		                      & of Events     &             & in Complete Catalog  &                  \\
 		\hline
-		Azerbaijan  &        271 &        93 &         3.5 &             1.02 \\
-		Alborz      &       1262 &       794 &         2.6 &             0.77 \\
-		Kopeh Dagh  &        399 &       282 &         2.6 &             0.58 \\
+		Azerbaijan     &        1047     &  3.5       &        202                     &    0.85491 $\pm$ 0.0506 \\
+		Alborz            &        1898     &  3.0       &        575                     &    0.81578 $\pm$ 0.0279 \\
+		Kopeh Dagh  &         640      &  3.5       &        117                     &    0.78297 $\pm$ 0.0494 \\
 		\hline
 	\end{tabular}
+	}
 	\label{tab:seismicity}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figures/pdf/figure-05} 
-	\caption{Time-magnitude sequences for the northern Iran seismic zones of Azerbaijan, Alborz and Kopeh Dagh, during the period between 1 January 2005 and 31 December 2015.
+	\includegraphics[width=\textwidth]{figures/pdf/figure-05-rev} 
+	\caption{Time-magnitude sequences for the northern Iran seismic zones of Azerbaijan, Alborz and Kopeh Dagh, during the period between 1 January 2005 and 31 December \myrevision{2016}.
 The event occurrences are represented by vertical bars or sticks of length equal to the $M_w$ magnitude of each earthquake.
-These sequences correspond to the declustered catalog but in each case we consider only events with $M_w \geq M_c$.
+These sequences correspond to the \myrevision{whole} catalog but in each case we consider only events with $M_w \geq M_c$.
 As shown in Fig.~\ref{fig:vg}, the dots at the top of each stick represent the nodes of the visibility graphs.
@@
 Figure \ref{fig:mag-time} shows the final time-magnitude sequences for Azerbaijan, Alborz and Kopeh Dagh.
-Note that in the case of Alborz and Kopeh Dagh, we consider events in the declustered catalog down to $M_w \geq 2.6$, whereas in the case of Azerbaijan all events are $M_w \geq 3.5$.
+Note that in the case of \myrevision{Azerbaijan} and Kopeh Dagh, we consider events in the \cmmnt{declustered} catalog down to $M_w \geq 3.5$, whereas in the case of \myrevision{Alborz} all events are $M_w \geq 3.0$.

### 2017-06-14 figures/gmtcode/figure3/Instrumental.sh

@@ -42,9 +42,9 @@ gmt pscoast -R -J -B -Dh -W0.25p -N1/0.25p -A500 -V -P -O -K -Lf73/23/23/1000 >>
 gmt pscoast -R -J -B -Slightblue -A500 -Dh -W0.25p -V -P -O -K >> ${PSNAME}
 
 
-awk '($7>2.8){print $9,$10,($7^2.5)/140}' Alborz_2005_all_mag.txt|gmt psxy -Sc -G196/19/19 -W0.5  -R$REGION $PROJ -K -O >> ${PSNAME}
-awk '($7>3.4){print $9,$10,($7^2.5)/140}' Azerbaijan_2005_all_mag.txt|gmt psxy -Sc -G102/178/255 -W0.5  -R $PROJ -K -O >> ${PSNAME}
-awk '($7>2.5){print $9,$10,($7^2.5)/140}' KopehDagh_2005_all_mag.txt|gmt psxy -Sc -G153/153/153 -W0.5  -R $PROJ -K -O >> ${PSNAME}
+awk '($7>3.0){print $9,$10,($7^2.5)/140}' Alborz_2005_2016.txt|gmt psxy -Sc -G196/19/19 -W0.5  -R$REGION $PROJ -K -O >> ${PSNAME}
+awk '($7>3.5){print $9,$10,($7^2.5)/140}' Azerbaijan_2005_2016.txt|gmt psxy -Sc -G102/178/255 -W0.5  -R $PROJ -K -O >> ${PSNAME}
+awk '($7>3.5){print $9,$10,($7^2.5)/140}' KopehDagh_2005_2016.txt|gmt psxy -Sc -G153/153/153 -W0.5  -R $PROJ -K -O >> ${PSNAME}
 
 cat << EOF |awk '{print $1,$2,($3^2.5)/140}' |gmt psxy -Sc -G196/19/19 -W0.5  -R $PROJ -O >> ${PSNAME}
 61 37.7   3

### 2017-06-15 introduction.tex
started editing changes made by naeem in response to paag review, with some aspects of the srl review also being considered

@@
 
-In a relatively recent study, \citet{Lacasa2008} introduced a simple and computationally inexpensive approach to convert time-series into a particular kind of mathematical graphs known as visibility graphs \myrevision{(VG)}.
+In a relatively recent study, \citet{Lacasa2008} introduced a simple and computationally inexpensive approach to convert time-series into a particular kind of mathematical graphs known as visibility graphs.
 In this approach, the connection between the nodes in a network---here understood as events in a time series---is based on the visibility of each node or event with respect to other previous and later events in a time sequence.
-Over the last decade, this method has been found to be applicable to multiple fields, including economics, medicine, and geophysics  \myrevision{in different ways, including directed and undirected 1D or 2D approaches} \citep[e.g.,][]{Yang_2009_PA, Elsner_2009_GRL, Telesca2012_CSF, Wang2012, Long2013}.
+Over the last decade, this method has been found to be applicable to multiple fields, including economics, medicine, and geophysics\myrevision{, including directed and undirected one- (1D) and two-directional (2D) approaches} \citep[e.g.,][]{Yang_2009_PA, Elsner_2009_GRL, Telesca2012_CSF, Wang2012, Long2013}.
 
@@
 Subsequently, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through the visibility graph approach and found that the properties of the graph were correlated to the seismic $b$-value in the Gutenberg-Richter law \citep{Gutenberg1944}.
-In particular, \citet{Telesca2013} extracted the characteristics of the visibility graph for five different tectonic seismic regions in the subduction zone and found that the slope in the linear relationship between earthquake magnitude, $M$, and the inter-event visibility in the graph defined as the connectivity degree parameter, $k$, was correlated with the $b$-value.
+In particular, \citet{Telesca2013} extracted the characteristics of the visibility graph for five different tectonic seismic regions in the Mexican subduction zone and found that the slope in the linear relationship between earthquake magnitude, $M$, and the inter-event visibility in the graph, defined as the connectivity degree parameter, $k$, was correlated with the $b$-value.
 
@@
 In this article we use the visibility graph method to analyze the seismicity of northern Iran from 2005 to \myrevision{2016}.
-We focus our analysis on these years because in a previous study we observed that the latest decade of seismic records in the region offered the most complete catalog of events \myrevision{\citep[][]{Khoshnevis2017}}.
+We focus our analysis on these years because in a previous study we observed that the latest decade of seismic records in the region offered the most complete catalog of events \citep[][]{Khoshnevis2017}.
 Upon a brief review of the basic concepts of the method and its applications, we describe the seismicity of northern Iran considering three dominant seismic regions: Azerbaijan, Alborz, and Kopeh Dagh.
@@
 The considerable amount of earthquakes registered in a \myrevision{11}-year period facilitates the analysis done with the visibility graph approach within what would otherwise be considered a relatively short period of time, and serves as a good case study to test the capabilities of the method.
-We first summarize the dataset, including a description of the seismic catalog and its completeness based on a recent work on the seismicity of the region \myrevision{\citep{Khoshnevis2017}}.
+We first summarize the dataset, including a description of the seismic catalog and its completeness based on a recent work on the seismicity of the region \citep{Khoshnevis2017}.
 We then present results obtained for the region regarding the relationship between the the graph's $k$-$M$ slope and the seismicity $b$-value for the three seismic areas, analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, and present results for the variation of <$T_c$> through time.

### 2017-06-15 methodology.tex
started editing changes made by naeem in response to paag review, with some aspects of the srl review also being considered

@@
 In graphs, the data---sometimes also referred to as the payload---resides at the vertices or nodes who are connected through links or edges, which may or may not have an associated direction.
-A visibility graph is a special type of undirected graphs in which the links are straight lines connecting intervisible nodes; that is, straight lines that do not overlap any obstacle while connecting nodes that can see each other in a physical space \citep{LozanoPerez_1979_CACM}.
-Visibility graphs have been mostly used in robotics for navigation path planning \citep[e.g.,][]{Huang_2004_Proc, Oommen_1987_JRA} but have also seen applications in other fields including urban studies, interior architecture, medicine and geosciences \citep[e.g.,][]{Raman_2010_UE, Ahmadlou_2010_JNT, Varoudis_2014_JSS, Phillips_2015_ESR}.
+A visibility graph is a special type of undirected graphs in which the links are straight lines connecting intervisible nodes; that is, straight lines that do not go across any obstacle while connecting nodes that can see each other in a physical space \citep{LozanoPerez_1979_CACM}.
+Visibility graphs have been mostly used in robotics for navigation path planning \citep[e.g.,][]{Huang_2004_Proc, Oommen_1987_JRA} but have also seen applications in other fields including urban studies, interior architecture, medicine, and geosciences \citep[e.g.,][]{Raman_2010_UE, Ahmadlou_2010_JNT, Varoudis_2014_JSS, Phillips_2015_ESR}.
 
@@
 For any seismic time series, two characteristics are attributed to each event: (a) its occurrence time, and (b) the value associated to the event, here considered as the magnitude.
-The obstacles in the time space are the vertical lines (or sticks) between the time axis and the magnitude of the event in a time-magnitude series.
-Two events are in connection, or visible to each other, whenever no other event interrupts their linear connection.
+The obstacles in the time-magnitude space are the vertical lines (or sticks) between the time axis and the magnitude of the event.
+Two events are in connection, or visible to each other, whenever the magnitude stick of no other event interrupts their linear connection.
 
@@
 And invariance: scaling or time-shifting the series does not change the resulting visibility graph, provided the transformation is done under affine conditions \citep{Lacasa2008}.
-\\
-\myrevision{In terms of earthquake catalog, the visibility graph studies the relation between earthquake events.
-Relation between small and large earthquakes are investigated in different studies.
-Lee et al (2009), based on developing LRCS model, in which is assumed that the occurrence of an earthquake leads to a release of energy with long range effects like in real earthquake fault systems, it has been known that earthquakes are long-range correlated.
-The visibility connections between the "hubs" (large events) and events even located very far on time could represent such long-range correlated behavior.}
 
 Figure \ref{fig:vg} shows an example of a visibility graph for a portion of one of the magnitude-time series to be considered later in this study.
-\myrevision{It is worth to mention that we apply 1D visibility graph analysis (which applies on time dimension and not space) on the catalog as a magnitude time series}.
+\myrevision{In this application, the visibility graph analysis is 1D (i.e., there is no actual physical space but simply events in a catalog), where the magnitude sticks play the role of virtual obstacles distributed along the time line and defined by the occurrence of the events, which are the nodes of the graph}.
 For each event $i$ we compute the connectivity degree, $k$, which is the sum of the connections to all other events $j$ visible by the $i$th event.
@@
 
+\myrevision{\color{red} In terms of earthquake catalog, the visibility graph studies the relation between earthquake events.
+Relation between small and large earthquakes are investigated in different studies.
+Lee et al (2009), based on developing LRCS model, in which is assumed that the occurrence of an earthquake leads to a release of energy with long range effects like in real earthquake fault systems, it has been known that earthquakes are long-range correlated.
+The visibility connections between the "hubs" (large events) and events even located very far on time could represent such long-range correlated behavior.}
+
 Plotting $k$ against magnitude results on a scattered set of points which have been shown to be acceptably represented by a linear regression.
-We referred to this correlation as the $k$-$M$ relationship.
+We refer to this correlation as the $k$-$M$ relationship.
 More important, the slope of the $k$-$M$ relationship also shows a linear regression with the seismicity $b$-value of the seismic zone under consideration.

### 2017-06-15 seismicity.tex
started editing changes made by naeem in response to paag review, with some aspects of the srl review also being considered

@@
 According to the tectonic settings and geologic provinces of the plateau, the seismic activity in Iran has been categorized into different seismic zones.
-These vary between four to nine major seismic zones, in the more traditional models \citep[e.g.,][]{Stocklin1968, Takin1972, Berberian1976}, up to twenty to twenty-three seismotectonic provinces in the most elaborate ones \citep[e.g.,][]{Nowroozi1976, Tavakoli1999}.
+These vary between four to nine major seismic zones, in the more traditional models \citep[e.g.,][]{Stocklin1968, Takin1972, Berberian1976}, and up to twenty to twenty-three seismotectonic provinces in the most elaborate ones \citep[e.g.,][]{Nowroozi1976, Tavakoli1999}.
 We adopt the model proposed by \citet{Mirzaei1998} with modifications introduced by \citet{Karimiparidari2013}.
 In it, Iran is divided into six seismic regions: Azerbaijan, Alborz, Kopeh Dagh, Zagros, Central-East Iran, and Makran.
-\myrevision{Each of these seismic regions and in general Iranian plateau are studied from different perspectives \citep[e.g.,][]{Zafarani2017testing,Sedaghati2017partially,Golara2014, Nemati2015}}.
-Our focus, however, is on the northern part of Iran, for which we define a region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:study_region}.
-Although this region encloses part of the Zagros and Central-East seismic zones, we concentrate in the analysis of the seismicity of Azerbaijan, Alborz and Kopeh Dagh.
+\myrevision{Each of these seismic regions, and in general, the whole Iranian plateau, have been studied from different perspectives in the past \citep[e.g.,][]{Zafarani2017testing, Sedaghati2017partially, Golara2014, Nemati2015}}.
+Our focus, here, is on the northern part of Iran, for which we define a region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:study_region}.
+Although this region encloses part of the Zagros and Central-East seismic zones, we concentrate in the analysis of the seismicity of Azerbaijan, Alborz, and Kopeh Dagh.
 
@@
 At the northwest, the seismic zone of Azerbaijan is strongly controlled by the North Tabriz Fault system in the vicinity of the city of Tabriz, shown in Fig.~\ref{fig:study_region}.
-Historical accounts document the occurrence of strong $M>6$ earthquakes in this region as far back as the ninth century \citep{Berberian1999}, and a few $M>7$ earthquakes in 1042, 1721 and 1780 \citep{Jones1834}.
-More recently, this region was struck by the $M_w$ 6.1 1997 Ardabil earthquake near the city of Ardabil and the $M_w$ 6.4 2012 Tabriz earthquake northeast of the city of Tabriz.
+Historical accounts document the occurrence of strong $M>6$ earthquakes in this region as far back as the ninth century \citep{Berberian1999}, and a few $M>7$ earthquakes in 1042, 1721, and 1780 \citep{Jones1834}.
+More recently, this region was struck by the $M_w$ 6.1 1997 Ardabil earthquake near the city of Ardabil, and the $M_w$ 6.4 2012 Tabriz earthquake northeast of the city of Tabriz.
 These earthquakes caused extensive damage and took the lives of more than 1,500 people.
@@
 In particular, we focus on events recorded in the last decade, between January 2005 and December \myrevision{2016}.
-We focus our analysis on this magnitude-time sequence period because in a previous study we observed that the latest decade of seismic records in northern Iran offered the most complete dataset of recorded events, especially for the case of small $M < 4$ earthquakes \myrevision{\citep[][]{Khoshnevis2017}}.
+We focus our analysis on this magnitude-time sequence period because in a previous study we observed that the latest decade of seismic records in northern Iran offered the most complete dataset of recorded events, especially for the case of small $M < 4$ earthquakes \citep{Khoshnevis2017}.
 
@@
 
-Figure \ref{fig:completeness} shows the \cmmnt{goodness-of-fit} \myrevision{$M_c\ vs\ Time$} values for the three seismic zones.
+Figure \ref{fig:completeness} shows the \cmmnt{goodness-of-fit} \myrevision{$M_c$ vs time} values for the three seismic zones.
 We indicate the selected value of $M_c$ for each region in the figure.
 We also obtained the $b$-value in the Gutenberg-Richter law for each region following the maximum likelihood estimation \citep{Aki1965}:
+% 
 \myrevision{
-% 
 \begin{equation}
@@
 %
+\noindent
 where $e$ is the mathematical constant or Euler's number, $\overline{M}$ is the average magnitude, and $M_{\min}$ is the minimum magnitude in the sample.

### 2017-06-15 srl-submission/abstract.tex
started editing changes made by naeem in response to paag review, with some aspects of the srl review also being considered

--- 2017-06-14 abstract.tex
@@
 %
-We present an analysis of the seismicity of northern Iran in the period between 2005 and \myrevision{2016} using a recently introduced method based on concepts of graph theory.
+We present an analysis of the seismicity of northern Iran in the period between 2005 and 2015 using a recently introduced method based on concepts of graph theory.
 The method relies on the inter-event visibility defined in terms of a connectivity degree parameter, $k$, which is correlated with the earthquake magnitude, $M$.

### 2017-06-16 seismicity.tex
little fix

@@
 In it, Iran is divided into six seismic regions: Azerbaijan, Alborz, Kopeh Dagh, Zagros, Central-East Iran, and Makran.
-\myrevision{Each of these seismic regions, and in general, the whole Iranian plateau, have been studied from different perspectives in the past \citep[e.g.,][]{Zafarani2017testing, Sedaghati2017partially, Golara2014, Nemati2015}}.
-Our focus, here, is on the northern part of Iran, for which we define a region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:study_region}.
+\myrevision{Each of these seismic regions, and in general, the whole Iranian plateau, have been the subject of various studies from different perspectives in the past \citep[e.g.,][]{Zafarani2017testing, Sedaghati2017partially, Golara2014, Nemati2015}.
+Here, our focus is on the northern part of the country,} for which we define a region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:study_region}.
 Although this region encloses part of the Zagros and Central-East seismic zones, we concentrate in the analysis of the seismicity of Azerbaijan, Alborz, and Kopeh Dagh.

### 2017-06-20 acknowledgements.tex
working revised version for paag

@@
 \section{Acknowledgments}
+\label{sec:acknowledgments}
 
+\myrevision{We are thankful for the comments and suggestions of two anonymous reviewers, which helped us improve the original manuscript.
+The data used to compile the seismic catalog employed in this analysis was obtained from the International Institute of Earthquake Engineering and Seismology, IIEES (\url{http://www.iiees.ac.ir/en/eqcatalog/})}.
 This research was possible thanks to support from the Center for Earthquake Research and Information (CERI) at the University of Memphis.

### 2017-06-20 introduction.tex
working revised version for paag

@@
 \section{Introduction}
+\label{sec:introduction}
 
@@
 In this approach, the connection between the nodes in a network---here understood as events in a time series---is based on the visibility of each node or event with respect to other previous and later events in a time sequence.
-Over the last decade, this method has been found to be applicable to multiple fields, including economics, medicine, and geophysics\myrevision{, including directed and undirected one- (1D) and two-directional (2D) approaches} \citep[e.g.,][]{Yang_2009_PA, Elsner_2009_GRL, Telesca2012_CSF, Wang2012, Long2013}.
+Over the last decade, this method has been found to be applicable to multiple fields, including economics, medicine, and geophysics\myrevision{, using both directed and undirected, in one- and two-directional approaches} \citep[e.g.,][]{Yang_2009_PA, Elsner_2009_GRL, Telesca2012_CSF, Wang2012, Long2013}.
 
@@
 More recently, \citet{Telesca2016} used the visibility graph method to gain insight about the timespan between earthquakes.
-The authors defined the parameter <$T_c$> as the window mean interval connectivity time, which provides information about the average of all the time intervals between visible events.
-Applying this concept to the 2003--2012 earthquake sequence in Kachchh, western India, \citet{Telesca2016} found that the variation of <$T_c$> in time exhibited a plausible relationship with the occurrence of earthquakes.
-In particular, they observed that the value of <$T_c$> decreases significantly before the largest shock in the Kachchh catalog.
+The authors defined the parameter $<$$T_c$$>$ as the window mean interval connectivity time, which provides information about the average of all the time intervals between visible events.
+Applying this concept to the 2003--2012 earthquake sequence in Kachchh, western India, \citet{Telesca2016} found that the variation of $<$$T_c$$>$ in time exhibited a plausible relationship with the occurrence of earthquakes.
+In particular, they observed that the value of $<$$T_c$$>$ decreases significantly before the largest shock in the Kachchh catalog.
 
@@
 We first summarize the dataset, including a description of the seismic catalog and its completeness based on a recent work on the seismicity of the region \citep{Khoshnevis2017}.
-We then present results obtained for the region regarding the relationship between the the graph's $k$-$M$ slope and the seismicity $b$-value for the three seismic areas, analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, and present results for the variation of <$T_c$> through time.
+We then present results obtained for the region regarding the relationship between the the graph's $k$-$M$ slope and the seismicity $b$-value for the three seismic areas, analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, and present results for the variation of $<$$T_c$$>$ through time.

### 2017-06-20 methodology.tex
working revised version for paag

@@
 \section{Methodology}
+\label{sec:methodology}
 
@@
 In a relatively recent study, \citet{Lacasa2008} applied the concepts of visibility graphs to the representation and analysis of time series.
-Multiple applications have been found to this idea in fields such as economics \citep{Yang_2009_PA, Wang2012} and climate studies \citep{Elsner_2009_GRL}.
+Multiple applications have been found to this idea in fields such as economics \citep{Yang_2009_PA, Wang2012} and climatology \citep{Elsner_2009_GRL}.
 In this study, we are particularly interested in the application of visibility graphs to the analysis of seismic sequences \citep{Telesca2012}.
-In this case, the nodes in the visibility graphs are considered to be seismic events distributed over time.
+In such an application, the nodes in the visibility graphs are considered to be seismic events distributed over time.
 For any seismic time series, two characteristics are attributed to each event: (a) its occurrence time, and (b) the value associated to the event, here considered as the magnitude.
@@
 Figure \ref{fig:vg} shows an example of a visibility graph for a portion of one of the magnitude-time series to be considered later in this study.
-\myrevision{In this application, the visibility graph analysis is 1D (i.e., there is no actual physical space but simply events in a catalog), where the magnitude sticks play the role of virtual obstacles distributed along the time line and defined by the occurrence of the events, which are the nodes of the graph}.
+\myrevision{In this application, the visibility graph analysis is one-dimensional (i.e., there is no actual physical space but simply events in a catalog), and the magnitude sticks play the role of virtual obstacles distributed along the time line as defined by the occurrence of the events, which represent the nodes of the graph}.
 For each event $i$ we compute the connectivity degree, $k$, which is the sum of the connections to all other events $j$ visible by the $i$th event.
-Events are often categorized in small magnitude bins with $\Delta M = 0.1$ and we plot the connectivity degree as a function of the bin magnitude.
+Events are often categorized in small magnitude bins with $\Delta M = 0.1$, and we plot the connectivity degree as a function of the bin magnitude.
 Note that two earthquakes with the same magnitude can have different $k$ values, which ultimately depend on the occurrence time of the event and whether the time-neighboring events are of a larger or smaller magnitude.
@@
 These times are given in minutes and correspond to individual $T_c$ values.
-The mean <$T_c^e$> value associated with this event is also shown at the top right.
-The mean value of all <$T_c^e$> for the events in the graph is the window mean interval connectivity time, <$T_c^e$>.
+The mean $<$$T_c^e$$>$ value associated with this event is also shown at the top right.
+The mean value of all $<$$T_c^e$$>$ for the events in the graph is the window mean interval connectivity time, $<$$T_c^e$$>$.
 The color version of this figure is available only in the electronic edition.}
@@
 
-\myrevision{\color{red} In terms of earthquake catalog, the visibility graph studies the relation between earthquake events.
+% \myrevision{\color{red} In terms of earthquake catalog, the visibility graph studies the relation between earthquake events.
 Relation between small and large earthquakes are investigated in different studies.
@@
 
-Plotting $k$ against magnitude results on a scattered set of points which have been shown to be acceptably represented by a linear regression.
+\myrevision{It follows from this description that, for a given earthquake catalog, the visibility graph offers an alternative mathematical approach to study the correlations that exist between seismic events and their distribution (occurrence) in time.
+Such analysis can be explored in global terms (i.e., for all the events in a catalog), where long-range correlations might be more relevant in terms of the inter-visibility between large earthquakes, and the buildup of small earthquakes leading to greater magnitude events; or in local terms (i.e., for limited-time windows), where the occurrence of foreshocks and aftershocks may be more dominant.
+We explore such correlations in terms of how the properties of the visibility graph relate to the seismicity of the region.}
+
+\myrevision{For instance,} plotting $k$ against magnitude results on a scattered set of points which have been shown to be acceptably represented by a linear regression.
 We refer to this correlation as the $k$-$M$ relationship.
-More important, the slope of the $k$-$M$ relationship also shows a linear regression with the seismicity $b$-value of the seismic zone under consideration.
-This is also true for a universal sample of $k$-$M$ slopes and $b$ values \citep{Telesca2013, Telesca2014}.
+\myrevision{This is of relevance because it happens that, for a significant number of earthquake catalogs from distinctive seismic zones,} the slopes of the $k$-$M$ relationships show a linear regression with the seismicity $b$-value of the seismic zones under consideration.
+{This observation seems to hold} for a universal sample of $k$-$M$ slopes and $b$ values \myrevision{from different regions, as suggested by} \citet{Telesca2013, Telesca2014}.
 \citet{Telesca2014} also observed that it was reasonable to draw a relationship between the distribution of the events when considering whether these were connected (visible to each other) or not, and time.
-Let $T_c$ be the interval connectivity time, which is nothing but the time difference between two inter-visible events (see Fig.~\ref{fig:vg}); and <$T_c^e$> be the average of all $T_c$ values computed for event $e$; then it is possible to compute the visibility graph mean interval connectivity time <$T_c$>, which is the mean value of all <$T_c^e$> in a given time sequence of events.
+Let $T_c$ be the interval connectivity time, which is nothing but the time difference between two inter-visible events (see Fig.~\ref{fig:vg}); and $<$$T_c^e$$>$ the average of all $T_c$ values computed for event $e$; then it is possible to compute the visibility graph mean interval connectivity time $<$$T_c$$>$, which is the mean value of all $<$$T_c^e$$>$ in a given time sequence of events.
 
-Because <$T_c$> can be obtained for any sub-graph within a larger graph, that is, for any time window in a larger magnitude-time series of events, then it is possible to investigate the evolution of <$T_c$> (and that of the $k$-$M$ slope and the $b$-value) for a moving window---with a constant number of events---sliding along the magnitude-time series.
+Because $<$$T_c$$>$ can be obtained for any sub-graph within a larger graph, that is, for any time window in a larger magnitude-time series of events, then it is possible to investigate the evolution of $<$$T_c$$>$ (and that of the $k$-$M$ slope and the $b$-value) for a moving window---with a constant number of events---sliding along the magnitude-time series.
 When doing so, \citet{Telesca2016} suggested to associate the values of each sub-sequence with the last event in the sub-sequence.
-Following this approach, \citet{Telesca2016} found that the variation of <$T_c$> over time exhibited a possible relationship with the occurrence of earthquakes.
+Following this approach, \citet{Telesca2016} found that the variation of $<$$T_c$$>$ over time exhibited a possible relationship with the occurrence of earthquakes.
 This and the aforementioned relationship between the $k$-$M$ slope and the $b$-value are aspects we explore next for our region and years-interval of interest.

### 2017-06-20 results.tex
working revised version for paag

@@
 
-We generate the \myrevision{1D} visibility graph for each sub-region of interest using the time-magnitude sequences shown in Fig.~\ref{fig:mag-time}.
-The number of nodes in each graph is the same as the (\myrevision{complete catalog}) number of events shown in Table \ref{tab:seismicity}, and the links between inter-visible events are established following the condition in equation (\ref{eq:vg}), as in the example shown in Fig.~\ref{fig:vg}.
-(We do not include a visualization of the complete sequence graphs because the links are so many, it is only practical to visualize the graphs of short sequences.) We then collect information about the number of inter-visibility links associated with each event (connectivity degree, $k$) and categorize the events in magnitude bins of size $\Delta M = 0.1$, as mentioned in the Methodology section.
-Figure \ref{fig:km} shows the scattered distribution of events in the magnitude-connectivity degree plane for each sub-region.
-The figure shows that, in general, the value of $k$ increases with $M_w$.
-Figure \ref{fig:km} also shows the results of obtaining linear $k$-$M$ regressions for each dataset and the values of the $k$-$M$ slopes for the three seismic zones.
+We generate the visibility graphs for each sub-region of interest using the time-magnitude sequences \myrevision{of both the complete and declustered catalogs.
+In the case of the complete catalog, that corresponds to the sequences shown in Fig.~\ref{fig:mag-time}.
+In every case, the numbers of nodes in each graph are the same as those shown in Table \ref{tab:seismicity}; and} the links between inter-visible events are established following the condition in equation (\ref{eq:vg}), as in the example shown in Fig.~\ref{fig:vg}.
+(We do not include a visualization of the graphs because the links are so many, that it is only practical to visualize the graphs of short sequences.) We collect information about the number of inter-visibility links associated with each event (connectivity degree, $k$) and categorize the events in magnitude bins of size $\Delta M_{\mathrm{bin}} = 0.1$, as mentioned in the Methodology section.
+Figure \ref{fig:km} shows the scattered distribution of events in the magnitude-connectivity degree plane for each sub-region\myrevision{, corresponding to the complete catalogs.} The figure shows that, in general, the value of $k$ increases with $M_w$\myrevision{; and includes the results of obtaining linear $k$-$M$ regressions for each dataset along with the values of the $k$-$M$ slopes for the three seismic zones, namely 10.0, 9.85, and 8.70 for the Azerbaijan, Alborz, and Kopeh Dagh regions.
+Similar results regressions were obtained for the declustered catalogs, which yielded slopes of 8.92, 8.97, and 7.96, respectively.}
 
@@
 
-Next, we examine the relationship between the $b$-values from Table \ref{tab:seismicity} and the $k$-$M$ slope values shown in Fig.~\ref{fig:km}.
-\myrevision{The b-value, by definition, represents the proportion between the amount of large events and that of small events.} Fig.~\ref{fig:regression} shows the scattered results for $k$-$M$ slope versus $b$-value for the three tectonic seismic regions in northern Iran along with the data-points obtained for the analysis of the magnitude-time sequences of the Mexican subduction zone \citep{Telesca2013} and the Pannoninan seismic zone \citep{Telesca2014}, as well as other experimental results \citep{Telesca2014-pone}.
+Next, we examine the relationship between the $b$-values from Table \ref{tab:seismicity} and the $k$-$M$ slopes.
+
+* * *
+
+\myrevision{The $b$-value, by definition, represents the proportion between the amount of large events and that of small events.} Fig.~\ref{fig:regression} shows the scattered results for $k$-$M$ slope versus $b$-value for the three tectonic seismic regions in northern Iran along with the data-points obtained for the analysis of the magnitude-time sequences of the Mexican subduction zone \citep{Telesca2013} and the Pannoninan seismic zone \citep{Telesca2014}, as well as other experimental results \citep{Telesca2014-pone}.
 \myrevision{According to Scholtz (1968) b-value for microfractures in rocks is reported ranging between 0.11 and 2.58.
@@
 On the other hand, as we will see below, if the sequence window is sufficiently small, then the $k$-$M$ slope value shows a relative dependence on time and thus provides insight about the variation of the seismicity as the sequence progresses.
-\cmmnt{Note also that the threshold value of $M_c$ is significantly smaller for Azerbaijan than for Alborz or Kopeh Dagh.
-This is due in part to the fact that the latter two zones were more seismically active in the time period under consideration} \myrevision{In this study due to using windowing method, we consider a very conservative completeness magnitude}.
+% \cmmnt{Note also that the threshold value of $M_c$ is significantly smaller for Azerbaijan than for Alborz or Kopeh Dagh.
+This is due in part to the fact that the latter two zones were more seismically active in the time period under consideration}
+\myrevision{In this study due to using windowing method, we consider a very conservative completeness magnitude}.
 However, according to \citet{Telesca2012}, the threshold magnitude has a minor effect in the graph parameters.
@@
 
-\cmmnt{
- The comparisons of the regressions, however, indicate that the analysis of the random sub-catalogs leads to a result more in line with the universal results obtained when considering multiple seismic zones.
+% \cmmnt{
+% The comparisons of the regressions, however, indicate that the analysis of the random sub-catalogs leads to a result more in line with the universal results obtained when considering multiple seismic zones.
 The linear regression of the random sub-catalogs yields the following equation:
-% 
-\begin{equation}
-   	b = 0.045  +0.390 m \, .
-	\label{eq:iran.bm}
-\end{equation}
+% % 
+% \begin{equation}
+%    	b = 0.045  +0.390 m \, .
+% 	\label{eq:iran.bm}
+% \end{equation}
 
-Note that equations (\ref{eq:universal.bm}) and (\ref{eq:iran.bm}) have similar intercepts with the $b$-value axis, and only slightly different slope constants.
+% Note that equations (\ref{eq:universal.bm}) and (\ref{eq:iran.bm}) have similar intercepts with the $b$-value axis, and only slightly different slope constants.
 In this particular case, the analysis for northern Iran leads to a relationship in which the $b$-value increases more rapidly with $m$ than in the case of the regression obtained for the universal data.

### 2017-06-20 seismicity.tex
working revised version for paag

@@
 \section{Seismicity of Northern Iran}
+\label{sec:seismicity}
 
@@
 Here, our focus is on the northern part of the country,} for which we define a region of interest between longitudes 43.5\textdegree{}E and 61.5\textdegree{}E, and latitudes 34\textdegree{}N and 40\textdegree{}N, as shown in Fig.~\ref{fig:study_region}.
-Although this region encloses part of the Zagros and Central-East seismic zones, we concentrate in the analysis of the seismicity of Azerbaijan, Alborz, and Kopeh Dagh.
+Although this region encloses part of the Zagros and Central-East seismic zones, we limit our analysis to the seismicity of Azerbaijan, Alborz, and Kopeh Dagh.
 
@@
 Last, there is the Kopeh Dagh seismic zone to the east and northeast.
-This region is dominated by the Main Kopeh Dagh Fault system, which exhibits active tectonic displacements along a distance of more than 500 km \citep{Trifonov1978}.
+This region is dominated by the main Kopeh Dagh fault system, which exhibits active tectonic displacements along a distance of more than 500 km \citep{Trifonov1978}.
 This fault is responsible for the $M_w$ 7.3 1948 earthquake, which struck the capital city of Ashgabat in Turkmenistan and destroyed more than 30 villages in Iran.
-Historically, the Kopeh Dagh seismic zone is also responsible for the $M_s$ 7.1 earthquake in 10 A.D.~\citep{Berberian2001} near Ashgabat, and two significant earthquakes in 1209 and 1405 at the boundary between the Neyshabur and Binalud faults near the city of Mashhad \citep{Berberian1999}.
+\myrevision{While no large magnitude events have been registered in recent years,} historically, the Kopeh Dagh seismic zone is responsible for the $M_s$ 7.1 earthquake in 10 A.D.~\citep{Berberian2001} near Ashgabat, and two significant earthquakes in 1209 and 1405 at the boundary between the Neyshabur and Binalud faults near the city of Mashhad \citep{Berberian1999}.
 
@@
 	\centering
+	a)
+	\includegraphics[width=\textwidth]{figures/pdf/figure-03} \\
+	b)
 	\includegraphics[width=\textwidth]{figures/pdf/figure-03} 
@@
 In particular, we focus on events recorded in the last decade, between January 2005 and December \myrevision{2016}.
-We focus our analysis on this magnitude-time sequence period because in a previous study we observed that the latest decade of seismic records in northern Iran offered the most complete dataset of recorded events, especially for the case of small $M < 4$ earthquakes \citep{Khoshnevis2017}.
+We limit our analysis to this magnitude-time sequence period because in a previous study we observed that the latest decade of seismic records in northern Iran offered the most complete dataset of recorded events, especially for the case of small $M < 4$ earthquakes \citep{Khoshnevis2017}.
 
-We compiled a catalog of all recorded earthquakes using data downloaded from the International Institute of Earthquake Engineering and Seismology, IIEES (see the Data and Resources section).
-\myrevision{Instrumental catalog provided by IIEES} contained a mixture of earthquake magnitude scales, including: moment, $M_w$; local, $M_L$; body wave, $m_b$; surface wave, $M_s$; and duration $M_D$ magnitudes.
-\myrevision{All earthquakes of this study are reported in local $M_L$ magnitude scale.
-However, in order to keep consistency with other studies (e.g., completeness magnitude) we converted them to moment magnitude, $M_w$}.
-Magnitudes were converted using the relationships defined in \citet{Zare2014}.
+We compiled a catalog of all recorded earthquakes using data downloaded from the International Institute of Earthquake Engineering and Seismology, IIEES (\url{http://www.iiees.ac.ir/en/eqcatalog/}).
+\myrevision{In general, data collected from IIEES contains a mixture of earthquake magnitude scales, including: moment, $M_w$; local, $M_L$; body wave, $m_b$; surface wave, $M_s$; and duration $M_D$ magnitudes.
+However, for our time-period of interest (2005--2016), all the events had local magnitude ($M_L$) values, which we, in turn, and in order to maintain international consistency with other studies, converted to moment magnitude ($M_w$)} using the relationships defined in \citet{Zare2014}.
 
-\myrevision{After conducting separate studies on the whole and declustered catalog, we found that the whole catalog results are ,although slightly different, comprehensive.
-On the other hand declustering could add some unwanted uncertainty (in using parameters for time and distance windows) to the resultant catalog and considerably reduce the number of events in each region's catalog}.
-Fig.~\ref{fig:seismicity} shows the epicenter location of instrumental earthquakes for the three seismic zones of interest.
+\myrevision{The whole dataset we downloaded from IIEES can be seen in Fig.~\ref{fig:seismicity}a, which shows events scaled by their magnitude $M_w$ at their epicenter location for the three seismic zones of interest.
+We refer to the catalog composed by the events shown in this figure as the \textit{whole} catalog.
+We then} determine the minimum magnitude of completeness, $M_c$, for each region\myrevision{, and based on the value of $M_c$, we filter out the smaller events and obtain a reduced dataset of events to which we refer to as the \textit{complete} catalog.}
 
-%Foreshocks and aftershocks were removed from the catalog following a Poissonian occurrence model using the declustering method of \citet{Gardner1974}, in a manner consistent with previous catalog compilations available for the region \citep[e.g.,][]{Zare2014}.
-Upon declustering, we divide the catalog into three sub-catalogs, each for one of the seismic zones under consideration.
+\myrevision{There are different alternatives to obtain $M_c$.
+In this initial part of the analysis for the whole subcatalogs of the three regions, we determined $M_c$ using the time-dependent MAXC method introduced and implemented in the ZMAP software by \citet{Wiemer2000}.
+This method allows one to investigate the behavior of $M_c$ as a function of time, and proposes to set $M_c$ to a value near the observed maximum over time.} Figure \ref{fig:completeness} shows the \myrevision{evolution of $M_c$} for the three seismic zones\myrevision{, including its variability over time, and indicates the chosen value for each region.
+In turn, Fig.~\ref{fig:seismicity}b shows the complete catalog that results after removing all the events with magnitudes smaller than $M_c$.}
 
-We \cmmnt{then proceeded to} determine the minimum magnitude of completeness, $M_c$, for each region's sub-catalog.
-The value of $M_c$ is often determined using simple numerical analyses in combination with data inspection.
-Two common approaches are the maximum curvature (MAXC) and the goodness-of-fit test (GFT) methods \citep{Wiemer2001}.
-\myrevision{We compute the $M_c$ versus time using the \myrevision{MAXC} \cmmnt{GFT} method coded in ZMAP software} as introduced by \citet{Wiemer2000}.
+\myrevision{We also considered a \textit{declustered} catalog, where} foreshocks and aftershocks were removed from the \myrevision{complete} catalog following a Poissonian occurrence model \myrevision{using the method introduced by \citet{Gardner1974}.
+While this is consistent with previous catalog compilations available for the region \citep[e.g.,][]{Zare2014}, we recognize that this declustering approach is not calibrated for Iran.
+Nonetheless, we were interested in investigating the impact that declustering may have on the visibility graph analysis, an aspect we discuss later.}
 
-\cmmnt{In this method, the completeness magnitude is obtained such that the catalog satisfies---at a certain acceptance threshold---the Gutenberg-Richter power low, given an extended dataset of events.
-This extended dataset is composed of predicted and observed events, where the predicted events are generated based on a trial minimum magnitude.
-The process is repeated for increasing values of the reference minimum magnitude until finding a desirable fit with the power law.
-\citet{Wiemer2000} suggests a goodness of fit of 90\% as an acceptable threshold to select $M_c$.
-However, not all frequency-magnitude distributions reach the 90\% mark, in which case $M_c$ can be selected by inspection.}
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=\textwidth]{figures/pdf/figure-04-rev} 
+	\caption{\myrevision{Completeness magnitude vs time results and selected $M_c$ values for the three tectonic seismic regions in northern Iran as evaluated from the time-magnitude sequence of earthquakes during the 2005--2016 period.}}
+	\label{fig:completeness}
+\end{figure*}
 
-Figure \ref{fig:completeness} shows the \cmmnt{goodness-of-fit} \myrevision{$M_c$ vs time} values for the three seismic zones.
-We indicate the selected value of $M_c$ for each region in the figure.
-We also obtained the $b$-value in the Gutenberg-Richter law for each region following the maximum likelihood estimation \citep{Aki1965}:
+\myrevision{Subsequently, we} obtained the $b$-value in the Gutenberg-Richter law for each region following the maximum likelihood estimation \citep{Aki1965}, in which
 % 
+\begin{equation}
 \myrevision{
+	b = \frac
+		{ log_{10}(e) }
+		{ \overline{M} - \left( M_{\min} - \frac{\Delta M_{\mathrm{bin}}}{2} \right) } \, ,
+}
+\end{equation}
+%
+\noindent%
+where $e$ is the mathematical constant or Euler's number, $\overline{M}$ is the average magnitude, \myrevision{$M_{\min}$ is the minimum magnitude in the sample, and $\Delta M_{\mathrm{bin}}$ is the bin size used to discretize the magnitude scale}.
+Here, the value of $M_{\min}$ is taken as the minimum completeness magnitude $M_c$ obtained or selected for each region's sub-catalog.
+\myrevision{In this study we assumed $\Delta M_{\mathrm{bin}} = 0.1$}.
+
+In addition to using $M_c$ to determine the $b$-value for each sub-catalog, we also use it as the threshold for limiting the minimum magnitude to be considered in the construction of the visibility graphs for each region.
+\myrevision{Table \ref{tab:seismicity} shows the number of events of the whole catalog, along with the number of events for each region's complete and declustered catalogs.
+It also includes the corresponding values of $M_c$, which happened to be the same for both catalogs, and the separate values of $b$, including the standard deviation, $\sigma_b$, which is calculated as}
+% 
 \begin{equation}
-	b = \frac{log_{10}(e)}{\overline{M} - (M_{min} - \frac{\Delta M_{bin}}{2})} \, ,
+\myrevision{
+	\sigma_b = 2.3 \, b^2 \sqrt{ \frac{ \sum_{i = 1}^{N} \left( M_i - \overline{M} \right)^2 }{ N \left(N - 1 \right) } } \, ,
+}
 \end{equation}
-}
 % 
 \noindent
-where $e$ is the mathematical constant or Euler's number, $\overline{M}$ is the average magnitude, and $M_{\min}$ is the minimum magnitude in the sample.
-Here, the value of $M_{\min}$ is taken as the minimum completeness magnitude $M_c$ obtained or selected for each region's sub-catalog.
-\myrevision{In this study we assumed $\Delta M_{bin} = 0.1$}.
-Table \ref{tab:seismicity} shows the corresponding values of $M_c$ and $b$.\myrevision{The standard deviation of the estimate of b is calculated by using \citet{Shi1982standard} formula:}
+where $N$ is the number of events in each catalog \citep{Shi1982standard}.
+
+\myrevision{Figure \ref{fig:mag-time} shows the final time-magnitude sequences for the complete catalogs of Azerbaijan, Alborz, and Kopeh Dagh.
+We omit here the sequences of the declustered catalogs, which are, in general, very similar to those shown in Fig.~\ref{fig:mag-time}.
+Note from Table \ref{tab:seismicity} that in the case of Azerbaijan and Kopeh Dagh, we consider events in the catalog with $M_w \geq 3.5$, whereas in the case of Alborz all events are $M_w \geq 3.0$.}
+
 \myrevision{
-\begin{equation}
-	\sigma b = 2.3b^2\sqrt{\frac{\sum_{i=1}^{N}(M_i - \overline{M})^2}{N(N-1)}},
-\end{equation}
-where $N$ is the number of events in each catalog.
-}
-
-\cmmnt{
-\begin{figure}%[t]
-	\centering
-	\includegraphics[width=0.45\textwidth]{figures/pdf/figure-04-rev} 
-	\caption{Completeness magnitude goodness-of-fit test (GFT) results and selected $M_c$ values for the three tectonic seismic regions in northern Iran as evaluated from the time-magnitude sequence of earthquakes during the 2005--2015 period.
-The symbols indicate the computed GFT values as function of the earthquake magnitude.
-The horizontal dashed line indicates the desired threshold for the GFT value at 90 percent.
-The vertical dashed lines and solid symbols indicate the selected completeness magnitude for each region.
-The color version of this figure is available only in the electronic edition.}
-	\label{fig:completeness}
-\end{figure} 
-}
-
-\begin{figure}%[t]
-	\centering
-	\includegraphics[width=0.8\textwidth]{figures/pdf/figure-04-rev.pdf}
-
-	\caption{\myrevision{Completeness magnitude vs time results and selected $M_c$ values for the three tectonic seismic regions in northern Iran as evaluated from the time-magnitude sequence of earthquakes during the 2005--2016 period.}}
-	\label{fig:completeness}
-\end{figure}
-
-\begin{table}
-	\fontfamily{lmss}\selectfont
-	\caption{Total number of earthquakes \myrevision{(before and after considering completeness magnitude)} and seismic parameters $M_c$ and $b$ for the three seismic zones of northern Iran.}
+\begin{table*}
+	\caption{Total number of earthquakes \myrevision{for the whole, complete, and declustered catalogs}, and seismic parameters $M_c$ and $b$ \myrevision{(including standard deviation) for the complete catalogs} of the three seismic zones of northern Iran.}
 	\centering\small
 	\myrevision{
-	\begin{tabular}{|ccccc|}
+	\begin{tabular}{lcccccc}
 		\hline
-		Region           & Total Num.  & $M_c$  & Num. of Events          & $b-value$ \\ 
-		                      & of Events     &             & in Complete Catalog  &                  \\
+		Region       & \multicolumn{3}{c}{Number of Events in Catalog} & $M_c$ & \multicolumn{2}{c}{$b$-value} \\
+		\cline{2-4} 
+		             & Whole & Complete & Declustered &     & Complete             & Declustered \\
 		\hline
-		Azerbaijan     &        1047     &  3.5       &        202                     &    0.85491 $\pm$ 0.0506 \\
-		Alborz            &        1898     &  3.0       &        575                     &    0.81578 $\pm$ 0.0279 \\
-		Kopeh Dagh  &         640      &  3.5       &        117                     &    0.78297 $\pm$ 0.0494 \\
+		Azerbaijan   & 1047  &  202     &     ?       & 3.5 & 0.85491 $\pm$ 0.0506 & ? \\
+		Alborz       & 1898  &  575     &     ?       & 3.0 & 0.81578 $\pm$ 0.0279 & ? \\
+		Kopeh Dagh   &  640  &  117     &     ?       & 3.5 & 0.78297 $\pm$ 0.0494 & ? \\
 		\hline
@@
 	\label{tab:seismicity}
-\end{table}
+\end{table*}
+}
 
-\begin{figure*}[t]
+\begin{figure*}%[t]
 	\centering
@@
 
-In addition to using $M_c$ to determine the $b$-value for each sub-catalog, we also use $M_c$ as the threshold for limiting the minimum magnitude to be considered in the construction of the visibility graph of each region.
-The resulting number of events for each region is included in Table \ref{tab:seismicity}.
-Figure \ref{fig:mag-time} shows the final time-magnitude sequences for Azerbaijan, Alborz and Kopeh Dagh.
-Note that in the case of \myrevision{Azerbaijan} and Kopeh Dagh, we consider events in the \cmmnt{declustered} catalog down to $M_w \geq 3.5$, whereas in the case of \myrevision{Alborz} all events are $M_w \geq 3.0$.
+% OLD MATERIAL
+% -----------------------------------------------------------------
+
+% \myrevision{After conducting separate studies on the whole and declustered catalog, we found that the whole catalog results are ,although slightly different, comprehensive.
+On the other hand declustering could add some unwanted uncertainty (in using parameters for time and distance windows) to the resultant catalog and considerably reduce the number of events in each region's catalog}.
+Fig.~\ref{fig:seismicity} shows the epicenter location of instrumental earthquakes for the three seismic zones of interest.
+
+%Foreshocks and aftershocks were removed from the catalog following a Poissonian occurrence model using the declustering method of \citet{Gardner1974}, in a manner consistent with previous catalog compilations available for the region \citep[e.g.,][]{Zare2014}.
+Upon declustering, we divide the catalog into three sub-catalogs, each for one of the seismic zones under consideration.
+
+% We 
+% \cmmnt{then proceeded to} 
+% determine the minimum magnitude of completeness, $M_c$, for each region's sub-catalog.
+The value of $M_c$ is often determined using simple numerical analyses in combination with data inspection.
+Two common approaches are the maximum curvature (MAXC) and the goodness-of-fit test (GFT) methods \citep{Wiemer2001}.
+\myrevision{We compute the $M_c$ versus time using the \myrevision{MAXC}
+% \cmmnt{GFT} 
+% method coded in ZMAP software} as introduced by \citet{Wiemer2000}.
+
+% \cmmnt{In this method, the completeness magnitude is obtained such that the catalog satisfies---at a certain acceptance threshold---the Gutenberg-Richter power low, given an extended dataset of events.
+This extended dataset is composed of predicted and observed events, where the predicted events are generated based on a trial minimum magnitude.
+The process is repeated for increasing values of the reference minimum magnitude until finding a desirable fit with the power law.
+\citet{Wiemer2000} suggests a goodness of fit of 90\% as an acceptable threshold to select $M_c$.
+However, not all frequency-magnitude distributions reach the 90\% mark, in which case $M_c$ can be selected by inspection.}
+
+% Figure \ref{fig:completeness} shows the 
+% % \cmmnt{goodness-of-fit} 
+% \myrevision{$M_c$ vs time} values for the three seismic zones. We indicate the selected value of $M_c$ for each region in the figure.
+
+% \cmmnt{
+% \begin{figure}%[t]
+% 	\centering
+% 	\includegraphics[width=0.45\textwidth]{figures/pdf/figure-04-rev} 
+% 	\caption{Completeness magnitude goodness-of-fit test (GFT) results and selected $M_c$ values for the three tectonic seismic regions in northern Iran as evaluated from the time-magnitude sequence of earthquakes during the 2005--2015 period.
+The symbols indicate the computed GFT values as function of the earthquake magnitude.
+The horizontal dashed line indicates the desired threshold for the GFT value at 90 percent.
+The vertical dashed lines and solid symbols indicate the selected completeness magnitude for each region.
+The color version of this figure is available only in the electronic edition.}
+% 	\label{fig:completeness}
+% \end{figure} 
+% }

### 2017-06-20 results.tex
updates on modifications of the revised version for paag

@@
 
-Next, we examine the relationship between the $b$-values from Table \ref{tab:seismicity} and the $k$-$M$ slopes.
+Next, we examine the relationship between the $b$ values from Table \ref{tab:seismicity} and the $k$-$M$ slopes.
+\myrevision{Figures \ref{fig:regression}a and \ref{fig:regression}a show the scattered results of the $k$-$M$ slope versus $b$-value, for the complete and declustered catalogs, respectively.
+Along with the data-points obtained for our analysis of the three seismic regions of northern Iran, in each plot, we also include the data points corresponding to the magnitude-time sequences of the Mexican subduction zone provided by \citet{Telesca2013}, the Pannoninan seismic zone from \citet{Telesca2014}, the experimental results obtained by \citet{Telesca2014-pone}, and the result from a similar preliminary analysis done by \citet{Azizzadeh_2017_SSA} for California.
+These figures also include the linear trends of the data points, as they are aggregated (i.e., each regression reflects the addition of new data-points from different studies).
+In the figure, we indicate which data points were considered for each of the computed linear regressions and their corresponding correlation coefficient, $R$.}
 
-* * *
+\myrevision{Here, as well as in other figures, we present our results for both the complete and declustered catalogs to shed light upon the local differences for the case of northern Iran, and to contribute, globally, to the discussion of the appropriate treatment and selection of catalogs for the use of the visibility graph method.
+We note, for instance, that the data points in Fig.~\ref{fig:regression} from \citet{Telesca2012} and \citet{Telesca2013} used whole catalogs, whereas those from \citet{Telesca2014} and \citet{Telesca2016} used declustered catalogs.}
 
-\myrevision{The $b$-value, by definition, represents the proportion between the amount of large events and that of small events.} Fig.~\ref{fig:regression} shows the scattered results for $k$-$M$ slope versus $b$-value for the three tectonic seismic regions in northern Iran along with the data-points obtained for the analysis of the magnitude-time sequences of the Mexican subduction zone \citep{Telesca2013} and the Pannoninan seismic zone \citep{Telesca2014}, as well as other experimental results \citep{Telesca2014-pone}.
-\myrevision{According to Scholtz (1968) b-value for microfractures in rocks is reported ranging between 0.11 and 2.58.
-Using different synthetic and real catalog, in this study we cover a broad range from low b-value (synthetics) to high b-value(subduction zone)}.
-Fig.~\ref{fig:regression} also includes the results of different linear regressions between the $b$-value and the $k$-$M$ slope.
-Each regression reflects the addition of new data-points from different studies.
-Note that the regression improves as new data-points are added, which is indicated by the correlation coefficient $R$, also included in the figure.
-The correlation fitting various regional seismic data was previously pointed out by \citet{Telesca2014}.
+\myrevision{Note that, overall, the linear trends shown in Fig.~\ref{fig:regression} hold independently of the differences in the studies in terms of number of events, seismic characteristics, and the treatment of the catalogs.
+Also note that these trends tend to improve with increasing number of data points, as reflected by the increasing value of $R$.
+Regarding this, we should note that the data points in Fig.~\ref{fig:regression} cover what would otherwise be considered a large span of $b$ values.
+While we recognize that most earthquake data lead to $b$ values ranging between 0.8 and 1.2, it is also known that there are regions with low- and high-$b$ values \citep[e.g.,][]{Singh_1983_BSSA, Pacheco_1992_N, Nakaya_2006_JGR}.
+In addition, \citet{Scholz_1968_BSSA} reported that experimental microfractures in rocks, similar to those observed in earthquakes, exhibit $b$ values ranging between 0.11 and 2.58.
+Considering that the $b$ value, by definition, represents the proportion between the amount of large and small events in a region, the trends shown in Fig.~\ref{fig:regression} contribute to the suggestion made by \citet{Telesca2014} about the universal character of the relationship between $b$ and the $k$-$M$ slope.}
 
-According to these results, a universal relationship between the $b$-value and the $k$-$M$ slope ($m$) can be expressed as:
+According to these results, a universal relationship between $b$ and the $k$-$M$ slope ($m$) can be expressed as
 % 
 \begin{equation}
-	b = 0.073 + 0.084 m \, .
+\myrevision{
+	b = 0.073 + 0.084 m
 	\label{eq:universal.bm}
+}
 \end{equation}
+%
+\myrevision{for the case in which we consider the complete catalogs for northern Iran, and}
+% 
+\begin{equation}
+\myrevision{
+	b = 0.077 + 0.085 m
+	\label{eq:universal.bm.dc}
+}
+\end{equation}
+%
+\myrevision{for the case in which we consider the declustered catalogs for northern Iran.
+This indicates that once combined with the data points of other regions, the option of considering either catalog leads to very similar results as, on average, the data points oscillate about the same universal relationship.
+Locally, however, for the case of northern Iran trends alone, it seems that the declustered catalog leads to a closer fit with the universal relationship.
+Separately (not shown here for brevity), we also observed that, for the particular sequences under study, the results seem to be more sensitive to less conservative values of $M_c$, as the choice of a smaller $M_c$ leads to larger datasets.
+\citet{Telesca2012} and \citet{Telesca2013}, however, pointed out that for sufficiently long sequences, the threshold magnitude have only small effects on the graph parameters.}
 
-\begin{figure}[h]%[t]
+\begin{figure*}[t]
 	\centering
-	\includegraphics[width=0.45\textwidth]{figures/pdf/figure-07-rev.pdf} 
+	\includegraphics[width=\textwidth]{figures/pdf/figure-07-rev.pdf} 
 	\caption{Correlation between $k$-$M$ slope and $b$-value as drawn from the results of the present study for the region of northern Iranian and three other previous studies, including analysis of the Mexican subduction zone \citep{Telesca2013}, the Pannonian seismic zone \citep{Telesca2014}, and results from two experiments \citep{Telesca2014-pone}.
@@
 	\label{fig:regression}
-\end{figure}
-
-Another aspect of interest is the stability of the data points themselves.
-Note that as presented in Fig.~\ref{fig:regression}, the analysis of the sequences shown in Fig.~\ref{fig:mag-time} only contribute one data point per region of interest.
-Furthermore, each data-point comes from sequences that vary significantly in terms of the number of events and seismic parameters (see Table \ref{tab:seismicity}).
-
-\citet{Telesca2013} observed that the value of the $k$-$M$ slope is not particularly sensitive to the sample size in the sequence---at least not when considering sufficiently large sequences.
-On the other hand, as we will see below, if the sequence window is sufficiently small, then the $k$-$M$ slope value shows a relative dependence on time and thus provides insight about the variation of the seismicity as the sequence progresses.
-% \cmmnt{Note also that the threshold value of $M_c$ is significantly smaller for Azerbaijan than for Alborz or Kopeh Dagh.
-This is due in part to the fact that the latter two zones were more seismically active in the time period under consideration}
-\myrevision{In this study due to using windowing method, we consider a very conservative completeness magnitude}.
-However, according to \citet{Telesca2012}, the threshold magnitude has a minor effect in the graph parameters.
+\end{figure*}
 
@@
 In total, for each region, we extracted 200 new sub-sequences from the \myrevision{whole} catalog.
-The number of events in each sub-sequence was varied randomly but chosen to be large enough to represent the seismic characteristics of each region.
-In particular, the minimum size of each sub-sequence was set to be $n \geq 200$, and the maximum size in the sequence was set to be as large as the original catalog (\myrevision{whole catalog}; see Table \ref{tab:seismicity}).
+The number of events in each sub-sequence, $n$, was varied randomly but chosen to be large enough to represent the seismic characteristics of each region.
+In particular, the minimum size of each sub-sequence was set to be $n \geq 200$, and the maximum size in the sequence was set to be as large as the original \myrevision{whole} catalog (see Table \ref{tab:seismicity}).
 We forced the random sub-sequences to progress positively in time without altering the natural occurrence of events.
 In other words, we randomly determined the initial event and the sub-sequence size (number of events to be considered), and then picked that number of events following the initial earthquake in the sub-sequence.
-Next, we determined the value of $M_c$ and $b$ as previously done for the complete catalogs, created the graph for all events with $M \geq M_c$, and extracted the connectivity degree of the events in each sub-sequence.
-\myrevision{Note that the results of the whole catalog for each seismic region is different from Fig.~\ref{fig:regression}.
-In Fig.~\ref{fig:regression} we choose a time dependent completeness magnitude which is conservative and requires inspection.
-In order to keep uniformity in the random data test we computed the completeness magnitude through GFT for all subsamples and the whole catalog of each seismic region.
-Determination of completeness magnitude based on the best score of GFT between synthetic catalog and subsamples could be controversial.
-It is possible to choose very large $M_c$ just because of slightly higher GFT score than smaller magnitudes.
-This could result in a sequence  of data where is not completely a representative of the domain.
-However, knowing these source of uncertainties, the randomly generated data conforms the fact that the method is fairly robust for the catalog size and completeness magnitude; where we can easily distinguish the 3 seismic region border.
-There are some outlier data due to subsamples of aftershocks of big earthquakes.
-These sequences represent different $k-M$ and $b-value$ relationship.
-These sequences do not represent the dominant seismicity pattern of the region.
-In the declustered catalog (is not presented here) we do not see these outliers.}
+Next, we determined the value of $M_c$ and $b$ \myrevision{to obtain the complete and declustered catalogs for each region}, created the graph for all events with $M \geq M_c$, and extracted the connectivity degree of the events in each sub-sequence.
+\myrevision{Because this needed to be done for a large number of sub-sequences, in this part of the analysis we used the goodness-of-fit test (GFT) method to determine $M_c$ systematically, instead of the MAXC method.
+The GFT method follows the recommendations of \citet{Wiemer2000} and \citet{Wiemer2001}, and leads to less conservative values of $M_c$, which is preferable to keep the subsequences large enough.}
 
@@
 
-Fig.~\ref{fig:random}a shows scattered points for all the individual $k$-$M$ slope and $b$-value pairs for all the sub-sequences that were randomly picked from the initial catalogs of each region in northern Iran (small symbols).
-Figures \ref{fig:random}b and \ref{fig:random}c show the variability of the $k$-$M$ slope and $b$-value, respectively.
-These latter figures show the mean values of each parameter for all the random sub-sequences and the amplitudes of $\pm 1$ standard deviation, as well as the coefficients of variation (in percentage).
-Figure \ref{fig:random}a also includes the data points corresponding to the complete catalogs (large solid symbols); the points corresponding to the mean values of the $k$-$M$ slope and $b$, from Figs.~\ref{fig:random}b and \ref{fig:random}c (large hollow symbols); and the universal linear regression from equation (\ref{eq:universal.bm}) (thick line), as well as the linear regressions for northern Iran when using the complete catalogs (dashed thin line) and the random sub-catalogs (continuous thin line).
+\myrevision{Fig.~\ref{fig:random} shows the results for this analysis on random subsequences for both the complete and declustered catalogs.
+In particular, Figs.~\ref{fig:random}a and \ref{fig:random}d show} scattered points for all the individual $k$-$M$ slope and $b$-value pairs for all the subsequences that were randomly picked from the \myrevision{complete and declustered} catalogs of each region in northern Iran (small symbols)\myrevision{, respectively}.
+Figures \ref{fig:random}b \myrevision{and \ref{fig:random}e show the variability of the $k$-$M$ slope, and Figs.~\ref{fig:random}c and \ref{fig:random}f show the variability of $b$.
+The variability plots} show the mean values of each parameter for all the random subsequences and the amplitudes of $\pm 1$ standard deviation, as well as the coefficients of variation (in percentage).
+\myrevision{Figures \ref{fig:random}a and \ref{fig:random}d also include the data points corresponding to the regional analysis of the catalogs, the points corresponding to the mean values of the $k$-$M$ slope and $b$, and the universal linear regression from equations (\ref{eq:universal.bm}) and (\ref{eq:universal.bm.dc}), as well as the linear regressions for northern Iran when using the full-sequence catalogs (dashed thin line) and the random subsequence catalogs (continuous thin line).}
 
-The comparison between the mean values of the random sequences analysis versus the complete catalogs presented in Fig.~\ref{fig:random} indicates that there exists only a small bias, which is well within the standard deviation of the different value samples.
-We note that the values of the $k$-$M$ slope are slightly smaller when obtained with the random sequence analysis, whereas the $b$ values seem more stable.
+\myrevision{In essence, the results in Fig.~\ref{fig:random} show that, despite the variability in the random subsequences and the differences in the computation of $M_c$, both of which are sources of additional uncertainty, the analysis produces an outcome in fair agreement with the universal relationships.
+Nonetheless, the analysis of the random subsequences in the complete catalogs produces some outliers, whereas the processing of the declustered subsequences tends to concentrate more evenly around the universal trend.
+Note that, likely due to the removal of foreshocks and aftershocks, the declustered random subsequences exhibit a clearer distinction between the three seismic zones.}
 
-% \cmmnt{
-% The comparisons of the regressions, however, indicate that the analysis of the random sub-catalogs leads to a result more in line with the universal results obtained when considering multiple seismic zones.
-The linear regression of the random sub-catalogs yields the following equation:
-% % 
-% \begin{equation}
-%    	b = 0.045  +0.390 m \, .
-% 	\label{eq:iran.bm}
-% \end{equation}
+\myrevision{While these sequences do not represent the dominant seismicity pattern of the region, the comparison between the mean values of the random sequences analysis versus the complete catalogs (large, empty and solid symbols in Fig.~\ref{fig:random}) indicates that there exists only a small bias, which is well within the standard deviation of the different value samples.
+Note also that the values of the $k$-$M$ slope in Fig.~\ref{fig:random} are slightly smaller when obtained with the random sequence analysis than when done for the regional sequences, whereas the $b$ values seem more stable.
+This explains why the regressions of the random subsequences are less steep than the universal regressions, in both cases.
+In a separate initial analysis, not included here for brevity, we observed that lower, less conservative selections of $M_c$ can lead to random subsequences that yield regressions in better agreement with the universal trend.
+Using lower values of $M_c$, however, may be misleading.
+In this sense, larger catalogs in better instrumented regions may shed light on the stability of the $m$-$b$ relationship, which is the reason we included the data point from \citet{Azizzadeh_2017_SSA} for southern California in Fig.~\ref{fig:regression}, which falls well in line with the universal regression.}
 
-% Note that equations (\ref{eq:universal.bm}) and (\ref{eq:iran.bm}) have similar intercepts with the $b$-value axis, and only slightly different slope constants.
-In this particular case, the analysis for northern Iran leads to a relationship in which the $b$-value increases more rapidly with $m$ than in the case of the regression obtained for the universal data.
-The similarity between the two equations, however, is a positive sign of the stability of the method.}
+* * * HERE * * *
 
@@
 	\includegraphics[width=0.75\textwidth]{figures/pdf/figure-09-rev.pdf} 
-	\caption{Variation of <$T_c$>, $k$-$M$ slope and $b$-value as with respect to time for three seismic zones for a moving window analysis of the visibility graphs of sub-sequences of \myrevision{50} consecutive events, along with the magnitude of events in the 2005--\myrevision{2016} period.
+	\caption{Variation of $<$$T_c$$>$, $k$-$M$ slope and $b$-value as with respect to time for three seismic zones for a moving window analysis of the visibility graphs of sub-sequences of \myrevision{50} consecutive events, along with the magnitude of events in the 2005--\myrevision{2016} period.
 Black triangles indicate the occurrence of major earthquakes in each of the regions, with the corresponding magnitude at the top of each symbol.
@@
 We recognize, however, that the lack of larger ($M>6$) events in our region of interest in the last decade prevents us from drawing a stronger conclusion on this regard.
+
+% OLD MATERIAL
+% -----------------------------------------------------------------
+
+% Another aspect of interest is the stability of the data points themselves.
+Note that as presented in Fig.~\ref{fig:regression}, the analysis of the sequences shown in Fig.~\ref{fig:mag-time} only contribute one data point per region of interest.
+Furthermore, each data-point comes from sequences that vary significantly in terms of the number of events and seismic parameters (see Table \ref{tab:seismicity}).
+
+% \myrevision{According to Scholtz (1968) b-value for microfractures in rocks is reported ranging between 0.11 and 2.58.
+Using different synthetic and real catalog, in this study we cover a broad range from low b-value (synthetics) to high b-value(subduction zone)}.
+
+% Fig.~\ref{fig:regression} also includes the results of different linear regressions between the $b$-value and the $k$-$M$ slope.
+Each regression reflects the addition of new data-points from different studies.
+Note that the regression improves as new data-points are added, which is indicated by the correlation coefficient $R$, also included in the figure.
+The correlation fitting various regional seismic data was previously pointed out by \citet{Telesca2014}.
+
+% \cmmnt{Note also that the threshold value of $M_c$ is significantly smaller for Azerbaijan than for Alborz or Kopeh Dagh.
+This is due in part to the fact that the latter two zones were more seismically active in the time period under consideration}
+% \myrevision{In this study due to using windowing method, we consider a very conservative completeness magnitude}.
+However, according to \citet{Telesca2012}, the threshold magnitude has a minor effect in the graph parameters.
+
+% Moving on, \citet{Telesca2013} observed that the value of the $k$-$M$ slope was not particularly sensitive to the sample size in the sequence---at least not when considering sufficiently large sequences.
+On the other hand, as we will see below, if the sequence window is sufficiently small, then the $k$-$M$ slope value shows a relative dependence on time and thus provides insight about the variation of the seismicity as the sequence progresses.
+
+% Note that the results of the whole catalog for each seismic region is different from Fig.~\ref{fig:regression}.
+In Fig.~\ref{fig:regression} we choose a time dependent completeness magnitude which is conservative and requires inspection.
+In order to keep uniformity in the random data test we computed the completeness magnitude through GFT for all subsamples and the whole catalog of each seismic region.
+Determination of completeness magnitude based on the best score of GFT between synthetic catalog and subsamples could be controversial.
+It is possible to choose very large $M_c$ just because of slightly higher GFT score than smaller magnitudes.
+This could result in a sequence of data where is not completely a representative of the domain.
+However, knowing these source of uncertainties, the randomly generated data conforms the fact that the method is fairly robust for the catalog size and completeness magnitude; where we can easily distinguish the 3 seismic region border.
+There are some outlier data due to subsamples of aftershocks of big earthquakes.
+These sequences represent different $k-M$ and $b-value$ relationship.
+These sequences do not represent the dominant seismicity pattern of the region.
+In the declustered catalog (is not presented here) we do not see these outliers.}
+
+% \cmmnt{
+% The comparisons of the regressions, however, indicate that the analysis of the random sub-catalogs leads to a result more in line with the universal results obtained when considering multiple seismic zones.
+The linear regression of the random sub-catalogs yields the following equation:
+% % 
+% \begin{equation}
+%    	b = 0.045  +0.390 m \, .
+% 	\label{eq:iran.bm}
+% \end{equation}
+
+% Note that equations (\ref{eq:universal.bm}) and (\ref{eq:iran.bm}) have similar intercepts with the $b$-value axis, and only slightly different slope constants.
+In this particular case, the analysis for northern Iran leads to a relationship in which the $b$-value increases more rapidly with $m$ than in the case of the regression obtained for the universal data.
+The similarity between the two equations, however, is a positive sign of the stability of the method.}

### 2017-06-21 results.tex
update to paag revision

@@
 
-* * * HERE * * *
-
 \begin{figure*}%[t]
@@
 We now investigate the relationship of the parameters obtained through the visibility graph analysis with time.
-Here, the visibility graph analysis is done by windows of equal number of events moving in time across the catalog sequence.
+Here, the visibility graph analysis is done by windows of equal number of events moving in time along the catalog sequence.
 The number of events in the window is kept fixed independently of the time between them, and the results are associated with the last event in the window.
 In this case, we are interested in using a small number of events to capture the relevance of each new event as the window moves in time.
-We tried different \myrevision{window size (20-100 events per window) for each seismic zone.
-The characteristics of major events are not considerably changing due to window size.
-There is a trade of in choosing the window size.
-Small windowing size will highlight the local changes in the time series, however, in the mean time it won't represent a true seismicity characteristic of the subsample (e.g., b-value).
-We choose window size as 50 to be small enough to represent the variation of k-M, b-value and Tc in time and large enough in agreement with Woessner and Wiemer (2005) who found that at least the number of events has to be 50 to get reliable estimate of b-value.} At this point it is also of interest to compute the value of <$T_c$> explained in the Methodology section.
+We tried different \myrevision{window sizes between 20 and 100 events per window for each seismic zone.
+As it is natural to expect, there are trade-offs between different window-sizes.
+Smaller window sizes emphasize the local changes in the time series, but are less reliable when it comes to the seismicity parameters (e.g., $b$ value).
+Larger window sizes, on the other hand, offer less insight into the time dependence of the window sequence characteristics.
+We chose a window size $n = 50$, which is consistent with the suggested minimum number of events acceptable to estimate $b$ according to \citet{Woessner_2005_BSSA}.}
 
-Figure \ref{fig:tc} shows the variation of <$T_c$>, the $k$-$M$ slope, and the $b$-value with time for each of the three seismic zones in northern Iran.
+\myrevision{In this windowing analysis, in addition to $b$ and the $k$-$M$ slope, we are interested in computing} the value of $<$$T_c$$>$ explained in the Methodology section.
+Figure \ref{fig:tc} shows the variation of the $k$-$M$ slope, the $b$-value, and $<$$T_c$$>$ with time for...
+
+* * * HERE * * *
+
+each of the three seismic zones in northern Iran.
 The time-magnitude sequence is also included for reference.

### 2017-06-21 seismicity.tex
update to paag revision

@@
 	\centering
-	a)
-	\includegraphics[width=\textwidth]{figures/pdf/figure-03} \\
-	b)
 	\includegraphics[width=\textwidth]{figures/pdf/figure-03} 
-	\caption{\myrevision{Instrumental} seismicity of northern Iran for the 2005--\myrevision{2016} period, considering only the events in the seismic zones of interest, namely Azerbaila, Alborz, and Kopeh Dagh.
-The size of symbols are proportional to the magnitude of the events, as indicated by the artificial scale shown on the right.
+	\caption{\myrevision{Instrumental seismicity of northern Iran for the 2005--2016 period, considering only the events in the seismic zones of interest, namely Azerbaila, Alborz, and Kopeh Dagh, for the whole (a) and complete (b) catalogs.} The size of symbols are proportional to the magnitude of the events, as indicated by the artificial scale shown on the right.
 The background shows fault lines and the shaded relief.
@@
 	\centering
-	\includegraphics[width=\textwidth]{figures/pdf/figure-04-rev} 
-	\caption{\myrevision{Completeness magnitude vs time results and selected $M_c$ values for the three tectonic seismic regions in northern Iran as evaluated from the time-magnitude sequence of earthquakes during the 2005--2016 period.}}
+	\includegraphics[width=\textwidth]{figures/pdf/figure-04} 
+	\caption{\myrevision{Completeness magnitude, $M_c$, as a function of time (in years) for the three seismic zones in the region of interest, corresponding to the time-magnitude sequences of earthquakes during the 2005--2016 period.}}
 	\label{fig:completeness}

### 2017-06-21 results.tex
update (cont.) to paag revision

@@
 	\centering
-	\includegraphics[width=\textwidth]{figures/pdf/figure-06-rev.pdf} 
+	\includegraphics[width=\textwidth]{figures/pdf/figure-06} 
 	\caption{Scattered distribution of events in the magnitude-connectivity degree plane and linear regressions obtained for the $k$-$M$ relationships for the three seismic regions in northern Iran.
@@
 	\centering
-	\includegraphics[width=\textwidth]{figures/pdf/figure-07-rev.pdf} 
-	\caption{Correlation between $k$-$M$ slope and $b$-value as drawn from the results of the present study for the region of northern Iranian and three other previous studies, including analysis of the Mexican subduction zone \citep{Telesca2013}, the Pannonian seismic zone \citep{Telesca2014}, and results from two experiments \citep{Telesca2014-pone}.
+	\includegraphics[width=\textwidth]{figures/pdf/figure-07} 
+	\caption{\myrevision{Correlation between $k$-$M$ slope ($m$) and the $b$ value as drawn from the results of the present study for the region of northern Iranian using the complete (a) and declustered (b) catalogs, along with other previous studies including analysis of the Mexican subduction zone \citep{Telesca2013}, the Pannonian seismic zone \citep{Telesca2014}, southern California \citep{Azizzadeh_2017_SSA}, and results from two experiments \citep{Telesca2014-pone}.
 The lines represent linear regressions obtained to fit the different data points, considering different combinations.
 The values of the correlation coefficient, $R$, are indicated for each regression line.
-The color version of this figure is available only in the electronic edition.}
+The color version of this figure is available only in the electronic edition.}}
 	\label{fig:regression}

### 2017-06-21 methodology.tex
updates on modifications of the revised version for paag
update (cont.) to paag revision

@@
 The mean $<$$T_c^e$$>$ value associated with this event is also shown at the top right.
-The mean value of all $<$$T_c^e$$>$ for the events in the graph is the window mean interval connectivity time, $<$$T_c^e$$>$.
-The color version of this figure is available only in the electronic edition.}
+The mean value of all $<$$T_c^e$$>$ for the events in the graph is the window mean interval connectivity time, $<$$T_c^e$$>$.}
 	\label{fig:vg}
 \end{figure*}
-
-% \myrevision{\color{red} In terms of earthquake catalog, the visibility graph studies the relation between earthquake events.
-Relation between small and large earthquakes are investigated in different studies.
-Lee et al (2009), based on developing LRCS model, in which is assumed that the occurrence of an earthquake leads to a release of energy with long range effects like in real earthquake fault systems, it has been known that earthquakes are long-range correlated.
-The visibility connections between the "hubs" (large events) and events even located very far on time could represent such long-range correlated behavior.}
 
@@
 This and the aforementioned relationship between the $k$-$M$ slope and the $b$-value are aspects we explore next for our region and years-interval of interest.
+
+% OLD MATERIAL
+% -----------------------------------------------------------------
+
+% \myrevision{\color{red} In terms of earthquake catalog, the visibility graph studies the relation between earthquake events.
+Relation between small and large earthquakes are investigated in different studies.
+Lee et al (2009), based on developing LRCS model, in which is assumed that the occurrence of an earthquake leads to a release of energy with long range effects like in real earthquake fault systems, it has been known that earthquakes are long-range correlated.
+The visibility connections between the "hubs" (large events) and events even located very far on time could represent such long-range correlated behavior.}

### 2017-06-21 results.tex
update (cont.) to paag revision

@@
 	\caption{Scattered distribution of events in the magnitude-connectivity degree plane and linear regressions obtained for the $k$-$M$ relationships for the three seismic regions in northern Iran.
-The value next to each of regression line corresponds to the slope of the line, which is referred here as the $k$-$M$ slope.
-The color version of this figure is available only in the electronic edition.}
+The value next to each of regression line corresponds to the slope of the line, which is referred here as the $k$-$M$ slope.}
 	\label{fig:km}
@@
 The lines represent linear regressions obtained to fit the different data points, considering different combinations.
-The values of the correlation coefficient, $R$, are indicated for each regression line.
-The color version of this figure is available only in the electronic edition.}}
+The values of the correlation coefficient, $R$, are indicated for each regression line.}}
 	\label{fig:regression}
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-08-rev.pdf} 
-	\caption{\textbf{(a)} Correlation between $k$-$M$ slope and $b$-values for 200 random sequences extracted from the \myrevision{whole} catalogs of the three northern Iranian seismic regions considered in this study (scattered symbols), including the mean values (empty symbols with thick border) and the data points obtained from the analysis of the complete catalog (solid symbols), along with the linear regressions of each sample as indicated in the legend.
-\textbf{(b)} Mean, $\pm1$ standard deviation, and coefficient of variation (in percent) for the $k$-$M$ slope values of the three seismic zones in northern Iran.
-\textbf{(c)} Same as part (b), but corresponding to the $b$-value.
-The color version of this figure is available only in the electronic edition.}
+	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-08} 
+	\caption{\myrevision{Correlation between the $k$-$M$ slope ($m$) and $b$ values for 200 random sequences extracted from the complete (a) and declustered (d) catalogs of the three northern Iranian seismic regions considered in this study (scattered symbols), including the mean values (empty symbols with thick border) and the data points obtained from the regional analyses (solid symbols), along with the linear regressions of each sample as indicated in the legend; and mean $\pm1$ standard deviation bar plots for $m$ (b,e) and $b$ (c,f) for the complete and declustered catalogs, respectively.
+In the latter, the values in the parentheses corresponds to the coefficients of variation.}}
 	\label{fig:random}

### 2017-06-21 seismicity.tex
update (cont.) to paag revision

@@
 This zonation follows the division proposed by \citet{Mirzaei1998} and later modified by \citet{Karimiparidari2013}.
-The background shows fault lines and the shaded relief.
-The color version of this figure is available only in the electronic edition.}
+The background shows fault lines and the shaded relief.}
 	\label{fig:study_region}
@@
 	\caption{\myrevision{Instrumental seismicity of northern Iran for the 2005--2016 period, considering only the events in the seismic zones of interest, namely Azerbaila, Alborz, and Kopeh Dagh, for the whole (a) and complete (b) catalogs.} The size of symbols are proportional to the magnitude of the events, as indicated by the artificial scale shown on the right.
-The background shows fault lines and the shaded relief.
-The color version of this figure is available only in the electronic edition.}
+The background shows fault lines and the shaded relief.}
 	\label{fig:seismicity}
@@
 		Region       & \multicolumn{3}{c}{Number of Events in Catalog} & $M_c$ & \multicolumn{2}{c}{$b$-value} \\
-		\cline{2-4} 
+		\cline{2-4}\cline{6-7} 
 		             & Whole & Complete & Declustered &     & Complete             & Declustered \\
@@
 	\centering
-	\includegraphics[width=\textwidth]{figures/pdf/figure-05-rev} 
+	\includegraphics[width=\textwidth]{figures/pdf/figure-05} 
 	\caption{Time-magnitude sequences for the northern Iran seismic zones of Azerbaijan, Alborz and Kopeh Dagh, during the period between 1 January 2005 and 31 December \myrevision{2016}.
@@
 The edges or links are omitted for visual convenience.
-Highlighted in the figure are the largest events in each sub-catalog, namely the 2012 $M_w$ 6.4 East Azerbaijan, 2010 $M_w$ 5.8 Damghan, and 2012 $M_w$ 5.4 Neyshabur earthquakes.
-The color version of this figure is available only in the electronic edition.}
+Highlighted in the figure are the largest events in each sub-catalog, namely the 2012 $M_w$ 6.4 East Azerbaijan, 2010 $M_w$ 5.8 Damghan, and 2012 $M_w$ 5.4 Neyshabur earthquakes.}
 	\label{fig:mag-time}

### 2017-06-22 abstract.tex
done with main changes, conclusions pending

@@
 The method relies on the inter-event visibility defined in terms of a connectivity degree parameter, $k$, which is correlated with the earthquake magnitude, $M$.
-Previous studies show that the slope of the $k$-$M$ correlation also observes a relationship with the $b$-value from the Gutenberg-Richter law, thus rendering the graph analysis useful to examine the seismicity of a region.
-In addition, other topological properties of the network and dynamic properties of the magnitude-time series exhibit characteristics that seem to be associated with the occurrence of earthquakes, offering the possibility of correlating seismicity parameters with time.
+Previous studies show that the slope of the $k$-$M$ correlation, $m$, also observes a relationship with the $b$-value from the Gutenberg-Richter law, thus rendering the graph analysis useful to examine the seismicity of a region.
+\myrevision{These correlations seem to hold for the analysis of relatively small sequences of earthquakes, offering the possibility of studying seismicity parameters in time}.
 We apply this approach to the case of the seismicity of northern Iran, using an earthquake catalog for the tectonic seismic regions of Azerbaijan, Alborz, and Kopeh Dagh.
-We use results drawn for this region with the visibility graph approach in combination with results from other similar studies to further improve the universal relationship between the slope of $k$-$M$ and $b$-value, and show that the visibility graph approach can be considered as a valid alternative for analyzing regional seismicity properties and earthquake sequences.
+We use results drawn for this region with the visibility graph approach in combination with results from other similar studies to further improve the universal relationship between $m$ and $b$, and show that the visibility graph approach can be considered as a valid alternative for analyzing regional seismicity properties and earthquake sequences.

### 2017-06-22 introduction.tex
done with main changes, conclusions pending

@@
 Subsequently, \citet{Telesca2013} studied the seismicity of the Mexican subduction zone through the visibility graph approach and found that the properties of the graph were correlated to the seismic $b$-value in the Gutenberg-Richter law \citep{Gutenberg1944}.
-In particular, \citet{Telesca2013} extracted the characteristics of the visibility graph for five different tectonic seismic regions in the Mexican subduction zone and found that the slope in the linear relationship between earthquake magnitude, $M$, and the inter-event visibility in the graph, defined as the connectivity degree parameter, $k$, was correlated with the $b$-value.
+In particular, \citet{Telesca2013} extracted the characteristics of the visibility graph for five different tectonic seismic regions in the Mexican subduction zone and found that the slope $m$ in the linear relationship between earthquake magnitude, $M$, and the inter-event visibility in the graph, defined as the connectivity degree parameter, $k$, was correlated with $b$.
 
 In a similar article, \citet{Telesca2014} studied the seismicity of the 2002--2011 Pannonian region using the visibility graph method for two sub-catalogs of shallow and deep earthquakes.
-They extracted the visibility graph characteristics for each group of events and confirmed that there was a close correlation between the Gutenberg-Richter $b$-value and the slope of the $k$-$M$ relationship obtained from the visibility graph.
-According to \citet{Telesca2014}, the high linear correlation coefficient value (close to 1.0) between the $b$-value and the $k$-$M$ slope indicates that this relationship exhibits a nearly universal character.
+They extracted the visibility graph characteristics for each group of events and confirmed that there was a close correlation between the Gutenberg-Richter $b$-value and the slope $m$ of the $k$-$M$ relationship obtained from the visibility graph.
+According to \citet{Telesca2014}, the high linear correlation coefficient value (close to 1.0) between the $b$ and $m$ indicates that this relationship exhibits a nearly universal character.
 This observation was reinforced experimentally by \citet{Telesca2014-pone}, who investigated the behavior of a mechanical stick-slip system with different asperities (sandpaper of different grades).
-After collecting data for different experiments emulating young and mature faults, \citet{Telesca2014-pone} found again that the $b$-value was linearly correlated with the $k$-$M$ slope derived from the visibility graph of the experimental events.
+After collecting data for different experiments emulating young and mature faults, \citet{Telesca2014-pone} found again that $b$ was linearly correlated with the value of $m$ derived from the visibility graph of the experimental events.
 
@@
 We first summarize the dataset, including a description of the seismic catalog and its completeness based on a recent work on the seismicity of the region \citep{Khoshnevis2017}.
-We then present results obtained for the region regarding the relationship between the the graph's $k$-$M$ slope and the seismicity $b$-value for the three seismic areas, analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, and present results for the variation of $<$$T_c$$>$ through time.
+We then present results obtained for the region regarding the relationship between the the graph's $k$-$M$ slope and the seismicity $b$-value for the three seismic areas, analyze the sensitivity \myrevision{of the results to the definition of the catalogs, the number of events and composition,} and present results for the variation of $<$$T_c$$>$ over time.

### 2017-06-22 methodology.tex
done with main changes, conclusions pending

@@
 We refer to this correlation as the $k$-$M$ relationship.
-\myrevision{This is of relevance because it happens that, for a significant number of earthquake catalogs from distinctive seismic zones,} the slopes of the $k$-$M$ relationships show a linear regression with the seismicity $b$-value of the seismic zones under consideration.
-{This observation seems to hold} for a universal sample of $k$-$M$ slopes and $b$ values \myrevision{from different regions, as suggested by} \citet{Telesca2013, Telesca2014}.
+\myrevision{This is of relevance because it happens that, for a significant number of earthquake catalogs from distinctive seismic zones,} the slope $m$ of the $k$-$M$ relationships show a linear regression with the seismicity $b$-value of the seismic zones under consideration.
+\myrevision{This observation seems to hold for a universal sample of $m$ and $b$ values from different regions, as suggested by} \citet{Telesca2013, Telesca2014}.
 \citet{Telesca2014} also observed that it was reasonable to draw a relationship between the distribution of the events when considering whether these were connected (visible to each other) or not, and time.
@@
 
-Because $<$$T_c$$>$ can be obtained for any sub-graph within a larger graph, that is, for any time window in a larger magnitude-time series of events, then it is possible to investigate the evolution of $<$$T_c$$>$ (and that of the $k$-$M$ slope and the $b$-value) for a moving window---with a constant number of events---sliding along the magnitude-time series.
-When doing so, \citet{Telesca2016} suggested to associate the values of each sub-sequence with the last event in the sub-sequence.
+Because $<$$T_c$$>$ can be obtained for any sub-graph within a larger graph, that is, for any time window in a larger magnitude-time series of events, then it is possible to investigate the evolution of $<$$T_c$$>$ (and that of $m$ and $b$) for a moving window---with a constant number of events---sliding along the magnitude-time series.
+When doing so, \citet{Telesca2016} suggested to associate the values of each subsequence with the last event in the subsequence.
 Following this approach, \citet{Telesca2016} found that the variation of $<$$T_c$$>$ over time exhibited a possible relationship with the occurrence of earthquakes.
-This and the aforementioned relationship between the $k$-$M$ slope and the $b$-value are aspects we explore next for our region and years-interval of interest.
+This and the aforementioned relationship between $m$ and $b$ are aspects we explore for our region and years-interval of interest.
 

### 2017-06-22 results.tex
done with main changes, conclusions pending

@@
 
-We generate the visibility graphs for each sub-region of interest using the time-magnitude sequences \myrevision{of both the complete and declustered catalogs.
+We generate the visibility graphs for each subregion of interest using the time-magnitude sequences \myrevision{of both the complete and declustered catalogs.
 In the case of the complete catalog, that corresponds to the sequences shown in Fig.~\ref{fig:mag-time}.
@@
 (We do not include a visualization of the graphs because the links are so many, that it is only practical to visualize the graphs of short sequences.) We collect information about the number of inter-visibility links associated with each event (connectivity degree, $k$) and categorize the events in magnitude bins of size $\Delta M_{\mathrm{bin}} = 0.1$, as mentioned in the Methodology section.
-Figure \ref{fig:km} shows the scattered distribution of events in the magnitude-connectivity degree plane for each sub-region\myrevision{, corresponding to the complete catalogs.} The figure shows that, in general, the value of $k$ increases with $M_w$\myrevision{; and includes the results of obtaining linear $k$-$M$ regressions for each dataset along with the values of the $k$-$M$ slopes for the three seismic zones, namely 10.0, 9.85, and 8.70 for the Azerbaijan, Alborz, and Kopeh Dagh regions.
-Similar results regressions were obtained for the declustered catalogs, which yielded slopes of 8.92, 8.97, and 7.96, respectively.}
+Figure \ref{fig:km} shows the scattered distribution of events in the magnitude-connectivity degree plane for each subregion\myrevision{, corresponding to the complete catalogs.} The figure shows that, in general, the value of $k$ increases with $M_w$\myrevision{; and includes the results of obtaining linear $k$-$M$ regressions for each dataset along with the values of the slope $m$ for the three seismic zones, namely 10.0, 9.85, and 8.70 for the Azerbaijan, Alborz, and Kopeh Dagh regions.
+Similar results regressions were obtained for the declustered catalogs, which yielded $m$ values of 8.92, 8.97, and 7.96, respectively.}
 
@@
 Next, we examine the relationship between the $b$ values from Table \ref{tab:seismicity} and the $k$-$M$ slopes.
-\myrevision{Figures \ref{fig:regression}a and \ref{fig:regression}a show the scattered results of the $k$-$M$ slope versus $b$-value, for the complete and declustered catalogs, respectively.
+\myrevision{Figures \ref{fig:regression}a and \ref{fig:regression}a show the scattered results of the $m$ versus $b$ for the complete and declustered catalogs, respectively.
 Along with the data-points obtained for our analysis of the three seismic regions of northern Iran, in each plot, we also include the data points corresponding to the magnitude-time sequences of the Mexican subduction zone provided by \citet{Telesca2013}, the Pannoninan seismic zone from \citet{Telesca2014}, the experimental results obtained by \citet{Telesca2014-pone}, and the result from a similar preliminary analysis done by \citet{Azizzadeh_2017_SSA} for California.
@@
 In addition, \citet{Scholz_1968_BSSA} reported that experimental microfractures in rocks, similar to those observed in earthquakes, exhibit $b$ values ranging between 0.11 and 2.58.
-Considering that the $b$ value, by definition, represents the proportion between the amount of large and small events in a region, the trends shown in Fig.~\ref{fig:regression} contribute to the suggestion made by \citet{Telesca2014} about the universal character of the relationship between $b$ and the $k$-$M$ slope.}
+Considering that, by definition, $b$ represents the proportion between the amount of large and small events in a region, the trends shown in Fig.~\ref{fig:regression} contribute to the suggestion made by \citet{Telesca2014} about the universal character of the relationship between $b$ and $m$.}
 
-According to these results, a universal relationship between $b$ and the $k$-$M$ slope ($m$) can be expressed as
+According to these results, a universal relationship between $b$ and $m$ can be expressed as
 % 
@@
 
-To further explore the sensitivity of the graph properties to the number of events in each catalog and the value of the minimum magnitude, we randomly picked a significant number of sub-sequences from within the initial catalog compiled for each region, and repeated the analysis for each sub-sequence.
-In total, for each region, we extracted 200 new sub-sequences from the \myrevision{whole} catalog.
-The number of events in each sub-sequence, $n$, was varied randomly but chosen to be large enough to represent the seismic characteristics of each region.
-In particular, the minimum size of each sub-sequence was set to be $n \geq 200$, and the maximum size in the sequence was set to be as large as the original \myrevision{whole} catalog (see Table \ref{tab:seismicity}).
-We forced the random sub-sequences to progress positively in time without altering the natural occurrence of events.
-In other words, we randomly determined the initial event and the sub-sequence size (number of events to be considered), and then picked that number of events following the initial earthquake in the sub-sequence.
-Next, we determined the value of $M_c$ and $b$ \myrevision{to obtain the complete and declustered catalogs for each region}, created the graph for all events with $M \geq M_c$, and extracted the connectivity degree of the events in each sub-sequence.
-\myrevision{Because this needed to be done for a large number of sub-sequences, in this part of the analysis we used the goodness-of-fit test (GFT) method to determine $M_c$ systematically, instead of the MAXC method.
+To further explore the sensitivity of the graph properties to the number of events in each catalog and the value of the minimum magnitude, we randomly picked a significant number of subsequences from within the initial catalog compiled for each region, and repeated the analysis for each subsequence.
+In total, for each region, we extracted 200 new subsequences from the \myrevision{whole} catalog.
+The number of events in each subsequence, $n$, was varied randomly but chosen to be large enough to represent the seismic characteristics of each region.
+In particular, the minimum size of each subsequence was set to be $n \geq 200$, and the maximum size in the sequence was set to be as large as the original \myrevision{whole} catalog (see Table \ref{tab:seismicity}).
+We forced the random subsequences to progress positively in time without altering the natural occurrence of events.
+In other words, we randomly determined the initial event and the subsequence size (number of events to be considered), and then picked that number of events following the initial earthquake in the subsequence.
+Next, we determined the value of $M_c$ and $b$ \myrevision{to obtain the complete and declustered catalogs for each region}, created the graph for all events with $M \geq M_c$, and extracted the connectivity degree of the events in each subsequence.
+\myrevision{Because this needed to be done for a large number of subsequences, in this part of the analysis we used the goodness-of-fit test (GFT) method to determine $M_c$ systematically, instead of the MAXC method.
 The GFT method follows the recommendations of \citet{Wiemer2000} and \citet{Wiemer2001}, and leads to less conservative values of $M_c$, which is preferable to keep the subsequences large enough.}
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-08} 
+	\includegraphics[width=\textwidth]{figures/pdf/figure-08} 
 	\caption{\myrevision{Correlation between the $k$-$M$ slope ($m$) and $b$ values for 200 random sequences extracted from the complete (a) and declustered (d) catalogs of the three northern Iranian seismic regions considered in this study (scattered symbols), including the mean values (empty symbols with thick border) and the data points obtained from the regional analyses (solid symbols), along with the linear regressions of each sample as indicated in the legend; and mean $\pm1$ standard deviation bar plots for $m$ (b,e) and $b$ (c,f) for the complete and declustered catalogs, respectively.
@@
 \myrevision{Fig.~\ref{fig:random} shows the results for this analysis on random subsequences for both the complete and declustered catalogs.
-In particular, Figs.~\ref{fig:random}a and \ref{fig:random}d show} scattered points for all the individual $k$-$M$ slope and $b$-value pairs for all the subsequences that were randomly picked from the \myrevision{complete and declustered} catalogs of each region in northern Iran (small symbols)\myrevision{, respectively}.
-Figures \ref{fig:random}b \myrevision{and \ref{fig:random}e show the variability of the $k$-$M$ slope, and Figs.~\ref{fig:random}c and \ref{fig:random}f show the variability of $b$.
-The variability plots} show the mean values of each parameter for all the random subsequences and the amplitudes of $\pm 1$ standard deviation, as well as the coefficients of variation (in percentage).
-\myrevision{Figures \ref{fig:random}a and \ref{fig:random}d also include the data points corresponding to the regional analysis of the catalogs, the points corresponding to the mean values of the $k$-$M$ slope and $b$, and the universal linear regression from equations (\ref{eq:universal.bm}) and (\ref{eq:universal.bm.dc}), as well as the linear regressions for northern Iran when using the full-sequence catalogs (dashed thin line) and the random subsequence catalogs (continuous thin line).}
+In particular, Figs.~\ref{fig:random}a and \ref{fig:random}d show} scattered points for all the individual $m$ and $b$ pairs for all the subsequences that were randomly picked from the \myrevision{complete and declustered} catalogs of each region in northern Iran (small symbols)\myrevision{, respectively}.
+Figures \ref{fig:random}b \myrevision{and \ref{fig:random}e show the variability of $m$, and Figs.~\ref{fig:random}c and \ref{fig:random}f show the variability of $b$.
+These variability plots} show the mean values of each parameter for all the random subsequences and the amplitudes of $\pm 1$ standard deviation, as well as the coefficients of variation (in percentage).
+\myrevision{Figures \ref{fig:random}a and \ref{fig:random}d also include the data points corresponding to the regional analysis of the catalogs, the points corresponding to the mean values of $m$ and $b$, and the universal linear regression from equations (\ref{eq:universal.bm}) and (\ref{eq:universal.bm.dc}), as well as the linear regressions for northern Iran when using the full-sequence catalogs (dashed thin line) and the random subsequence catalogs (continuous thin line).}
 
@@
 \myrevision{While these sequences do not represent the dominant seismicity pattern of the region, the comparison between the mean values of the random sequences analysis versus the complete catalogs (large, empty and solid symbols in Fig.~\ref{fig:random}) indicates that there exists only a small bias, which is well within the standard deviation of the different value samples.
-Note also that the values of the $k$-$M$ slope in Fig.~\ref{fig:random} are slightly smaller when obtained with the random sequence analysis than when done for the regional sequences, whereas the $b$ values seem more stable.
+Note also that the values of $m$ in Fig.~\ref{fig:random} are slightly smaller when obtained with the random sequence analysis than when done for the regional sequences, whereas the $b$ values seem more stable.
 This explains why the regressions of the random subsequences are less steep than the universal regressions, in both cases.
@@
 
-\begin{figure*}%[t]
+\begin{figure*}[t]
 	\centering
-	\includegraphics[width=0.75\textwidth]{figures/pdf/figure-09-rev.pdf} 
-	\caption{Variation of $<$$T_c$$>$, $k$-$M$ slope and $b$-value as with respect to time for three seismic zones for a moving window analysis of the visibility graphs of sub-sequences of \myrevision{50} consecutive events, along with the magnitude of events in the 2005--\myrevision{2016} period.
-Black triangles indicate the occurrence of major earthquakes in each of the regions, with the corresponding magnitude at the top of each symbol.
-In the middle frame of each region, the dashed line corresponds to the $k$-$M$ values, whereas the continuous plot shows the variation of the $b$-value.
-The color version of this figure is available only in the electronic edition.}
+	\includegraphics[width=\textwidth]{figures/pdf/figure-09} 
+	\caption{\myrevision{Variation of $<$$T_c$$>$, $k$-$M$ slope ($m$) and the $b$ value with respect to time for the seismic zone of Alborz for a moving window analysis of the visibility graphs of subsequences of $n=50$ consecutive events, along with the magnitude and the connectivity degree ($k$) of events in the 2016 period.
+Black triangles indicate the occurrence of significant earthquakes in each of the regions, with the corresponding magnitude at the top of each symbol.}}
 	\label{fig:tc}
@@
 
-We now investigate the relationship of the parameters obtained through the visibility graph analysis with time.
+We now investigate the relationship of the parameters obtained through the visibility graph analysis over time.
 Here, the visibility graph analysis is done by windows of equal number of events moving in time along the catalog sequence.
@@
 
-\myrevision{In this windowing analysis, in addition to $b$ and the $k$-$M$ slope, we are interested in computing} the value of $<$$T_c$$>$ explained in the Methodology section.
-Figure \ref{fig:tc} shows the variation of the $k$-$M$ slope, the $b$-value, and $<$$T_c$$>$ with time for...
+\myrevision{In this windowing analysis, in addition to $b$ and $m$, we are interested in computing the value of $<$$T_c$$>$ explained in the Methodology section.
+Figure \ref{fig:tc} shows the earthquake sequence for the region of Alborz, and the variation of $k$, $m$, $b$, and $<$$T_c$$>$ with time.
+Although we performed the analysis for all three seismic zones, we concentrate in the region of Alborz because is the one with the larger number of events for the fixed-size moving window.
+We can see here how larger values of $k$ are associated with the larger magnitude earthquakes, and how the resulting values of $m$ for each 50-event sequence compares with $b$.
+In particular, we observe a good correlation between $m$ and $b$ fore the period prior to the 2010 $M_w$ 5.8 Damaghan earthquake, but after this event the correlation is not as clear.
+Unfortunately, contrary to the suggestions of \citet{Telesca2016}, we do not observe any clear correlation between the behavior of $<$$T_c$$>$ and the occurrence of the larger magnitude ($M_w \geq 5$) earthquakes in this region.
+Similarly, while the occurrence of larger events does seem to coincide with drops in $m$ and $b$, there are other similar changes in the values of $m$ and $b$ that are not associated with any significant event, making it difficult to draw strong conclusions.
+Nonetheless, in the region of Azerbaijan, we did observe more prominent changes in $m$ and $b$ with the occurrence of the 2012 $M_w$ 6.4 Tabriz earthquake, which leaves open the possibility of further study for regions with larger magnitude events.}
 
-* * * HERE * * *
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=\textwidth]{figures/pdf/figure-10} 
+	\caption{\myrevision{Correlation between $m$ and $b$ based on the fixed-size windowing analysis done for the region of Alborz, for both the complete (a) and declustered (b) catalogs, along with the linear regressions of each case.
+While a direct comparison is not appropriate, the universal regression is shown as well for reference.}}
+	\label{fig:alborz-bm}
+\end{figure*}
 
-each of the three seismic zones in northern Iran.
-The time-magnitude sequence is also included for reference.
-Note that the behavior of the $k$-$M$ slope and the $b$-value is very similar along time for all three zones.
-\myrevision{Specially in the case of Alborz where because of higher number of events the correlation is easily seen.} This is consistent with the results presented before.
-We note that there seems to be a correlation between the behavior of the $b$-value in time with the occurrence of some of these larger events.
-In particular, some of the events in the figure seem to coincide with a drop in the $b$-value.
-
-The decline of the $b$-value before large earthquakes has been studied in other regions before \citep[e.g.,][]{Wyss2000, Wyss2006, Schorlemmer2005, Chan2012}.
-In the context of the visibility graph analysis, \citet{Telesca2016} observed a decrease in <$T_c$> before the large earthquake of the western India earthquake sequence.
-We recognize, however, that the lack of larger ($M>6$) events in our region of interest in the last decade prevents us from drawing a stronger conclusion on this regard.
+\myrevision{Finally, we explore the correlation between $k$ and $b$ by aggregating the results of the windowing analysis.
+Figure \ref{fig:alborz-bm}a shows condensed (scattered) results for all the values $k$ and $b$ from Fig.~\ref{fig:tc} for the complete catalog of Alborz, and Fig.~\ref{fig:alborz-bm}b shows the same results but for the declustered catalog.
+Both plots exhibit reasonable linear regressions for an ample range of $m$ and $b$ values.
+While it is not entirely fair to compare these results (which are exclusive to the Alborz region) with the universal results discussed before, Fig.~\ref{fig:alborz-bm} also includes the universal correlations for reference.
+The results for Alborz also show $b$ to increase proportionally with $m$, although at a smaller rate.}
 
@@
 The similarity between the two equations, however, is a positive sign of the stability of the method.}
+
+% each of the three seismic zones in northern Iran.
+The time-magnitude sequence is also included for reference.
+Note that the behavior of the $k$-$M$ slope and the $b$-value is very similar along time for all three zones.
+\myrevision{Specially in the case of Alborz where because of higher number of events the correlation is easily seen.} This is consistent with the results presented before.
+We note that there seems to be a correlation between the behavior of the $b$-value in time with the occurrence of some of these larger events.
+In particular, some of the events in the figure seem to coincide with a drop in the $b$-value.
+
+% The decline of the $b$-value before large earthquakes has been studied in other regions before \citep[e.g.,][]{Wyss2000, Wyss2006, Schorlemmer2005, Chan2012}.
+In the context of the visibility graph analysis, \citet{Telesca2016} observed a decrease in <$T_c$> before the large earthquake of the western India earthquake sequence.
+We recognize, however, that the lack of larger ($M>6$) events in our region of interest in the last decade prevents us from drawing a stronger conclusion on this regard.

### 2017-06-22 seismicity.tex
done with main changes, conclusions pending

@@
 
-In addition to using $M_c$ to determine the $b$-value for each sub-catalog, we also use it as the threshold for limiting the minimum magnitude to be considered in the construction of the visibility graphs for each region.
+In addition to using $M_c$ to determine $b$ for each sub-catalog, we also use it as the threshold for limiting the minimum magnitude to be considered in the construction of the visibility graphs for each region.
 \myrevision{Table \ref{tab:seismicity} shows the number of events of the whole catalog, along with the number of events for each region's complete and declustered catalogs.

### 2017-06-22 conclusion.tex
done with main changes, conclusions pending
completed revision of conclusions

--- 2016-08-21 conclusion.tex
@@
 
-Pending...
+We studied the seismicity of the three main seismic regions in northern Iran in the time period between January 2005 and December \myrevision{2016} using an approach based on the visibility graph method.
+We tested the applicability of this method for the specific region of interest and in reference to previous results from similar studies.
+The results confirm previous observations about the correlation that exists between the connectivity parameter $k$, the magnitude of the events in the sequence, \myrevision{the slope $m$ of the linear regression adjusted to the relationship between $k$ and $M$, and the correlation of the $b$-value from the Gutenberg-Richter law with $m$.
+We used the data points computed from the visibility graph analysis of the seismicity of northern Iran to obtain updated mathematical expressions for a universal relationship between $b$ and $m$, including data collected from previous studies done} for other regions as well as data from experiments.
+We found the relationships to have a good level of similarity, \myrevision{independently of the alternative manipulations of the seismic catalog, but noted that the results were somewhat sensitive to the completeness magnitude.
+Overall, our results are} indicative of the general nature of the relationship between $m$ and $b$.
+We also explored the relationships \myrevision{between the visibility graph properties and the seismicity parameters for a random selection of earthquake subsequences and for a progression of subsequences in time.
+In these cases, we found the relationship between $b$ and $m$ to hold for subsequences with a sufficiently large number of events ($n \geq 50$), but noticed they are in better agreement with the universal regressions when larger, entire regional sequences are considered.
+Unfortunately, for the particular regions considered in this study, we were not able to detect conclusive evidence of other relationships between the visibility graph properties and the temporal occurrence of large earthquakes, as it has been suggested in previous similar studies.
+We believe this is due to the lack of larger magnitude events ($M_w > 6$) in the selected catalogs.}
+
+\myrevision{While the connection between the topological properties of the visibility graph of an earthquake sequence and the seismicity parameters of a region is an attractive finding, it remains to be seen how this can be put to use in a more practical scientific sense.
+We believe future efforts in understanding the mathematical nature of the observed relationships is a natural first step to follow.
+It will also be necessary to test the relationships in additional seismic regions with uncharacteristic $b$ values, especially in the ranges outside the typical $b$-values (0.8--1.2).
+It would also be of interest to build visibility graphs based on other earthquake parameters (e.g., moment) or considering directionality, and investigate other relationships.
+At this point, nonetheless, the method as used here} seems to provide an alternative and interesting approach to the analysis of the seismicity of a region.
+
+% OLD MATERIAL
+% -----------------------------------------------------------------
+
+% that can be drawn from a moving window visibility graph analysis and the variation of the seismicity in the region of interest in time. \myrevision{We found that the }
+
+% \myrevision{The relationship found between k-M slope and b-value suggest that the topological properties of the VG are not unlinked with the seismological properties of  an earthquake sequence.}
+
+% We found there may be a potential relationship between the $b$ value and the occurrence of earthquakes as well as with the graph's mean interval connectivity time parameter <$T_c$>, but additional research in regions with stronger events may be necessary before drawing stronger conclusions in this regard.
+\myrevision{Also further investigation has to be performed in the future to clarify the relationship between the k-M slopes as a pure mathematical object and the b-value and investigate the k-M slope with other earthquake network models.} The method used here, nonetheless, seems to provide an alternative and interesting approach to the analysis of the seismicity of a region.
 

### 2017-06-22 response.tex
response letter added.

@@
 
-Here are the main changes:
-
-1) We use the whole catalog instead of declustered catalog
-2) We added also 2016 seismicity
-3)
-
 \begin{center}
@@
 \introcomment{~}{%
-The authors perform a seismic hazard analysis for northern Iran using a newly developed source model from smoothed seismicity.
-The work is an important contribution to seismic hazard analyses in Iran.
-Development of the seismic source model follows a careful analysis of the earthquake catalogs for information about spatially varying earthquake rates, maximum magnitudes and b-values.
-The authors are careful to acknowledge that alternative means for estimating earthquake recurrence - and for other components of the source and ground motion characterization - also exist, and that this work is only one approach for characterizing hazard in the region.
+This is an interesting paper that applies a relatively new technique to the seismicity data in Northern Iran.
+The manuscript is well-written and would be a worthy contribution to the Pageoph journal.
+I have a few moderate-to-major concerns that I recommend to be addressed by the authors in a revised manuscript.
 }
@@
 \comment{1}{%
-Page 3, Line 71: A short, summary description of previous source models would highlight the contribution of this work.
-In particular, summary details of the work by Khodaverdian et al should be included to indicate how the approach of the authors differs from previous work.
+Please explain why you decluster the catalog and be more specific on the declustering method/declustering-parameters and the results of the declustering procedure.
+How many events are in the catalog before/after declustering?
 }
@@
 \response{%
-We modified parts of the introduction as well as other sections to highlight in a more explicit manner the differences in our study with respect to other previous efforts.
-In the case of Khodaverdian et al (2016), the major difference is in the way the seismicity parameters $b$ and $M_{\max}$ are calculated.
-This is mentioned in the Introduction, and addressed with more clarity in Section 4 (page 11, line 312) and in Section (page 17, line 495).
-As mentioned there, the difference resides in the fact that Khodaverdian et al (2016) compute seismic parameters for grid cells of size 1\textdegree{} $\times$ 1\textdegree{}.
-This means the they compile earthquake catalogs for each grid point considering events within 200 km radius from the grid point, whereas we assume the seismic parameters to be uniform for each tectonic seismic region.
+Application of VG approach in the seismic catalog is a novel approach.
+Recent studies have used both declustered (e.g., Telesca et al (2014b) and Telesca et al (2016)) and the whole catalog (Telesca and Lovallo (2012) and Telesca et al (2013)).
+Based on this comment and subsequent comment of the reviewer (and also the comments of second reviewers), we consider both whole and declustered catalog.
+We used Gardner and Knopoff (1974) method for declustering the catalog and reported the catalog size for original data (whole catalog), whole catalog after considering completeness magnitude and also declustered catalog in Table 1.
 }
@@
 \comment{2}{%
-Page 3, line 77: Fault-based/geologic-based earthquake recurrence estimates
+In order to check how well the declustering method worked for the analyzed datasets, would be useful to show the earthquakes in a plot of longitude versus time.
 }
@@
 \response{%
-Added, thanks.
+That is a good point.
+However, we think it gives an idea of distance based analysis of VG which is far from the scope of this article.
+We add the figure of original catalog before and after considering the completeness magnitude (whole and complete catalogs.)
 }
@@
 \comment{3}{%
-Page 4, line 106: Should this be northwest?
+I think would be interesting to check/discuss/compare the k-M slope and b-value relation for both the original and the declustered catalogs.
 }
@@
 \response{%
-Yes. Fixed.
+Thanks for the comment. We considered both catalogs and presented the results. Please see Fig. 7. 
 }
@@
 \comment{4}{%
-Page 6, line 168: It would be good to add a reference for the GEM effort.
+I would suggest to check the results for several magnitude thresholds above the completeness magnitude. Are the conclusions robust or do they depend on the chosen magnitude thresholds?
 }
@@
 \response{%
-We do not have a direct reference to GEM but added a citation to Zare et al (2014), where the connection to GEM is mentioned explicitly.
+The seismicity parameters change based on completeness magnitude.
+The parameters which come from the VG analysis also follow this pattern.
+According to this comment and comment \#3 of second reviewer we compute time dependent completeness test and choose a conservative completeness magnitude.
 }
@@
 \comment{5}{%
-Pages 7--8: Discussion about identifying the completeness level of the earthquake catalogs is a bit confusing.
-Typically, one either specifies a minimum magnitude of completeness ($M_c$) and then tries to identify the earliest time for which events or complete; or, one specifies a year and computes the corresponding $M_c$.
-In reading the text, it appears that both methods were used.
-Please clarify.
+Would it be possible to calculate a correlation coefficient for the $k-M$ slopes and the $b-values$ in Figure 9 (middle plot)?
 }
@@
 \response{%
-The new version of the Completeness sub-section now clarifies this point.
-The reviewer is right in that we used both methods, but we originally did not clearly explain the procedure.
-We first compute the $b$ and $M_{\max}$ values for each region, or the uniform model, using the HA3 package written by Dr.~Kijko.
-At this point, $M_c$ is used as an input to the HA3 software.
-We then used the Seiskit package written by Dr.~Frankel to compute the smoothed seismicity $a$-values.
-At this point, SeisKit uses the start year of completeness for each magnitude range.
-Please see changes in page 8, lines 211 and 229.
+We can add the numbers into figure 10. \\
+ (Dec catalog:\ \ \ \   $ k_m :  Az =  4.4\%  Al =  7.1 \%  Ko =  6.6\% -- b: Az = 6.1\%  Al = 3.3\% Ko=4.8\%$)\\
+ (Whole catalog: $ k_m :  Az =  9.4\%  Al =  7.4 \%  Ko =  6.2\% -- b: Az = 5.4\%  Al = 4.8\% Ko=5.5\%$)
 }
@@
 \comment{6}{%
-Pages 7--8: The authors should note that some authors use an alternative smoothing kernel $(~exp(-(D/2*sigma)^2)$.
-Comparison of the smoothing length between different studies may require consideration of a $sqrt(2)$ factor.
+The authors use 20 events (in a moving window) for estimating the b-values and k-M slopes in Figure 9.
+I think this is an extremely small number and I am concerned about the reliability of the b-value estimates.
+At least for the areas of higher seismicity the authors should also present graphs obtained using a larger number of events per moving window.
 }
@@
 \response{%
-We added a note to this effect in Section 4, and cite the work of Moschetti (2015) as an example.
-A complete analysis of the smoothing length and its influence on the hazard analysis, however, is out of the scope of the present study.
-The modifications done can be found in page 10, line 295.
+Thanks for the comment.
+We tried different window size from 20 to 100.
+As it is natural to expect, there are trade-offs between different window sizes.
+Smaller window sizes emphasize the local changes in the time series, but are less reliable when it comes to the seismicity parameters (e.g., b value).
+Larger window sizes, on the other hand, offer less insight into the time dependence of the window sequence characteristics.
+We chose a window size $n=50$, which is consistent with the suggested minimum number of events acceptable to estimate b according to  Woessner and Wiemer (2005).
+We modified the text accordingly.
 }
@@
 \comment{7}{%
-Page 7--8: In addition to the Mirzaei et al (1997) reference, some authors employ likelihood testing of smoothed seismicity rate models to identify optimal smoothing lengths for adaptive and fixed smoothed seismicity methods (e.g., Werner et al., 2011; Moschetti, 2015).
+The discussion of b-values in relation with larger earthquakes (page 10) in Figure 9 is unclear.
+From a quick visual inspection, I fail to see any distinct anomalies before larger (M > 5.0) events.
+I think that a lack of correlation should be also discussed in the manuscript, if true.
 }
@@
 \response{%
-We included a note to reflect this and added the references suggested by the reviewer. The changes can be seen in page 11, line 304.
-}
-
-\comment{7}{%
-Page 9: Kagan and Jackson (1994) should also be included in the reference list.
-}
-
-\response{%
-We added the suggested reference to the list provided in page 10, line 278.
-}
-
-\comment{8}{%
-Page 10, line 302: ``...subjective decisions and any reasonable choice...'' I would disagree that these are subjective decisions.
-My opinion is that you have applied scientific judgment.
-You clearly need to communicate where judgment is applied; however:
-\\[5pt]
-Details about the implementation of the two seismicity rate models (U, R) should be expanded.
-Are sub-catalogs developed for the five separate regions and then used to develop separate a-grids?
-Presumably, the separate rate files are then used to compute hazard curves and are summed at each location.
-\\[5pt]
-A logic tree would be of great benefit in clarifying how the source models are combined. In particular, it would clarify the weighting from different completeness levels.
-\\[5pt]
-Plots of seismicity rates from the R and U models would be of interest and particularly relevant given that the smoothed seismicity model is the main contribution of this work to hazard analyses for Iran.
-}
-
-\response{%
-The reviewer was right to suggest that our original approach to present a combination of the R and U models was not the best.
-In the revised manuscript we have addressed this in two basic manners.
-First, we now provide a better explanation of the rationale behind both models and the reasons to provide a combined result.
-Second, we adopted the suggestion of implementing a logic tree approach in our analysis.
-The adopted logic tree allows us to consider the epistemic uncertainty in the defintion of the seismic zones and also allowed us to include uncertainties in the seismic parameters $b$ and $M_{\max}$.
-For each branch of the logic tree we assigned weights following literature recommendations and our own judgement.
-In total, traversing and combining the different branches meant to conduct 162 runs ( $3 M_{\max} \times 3 b \times (5 \mbox{regions} + 1 \mbox{uniform}) \times 3 \mbox{GMPE}$) to get the combined results of the 2 basic models (R and U), three values of $b$ and $M_{\max}$ and three GMPE alternatives.
-The associated changes can be seen in various sections of the revised manuscript, and in particular in the new Section 7 and the Results Section 8.
-}
-
-\comment{9}{%
-Page 14, line 391: The incorporation of smaller earthquakes $(M<5)$ will have a significant influence on the hazard associated with PGA.
-Recent papers by Atkinson and others have demonstrated this effect.
-You may wish to argue that $M_{\min}$ was chosen based on the expected smallest magnitude capable of causing damage.
-}
-
-\response{%
-We revised the computations and now present results for events with $M_w > 4.5$. The text was modified accordingly (see page 4, line 94).
-}
-
-\comment{10}{%
-Figure 7: Is the magnitude-frequency distribution just a truncated ($M_{\min}$, $M_{\max}$) Gutenberg-Richter model? Figure 7 suggests that the MFD may be tapered?
-}
-
-\response{%
-Yes, it is truncated Gutenberg-Richter model. We now make this explicit in the caption of the figure.
-}
-
-\comment{11}{%
-Page 12, line 345: ``...controls the spatial extent to which the local occurrence of earthquakes...'' I would argue that the smoothed seismicity controls the local occurrence and spatial distribution of earthquakes and that the GMPEs control the intensity level at a particular site given earthquake locations and magnitudes from your source model.
-}
-
-\response{%
-That is correct. We have modified this sentence accordingly. Please se changes in page 13, line 365.
-}
-
-\comment{12}{%
-Page 13, line 361: Change ``approached'' to ``approach'' and ``lead'' to ``led.''
-}
-
-\response{%
-This part of the text was modified and the requested change may no longer apply, at least in regard to the first suggestion.
-Regarding the second suggestion, we do not quite agree.
-Although there was a typo, the way the sentence was structured, the corrected version uses ``leads'' instead.
-}
-
-\comment{13}{%
-The approach to generating Figure 10 should be clarified.
-It appears that the probabilistic ground motions from the R and U model are averaged and used to compute a standard deviation.
-The formal method for combining alternative models in PSHA is through the logic tree; this is equivalent to weighting the models in hazard (rate) space, rather than in ground motion (intensity, PGA) space.
-It appears that the authors have done the latter, though I may be incorrect.
-If this is the case, please correct.
-It is very reasonable to combine the R and U models to produce another alternative model.
-This work is not a comprehensive seismic hazard analysis, and presentation of probabilistic ground motions from the R, U and a weighted model would be reasonable goal.
-However, I would caution against comparing probabilistic ground motion maps with maps of seismicity because the varying $b$- and $M_{\max}$-values for the R model greatly complicate the comparison.
-As mentioned earlier, formal testing methods exist for ensuring consistency of observed earthquake locations with the smoothed seismicity models (see CSEP references, Zechar, Schorlemmer, Werner, Helmstetter, Jackson; Moschetti, 2015).
-Applying these methods is beyond the scope of this work, but might be recognized as a future direction.
-}
-
-\response{%
-Thanks for the informative comment.
-In the original figure 10 we combined the regional (R) and uniform (U) results (i.e., we combined the probabilities of exceedance, and then computed the PGA) with similar weights (i.e., 0.5).
-The positive and negative standard deviation plots came from GMPE + Uncertainty and GMPE -- Uncertainty.
-Our original intention was to show the range of variation for PGA around the median value.
-However, in the revised version of the manuscript this is no longer done.
-The new figure corresponding to the (R,U) combined model (Fig.~12) is now the result of the complete logic tree analysis, which is a more appropriate approach to presenting the results of our analysis.
+The correlation for 2012 Mw 6.4 Azerbaijan earthquake is clear to see.
+However, we agree with the reviewer that the drops of b-value is not consistent.
+Or we should say in the case of big earthquake there is always a drop in b and k-m value, however, there are some drops in the window analysis which is not aligned with big earthquake.
+We addressed the lack of correlation for the KopehDagh region.
+We also discussed that the lack of correlation could be the results of relatively high completeness magnitude.
+The text is modified accordingly.
 }
@@
 \introcomment{~}{%
-Review of Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity by Naeem Khoshnevis, Ricardo Taborda, Shima Azizzadeh-Roodpish, and Chris H. Cramer
-}
-
-\introcomment{~}{%
-In this paper, the researchers present a new seismic hazard analysis of northern Iran.
-The paper makes use of the latest available data and methods, is thorough in its review of previous work, and is very well presented and written.
-I have a few suggestions that I think would improve the impact of their results.
-The annotated version of the manuscript contains additional and more specific suggestions.
+The authors present an analytical method to estimate statistical properties of earthquake catalogs and they apply their method in Iranian catalog.
+Although I find some promise in the method I suggest that more analysis is required for the study to be comprehensive.
 }
@@
 \comment{1}{%
-The authors present uncertainty in their hazard estimate but do not include a more exhaustive logic tree analysis.
-Effectively, they have two branches: a regional model and uniform model.
-It appears that they apply the aleatory uncertainty in the ground motion prediction relation to a form of epistemic uncertainty, effectively double counting this uncertainty in the hazard analysis.
-I would prefer to see a more standard logic tree analysis where multiple GMPEs (or a backbone plus and minus one standard deviation) and uncertainty in $a$-value, $b$-value, and $M_{\max}$, for example, are considered.
-Barring this analysis, I would remove figure 10 and references to hazard uncertainty.
+1) Declustering the earthquake catalog, especially using parameters derived for California seismicity under modest monitoring conditions only brings additional uncertainty in the analysis.
+I am not sure why the authors believe that they should declutter the catalog.
+They could report if they find any time variability of b-value before/after aftershock sequences.
+i would suggest not going ahead with declustering.
 }
 
-\response{Thanks for the comment.
-Based on explanation of GMPEs section (please also see comment No.~27) we decided to address uncertainty with a backbone GMPE plus and minus one standard deviation.
-We also consider uncertainty in tectonic seismic regions through variations in the seismicity parameters $M_{\max}$, $b$, and combine the results using a standard logic tree analysis, as suggested.
-These changes are reflected at various points throughout the revised manuscript.}
+\response{%
+Thanks for the comment. We consider both catalogs.
+}
 
 \comment{2}{%
-While I think that the regional and uniform models are generally correct within 1.5 degrees of the border, I think that outside of this region, they may be moderately underestimating hazard by not considering sources with 200 km of their region of interest.
-Their buffer zone for sources is presently 50 km.
-}
-
-\response{That is right. We increased the buffer zone up to 2 degrees. See page 4, line 100.}
-
-\comment{3}{%
-It would be good if the abstract is more specific about the results. Where is the hazard greatest? What sources contribute to regions of higher hazard?
-}
-
-\response{We modified the abstract accordingly, but do not provide too much detail as that would significantly increase the length of the abstract, which is not desirable. See new lines 23--25.}
-
-\comment{4}{%
-In the second paragraph of the introduction, I would include a reference to a figure of the region to help readers less familiar with the area.
-This figure should also be referred to in subsequent paragraphs.
-It is probably sufficient to move reference to figure 1 here.
-}
-
-\response{We added a reference to figure 1 in page 2, line 40.}
-
-\comment{5}{%
-Line 39: eight $\to$ eighth
-}
-
-\response{Fixed.}
-
-\comment{6}{%
-Line 55: focuses in $\to$ focuses on
-}
-
-\response{Done. Thanks.}
-
-\comment{7}{%
-Line 56: Please be more specific about how your analysis differs from previous analyses.
-}
-
-\response{We modified the introduction to better explain the method and parameters.
-However, there are some details we still believe go better within the subsequent sections.
-Changes correspond to lines 54 to 76.}
-
-\comment{8}{%
-Line 60: Can you be more specific? What are the other indicators?
-}
-
-\response{In hindsight that was not the best choice of words. Since we modified this part of the introduction, the new text does no longer includes this sentence.}
-
-\comment{9}{%
-Line 71: Include reference.
-}
-
-\response{Done. Thanks.}
-
-\comment{10}{%
-Line 78: reduce $\to$ acknowledge
-}
-
-\response{Fixed.}
-
-\comment{11}{%
-Line 99: Is 0.5 degrees enough?
-To what distance do you do your ground motion calculations?
-In the western United States, they are done to 200 km.
-In the central and eastern, they are done to 1000 km.
-Depending on this value, you should include sources up to this distance from your region of interest.
-}
-
-\response{We reanalyze the hazard with 2 degrees buffer zone. This is reflected in the new Figures 1 and 3, and in the text (line 100) as well as, of course, in the results.}
-
-\comment{12}{%
-Line106: northeast $\to$ northwest
-}
-
-\response{Done. Thanks}
-
-\comment{13}{%
-Line 114: There is no previous mention of this earthquake. I am not sure to which earthquake you are referring. Should either the 1721 or 1780 earthquakes be the Shebli earthquake?
-}
-\response{Thanks for the comment. It is the 26 April 1721 $M_s$ 7.7 earthquake. The change is now in page 4, line 114.}
-
-\comment{14}{%
-Line 180: The smaller events should also help to inform the G-R relationship.
-}
-
-\response{Thanks for the comment. Added to the text in line 182.}
-
-\comment{15}{%
-Line 182: How come this study doesn't appear in Table 3. Do they not calculate PGA for 2 and 10\% exceedance in 50 years?
-}
-
-\response{They did not provide a numerical value, or numbers on the contour lines. However, we read the images with Matlab and located the values and now include them in the new version of Table 3.}
-
-\comment{16}{%
-Line 192: What is the total number of events before and after declustering?
-}
-
-\response{Number of events before decluttering: 10,441; total foreshocks: 971; total aftershocks: 4,206; declustered data: 5,254.
-It should be noted that these numbers are representing the events in the complete study region (including the buffer zone).
-It partly includes events from Central and Zagros region.
-For the completeness, we studied the whole data for each region.
-This is now explained in page 7, line 195.}
-
-\comment{17}{%
-Line 224: Why did you use this method? What are the benefits of one or the other?
-}
-
-\response{Both methods have been used extensively in previous studies.
-We just picked one, mainly so due to ease of implementation, which also allowed us to have complete control over the final selection.
-The text was incorrectly implying that the goodness-of-fit rest method had benefits over the MAXC method.
-We fixed this and now state our reasons in a more transparent way.
-See page 8, line 229.}
-
-\comment{18}{%
-Line 232: It is unclear how you chose $M_c$. In some cases, it looks like you chose the peak goodness-of-fit value, but in others you did not. Please be more specific about how Mc was chosen.
-}
-
-\response{According to Wiemer and Wyss (2000), the priority is picking the magnitude which has the peak goodness-of-fit value.
-However, in some cases for two or a couple of magnitudes the goodness-of-fit scores are not considerably different.
-In these cases, we pick the minimum magnitude, even though it does not have the peak goodness-of-fit value, in order to preserve more data.
-We also consider the decay of the cumulative number of events.
-This is now explained in the revised manuscript in pages 8 and 9.}
-
-\comment{19}{%
-Line 267: add 'and'
-}
-\response{Added. Thanks.}
-
-\comment{20}{%
-Line 289: You might also cite the 2014 USGS National Model (Petersen et al., 2014) and the Afghanistan seismic hazard maps (Boyd et al, 2007), which include spatial variability in the smoothing parameter.
-}
-
-\response{We included the suggested reference, though the actual publication year is 2015.}
-
-\comment{21}{%
-Line 297: provided below $\to$ provided in the next section.
-}
-
-\response{Fixed.}
-
-\comment{22}{%
-Line 300: allows to draw information $\to$ allows one to draw information
-}
-
-\response{Done.}
-
-\comment{23}{%
-Line 323: Be more specific about how HA3 computes $b$ and $M_{\max}$. What is its method?
-}
-
-\response{This code uses the procedure described in Kijko and Sellevoll (1989). We added a sentence making this explicit in page 12, line 341.}
-
-\comment{24}{%
-Line 335: Different seismic zone will not necessarily have difference values of $b$ and $M_{\max}$. Change to this: Different seismic zone may have different values of $b$ and $M_{\max}$.
-}
-
-\response{Modified. Thanks. See line 354.}
-
-\comment{25}{%
-Line 337: a means to reduce epistemic $\to$ a means to account for epistemic
-}
-
-\response{Done.}
-
-\comment{26}{%
-Line 361: lead $\to$ leads
-}
-
-\response{Fixed. Thanks.}
-
-\comment{27}{%
-Line 364: How do you address the epistemic uncertainty generally introduced by using a suite of GMPEs?
-}
-
-\response{This is a point that was also raised by Reviewer 1.
-As mentioned in Atkinson and Adam (2013) and Atkinson et al (2014), using different GMPEs with different logic tree weights from different literature is not necessarily the best way to model the epistemic uncertainty in GMPEs.
-Especially when the mean of various GMPEs are too close to each other.
-We prefer to use the alternative GMPEs and applicable data to guide the choice of a representative or central GMPE, and to define representative upper and lower GMPEs using the standard deviation of the chosen relationship.
-In order to address these concerns we now use the logic tree scheme shown in Fig.~9 and make comments with respect to this in various points throughout the revised version of the manuscript, but in particular in pages 13 and 14, lines 380--397.}
-
-\comment{28}{%
-Line 365: add 'and'
-}
-
-\response{Added. Thanks.}
-
-\comment{29}{%
-Line 370: Could you consider other depths to help fill out your range of epistemic uncertainty?
-}
-
-\response{Not really.
-At least we think it would not be appropriate to do so.
-The Kalkan and Gulkan (2004) attenuation relationship was originally generated for Turkey.
-Later, Zafarani and Mousavi (2014) found that this GMPE yielded acceptable results for PGA for northern Iran if calibrated with the values we report in the manuscript.
-Since the high accuracy achieved by using this GMPE depends on the the current choice of depth, we ignore what would be the effect of considering the variability of $h$, and suspect it will likely be to the detriment of the analysis.
-We make tangential mention to this in the new Section 7.
-See page 15, line 424.}
-
-\comment{30}{%
-Line 371: How does this value compare with the models you decided not to use?
-}
-
-\response{In the revised version we use a backbone GMPE, in addition to GMPEs derived using plus and minus one standard deviation. Therefore, this comment does no longer apply.}
-
-\comment{31}{%
-Line 376: In this case, you should consider all sources with 200 km of your area of interest.
-}
-\response{We modified the buffer zone and now do this. Thanks.}
-
-\comment{32}{%
-Line 394: 50-years $\to$ 50-year
-}
-\response{Done.}
-
-\comment{33}{%
-Line 420: with concentration $\to$ with a concentration
-}
-
-\response{Added. Thanks.}
-
-\comment{34}{%
-Line 422: I would have stated this differently.
-It looks like the lower $b$-value in Kopeh Dagh yields relatively high hazard in the R model whereas in the U model, this low b-value has leaked into the entire region and subsequently elevated seismic hazard in all areas outside of Kopeh Dagh.
-}
-
-\response{Based on the modification in GMPEs and uncertainties, we rewrote this description.}
-
-\comment{35}{%
-Line 428: Why equal weights?
-}
-
-\response{We added a comprehensive logic tree analysis and modified the weights. Please see figure 9, and the description given in the new Section 7.}
-
-\comment{36}{%
-Line 431: I'm not sure I quite understand this.
-The standard deviation in the attenuation relation is considered aleatory uncertainty and is present within the hazard curve.
-Adding it as epistemic as well will cause double counting.
-If you want to include figure 10, a proper logic tree analysis to include more forms of epistemic uncertainty should be performed.
-For example, add branches for uncertainty in which GMPE you choose, uncertainty in $b$-value, uncertainty in $M_{\max}$, uncertainty in $a$-value, uncertainty in smoothing parameter, etc.
-}
-
-\response{We modified the approach and now consider the uncertainties explicitly via a logic tree analysis. Therefore, we believe this no longer applies as the new approach is more appropriate.}
-
-\comment{37}{%
-Line 434: Just because the basic pattern appears to better follow faults in the region does not mean it's a better assessment, especially if the $b$-values are truly different between regions and better represented by the regional analysis.
-}
-
-\response{Agree. We believe, however, that this can be interpreted as a good indication of how the data is being captured by the analysis. We modified this.}
-
-\comment{38}{%
-Line 439: of city of Tabriz $\to$ of the city of Tabriz.
-}
-
-\response{Fixed. Thanks.}
-
-\comment{39}{%
-Line 450: for 2 and 10\%, respectively $\to$ for 2 and 10\% in 50 years, respectively.
-}
-
-\response{Done.}
-
-\comment{40}{%
-Line 453: for a 10\% probability of exceedance $\to$ for a 10\% probability of exceedance in 50 years.
-}
-
-\response{Done.}
-
-\comment{41}{%
-Line 455: 0.27--0.31 g for 10\% probability of exceedance $\to$ 0.27-0.31 g for the same exceedance probability
-}
-
-\response{Done.}
-
-\comment{42}{%
-Line 458: for 2 and 10\% $\to$ for 2 and 10\% in 50 years
-}
-
-\response{Done.}
-
-\comment{43}{%
-Line 461: our results are close or within $\to$ our results are close to or within
-}
-
-\response{Done.}
-
-\comment{44}{%
-Line 462: Can you explain the differences in their analysis relative to yours that lead to higher values?
-}
-
-\response{They used Maximum Credible Earthquake as $M_{\max}$.
-The maximum credible earthquake is largest earthquake that appears capable of occurring under the known tectonic framework for a specific fault or seismic source, as based on geologic and seismologic data, so it is higher than observation or data driven $M_{\max}$.
-We added the explanation to the text (see page 18, line 511).}
-
-\comment{45}{%
-Line 466: exceedance as functions of PGA $\to$ exceedance as functions of PGA, also known as hazard curves}
-
-\response{Done.}
-
-\comment{46}{%
-Line 475: Can you explain the differences in the hazard analysis that led to differences in hazard?}
-
-\response{We modified this paragraph and included a better description of the differences and results. See pages 18 and 19, lines 524--549.}
-
-\comment{47}{%
-Line 488: Not sure you can say this because you don't include fault specific sources, and you do not consider a more full range of epistemic uncertainty, e.g.
-you only use one GMPE (though you do consider two $b$-value and $M_{\max}$ based models).
-}
-
-\response{That is right. We restate the sentence and modified the conclusions accordingly.}
-
-\comment{48}{%
-Line 488: hazard analysis $\to$ hazard analyses
-}
-
-\response{Done.}
-
-\comment{49}{%
-Line 490: models as a mean $\to$ models as a means}
-
-\response{Done.}
-
-\comment{50}{%
-Line 493: Though you suggest the uniform model is unrealistic on line 334.
-}
-
-\response{Our choice of words was not the best. We meant to say less realistic. We fixed the text accordingly.}
-
-\comment{51}{%
-Line 502: for providing advise $\to$ for providing advice}
-\response{Done.}
-
-\comment{52}{%
-Line 509: Should this be Sunset?
-}
-
-\response{Yes. Thank you.}
-
-\comment{53}{%
-Page 25, Table 2: What did you do for the earthquakes occurring outside of these five zones?
+ Uncertainty analysis for standard b-value estimation for sample population, magnitude correction
 }
@@
 \response{
-As it can be seen in Figure 1, earthquakes outside the regions would be too far to be included.
-There are earthquakes above the Caspian see, for instance, and others in the country of Azerbaijan which were ignored because they were beyond the buffer zone (which as it was mentioned before, was expanded).}
-
-\comment{54}{%
-Page 26, Table 3: Specify units.}
-
-\response{Done. Thanks.}
-
-\comment{55}{%
-Page 32, Figure 3: You should also show events in the buffer zone used to compute hazard.}
-
-\response{Done.}
-
-\comment{56}{%
-Page 34, Figure 5: Which seismic zone corresponds to which color?
-It looks like either reporting or rates have changed over time.
-For example, I might argue that the red region was not complete for M3 and above until 2005.
+Thanks. We conduct the uncertainty analysis according to Shi and Bolt 1982. Please see equation 3 and Table 1. 
 }
 
-\response{%
-Thanks for the comment.
-The problem with that region is having less than and equal sign on magnitude 4.
-There are many earthquakes go to that category because of that condition.
-Since converting earthquake magnitude always has an error margin, we think the comment is relevant.
-Based on the data we assume 2005 as a completeness magnitude.
-We presented the legends at the bottom of the figure.
+\comment{3}{%
+I find that Mc (magnitude of completeness) determination, should be done in a time-dependent manner since from the Fig. 5 it is obvious that monitoring conditions change.
 }
 
-\comment{57}{%
-Page 37: 10 percent of probability $\to$ 10 percent probability
+\response{
+That is right. We conduct a time dependent Mc estimation through Maximum Curvature method implemented in ZMAP software. Please see Fig. 4.  The results modified accordingly. 
 }
 
-\response{Done.}
-
-\comment{58}{%
-Page 39, Figure 11: Include horizontal lines indicating 2 and 10\% probability of exceedance in 50 years.
+\comment{4}{%
+How the Authors account for Bam earthquake in 2003 that has aftershock in the early part of their catalog?
 }
 
-\response{Included.}
-
-\comment{59}{%
-Page 41, Figure 12: Can you include curves or points for the other studies in Table 3?
+\response{
+Our catalog starts from 2005.
+We agree the fact that  the earthquake could affect the seismicity pattern several consequent years, however, the spatial distance of the epicenter from the study region is fairly large ($d > 400 miles$).
+Therefore, we believe $2003 Mw 6.6$ Bam earthquake's aftershocks is not included in the current study regions' catalog.
 }
 
-\response{We did and made comments about this in the Results section.}
-
 \end{document}

### 2017-06-22 methodology.tex

@@
 In graphs, the data---sometimes also referred to as the payload---resides at the vertices or nodes who are connected through links or edges, which may or may not have an associated direction.
-A visibility graph is a special type of undirected graphs in which the links are straight lines connecting intervisible nodes; that is, straight lines that do not go across any obstacle while connecting nodes that can see each other in a physical space \citep{LozanoPerez_1979_CACM}.
+A visibility graph is a special type of graphs in which the links are straight lines connecting intervisible nodes; that is, straight lines that do not go across any obstacle while connecting nodes that can see each other in a physical space \citep{LozanoPerez_1979_CACM}.
 Visibility graphs have been mostly used in robotics for navigation path planning \citep[e.g.,][]{Huang_2004_Proc, Oommen_1987_JRA} but have also seen applications in other fields including urban studies, interior architecture, medicine, and geosciences \citep[e.g.,][]{Raman_2010_UE, Ahmadlou_2010_JNT, Varoudis_2014_JSS, Phillips_2015_ESR}.

### 2017-06-22 results.tex

@@
 (We do not include a visualization of the graphs because the links are so many, that it is only practical to visualize the graphs of short sequences.) We collect information about the number of inter-visibility links associated with each event (connectivity degree, $k$) and categorize the events in magnitude bins of size $\Delta M_{\mathrm{bin}} = 0.1$, as mentioned in the Methodology section.
-Figure \ref{fig:km} shows the scattered distribution of events in the magnitude-connectivity degree plane for each subregion\myrevision{, corresponding to the complete catalogs.} The figure shows that, in general, the value of $k$ increases with $M_w$\myrevision{; and includes the results of obtaining linear $k$-$M$ regressions for each dataset along with the values of the slope $m$ for the three seismic zones, namely 10.0, 9.85, and 8.70 for the Azerbaijan, Alborz, and Kopeh Dagh regions.
+Figure \ref{fig:km} shows the scattered distribution of events in the magnitude-connectivity degree plane for each subregion\myrevision{, corresponding to the complete catalogs.} The figure shows that, in general, the value of $k$ increases with $M_w$\myrevision{; and includes the results of obtaining linear $k$-$M$ regressions for each dataset along with the values of the slope $m$ for the three seismic zones, namely 10.05, 9.85, and 8.71 for the Azerbaijan, Alborz, and Kopeh Dagh regions.
 Similar results regressions were obtained for the declustered catalogs, which yielded $m$ values of 8.92, 8.97, and 7.96, respectively.}
@@
 Next, we examine the relationship between the $b$ values from Table \ref{tab:seismicity} and the $k$-$M$ slopes.
-\myrevision{Figures \ref{fig:regression}a and \ref{fig:regression}a show the scattered results of the $m$ versus $b$ for the complete and declustered catalogs, respectively.
+\myrevision{Figures \ref{fig:regression}a and \ref{fig:regression}b show the scattered results of the $m$ versus $b$ for the complete and declustered catalogs, respectively.
 Along with the data-points obtained for our analysis of the three seismic regions of northern Iran, in each plot, we also include the data points corresponding to the magnitude-time sequences of the Mexican subduction zone provided by \citet{Telesca2013}, the Pannoninan seismic zone from \citet{Telesca2014}, the experimental results obtained by \citet{Telesca2014-pone}, and the result from a similar preliminary analysis done by \citet{Azizzadeh_2017_SSA} for California.
@@
 The number of events in each subsequence, $n$, was varied randomly but chosen to be large enough to represent the seismic characteristics of each region.
-In particular, the minimum size of each subsequence was set to be $n \geq 200$, and the maximum size in the sequence was set to be as large as the original \myrevision{whole} catalog (see Table \ref{tab:seismicity}).
+In particular, the minimum size of each subsequence was set to be \myrevision{$n \geq 200$}, and the maximum size in the sequence was set to be as large as the original \myrevision{whole} catalog (see Table \ref{tab:seismicity}).
 We forced the random subsequences to progress positively in time without altering the natural occurrence of events.
@@
 	\includegraphics[width=\textwidth]{figures/pdf/figure-08} 
-	\caption{\myrevision{Correlation between the $k$-$M$ slope ($m$) and $b$ values for 200 random sequences extracted from the complete (a) and declustered (d) catalogs of the three northern Iranian seismic regions considered in this study (scattered symbols), including the mean values (empty symbols with thick border) and the data points obtained from the regional analyses (solid symbols), along with the linear regressions of each sample as indicated in the legend; and mean $\pm1$ standard deviation bar plots for $m$ (b,e) and $b$ (c,f) for the complete and declustered catalogs, respectively.
+	\caption{\myrevision{Correlation between the $k$-$M$ slope ($m$) and $b$ values for the random subsequences extracted from the catalogs of the three northern Iranian seismic regions considered in this study (scattered symbols, 200 each region, 600 total) for both the complete (a) and declustered (d) catalogs, including the mean values (empty symbols with thick border) and the data points obtained from the regional analyses (solid symbols), along with the linear regressions of each sample as indicated in the legend; and mean $\pm1$ standard deviation bar plots for $m$ (b,e) and $b$ (c,f) for the complete and declustered catalogs, respectively.
 In the latter, the values in the parentheses corresponds to the coefficients of variation.}}
@@
 
-\begin{figure*}[t]
+\begin{figure*}%[t]
 	\centering
 	\includegraphics[width=\textwidth]{figures/pdf/figure-09} 
-	\caption{\myrevision{Variation of $<$$T_c$$>$, $k$-$M$ slope ($m$) and the $b$ value with respect to time for the seismic zone of Alborz for a moving window analysis of the visibility graphs of subsequences of $n=50$ consecutive events, along with the magnitude and the connectivity degree ($k$) of events in the 2016 period.
+	\caption{\myrevision{Variation of $<$$T_c$$>$, $k$-$M$ slope ($m$) and the $b$ value with respect to time for the seismic zone of Alborz for a moving window analysis of the visibility graphs of subsequences of $n=50$ consecutive events, along with the magnitude and the connectivity degree ($k$) of events in the 2005--2016 period.
 Black triangles indicate the occurrence of significant earthquakes in each of the regions, with the corresponding magnitude at the top of each symbol.}}
@@
 We can see here how larger values of $k$ are associated with the larger magnitude earthquakes, and how the resulting values of $m$ for each 50-event sequence compares with $b$.
-In particular, we observe a good correlation between $m$ and $b$ fore the period prior to the 2010 $M_w$ 5.8 Damaghan earthquake, but after this event the correlation is not as clear.
-Unfortunately, contrary to the suggestions of \citet{Telesca2016}, we do not observe any clear correlation between the behavior of $<$$T_c$$>$ and the occurrence of the larger magnitude ($M_w \geq 5$) earthquakes in this region.
-Similarly, while the occurrence of larger events does seem to coincide with drops in $m$ and $b$, there are other similar changes in the values of $m$ and $b$ that are not associated with any significant event, making it difficult to draw strong conclusions.
-Nonetheless, in the region of Azerbaijan, we did observe more prominent changes in $m$ and $b$ with the occurrence of the 2012 $M_w$ 6.4 Tabriz earthquake, which leaves open the possibility of further study for regions with larger magnitude events.}
+In particular, we observe a good correlation between $m$ and $b$ for the period prior to the 2010 $M_w$ 5.8 Damaghan earthquake, but after this event the correlation is not as clear.
+We do not observe any clear correlation between the behavior of $<$$T_c$$>$ and the occurrence of the larger magnitude ($M_w \geq 5$) earthquakes in this region.
+Furthermore, while the occurrence of larger events does seem to coincide with drops in $m$ and $b$, there are other similar changes in the values of $m$ and $b$ that are not associated with any significant event, making it difficult to draw strong conclusions.
+Nonetheless, in the region of Azerbaijan, we did observe more prominent changes in $m$ and $b$ with the occurrence of the 2012 $M_w$ 6.4 Tabriz earthquake, which leaves open the possibility to further study this for regions with larger magnitude events.}
 

### 2017-06-22 results.tex
general fixes

@@
 	\includegraphics[width=\textwidth]{figures/pdf/figure-09} 
-	\caption{\myrevision{Variation of $<$$T_c$$>$, $k$-$M$ slope ($m$) and the $b$ value with respect to time for the seismic zone of Alborz for a moving window analysis of the visibility graphs of subsequences of $n=50$ consecutive events, along with the magnitude and the connectivity degree ($k$) of events in the 2005--2016 period.
+	\caption{\myrevision{Variation of $<$$T_c$$>$, $k$-$M$ slope ($m$) and the $b$ value with respect to time for the seismic regions of Azerbaijan (a) and Alborz (b) considering a moving window analysis of the visibility graphs of subsequences of $n=50$ consecutive events, along with the magnitude and the connectivity degree ($k$) of events in the 2005--2016 period.
 Black triangles indicate the occurrence of significant earthquakes in each of the regions, with the corresponding magnitude at the top of each symbol.}}
@@
 \myrevision{In this windowing analysis, in addition to $b$ and $m$, we are interested in computing the value of $<$$T_c$$>$ explained in the Methodology section.
-Figure \ref{fig:tc} shows the earthquake sequence for the region of Alborz, and the variation of $k$, $m$, $b$, and $<$$T_c$$>$ with time.
-Although we performed the analysis for all three seismic zones, we concentrate in the region of Alborz because is the one with the larger number of events for the fixed-size moving window.
-We can see here how larger values of $k$ are associated with the larger magnitude earthquakes, and how the resulting values of $m$ for each 50-event sequence compares with $b$.
-In particular, we observe a good correlation between $m$ and $b$ for the period prior to the 2010 $M_w$ 5.8 Damaghan earthquake, but after this event the correlation is not as clear.
-We do not observe any clear correlation between the behavior of $<$$T_c$$>$ and the occurrence of the larger magnitude ($M_w \geq 5$) earthquakes in this region.
-Furthermore, while the occurrence of larger events does seem to coincide with drops in $m$ and $b$, there are other similar changes in the values of $m$ and $b$ that are not associated with any significant event, making it difficult to draw strong conclusions.
-Nonetheless, in the region of Azerbaijan, we did observe more prominent changes in $m$ and $b$ with the occurrence of the 2012 $M_w$ 6.4 Tabriz earthquake, which leaves open the possibility to further study this for regions with larger magnitude events.}
+Figure \ref{fig:tc} shows the earthquake sequence for the regions of Azerbaijan and Alborz, and the variation of $k$, $m$, $b$, and $<$$T_c$$>$ with time.
+Although we performed the analysis for all three seismic zones, we concentrate in this two regions because the windowed sequence of Kopeh Dagh was too short and did not add value to the discussion.
+In the two cases in Fig.~\ref{fig:tc} we can see here how larger values of $k$ are associated with the larger magnitude earthquakes, and how the resulting values of $m$ for each 50-event sequence compares with $b$.
+For the case of Alborz, we observe a good correlation between $m$ and $b$ for the period prior to the 2010 $M_w$ 5.8 Damaghan earthquake, but after this event the correlation is not as clear.
+For Azerbaijan, the relationship between $m$ and $b$ is less evident, except for the timespan around the occurrence of the 2012 $M_w$ 6.4 Tabriz earthquake, in which case both all three parameters ($b$, $m$ and $<$$T_c$$>$) show a clear drop in their values.
+By contrast, in the case of Alborz, we do not observe any clear correlation between the behavior of $<$$T_c$$>$ and the occurrence of the largest ($M_w \geq 5$) earthquakes in this region.
+We notice that while the occurrence of the larger events does seem to coincide with drops in $m$ and $b$, there are other similar changes in the values of $m$ and $b$ that are not associated with any significant event, making it difficult to draw strong conclusions solely based on the results for the region of Azerbaijan and the 2012 Tabriz earthquake.
+It is possible, however, that regions with larger events or catalogs with lower $M_c$ lead to better insight on this matter.}
 
@@
 	\includegraphics[width=\textwidth]{figures/pdf/figure-10} 
-	\caption{\myrevision{Correlation between $m$ and $b$ based on the fixed-size windowing analysis done for the region of Alborz, for both the complete (a) and declustered (b) catalogs, along with the linear regressions of each case.
-While a direct comparison is not appropriate, the universal regression is shown as well for reference.}}
-	\label{fig:alborz-bm}
+	\caption{\myrevision{Correlation between $m$ and $b$ based on the fixed-size windowing analysis done for the regions of Azerbaijan (a) and Alborz (b), along with the linear regressions of each case.
+While a direct comparison is not appropriate, the universal regression is shown here for reference.}}
+	\label{fig:azal-bm}
 \end{figure*}
 
-\myrevision{Finally, we explore the correlation between $k$ and $b$ by aggregating the results of the windowing analysis.
-Figure \ref{fig:alborz-bm}a shows condensed (scattered) results for all the values $k$ and $b$ from Fig.~\ref{fig:tc} for the complete catalog of Alborz, and Fig.~\ref{fig:alborz-bm}b shows the same results but for the declustered catalog.
-Both plots exhibit reasonable linear regressions for an ample range of $m$ and $b$ values.
-While it is not entirely fair to compare these results (which are exclusive to the Alborz region) with the universal results discussed before, Fig.~\ref{fig:alborz-bm} also includes the universal correlations for reference.
-The results for Alborz also show $b$ to increase proportionally with $m$, although at a smaller rate.}
+\myrevision{The better correlation observed between $m$ and $b$ for Alborz than for Azerbaijan is further explored in Fig.~\ref{fig:azal-bm}, which presents the condensed (scattered data-point) results for all the values $k$ and $b$ from Fig.~\ref{fig:tc}.
+The plots in this figure confirm that the values of $m$ and $b$ correlate better for Alborz.
+Also included in Fig.~\ref{fig:azal-bm}, for reference, is the universal regression.
+While a direct comparison with the local regressions is not appropriate, the closer proximity of the Alborz trend line to the universal regression line suggests that the larger number of data points improves the quality of the regression, bringing it closer to the universal correlation line.
+The results for Kopeh Daght, not included here for brevity, show the poorest correlation, likely due to the least amount of data points, which reinforces the point made about the quality of the regression being dependent on a sufficiently large number of data points.}
 

### 2017-06-22 response.tex
modified response to reviewers

@@
 \introcomment{~}{%
-This is an interesting paper that applies a relatively new technique to the seismicity data in Northern Iran.
+This is an interesting paper that applies a relatively new technique to the seismicity data in northern Iran.
 The manuscript is well-written and would be a worthy contribution to the Pageoph journal.
@@
 \response{%
-Application of VG approach in the seismic catalog is a novel approach.
-Recent studies have used both declustered (e.g., Telesca et al (2014b) and Telesca et al (2016)) and the whole catalog (Telesca and Lovallo (2012) and Telesca et al (2013)).
-Based on this comment and subsequent comment of the reviewer (and also the comments of second reviewers), we consider both whole and declustered catalog.
-We used Gardner and Knopoff (1974) method for declustering the catalog and reported the catalog size for original data (whole catalog), whole catalog after considering completeness magnitude and also declustered catalog in Table 1.
+We initially declustered the catalog out of personal choice.
+Other recent studies using the visibility graph method have used complete and declustered catalogs indistinctively, and with the method being only recently applied in seismology, there is still no clear consensus on what is the appropriate approach when it comes to the treatment of the catalog to be used.
+Telesca et al.~(2014b) and Telesca et al.~(2016), for instance, used declustered catalogs, whereas Telesca and Lovallo (2012) and Telesca et al.~(2013) used complete catalogs.
+In the revised version include results for both cases, although we tend to focus on the complete catalog.
+It seems the rsults are not particularly sensitive to the presence or basence of foreshocks and aftershocks.
+Instead, as we discuss now in the revised version and in response to other questions by the reviewers, it seems the visibility graph results are more sensitive to the completeness itself (i.e., to $M_c$) and the number of events.
+In the revised version of Table 1 we now include the number of events in each type of catalog.
+We also improved the language in the text to make it very clear when we refer to either the whole, complete, or declustered catalogs.
+The methodology used for declustering is that of Gardner and Knopoff (1974).
+In the revised version we make a note to make it clear that we recognize that this method was calibrated for a different region (California), but we believe the results are still acceptable.
 }
@@
 \response{%
-That is a good point.
-However, we think it gives an idea of distance based analysis of VG which is far from the scope of this article.
-We add the figure of original catalog before and after considering the completeness magnitude (whole and complete catalogs.)
+Given the changes made to the paper, and most of the figures now focusing on the complete catalog (with only contrasting references with respect to declustered catalog results), we believe this is not entirely necesary.
+Besides, it is out of the scope of the paper to determine the effectiveness of the declustering method or its appropriateness for northern Iran.
+We prefer to focus on the sensibility of the results obtained with the visibility graph method to the general uncertainties in data manipulation, and for that objective, the declustering applied serves the purpose sought.
+Nonetheless, we modified Figure 1 to include both the whole and complete catalogs, to show the contrast after evaluating completeness, and include the number of events for the whole, complete, and declustered catalogs in Table 1.
+We feel that additional figures with the declustered catalog event locations would not necessarily add value to the discussion about the visibility graph method.
 }
@@
 \response{%
-Thanks for the comment. We considered both catalogs and presented the results. Please see Fig. 7. 
+Thank you for suggesting this.
+The new version of the manuscrip now considers comparisons between results obtained for the complete and declustered catalogs.
+In particular, we show the differences in the results of the analyses of the different catalogs in Figures 7 and 8.
+In addition, in several places in the manuscript, we now make mention to results obtained for the declustered catalogs in contrast to the complete catalogs.
+Due to space limitations we do not include all results in all figures, but we did make an effort to coment on this when appropriate.
+In general, we found that the differences introduced by declustering were more due to the reduced number of events than to anything else.
+Same happens with changes in the value of $M_c$.
 }
@@
 \response{%
-The seismicity parameters change based on completeness magnitude.
-The parameters which come from the VG analysis also follow this pattern.
-According to this comment and comment \#3 of second reviewer we compute time dependent completeness test and choose a conservative completeness magnitude.
+We did some of these tests off-line and included comments about it in the manuscript.
+In general, we observed that the parameters extracted from the graph and its relationship with $b$ can be affected by changes in the completeness magnitude threshold, but because the seismicity parameters also change based on completeness magnitude, the net effect on the universal relationship between $m$ and $b$ do not seem to be significant.
+In general, upon reviewing the manner in which we compute $M_c$ as suggested by Reviewer \#2, we found the more relevant effect to be in the number of events, which seem to influence the quality of the relationship between $m$ and $b$.
+We now make comments about these changes and their effect in the revised manuscript in the Results and Conclusions sections.
+The changes to the method used to compute $M_c$ are decribed in the Methodlogy section, and in the answer to Comment \#3 from Reviewer \#2.
 }
@@
 \response{%
-We can add the numbers into figure 10. \\
- (Dec catalog:\ \ \ \   $ k_m :  Az =  4.4\%  Al =  7.1 \%  Ko =  6.6\% -- b: Az = 6.1\%  Al = 3.3\% Ko=4.8\%$)\\
- (Whole catalog: $ k_m :  Az =  9.4\%  Al =  7.4 \%  Ko =  6.2\% -- b: Az = 5.4\%  Al = 4.8\% Ko=5.5\%$)
+Rather than including these numbers, we include a new figure (Fig.~10) in which we show regresions between $b$ and $m$ for the condensed data-points from Figure 9.
+We thought this was a better way of showing the correlation between $b$ and $m$.
+The Results section now includes a paragraph with comments on this new figure.
+% We can add the numbers into figure 10. \\
+%  (Dec catalog:\ \ \ \   $ k_m :  Az =  4.4\%  Al =  7.1 \%  Ko =  6.6\% -- b: Az = 6.1\%  Al = 3.3\% Ko=4.8\%$)\\
+%  (Whole catalog: $ k_m :  Az =  9.4\%  Al =  7.4 \%  Ko =  6.2\% -- b: Az = 5.4\%  Al = 4.8\% Ko=5.5\%$)
 }
@@
 \comment{6}{%
-The authors use 20 events (in a moving window) for estimating the b-values and k-M slopes in Figure 9.
-I think this is an extremely small number and I am concerned about the reliability of the b-value estimates.
+The authors use 20 events (in a moving window) for estimating the $b$-values and $k$-$M$ slopes in Figure 9.
+I think this is an extremely small number and I am concerned about the reliability of the $b$-value estimates.
 At least for the areas of higher seismicity the authors should also present graphs obtained using a larger number of events per moving window.
@@
 Thanks for the comment.
-We tried different window size from 20 to 100.
+We tried different window sizes from 20 to 100 events.
 As it is natural to expect, there are trade-offs between different window sizes.
-Smaller window sizes emphasize the local changes in the time series, but are less reliable when it comes to the seismicity parameters (e.g., b value).
+Smaller window sizes emphasize the local changes in the time series, but are less reliable when it comes to the seismicity parameters (e.g., $b$ value).
 Larger window sizes, on the other hand, offer less insight into the time dependence of the window sequence characteristics.
-We chose a window size $n=50$, which is consistent with the suggested minimum number of events acceptable to estimate b according to  Woessner and Wiemer (2005).
+In the end, we chose a window size $n=50$, which is consistent with the suggested minimum number of events acceptable to estimate $b$ according to Woessner and Wiemer (2005).
 We modified the text accordingly.
@@
 \comment{7}{%
-The discussion of b-values in relation with larger earthquakes (page 10) in Figure 9 is unclear.
-From a quick visual inspection, I fail to see any distinct anomalies before larger (M > 5.0) events.
+The discussion of $b$-values in relation with larger earthquakes (page 10) in Figure 9 is unclear.
+From a quick visual inspection, I fail to see any distinct anomalies before larger ($M > 5.0$) events.
 I think that a lack of correlation should be also discussed in the manuscript, if true.
@@
 The correlation for 2012 Mw 6.4 Azerbaijan earthquake is clear to see.
-However, we agree with the reviewer that the drops of b-value is not consistent.
-Or we should say in the case of big earthquake there is always a drop in b and k-m value, however, there are some drops in the window analysis which is not aligned with big earthquake.
-We addressed the lack of correlation for the KopehDagh region.
-We also discussed that the lack of correlation could be the results of relatively high completeness magnitude.
-The text is modified accordingly.
+However, we agree with the reviewer that the drops in $b$ and $m$ are not consistent.
+We now make a more transparent assessment of the results and comment on this in the revised Results and Conclusions sections.
+There, we address the lack of correlation for the some of the events in the Alborz and Kopeh Dagh regions.
+Based on the experience we gaing through working with the method, we suggest that the lack of correlation may be the results of relatively high completeness magnitude values, or lack of distinctive large magnitide ($M>6$) events.
+The text was modified accordingly.
 }
@@
 \comment{1}{%
-1) Declustering the earthquake catalog, especially using parameters derived for California seismicity under modest monitoring conditions only brings additional uncertainty in the analysis.
+Declustering the earthquake catalog, especially using parameters derived for California seismicity under modest monitoring conditions only brings additional uncertainty in the analysis.
 I am not sure why the authors believe that they should declutter the catalog.
 They could report if they find any time variability of b-value before/after aftershock sequences.
-i would suggest not going ahead with declustering.
+I would suggest not going ahead with declustering.
 }
@@
 \response{%
-Thanks for the comment. We consider both catalogs.
+The reviewer brings up an interesting point.
+For the most part, this is addressed in the response to comment \#1 from Reviewer \#1, who also raised the issue about whether we should decluster the catalog or not.
+In essence, there is still no clear consensus on what catalog should be used.
+Telesca et al.~(2014b) and Telesca et al.~(2016) used declustered catalogs, whereas Telesca and Lovallo (2012) and Telesca et al.~(2013) used complete catalogs.
+We initially declustered the catalog out of personal choice, but in light of the comments we revised the results for both complete and declustered catalogs.
+We now include both results for Figures 7 and 8, include number of events for noth catalogs in Table 1, and make comments about the differences observed in the treatment of the catalog in several places in the manuscript.
+We also improved our description of the methodology used for declustering (Gardner and Knopoff, 1974), and made an effort to make it clear that we recognize that this method was calibrated for a different region (California).
+We now concentrate on the results from the complete catalog.
 }
@@
 \comment{2}{%
- Uncertainty analysis for standard b-value estimation for sample population, magnitude correction
+Uncertainty analysis for standard $b$-value estimation for sample population, magnitude correction.
 }
@@
 \response{
-Thanks. We conduct the uncertainty analysis according to Shi and Bolt 1982. Please see equation 3 and Table 1. 
+Thanks you. We computed uncertainty according to Shi and Bolt (1982). Please see equation 3 and the results included in the new version of Table 1.
 }
@@
 \comment{3}{%
-I find that Mc (magnitude of completeness) determination, should be done in a time-dependent manner since from the Fig. 5 it is obvious that monitoring conditions change.
+I find that $M_c$ (magnitude of completeness) determination, should be done in a time-dependent manner since from the Fig. 5 it is obvious that monitoring conditions change.
 }
@@
 \response{
-That is right. We conduct a time dependent Mc estimation through Maximum Curvature method implemented in ZMAP software. Please see Fig. 4.  The results modified accordingly. 
+We agree with the reviewer.
+We initially used the GFT method because we had issues with the sofware we were using to do this calculation using the MAXC method in a time-dependent manner.
+For the revised version, we fixzed those issues and were able to recompute $M_c$ using MAXC as impleemted in ZMAP.
+The new values of $M_c$ are reported in Table 1, and the time dependent analysis is shown in the new version of Figure 4.
+The new values of $M_c$ resulted to be more conservative than those we obtained in our initial calculation and this resulted in smaller catalogs, which affected some of the analysis (especially in the case of the Kopeh Dagh region).
+We comment on this in the new version of the manuscript, and proceeded to recompute the results.
 }
@@
 \response{
-Our catalog starts from 2005.
-We agree the fact that  the earthquake could affect the seismicity pattern several consequent years, however, the spatial distance of the epicenter from the study region is fairly large ($d > 400 miles$).
-Therefore, we believe $2003 Mw 6.6$ Bam earthquake's aftershocks is not included in the current study regions' catalog.
+We limite the start date of the catalogs to 2005 because increased quality in monitoring earthquakes in the region around this time has been well documented.
+While it is possible that the 2003 Bam earthquake had affect the seismicity pattern in subsequent years, we think that the distance of the from the epicenter to the study region ($R > 400 miles$) is sufficiently large not to significantly affect the overall results.
 }

### 2017-06-22 response.tex
Fixed some typos

@@
 In the revised version include results for both cases, although we tend to focus on the complete catalog.
-It seems the rsults are not particularly sensitive to the presence or basence of foreshocks and aftershocks.
+It seems the results are not particularly sensitive to the presence or absence of foreshocks and aftershocks.
 Instead, as we discuss now in the revised version and in response to other questions by the reviewers, it seems the visibility graph results are more sensitive to the completeness itself (i.e., to $M_c$) and the number of events.
@@
 \response{%
-Given the changes made to the paper, and most of the figures now focusing on the complete catalog (with only contrasting references with respect to declustered catalog results), we believe this is not entirely necesary.
+Given the changes made to the paper, and most of the figures now focusing on the complete catalog (with only contrasting references with respect to declustered catalog results), we believe this is not entirely necessary.
 Besides, it is out of the scope of the paper to determine the effectiveness of the declustering method or its appropriateness for northern Iran.
@@
 Thank you for suggesting this.
-The new version of the manuscrip now considers comparisons between results obtained for the complete and declustered catalogs.
+The new version of the manuscript now considers comparisons between results obtained for the complete and declustered catalogs.
 In particular, we show the differences in the results of the analyses of the different catalogs in Figures 7 and 8.
 In addition, in several places in the manuscript, we now make mention to results obtained for the declustered catalogs in contrast to the complete catalogs.
-Due to space limitations we do not include all results in all figures, but we did make an effort to coment on this when appropriate.
+Due to space limitations we do not include all results in all figures, but we did make an effort to comment on this when appropriate.
 In general, we found that the differences introduced by declustering were more due to the reduced number of events than to anything else.
@@
 We now make comments about these changes and their effect in the revised manuscript in the Results and Conclusions sections.
-The changes to the method used to compute $M_c$ are decribed in the Methodlogy section, and in the answer to Comment \#3 from Reviewer \#2.
+The changes to the method used to compute $M_c$ are described in the Methodology section, and in the answer to Comment \#3 from Reviewer \#2.
 }
@@
 \response{%
-Rather than including these numbers, we include a new figure (Fig.~10) in which we show regresions between $b$ and $m$ for the condensed data-points from Figure 9.
+Rather than including these numbers, we include a new figure (Fig.~10) in which we show regressions between $b$ and $m$ for the condensed data-points from Figure 9.
 We thought this was a better way of showing the correlation between $b$ and $m$.
@@
 There, we address the lack of correlation for the some of the events in the Alborz and Kopeh Dagh regions.
-Based on the experience we gaing through working with the method, we suggest that the lack of correlation may be the results of relatively high completeness magnitude values, or lack of distinctive large magnitide ($M>6$) events.
+Based on the experience we gain through working with the method, we suggest that the lack of correlation may be the results of relatively high completeness magnitude values, or lack of distinctive large magnitude ($M>6$) events.
 The text was modified accordingly.
@@
 We initially declustered the catalog out of personal choice, but in light of the comments we revised the results for both complete and declustered catalogs.
-We now include both results for Figures 7 and 8, include number of events for noth catalogs in Table 1, and make comments about the differences observed in the treatment of the catalog in several places in the manuscript.
+We now include both results for Figures 7 and 8, include number of events for both catalogs in Table 1, and make comments about the differences observed in the treatment of the catalog in several places in the manuscript.
 We also improved our description of the methodology used for declustering (Gardner and Knopoff, 1974), and made an effort to make it clear that we recognize that this method was calibrated for a different region (California).
@@
 We agree with the reviewer.
-We initially used the GFT method because we had issues with the sofware we were using to do this calculation using the MAXC method in a time-dependent manner.
-For the revised version, we fixzed those issues and were able to recompute $M_c$ using MAXC as impleemted in ZMAP.
+We initially used the GFT method because we had issues with the software we were using to do this calculation using the MAXC method in a time-dependent manner.
+For the revised version, we fixed those issues and were able to recompute $M_c$ using MAXC as implemented in ZMAP.
 The new values of $M_c$ are reported in Table 1, and the time dependent analysis is shown in the new version of Figure 4.
@@
 \response{
-We limite the start date of the catalogs to 2005 because increased quality in monitoring earthquakes in the region around this time has been well documented.
-While it is possible that the 2003 Bam earthquake had affect the seismicity pattern in subsequent years, we think that the distance of the from the epicenter to the study region ($R > 400 miles$) is sufficiently large not to significantly affect the overall results.
+We limit the start date of the catalogs to 2005 because increased quality in monitoring earthquakes in the region around this time has been well documented.
+While it is possible that the 2003 Bam earthquake had affect the seismicity pattern in subsequent years, we think that the distance of the epicenter to the study region ($R > 400\  miles$) is sufficiently large not to significantly affect the overall results.
 }

### 2017-06-22 conclusion.tex
Fixed some typos

@@
 We also explored the relationships \myrevision{between the visibility graph properties and the seismicity parameters for a random selection of earthquake subsequences and for a progression of subsequences in time.
-In these cases, we found the relationship between $b$ and $m$ to hold for subsequences with a sufficiently large number of events ($n \geq 50$), but noticed they are in better agreement with the universal regressions when larger, entire regional sequences are considered.
-Unfortunately, for the particular regions considered in this study, we were not able to detect conclusive evidence of other relationships between the visibility graph properties and the temporal occurrence of large earthquakes, as it has been suggested in previous similar studies.
-We believe this is due to the lack of larger magnitude events ($M_w > 6$) in the selected catalogs.}
+In these cases, we found the relationship between $b$ and $m$ to hold for subsequences with a sufficiently large number of events ($n \geq 200$), but noticed they are in better agreement with the universal regressions when larger, entire regional sequences are considered.
+For the particular regions considered in this study, we were not able to detect conclusive evidence of other relationships between the visibility graph properties and the temporal occurrence of large earthquakes, as it has been suggested in previous similar studies.
+We believe this is due to the lack of larger magnitude events ($M_w > 6$) or relatively high values of $M_c$ in the selected catalogs.}
 

### 2017-06-22 results.tex
Fixed some typos

@@
 	\includegraphics[width=\textwidth]{figures/pdf/figure-10} 
-	\caption{\myrevision{Correlation between $m$ and $b$ based on the fixed-size windowing analysis done for the regions of Azerbaijan (a) and Alborz (b), along with the linear regressions of each case.
+	\caption{\myrevision{Correlation between $m$ and $b$ based on the fixed-size windowing analysis done for the regions of Azerbaijan (a) and Alborz (b), along with the linear regressions of each case for the complete catalog.
 While a direct comparison is not appropriate, the universal regression is shown here for reference.}}

### 2017-06-23 abstract.tex
Suggested changes by Luciano added.

@@
 The method relies on the inter-event visibility defined in terms of a connectivity degree parameter, $k$, which is correlated with the earthquake magnitude, $M$.
-Previous studies show that the slope of the $k$-$M$ correlation, $m$, also observes a relationship with the $b$-value from the Gutenberg-Richter law, thus rendering the graph analysis useful to examine the seismicity of a region.
+\myrevision{Previous studies show that the slope $m$ of the line fitting the  $k-M$  plot by the least square method}, also observes a relationship with the $b$-value from the Gutenberg-Richter law, thus rendering the graph analysis useful to examine the seismicity of a region.
 \myrevision{These correlations seem to hold for the analysis of relatively small sequences of earthquakes, offering the possibility of studying seismicity parameters in time}.

### 2017-06-23 seismicity.tex
full table 1
Suggested changes by Luciano added.

@@
 We refer to the catalog composed by the events shown in this figure as the \textit{whole} catalog.
-We then} determine the minimum magnitude of completeness, $M_c$, for each region\myrevision{, and based on the value of $M_c$, we filter out the smaller events and obtain a reduced dataset of events to which we refer to as the \textit{complete} catalog.}
+We then} determine the magnitude of completeness, $M_c$, for each region\myrevision{, and based on the value of $M_c$, we filter out the smaller events and obtain a reduced dataset of events to which we refer to as the \textit{complete} catalog.}
 
@@
 where $e$ is the mathematical constant or Euler's number, $\overline{M}$ is the average magnitude, \myrevision{$M_{\min}$ is the minimum magnitude in the sample, and $\Delta M_{\mathrm{bin}}$ is the bin size used to discretize the magnitude scale}.
-Here, the value of $M_{\min}$ is taken as the minimum completeness magnitude $M_c$ obtained or selected for each region's sub-catalog.
+Here, the value of $M_{\min}$ is taken as the completeness magnitude $M_c$ obtained or selected for each region's sub-catalog.
 \myrevision{In this study we assumed $\Delta M_{\mathrm{bin}} = 0.1$}.
@@
 		\hline
-		Azerbaijan   & 1047  &  202     &     ?       & 3.5 & 0.85491 $\pm$ 0.0506 & ? \\
-		Alborz       & 1898  &  575     &     ?       & 3.0 & 0.81578 $\pm$ 0.0279 & ? \\
-		Kopeh Dagh   &  640  &  117     &     ?       & 3.5 & 0.78297 $\pm$ 0.0494 & ? \\
+		Azerbaijan   & 1047  &  202     &   102       & 3.5 & 0.85 $\pm$ 0.05 & 0.88 $\pm$ 0.07 \\
+		Alborz       & 1898  &  575     &   440       & 3.0 & 0.82 $\pm$ 0.03 & 0.79 $\pm$ 0.03 \\
+		Kopeh Dagh   &  640  &  117     &    96       & 3.5 & 0.78 $\pm$ 0.05 & 0.73 $\pm$ 0.05 \\
 		\hline
@@
 The event occurrences are represented by vertical bars or sticks of length equal to the $M_w$ magnitude of each earthquake.
-These sequences correspond to the \myrevision{whole} catalog but in each case we consider only events with $M_w \geq M_c$.
+These sequences correspond to the \myrevision{complete} catalog.
 As shown in Fig.~\ref{fig:vg}, the dots at the top of each stick represent the nodes of the visibility graphs.

### 2017-06-23 abstract.tex
minor fix

--- 2017-06-22 abstract.tex
@@
 The method relies on the inter-event visibility defined in terms of a connectivity degree parameter, $k$, which is correlated with the earthquake magnitude, $M$.
-Previous studies show that the slope of the $k$-$M$ correlation, $m$, also observes a relationship with the $b$-value from the Gutenberg-Richter law, thus rendering the graph analysis useful to examine the seismicity of a region.
+\myrevision{Previous studies show that the slope $m$ of the line fitting the  $k$-$M$  plot by the least squares method}, also observes a relationship with the $b$-value from the Gutenberg-Richter law, thus rendering the graph analysis useful to examine the seismicity of a region.
 \myrevision{These correlations seem to hold for the analysis of relatively small sequences of earthquakes, offering the possibility of studying seismicity parameters in time}.

### 2017-06-23 abstract.tex
minor fix

--- 2017-06-22 abstract.tex
@@
 The method relies on the inter-event visibility defined in terms of a connectivity degree parameter, $k$, which is correlated with the earthquake magnitude, $M$.
-Previous studies show that the slope of the $k$-$M$ correlation, $m$, also observes a relationship with the $b$-value from the Gutenberg-Richter law, thus rendering the graph analysis useful to examine the seismicity of a region.
+\myrevision{Previous studies show that the slope $m$ of the line fitting the  $k$-$M$  plot by the least squares method} also observes a relationship with the $b$-value from the Gutenberg-Richter law, thus rendering the graph analysis useful to examine the seismicity of a region.
 \myrevision{These correlations seem to hold for the analysis of relatively small sequences of earthquakes, offering the possibility of studying seismicity parameters in time}.
